---
title: "organizing demographics"
author: "Michelle.VanTieghem"
date: "November 26, 2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
    collapsed: no
    smooth_scroll: yes
    df_print: paged
  pdf_document:
    toc: yes
---

# notes 
updated Nov 26, 2019 to just use updated groups from master for deciding PI_DA/ COMP_DC groupings. 
old version had wrongly been including 4 DA subjects as comps becuase they didn't have any CGH_IFC or CGH_FC ...

# load data 
## master 
```{r, include = F,warnings = F, error = F}
library(readxl)
library(tidyverse)


master <- read_excel("../../subj_demo/masters/MASTER_20191118_updated_MICM.xlsx") 
demo <- master %>%
  select(IDENT_SUBID, GROUP, SUBAGE_Session1, DEM_3_GENDER_CHILD, WASI_FSIQ, 
           INC_ITN_HOUSE) %>%
  mutate(SUBJECTID =substr(IDENT_SUBID, 1, 5), 
# comps are the non-adopted kids!
        PI_DA = as.factor(ifelse(GROUP == "C" | GROUP == "DC", 0, 1)))  %>%
  rename(AGE = SUBAGE_Session1, 
         SEX = DEM_3_GENDER_CHILD)

```

## pull race variables
set up for enrollment reporting
get from SUBIDKEY DEMO! not MASTER! 
Races	Code
American Indian	1
Asian	2
Native Hawaiian/ pacific islander	3
Black	4
White	5
More than 1 race	6
Unknown/ not reported	7
```{r}
race_vars <- read.csv("../../subj_demo/DEMO_OLD/PACCT_DEMO_4_9_19.csv") %>%
  rename(Race = RACE) %>%
  mutate(IDENT_SUBID = paste0(trimws(SUBJECTID), "_V1"),
         Race = ifelse(Race == 1, "American Indian", 
                       ifelse(Race == 2, "Asian", 
                              ifelse(Race == 3, "Hawaiian",
                                     ifelse(Race == 4, "Black", 
                                            ifelse(Race == 5, "White", 
                                                   ifelse(Race == 6, "More than one race", 
                                                          ifelse(Race == 7, "Unknown", "FIX"))))))), 
         Ethnicity = ifelse(HISPANIC == 1, "Hispanic or Latino", "Not Hispanic or Latino")) %>%
  select(IDENT_SUBID, Race, Ethnicity)

```


# add better race variable into demo
going to want to add the NAs here later! 
```{r}
demo <- left_join (demo, race_vars, by= "IDENT_SUBID", all = T)
sum(is.na(demo$Race))
# get them from here, later
names(master)[grepl("RACE", names(master))]
```

# save it! 
```{r}

save(demo,file =  "data/demographics_from_MASTER_20191118.Rdata")
```
