---
title: "Quality control for effort task data"
author: "Michelle.VanTieghem"
date: "April 2, 2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# notes on Exclusion criterion
Behavioral data:  All behavioral data, collected in or out of the scanner, will be considered for these analyses. Participants who completed at least 1 run of usable behavioral data will be included in the analyses. Runs with <70% responses during the choice phase will be excluded from all behavior analyses.


# load data 
all behavior data combined, by run.
```{r, warning = F, message = F}
library(tidyverse)
load( "../../behavioral_data/combined_behavior_master/combined_effort_ft_pt_behavior_by_run_all_data.Rata")

# get rid of fake subjectIDs - test things 
beh_master <- beh_master %>%
 filter(SUBJECTID != "PA999" & SUBJECTID != "PAPA1" & SUBJECTID != "PApa1" &
          SUBJECTID != "PApa0" & SUBJECTID != "PAPA0" & SUBJECTID != "PA000")

```


# filter data 
## how many subjects did the task.
```{r}
N_runs_attempted <- nrow(beh_master)
N_runs_attempted
sublist_attempted <- unique(beh_master$SUBJECTID)
N_subs_attempted <- length(sublist_attempted) # 174
N_subs_attempted
```

## how many complete runs ( 18 out of 21 trials)

```{r}

beh_master <- beh_master %>%
  mutate(beh_QC_complete_run = ifelse(N_trials > 18, 1, 0))
N_runs_complete <- sum(beh_master$beh_QC_complete_run, na.rm = T)
N_runs_complete
N_subs_complete <- beh_master %>%
  filter(beh_QC_complete_run == 1) %>% 
  group_by(SUBJECTID) %>%
  summarize(n = n()) %>%
  summarize(n = n())
N_subs_complete
```


## of complete runs, how many  subjects missed too many choices?
13 Runs from 11 subjects 
```{r}

beh_master <- beh_master %>% 
  mutate(beh_QC_choices_resp_70_include = ifelse(N_choices_resp >= (0.7*N_trials), 1, 0))

N_runs_exclude_for_missed_choices <- beh_master %>% 
  filter(beh_QC_complete_run == 1) %>% # of only complete runs
  filter (beh_QC_choices_resp_70_include == 0) %>%
  summarize(n = n())
N_runs_exclude_for_missed_choices 

N_subs_exclude_for_missed_choices <- beh_master %>% 
  filter(beh_QC_complete_run == 1) %>% # of only complete runs
  filter (beh_QC_choices_resp_70_include == 0) %>%
  group_by(SUBJECTID) %>%
  summarize(n = n()) %>%
  summarize(n = n())
N_subs_exclude_for_missed_choices 

```

## of remaining, how many "too slow" too often? 
```{r}
## exclusion numbers
exclude_for_too_slow <- beh_master %>%
  filter(N_tooslow > 0.5*N_trials)

beh_master <- beh_master %>% 
  mutate(beh_QC_tooslow_50_include = ifelse(N_tooslow < 0.5*N_trials, 1, 0))

N_runs_exclude_for_too_slow <- beh_master %>% 
  filter(beh_QC_complete_run == 1) %>% # of only complete runs
  filter (beh_QC_choices_resp_70_include == 1) %>% # of people who responded enough
  filter(beh_QC_tooslow_50_include == 0) %>%
  summarize(n = n())
N_runs_exclude_for_too_slow <- nrow(N_runs_exclude_for_too_slow) # 0

#This code chunk doesn't work because there are no runs that count!
#N_subs_exclude_for_too_slow <- beh_master %>% 
 # filter(beh_QC_complete_run == 1) %>% # of only complete runs
#  filter (beh_QC_choices_resp_70_include == 1) %>% # of people who responded enough
#  filter(beh_QC_tooslow_50_include == 0) %>%
 # group_by(SUBJECTID) %>%
#  summarize(n = n()) %>%
#  summarize(n = n())
N_subs_exclude_for_too_slow <- 0

```


## summary of N inclusion/exclusion
```{r}
subs <- rbind(N_subs_attempted, N_subs_complete, N_subs_exclude_for_missed_choices, N_subs_exclude_for_too_slow) %>%
  rename(subs = n)
runs <-  rbind(N_runs_attempted, N_runs_complete, N_runs_exclude_for_missed_choices, N_runs_exclude_for_too_slow) %>%
  rename(runs  = n)

exclusion_behavior_table <- data.frame(cbind(subs, runs)) %>%
  mutate(categories = c("effort attempted", "complete", "excluded for missed choices", "excluded for too slow")) %>%
  select(categories, subs, runs)


exclusion_behavior_table

save(exclusion_behavior_table, file = "tables/exclusion_behavior_table.Rdata")
```

## check reinforcement rates 
not excluding for now, but marking for secondary analyses later.

### reinforcement rate by run 
 3 runs that exceed 3 sd from the mean reinforcement - to be excluded.
```{r}
reinf_run_mean <- mean(beh_master$Reinforce_rate, na.rm = T)
reinf_run_sd <- sd(beh_master$Reinforce_rate, na.rm = T)
reinf_run_upper <- reinf_run_mean + 3*reinf_run_sd
reinf_run_lower <- reinf_run_mean - 3*reinf_run_sd
range(beh_master$Reinforce_rate)

beh_master <- beh_master %>% 
  mutate(extreme_reinforce = ifelse(Reinforce_rate > reinf_run_upper |
                                      Reinforce_rate < reinf_run_lower, 1, 0))
sum(beh_master$extreme_reinforce, na.rm = T)
```

### reinforcement rate by subject
no individual subject had extreme reinforcement across BOTH runs that exceeds 3SD from mean
```{r}

reinforce_subj <- beh_master %>%
  select(SUBJECTID, Run_number, Reinforce_rate) %>%
  group_by(SUBJECTID) %>%
  # absolute value of differences between runs. 
  summarize(Reinforce_diff_runs = max(Reinforce_rate) - min(Reinforce_rate), 
            Reinforce_mean_runs = mean(Reinforce_rate))

hist(reinforce_subj$Reinforce_diff_runs)
hist(reinforce_subj$Reinforce_mean_runs)

```

# save data with QC info and sublist to include. 
```{r}
# save this data ! 
save(beh_master, file ="../../behavioral_data/3_effort_task_data/compiled/compiled_effort_scan_version_with_QC.Rdata")

# save this subject-by-run list! 
include_behavior_df <- beh_master %>%
  filter(beh_QC_complete_run == 1 & 
           beh_QC_choices_resp_70_include == 1 &
           beh_QC_tooslow_50_include == 1) %>%
  select(SUBJECTID, Run_number)

write.table(include_behavior_df, file = paste0("sublists/include_behavior_only_", Sys.Date(), ".txt"))

# double checking that re-runnign the preprocessing on Nov 26, 2019 didn't change sublist. 
test <- read.table("../../Sublists/sublist_include_behavior_only_2019-08-16.txt")
# confirmed!! 
identical(as.character(test$SUBJECTID), as.character(include_behavior_df$SUBJECTID))
```

