---
title: "Data cleaning for analysis for COMPS"
author: "Michelle.VanTieghem"
date: "Dec 1, 2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

updated Dec 16, 2019 to add key press RT from effort tasks


```{r, warning = F, message = F}
source("../0_R_analysis_setup_file.R", echo=F)
```


# Set up data
## load behavior master, which includes demographic variables 
generated: 3_progress_report_Scans_and_behavior.Rmd 
has all behavior data, QC info, and demographics. long format, by run.
```{r}
load("../../behavioral_data/3_Effort_task_data/compiled/compiled_effort_scan_version_filtered_usable_with_demo.Rdata")
nrow(df_by_run_usable_beh)

# finish cleaning this data
beh_by_run <- df_by_run_usable_beh %>%
  rename(proportion_hard = N_prop_hard) %>%
  mutate(Run_Number.n = ifelse(Run_number == "RUN1", 1, 2), 
         # answers of 4 for perceived control are not plausible, error data!! 
         perceived_control = ifelse(perceived_control == 4, NA, perceived_control))

```


## load in long-formatted behavioral data per subject 
generated in behavior_perproc_scripts/1_effort_task_behavior_preproc.Rmd
add a couple more variables 
```{r}
load("../../behavioral_data/3_effort_task_data/compiled/compiled_long_format_all_data_with_buttonpress.Rdata")

behavior_long_data <- behavior_long_data %>%
  rename(SUBJECTID = SUB) %>%
  # add turtle feedback! if they didn't make it to top of green bar.
  mutate(Feedback = as.factor(ifelse(Accuracy == 0, "Too_slow",
                                    ifelse(Accuracy == 1 & Reward_received == 1, "Reward", 
                                           ifelse(Accuracy == 1 & Reward_received == 0, "Setback", 
                                                  ifelse(is.na(Reward_received), NA, "fix"))))))
summary(behavior_long_data$keyboard_version)

# NA = missed choice, so no feedback phase.s
summary(behavior_long_data$Feedback)

# get the max that their hard task was titrated to.
by_subj <- behavior_long_data %>%
  group_by(SUBJECTID) %>%
  dplyr::summarize(hard_task_titration = max(max_keys, na.rm = T)) 
#head(by_subj)
# everyone is a 3!!! so no point in caring about easy task.
#summary(by_subj$hard_task_titration[by_subj$Effort_Choice == "Easy"])
# add this subject-level covariate into the long df.
behavior_long_data <- merge(behavior_long_data, by_subj, by = "SUBJECTID")

```

### merge into a long dataframe (by trial) 
beh_by_run is already filtered for usable, long data is not. do not say "all = T"
```{r}
beh_long <- merge(beh_by_run, behavior_long_data, by = c("SUBJECTID", "Run_number"))
nrow(beh_long)

### CHECKS BEFORE MOVING FORWARD ### 
# any dupliocated trials? 
trial_check <- beh_long %>%
  group_by(SUBJECTID, Run_number) %>%
  dplyr::summarize(N_trials = n()) %>% 
  filter(N_trials > 22)
trial_check # none!

# any duplicated runs?
run_check <- beh_by_run %>%
  group_by(SUBJECTID) %>%
  dplyr::summarize(N_runs = n()) %>%
  filter(N_runs > 2)
run_check # none! 

```


## Set up long data for behavior analysis 

### clean data 
double check that we excluded subjects with extreme reinforcement rates, too many "too slow" resps, or not enough choices.

```{r}

# re-ordering the entire dataframe by Trial Number and run number! 
beh_long2 <- beh_long[order(beh_long$SUBJECTID, beh_long$Run_Number.n, beh_long$Trial_Number),]


beh_long3 <- beh_long2 %>%
    # rename motor variables - subject level covariates.
  rename(median_motor_RT_easy = median_RT_thumb, 
         median_motor_RT_hard = median_RT_ring,
         mean_motor_RT_easy = mean_RT_thumb, 
         mean_motor_RT_hard = mean_RT_ring,
         motor_key_count_easy = thumb_key_count, 
         motor_key_count_hard = ring_key_count,
         effort_key_count = key_count,
         IQ = WASI_FSIQ) %>%
  mutate(Trial_Number = as.numeric(as.character(Trial_Number)),
         # these are all subject-level covariaces
         # self-report measures 
         hard_effort_perceived = as.numeric(hard_effort), 
         easy_effort_perceived = as.numeric(easy_effort), 
         perceived_effort_ave = (hard_effort_perceived + easy_effort_perceived)/2,
         perceived_effort_diff = (hard_effort_perceived - easy_effort_perceived),
         fun = as.numeric(fun),
         motivated = as.numeric(motivated),
         sleepy = as.numeric(sleepy),
         frustrated = as.numeric(frustrated),
         win_feeling = as.numeric(win_feeling),
         lose_feeling = as.numeric(lose_feeling),
         perceived_reinforce = as.numeric(perceived_reinforce),
         perceived_control = as.numeric(perceived_control),
        # motor confounds 
          mean_motor_RT_ave = (mean_motor_RT_easy + mean_motor_RT_hard)/2, 
          median_motor_RT_ave = (median_motor_RT_easy + median_motor_RT_hard)/2,
          motor_key_count_ave = (motor_key_count_hard + motor_key_count_easy)/2,
         # TRIAL BY TRIAL MEASURES
         Effort_Choice.n = ifelse(Effort_Choice == "Hard", 1,
                                  ifelse(Effort_Choice == "Easy", 0, NA)),
         # key overshoot = reflecting their presses relative to titration.
          max_keys_easy = ifelse(Effort_Choice.n == 0, max_keys, NA),
          max_keys_hard = ifelse(Effort_Choice.n == 1, max_keys, NA),
          effort_key_overshoot = (effort_key_count - max_keys),
          effort_key_overshoot_easy = ifelse(Effort_Choice.n == 0, effort_key_count - max_keys, NA), 
          effort_key_overshoot_hard = ifelse(Effort_Choice.n == 1, effort_key_count - max_keys, NA),
        # key- count: don't need to calculate!! 
          mean_RT_button_press = ifelse(Effort_Choice.n == 0, mean_RT_easy_button_press, 
                                        ifelse(Effort_Choice.n == 1, mean_RT_hard_button_press, NA)),
          median_RT_button_press = ifelse(Effort_Choice.n == 0, median_RT_easy_button_press, 
                                          ifelse(Effort_Choice.n == 1, median_RT_hard_button_press, NA)),
          perceived_effort = ifelse(Effort_Choice.n == 1, hard_effort_perceived,
                                   ifelse(Effort_Choice.n == 0, easy_effort_perceived, NA)))
          
# make trial 1-42 instead of 2 blocks of 21 
beh_long3$Trial_Number_all <- ifelse(beh_long3$Run_number == "RUN1", beh_long3$Trial_Number, ifelse(beh_long3$Run_number == "RUN2", beh_long3$Trial_Number + 21, NA))

#names(beh_long)
```


### create mean centered covariates
```{r}
beh_long <- beh_long3 %>%
  mutate (Reinforce_rate.c = Reinforce_rate - mean(Reinforce_rate, na.rm = T), 
          Reinforce_easy.c = Reinforce_easy - mean(Reinforce_easy, na.rm = T), 
          Reinforce_hard.c = Reinforce_hard - mean(Reinforce_hard, na.rm = T), 
          AGE.c = AGE - mean(AGE, na.rm = T), 
          SEX.c = SEX - mean(SEX, na.rm = T), 
          Trial_Number.c = Trial_Number - mean(Trial_Number, na.rm= T), 
          proportion_hard.c = proportion_hard - mean(proportion_hard), 
         IQ.c = IQ - mean(IQ, na.rm = T), 
         perceived_effort.c = perceived_effort - mean(perceived_effort, na.rm =T),
         perceived_effort_diff.c = perceived_effort_diff - mean(perceived_effort_diff, na.rm =T),
         perceived_effort_ave.c = perceived_effort_ave - mean(perceived_effort_ave, na.rm =T), 
         hard_effort_perceived.c = hard_effort_perceived - mean(hard_effort_perceived, na.rm = T))
          
```

## make WSLS dataset (separate from regular)
add WSLS variables, shifted to prior trial
using the entire dataset, including misses...
NOTE: this excludes the first trial of each run because the prior trial is NA. 
```{r}
# make a copy of the dataset, remove all of the first trials, and mark them as 100 to keep out of place.
df_copy2 <- beh_long %>%
  # making a copy that adds 1 to trial number
  mutate(Trial_Number = Trial_Number + 1) %>%
  # so effort choice prior for trial 2 represents the effort choice from trial 1 
  dplyr::select(SUBJECTID, Run_number, Trial_Number, Effort_Choice, Feedback) %>%
  rename(Effort_Choice_prior = Effort_Choice, 
         Feedback_prior = Feedback) 

# now re-sort the data, so that all trials are shifted up 1 place. 
df_copy2 <- df_copy2[order(df_copy2$SUBJECTID, df_copy2$Run_number, df_copy2$Trial_Number),]

# now merge this new thing with orig data, by sub, run, and Trial_Number! 
beh_long_WSLS <- merge(beh_long, df_copy2, by = c("SUBJECTID", "Run_number", "Trial_Number"), all = T) %>%
  # exclude the first trial of each run because the prior trial is NA.
  filter(!is.na(Effort_Choice) & Trial_Number != 1) %>% 
## calculate stay-shift variables, 1 = stay, 0 = shift
  ## don't count missed choices for current or prior trial! 
  mutate(stay_shift = ifelse(Effort_Choice == "Miss" | Effort_Choice_prior == "Miss", NA, 
                             ifelse(Effort_Choice == Effort_Choice_prior, 1, 0)),
         # making a new variable that counts turtles as setbacks.
         Feedback_prior_inclturtle = as.factor(ifelse(Feedback_prior == "Too_slow", "Setback", as.character(Feedback_prior)))) %>%
  filter(Effort_Choice_prior != "Miss")
```

### sanity check for WSLS variables
```{r}
# NA = choices that were missed for current or prior trial - excluding both!! 
summary(as.factor(beh_long_WSLS$stay_shift)) 

# missed choices are coded here, just making sure formatted correctly.
summary(as.factor(beh_long_WSLS$Effort_Choice_prior)) 

# NA = choices that were missed, keeping too slow as a separate level.
summary(as.factor(beh_long_WSLS$Feedback_prior)) 

# NA = choices that were missed, too slow feedback was counted as setback
summary(as.factor(beh_long_WSLS$Feedback_prior_inclturtle)) 
```


## Make subject-level dataframe
```{r}

# make a subject-specific summary of their overall choices
beh_wide <- beh_long %>%
  group_by(SUBJECTID) %>%
  dplyr::summarize(PI_DA = PI_DA[1], 
                   Recruitment_group = Recruitment_group[1],
                   ft_version = ft_version[1],
            keyboard_version = keyboard_version[1],
            SEX = mean(SEX), 
            AGE = mean(AGE, na.rm = T),
            IQ = mean(IQ, na.rm = T),
            Fam_inc_needs = mean(INC_ITN_HOUSE, na.rm = T),
            N_trials = n(), 
            prop_hard_choices = mean(Effort_Choice.n, na.rm = T),
            Reinforce_rate  = mean(Reinforce_rate, na.rm = T), # MEAN
            Reinforce_hard = mean(Reinforce_hard, na.rm = T),
            Reinforce_easy = mean(Reinforce_easy, na.rm = T),
            # self-report measures 
           hard_effort_perceived = mean(hard_effort_perceived, na.rm = T),
           easy_effort_perceived = mean(easy_effort_perceived, na.rm = T),
           perceived_effort_ave = mean(perceived_effort_ave, na.rm = T),
           perceived_effort_diff = mean (perceived_effort_diff, na.rm = T),
           fun = mean(fun, na.rm = T),
           motivated = mean(motivated, na.rm = T),
           sleepy = mean(sleepy, na.rm = T),
           frustrated = mean(frustrated, na.rm = T),
           win_feeling = mean(win_feeling, na.rm = T),
           lose_feeling = mean(lose_feeling, na.rm = T),
           perceived_reinforce = mean(perceived_reinforce, na.rm = T),
           perceived_control = mean(perceived_control, na.rm = T),
           # motor pre-test finger tapping
           # median of the within-trial RT for the task  ... 
            mean_motor_RT_easy = mean(mean_motor_RT_easy, na.rm = T),
            mean_motor_RT_hard = mean(mean_motor_RT_hard, na.rm = T),
            mean_motor_RT_ave = mean(mean_motor_RT_ave, na.rm = T),
            median_motor_RT_easy = mean(median_motor_RT_easy, na.rm = T),
            median_motor_RT_hard = mean(median_motor_RT_hard, na.rm = T),
            median_motor_RT_ave = mean(median_motor_RT_ave, na.rm = T), 
            motor_key_count_easy = mean(motor_key_count_easy, na.rm = T), 
            motor_key_count_hard = mean(motor_key_count_hard, na.rm = T),
            motor_key_count_ave = mean(motor_key_count_ave, na.rm = T),
           ## effort button presses 
            max_keys_hard = mean(max_keys_hard, na.rm = T), 
            max_keys_easy = mean(max_keys_easy, na.rm = T),
            effort_key_overshoot = mean (effort_key_overshoot, na.rm = T),
            effort_key_overshoot_easy = mean(effort_key_overshoot_easy, na.rm = T), 
           effort_key_overshoot_hard = mean(effort_key_overshoot_hard, na.rm = T),
          # key- count: don't need to calculate!! 
            mean_RT_button_press = mean(mean_RT_button_press, na.rm = T),
            median_RT_button_press = mean(median_RT_button_press, na.rm = T),
            mean_RT_hard_button_press = mean(mean_RT_hard_button_press, na.rm = T),
            median_RT_hard_button_press = mean(median_RT_hard_button_press, na.rm = T),          
            mean_RT_easy_button_press = mean(mean_RT_easy_button_press, na.rm = T),
            median_RT_easy_button_press = mean(median_RT_easy_button_press, na.rm = T))  %>%

  # add mean centered variables
  mutate(Reinforce_rate.c = Reinforce_rate - mean(Reinforce_rate, na.rm = T), 
          Reinforce_easy.c = Reinforce_easy - mean(Reinforce_easy, na.rm = T), 
          Reinforce_hard.c = Reinforce_hard - mean(Reinforce_hard, na.rm = T), 
          AGE.c = AGE - mean(AGE, na.rm = T), 
          SEX.c = SEX - mean(SEX, na.rm = T), 
          Trial_Number.c = N_trials - mean(N_trials, na.rm= T), 
          prop_hard_choices.c = prop_hard_choices - mean(prop_hard_choices), 
          IQ.c = IQ - mean(IQ, na.rm = T), 
          N_trials.c = N_trials- mean(N_trials, na.rm = T), 
          Fam_inc_needs.c = Fam_inc_needs- mean(Fam_inc_needs, na.rm = T)) # task titration

nrow(beh_wide)
```

### checks: PA233 and PA253 are missing IQ -WASI not completed at visit! 
```{r}
# missing IQ 
NA_Check <- beh_wide %>%
  filter(is.na(IQ)) 
NA_Check
```

## make subject-level data-frame for WSLS too 
```{r}

# make a subject-specific summary for WSLS - so grouped by feedback X effort! 
beh_wide_WSLS <- beh_long_WSLS %>%
  group_by(SUBJECTID, Feedback_prior, Effort_Choice_prior) %>%
  dplyr::summarize(PI_DA = PI_DA[1], 
                   Recruitment_group = Recruitment_group[1],
                   ft_version = ft_version[1],
            keyboard_version = keyboard_version[1],
            SEX = mean(SEX, na.rm = T), 
            SEX.c = mean(SEX.c, na.rm = T),
            AGE = mean(AGE, na.rm = T),
            AGE.c = mean(AGE.c, na.rm = T),
            IQ = mean(IQ, na.rm = T),
            Fam_inc_needs = mean(INC_ITN_HOUSE, na.rm = T),
            N_trials = n(), 
            prop_hard_choices = mean(Effort_Choice.n, na.rm = T),
            stay_shift = mean(stay_shift, na.rm = T),
            Reinforce_rate  = mean(Reinforce_rate, na.rm = T), # MEAN
            Reinforce_hard = mean(Reinforce_hard, na.rm = T),
            Reinforce_easy = mean(Reinforce_easy, na.rm = T),
            # self-report measures 
           hard_effort_perceived = mean(hard_effort_perceived, na.rm = T),
           easy_effort_perceived = mean(easy_effort_perceived, na.rm = T),
           perceived_effort_ave = mean(perceived_effort_ave, na.rm = T),
           perceived_effort_diff = mean (perceived_effort_diff, na.rm = T),
           fun = mean(fun, na.rm = T),
           motivated = mean(motivated, na.rm = T),
           sleepy = mean(sleepy, na.rm = T),
           frustrated = mean(frustrated, na.rm = T),
           win_feeling = mean(win_feeling, na.rm = T),
           lose_feeling = mean(lose_feeling, na.rm = T),
           perceived_reinforce = mean(perceived_reinforce, na.rm = T),
           perceived_control = mean(perceived_control, na.rm = T),
           # motor pre-test finger tapping
           # median of the within-trial RT for the task  ... 
            mean_motor_RT_easy = mean(mean_motor_RT_easy, na.rm = T),
            mean_motor_RT_hard = mean(mean_motor_RT_hard, na.rm = T),
            mean_motor_RT_ave = mean(mean_motor_RT_ave, na.rm = T),
            median_motor_RT_easy = mean(median_motor_RT_easy, na.rm = T),
            median_motor_RT_hard = mean(median_motor_RT_hard, na.rm = T),
            median_motor_RT_ave = mean(median_motor_RT_ave, na.rm = T), 
            motor_key_count_easy = mean(motor_key_count_easy, na.rm = T), 
            motor_key_count_hard = mean(motor_key_count_hard, na.rm = T),
            motor_key_count_ave = mean(motor_key_count_ave, na.rm = T),
           ## effort button presses 
            max_keys_hard = mean(max_keys_hard, na.rm = T), 
            max_keys_easy = mean(max_keys_easy, na.rm = T),
            effort_key_overshoot = mean (effort_key_overshoot, na.rm = T),
            effort_key_overshoot_easy = mean(effort_key_overshoot_easy, na.rm = T), 
           effort_key_overshoot_hard = mean(effort_key_overshoot_hard, na.rm = T),
          # key- count: don't need to calculate!! 
            mean_RT_button_press = mean(mean_RT_button_press, na.rm = T),
            median_RT_button_press = mean(median_RT_button_press, na.rm = T),
            mean_RT_hard_button_press = mean(mean_RT_hard_button_press, na.rm = T),
            median_RT_hard_button_press = mean(median_RT_hard_button_press, na.rm = T),          
            mean_RT_easy_button_press = mean(mean_RT_easy_button_press, na.rm = T),
            median_RT_easy_button_press = mean(median_RT_easy_button_press, na.rm = T))  %>%

  # add mean centered variables
  mutate(Reinforce_rate.c = Reinforce_rate - mean(Reinforce_rate, na.rm = T), 
          Reinforce_easy.c = Reinforce_easy - mean(Reinforce_easy, na.rm = T), 
          Reinforce_hard.c = Reinforce_hard - mean(Reinforce_hard, na.rm = T), 
         # AGE.c = AGE - mean(AGE, na.rm = T), 
        #  SEX.c = SEX - mean(SEX, na.rm = T), 
          Trial_Number.c = N_trials - mean(N_trials, na.rm= T), 
          prop_hard_choices.c = prop_hard_choices - mean(prop_hard_choices), 
          IQ.c = IQ - mean(IQ, na.rm = T), 
          N_trials.c = N_trials- mean(N_trials, na.rm = T), 
          Fam_inc_needs.c = Fam_inc_needs- mean(Fam_inc_needs, na.rm = T)) # task titration

length(unique(beh_wide_WSLS$SUBJECTID))

```



# Add ROI analysis brain data 
updated october 8, 2019 to include teh complete model with all possible copes...
needs to be updated to include PA255
```{r}
load(file = "FSL_cope_files/complete_EV_copes.Rdata")
nrow(complete_EV_copes)
```


### load data from progress report QC and merge with betas 
```{R}
load("../5_brain_behav_inclusion/data/all_data_QC_and_demographics_wide2019-12-04.Rdata")
df_wide <-  df_wide %>%
  dplyr::select(-SEX, -AGE)
names(df_wide)

# only keep people in this usable list!! 
cope_df2 <- merge(complete_EV_copes, df_wide, by = "SUBJECTID")
nrow(cope_df2)
```

### add motion!
```{r}
load("../../FSL_pipeline/1.motion_assess/compiled_motion_info_2019-08-07.Rdata")
motion_df <- merged_df %>%
  group_by(SUBJECTID) %>%
  dplyr::summarize(total_TRs_censored = sum(censored_TRs, na.rm = T), 
            meanFD_included_trs = mean(meanFD_included_trs, na.rm = T), 
            meanFD_all_trs = mean(meanFD_all_trs, na.rm = T))

cope_df3 <- merge(cope_df2, motion_df, by = "SUBJECTID")
nrow(cope_df3)
```


## combine behavior & scan data (wide & long) for all subjects (ECA sample) & save
calling this "ECA" because will be used for ECA paper.
```{r}
beh_ECA_wide <- beh_wide 
beh_ECA_long <- beh_long
beh_ECA_wide_WSLS <- beh_wide_WSLS
beh_ECA_long_WSLS <- beh_long_WSLS


beh_scan_ECA_wide <- cope_df3 %>%
  left_join(., beh_ECA_wide, by = c("SUBJECTID", "Recruitment_group", "PI_DA"))

nrow(beh_scan_ECA_wide)

beh_scan_ECA_wide_WSLS <- cope_df3 %>%
  left_join(., beh_ECA_wide_WSLS, by = c("SUBJECTID", "Recruitment_group", "PI_DA"))
 # double checking subjects in data
length(unique(beh_scan_ECA_wide_WSLS$SUBJECTID))

beh_scan_ECA_long <- cope_df3 %>%
  left_join(., beh_ECA_long, by = c("SUBJECTID", "Recruitment_group", "PI_DA"))

beh_scan_ECA_long_WSLS <- cope_df3 %>%
  merge(beh_ECA_long_WSLS, by = c("SUBJECTID", "Recruitment_group", "PI_DA"))

save(beh_ECA_wide, beh_ECA_long, beh_ECA_wide_WSLS, beh_ECA_long_WSLS, 
     beh_scan_ECA_wide, beh_scan_ECA_wide_WSLS, beh_scan_ECA_long, beh_scan_ECA_long_WSLS, file = "cleaned_data/COMP_ECA/all_pacct_effort_data.Rda")

```


## filter out for only COMPS & save

```{r}
# COMPs are all non-adopted children! 
summary(as.factor(beh_ECA_wide$Recruitment_group))
summary(as.factor(beh_ECA_wide$PI_DA))

## beahvior versions

beh_comp_wide <- beh_ECA_wide %>% filter(PI_DA == 0)

beh_comp_wide_WSLS <- beh_ECA_wide_WSLS %>% filter(PI_DA == 0)
beh_comp_long <- beh_ECA_long  %>% filter(PI_DA == 0)
beh_comp_long_WSLS <- beh_ECA_long_WSLS  %>% filter(PI_DA == 0)

## scan versions
beh_scan_comp_wide <- beh_scan_ECA_wide %>% filter(PI_DA == 0)
beh_scan_comp_wide_WSLS <- beh_scan_ECA_wide_WSLS %>% filter(PI_DA == 0)
beh_scan_comp_long <- beh_scan_ECA_long  %>% filter(PI_DA == 0)
beh_scan_comp_long_WSLS <- beh_scan_ECA_long_WSLS  %>% filter(PI_DA == 0)

save(beh_comp_wide, beh_comp_long, beh_comp_wide_WSLS, beh_comp_long_WSLS, 
     beh_scan_comp_wide, beh_scan_comp_wide_WSLS, beh_scan_comp_long, beh_scan_comp_long_WSLS, file = "cleaned_data/COMPS_ONLY/COMP_pacct_effort_data.Rda")

```

