---
title: "Aim2, Hypothesis 3"
author: "Michelle.VanTieghem"
date: "10/10/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# notes 
Dec 1 2019: updated with new MICM variables and using PC1_log instead of sqrt. \
Note: coef plot is deceiving because 85% CI not 95% CI!



```{r, include = F, warnings = F, echo=FALSE}
source("../../../0_R_analysis_setup_file.R")
```

```{r}
# load all data with PCA added!
load("../1_PCA/data/all_pacct_effort_data_with_PCA.rda")
```


## Aim 2: ECA and internalizing problems, moderated by persistence measures 
Identify individual-level associations between the neurobehavioral phenotype of persistence and resilience in ECA-exposed children. Hypothesis 3: Effort-based motivation will moderate the links between ECAs and internalizing problems. stronger frontal-striatal recruitment when making effort-based decisions


# main effects of ECA on internalizing
graph by group 
```{r}

ggplot(data = beh_ECA_wide, aes(x = GROUP_ECA, y = CBCL_4_INTERNPROB_T)) + 
  geom_boxplot() + theme_classic()
```

```{r}
ggplot(data = beh_ECA_wide, aes(x = PC1_log, y = CBCL_4_INTERNPROB_T)) + 
  geom_point() + theme_classic() + geom_smooth(method = "lm")
```

## PC1
```{r}
mod2_CBCL <- lm(CBCL_4_INTERNPROB_T ~ PC1_log + AGE.c + SEX.c + prop_hard_choices.c, 
                data = beh_ECA_wide)

summary(mod2_CBCL)
#coefplot(mod2_CBCL)
```

## Group 
```{r}
mod1_CBCL <- lm(CBCL_4_INTERNPROB_T ~ GROUP_ECA + AGE.c + SEX.c, 
                data = beh_ECA_wide)

summary(mod1_CBCL)
#coefplot(mod1_CBCL)
```

## when added to model together, PC1 is significant. 
```{r}

mod1_CBCL <- lm(CBCL_4_INTERNPROB_T ~ GROUP_ECA + PC1_log + AGE.c + SEX.c, 
                data = beh_ECA_wide)

summary(mod1_CBCL)
#coefplot(mod1_CBCL)
```

## PC1 x Age: SIG
relationship is stronger in younger children than older children?
```{r}

mod1_CBCL <- lm(CBCL_4_INTERNPROB_T ~  PC1_log * AGE.c + SEX.c, 
                data = beh_ECA_wide)

summary(mod1_CBCL)
```


# Effort-based motivation 
## Choice behavior 
more hard-effort choices, will be associated with reduced internalizing symptoms within the ECA group. 

```{r}
mod1b_CBCL <- lm(CBCL_4_INTERNPROB_T ~ GROUP_ECA * prop_hard_choices.c + AGE.c + SEX.c, 
                data = beh_ECA_wide)

summary(mod1b_CBCL)
#coefplot(mod1b_CBCL)
```

```{r}
mod2b_CBCL <- lm(CBCL_4_INTERNPROB_T ~ PC1_log * prop_hard_choices.c +
                  + AGE.c + SEX.c, 
                data = beh_ECA_wide)

summary(mod2b_CBCL)
```



## perceived effort (significantly different between groups)
```{r}
# make a mean perceived effort score
beh_scan_ECA_wide <- beh_scan_ECA_wide %>%
  mutate(mean_effort_perceived = (easy_effort_perceived + hard_effort_perceived)/2)

```

### perceived effort x group: trend
```{r}
mod_CBCL_effort <- lm(CBCL_4_INTERNPROB_T ~ mean_effort_perceived * GROUP_ECA + 
                        AGE.c + SEX.c, data = beh_scan_ECA_wide)

summary(mod_CBCL_effort)
```

### perceived effort x PC1: NS
```{r}
mod_CBCL_effort <- lm(CBCL_4_INTERNPROB_T ~ mean_effort_perceived * PC1_log + 
                        AGE.c + SEX.c, data = beh_scan_ECA_wide)

summary(mod_CBCL_effort)
```

# Neural FB reactivity 
## remove outliers from neural measures
```{r}
load("tables/Feedback_betas_outlier_subjects.Rdata")
reward_vmPFC_outliers <- FB_outlier_subjects %>% filter(contrast == "reward" & ROI == "vmPFC")
reward_vmPFC_df <- beh_scan_ECA_wide %>% 
  filter(!SUBJECTID  %in% reward_vmPFC_outliers$SUBJECTID)
nrow(reward_vmPFC_df)

setback_amygdala_outliers <- FB_outlier_subjects %>% filter(contrast == "setback" & ROI == "Amyg")
setback_amygdala_df <- beh_scan_ECA_wide %>% 
  filter(!SUBJECTID  %in% setback_amygdala_outliers$SUBJECTID)
nrow(setback_amygdala_df)

```


## reward vmPFC
### 1:  does reactivity to  reward (that relates to ECA) also relate to CBCL? 
if you don't exclude the outliers, it is significant :( 
```{r}
mod1_vmPFC <- lm(CBCL_4_INTERNPROB_T ~ reward_vmPFC + AGE.c + SEX.c + 
                   total_TRs_censored, 
           data = reward_vmPFC_df)
summary(mod1_vmPFC)

#### 2:  add ECA? 
mod1_vmPFC <- lm(CBCL_4_INTERNPROB_T ~ PC1_log + reward_vmPFC + AGE.c + SEX.c + 
                   total_TRs_censored, 
           data = reward_vmPFC_df)
summary(mod1_vmPFC)


#### 3. does reactivity moderate effect of ECA on internalizing? NS
mod1_vmPFC <- lm(CBCL_4_INTERNPROB_T ~ PC1_log * reward_vmPFC + AGE.c + SEX.c, 
           data = reward_vmPFC_df)
summary(mod1_vmPFC)
```


showing outliers not included in model
```{r}
effect_df <- data.frame(effect("reward_vmPFC", mod1_vmPFC))

ggplot(effect_df, aes(x = reward_vmPFC, y = fit)) + 
  geom_line() + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.3)  + 
  theme_classic()  + ylab("CBCL Internalizing") + 
  geom_point(data = beh_scan_ECA_wide, aes(x = reward_vmPFC, y = CBCL_4_INTERNPROB_T), 
             alpha = 0.5)
```

## Amygdala setback reactivity (which is significantly related to PC1)
### moderation
```{r}
mod1_amyg <- lm(CBCL_4_INTERNPROB_T ~ setback_Amyg + AGE.c + SEX.c + total_TRs_censored, 
           data = setback_amygdala_df)
summary(mod1_amyg)

mod1_amyg <- lm(CBCL_4_INTERNPROB_T ~ setback_Amyg + PC1_log +  AGE.c + SEX.c + total_TRs_censored, 
           data = setback_amygdala_df)
summary(mod1_amyg)

mod1_amyg <- lm(CBCL_4_INTERNPROB_T ~ setback_Amyg * PC1_log +  AGE.c + SEX.c + total_TRs_censored, 
           data = setback_amygdala_df)
summary(mod1_amyg)

```


showing outliers not included in model
```{r}
effect_df <- data.frame(effect("setback_Amyg", mod1_amyg))

ggplot(effect_df, aes(x =setback_Amyg, y = fit)) + 
  geom_line() + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.3)  + 
  theme_classic()  + ylab("CBCL Internalizing") + 
  geom_point(data = beh_scan_ECA_wide, aes(x = setback_Amyg, y = CBCL_4_INTERNPROB_T), 
             alpha = 0.5)
```
