---
title: "Aim2_hypothesis4"
author: "Michelle.VanTieghem"
date: "10/10/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r, include = F, warnings = F, echo=FALSE}
library(tidyverse)
library(lmerTest)
library(ggplot2)
library(effects)
library(corrplot) # for pretty correlation plots 
library(psycho) # for pretty correlation tables.
library(gridExtra) # to combine plots nicely
library(coefplot) # to make jared's coefficient plots

# color scheme 
my_colors <-  scale_color_manual(values=c("#0006CC", "#CC0000", "black", "black"))
my_colors2 <- scale_fill_manual(values=c("#0006CC", "#CC0000","black", "black"))
dark_blue = "#0006CC"
dark_Red = "#CC0000"

```

```{r}
# load all data with PCA added!
load("../1_PCA/data/all_pacct_effort_data_with_PCA.rda")
```


# Aim 2: ECA and internalizing problems, moderated by persistence measures 
Identify individual-level associations between the neurobehavioral phenotype of persistence and resilience in ECA-exposed children

## Hypothesis 4: Children’s regulation following setbacks will moderate the effects of ECA on internalizing problems: 
### (4a) Neural: stronger amygdala-prefrontal regulatory connectivity in response to setbacks
not doing conectivity!! 
```{r}
#remove outliers!

```

#### result: Amygdala trend main effect on internalizing, no moderation.
```{r}
setbackAmyg_mod1_CBCL <- lm(CBCL_4_INTERNPROB_T ~ GROUP + reward_setback_Amyg + AGE.c + SEX.c + total_TRs_censored, 
                      data = beh_scan_ECA_wide)
summary(setbackAmyg_mod1_CBCL)


setbackAmyg_mod1b_CBCL <- lm(CBCL_4_INTERNPROB_T ~ GROUP *reward_setback_Amyg + AGE.c + SEX.c + total_TRs_censored, 
                      data = beh_scan_ECA_wide)
summary(setbackAmyg_mod1b_CBCL)


setbackAmyg_mod2_CBCL <- lm(CBCL_4_INTERNPROB_T ~ PC1_sqrt + reward_setback_Amyg + AGE.c + SEX.c + total_TRs_censored, 
                      data = beh_scan_ECA_wide)

setbackAmyg_mod2b_CBCL <- lm(CBCL_4_INTERNPROB_T ~ PC1_sqrt * reward_setback_Amyg + AGE.c + SEX.c+ total_TRs_censored, 
                      data = beh_scan_ECA_wide)
summary(setbackAmyg_mod2b_CBCL)
```

#### Sanity check, reward VS reactivity? NS
```{r}
RewVS_mod1_CBCL <- lm(CBCL_4_INTERNPROB_T ~ GROUP + reward_setback_VS + AGE.c + SEX.c + total_TRs_censored, 
                      data = beh_scan_ECA_wide)
summary(RewVS_mod1_CBCL)


RewVS_mod1b_CBCL <- lm(CBCL_4_INTERNPROB_T ~ GROUP *reward_setback_VS + AGE.c + SEX.c + total_TRs_censored, 
                      data = beh_scan_ECA_wide)
summary(RewVS_mod1b_CBCL)


RewVS_mod2_CBCL <- lm(CBCL_4_INTERNPROB_T ~ PC1_sqrt + reward_setback_VS + AGE.c + SEX.c + total_TRs_censored, 
                      data = beh_scan_ECA_wide)

RewVS_mod2b_CBCL <- lm(CBCL_4_INTERNPROB_T ~ PC1_sqrt * reward_setback_VS + AGE.c + SEX.c+ total_TRs_censored, 
                      data = beh_scan_ECA_wide)
summary(RewVS_mod2b_CBCL)
```


#### Sanity check, vmPFC reactivity? NS
```{r}
RewVS_mod1_CBCL <- lm(CBCL_4_INTERNPROB_T ~ GROUP + reward_setback_vmPFC + AGE.c + SEX.c + total_TRs_censored, 
                      data = beh_scan_ECA_wide)
summary(RewVS_mod1_CBCL)


RewVS_mod1b_CBCL <- lm(CBCL_4_INTERNPROB_T ~ GROUP *reward_setback_vmPFC + AGE.c + SEX.c + total_TRs_censored, 
                      data = beh_scan_ECA_wide)
summary(RewVS_mod1b_CBCL)


RewVS_mod2_CBCL <- lm(CBCL_4_INTERNPROB_T ~ PC1_sqrt + reward_setback_vmPFC + AGE.c + SEX.c + total_TRs_censored, 
                      data = beh_scan_ECA_wide)

RewVS_mod2b_CBCL <- lm(CBCL_4_INTERNPROB_T ~ PC1_sqrt * reward_setback_vmPFC + AGE.c + SEX.c+ total_TRs_censored, 
                      data = beh_scan_ECA_wide)
summary(RewVS_mod2b_CBCL)
```


#### Sanity check, mPFC reactivity? NS
```{r}
RewVS_mod1_CBCL <- lm(CBCL_4_INTERNPROB_T ~ GROUP + reward_setback_FB_mPFC + AGE.c + SEX.c + total_TRs_censored, 
                      data = beh_scan_ECA_wide)
summary(RewVS_mod1_CBCL)


RewVS_mod1b_CBCL <- lm(CBCL_4_INTERNPROB_T ~ GROUP *reward_setback_FB_mPFC + AGE.c + SEX.c + total_TRs_censored, 
                      data = beh_scan_ECA_wide)
summary(RewVS_mod1b_CBCL)


RewVS_mod2_CBCL <- lm(CBCL_4_INTERNPROB_T ~ PC1_sqrt + reward_setback_FB_mPFC + AGE.c + SEX.c + total_TRs_censored, 
                      data = beh_scan_ECA_wide)

RewVS_mod2b_CBCL <- lm(CBCL_4_INTERNPROB_T ~ PC1_sqrt * reward_setback_FB_mPFC + AGE.c + SEX.c+ total_TRs_censored, 
                      data = beh_scan_ECA_wide)
summary(RewVS_mod2b_CBCL)
```

### (4b) Behavioral: greater persistence following a setback (indexed by greater lose-stay strategies) will be associated with fewer internalizing problems within the ECA group

result: no main effect or interaction of persistence after hard-effort setback.
```{r}
WSLS_mod1_CBCL <- lm(CBCL_4_INTERNPROB_T ~ GROUP*stay_shift+ AGE + SEX,  #Fam_inc_needs, , 
                     data = subset(beh_ECA_subj_WSLS, Feedback_prior == "Setback" & Effort_Choice_prior == "Hard"))

#hist(beh_ECA_subj_WSLS$AGE)

summary(WSLS_mod1_CBCL)
coefplot(WSLS_mod1_CBCL)
```

family income to needs isnt' sig, so omitting because some subejcts missing data.
```{r}
WSLS_mod2_CBCL <- lm(CBCL_4_INTERNPROB_T ~ PC1_sqrt*stay_shift+ AGE + SEX, # Fam_inc_needs, 
                     data = subset(beh_ECA_subj_WSLS, Feedback_prior == "Setback" & Effort_Choice_prior == "Hard"))

#hist(beh_ECA_subj_WSLS$AGE)

summary(WSLS_mod2_CBCL)
coefplot(WSLS_mod2_CBCL)

```

