---
title: "Does Amyg to setbacks mediate role of motivation on persistence?"
author: "Michelle.VanTieghem"
date: "10/10/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# results:
A) ECA predicts motivation & amyg to setbacks, and motivation predicts amyg to setbacks. but motivation does not mediate effect of ECA on amyg to setbacks. \
B) Amyg to setbacks, motivation, and PC1: NOT related to: prop hard choices, prop stay after all setbacks, or prop stay after hard setbacks. 



# load data 
```{r}
# load all data with PCA added!
source("../../../0_R_analysis_setup_file.R", echo=F)
load("data/all_pacct_effort_data_with_PCA.rda")
library(mediation)
```

## get outliers for ROI contrasts of interest
```{r}
load("tables/Feedback_betas_outlier_subjects.Rdata")
outlier_remove <- FB_outlier_subjects %>%
  filter((ROI == "vmPFC" & contrast == "setback") |
           (ROI == "Amyg" & contrast == "setback"))

```

## reformat data and remove nas
```{r}
 
beh_scan_ECA_wide2 <- beh_scan_ECA_wide %>%
  dplyr::select(SUBJECTID, GROUP_ECA, PC1_log,  AGE.c, SEX.c, 
                Fam_inc_needs, IQ, 
         perceived_effort_ave, 
         perceived_reinforce, Reinforce_rate,
         perceived_control, 
         win_feeling, lose_feeling, 
         motivated, frustrated,
        median_motor_RT_ave, 
        setback_Amyg, reward_Amyg,
        setback_vmPFC, reward_vmPFC, 
        total_TRs_censored, 
        choice_choice_mPFC, 
        prop_hard_choices, 
        N_trials) %>%
  mutate(diff_pos_affect = win_feeling - lose_feeling) %>%
  # remove outliers! 
  filter(!SUBJECTID %in% outlier_remove$SUBJECTID) %>%
  na.omit() 

nrow(beh_scan_ECA_wide2)
```

## reformat WSLS data
```{r}
beh_scan_ECA_wide_WSLS2 <- beh_scan_ECA_wide_WSLS %>%
    dplyr::select(SUBJECTID, GROUP_ECA, PC1_log,  AGE.c, SEX.c, 
                Fam_inc_needs, IQ, 
         perceived_effort_ave, 
         perceived_reinforce, Reinforce_rate,
         perceived_control, 
         win_feeling, lose_feeling, 
         motivated, frustrated,
        median_motor_RT_ave, 
        setback_Amyg, reward_Amyg,
        setback_vmPFC, reward_vmPFC, 
        total_TRs_censored, 
        choice_choice_mPFC, 
        stay_shift, 
        N_trials, 
        Feedback_prior, Effort_Choice_prior)%>%
  mutate(diff_pos_affect = win_feeling - lose_feeling) %>%
  # remove missed feedback
  filter(Feedback_prior != "Too_slow") %>%
  
  # remove outliers! 
  filter(!SUBJECTID %in% outlier_remove$SUBJECTID) %>%
  na.omit() 
  
nrow(beh_scan_ECA_wide_WSLS2)

beh_scan_ECA_wide_WSLS2 %>%
  group_by(Effort_Choice_prior, Feedback_prior) %>%
  dplyr::summarize(mean(stay_shift))

```

## make a WSLS dataset: setbacks only, collapsed harrd & easy
need 1 row per subj
```{r}
beh_scan_ECA_wide_WSLS_FB <- beh_scan_ECA_wide_WSLS2 %>%
  group_by(SUBJECTID, Feedback_prior) %>%
    dplyr::summarize(GROUP_ECA = GROUP_ECA[1],
                     PC1_log = mean(PC1_log, na.rm = T),
                     AGE.c = AGE.c[1],
                     SEX.c = SEX.c[1], 
                Fam_inc_needs = Fam_inc_needs[1],
                IQ = IQ[1], 
         perceived_effort_ave = perceived_effort_ave[1], 
         perceived_reinforce = perceived_reinforce[1],
        Reinforce_rate = Reinforce_rate[1],
         perceived_control = perceived_control[1], 
         win_feeling = win_feeling[1],
        lose_feeling = lose_feeling[1],
         motivated = motivated[1],
        frustrated = frustrated[1],
        diff_pos_affect = diff_pos_affect[1],
        median_motor_RT_ave = median_motor_RT_ave[1],
        setback_Amyg = setback_Amyg[1],
        reward_Amyg = reward_Amyg[1],
        setback_vmPFC = setback_vmPFC[1],
        reward_vmPFC = reward_vmPFC[1], 
        total_TRs_censored = total_TRs_censored[1], 
        choice_choice_mPFC = choice_choice_mPFC[1], 
        stay_shift = mean(stay_shift, na.rm = T), 
        N_trials = mean(N_trials, na.rm = T))

beh_scan_ECA_wide_WSLS_setbacks <- beh_scan_ECA_wide_WSLS_FB %>%
  filter(Feedback_prior == "Setback")

```

# what predicts amyg to setbacks? 
confirming specification curve analysis 

## amygdala and motivation: SIG 
```{r}

amyg_mod_motiv  <- lm(setback_Amyg ~  motivated +  total_TRs_censored + 
                        AGE.c + SEX.c, 
                      data =  beh_scan_ECA_wide_WSLS_setbacks)

summary(amyg_mod_motiv)
```

## amygdala by motivation and ECA : both sig
```{r}

amyg_mod_motiv_PC1 <- lm(setback_Amyg ~  motivated +  total_TRs_censored + 
                        PC1_log + perceived_control + median_motor_RT_ave +
                        AGE.c + SEX.c, 
                      data =  beh_scan_ECA_wide_WSLS_setbacks)

summary(amyg_mod_motiv_PC1)

```

motivation is related to your ability to lower reactivity to setbacks!
```{r}
effect_df <- data.frame(effect("motivated", amyg_mod_motiv_PC1), conf_int = T)

effect_plot <- ggplot(data = effect_df, aes(x = motivated, y = fit)) + 
  geom_line(color = dark_blue) + 
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = dark_blue, alpha = 0.2) + 
  geom_jitter(data =  beh_scan_ECA_wide_WSLS_setbacks, color = dark_blue,
             aes(x = motivated, y = setback_Amyg), alpha = 0.2, width = 0.05, height = 0) + 
  theme_classic() + ylab("Amygdala response to setbacks") + 
  xlab("Self-reported motivation")
effect_plot
ggsave(effect_plot, file = "figures/amyg_motivation_behavior/amyg_to_setbacks_by_motivation.png", 
     height = 4, width = 6)
```


plot effect 
```{r}
effect_df <- data.frame(effect("PC1_log", amyg_mod_motiv_PC1), conf_int = T)

effect_plot <- ggplot(data = effect_df, aes(x = PC1_log, y = fit)) + 
  geom_line(color = dark_blue) + 
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = dark_blue, alpha = 0.2) + 
  geom_jitter(data = beh_scan_ECA_wide2, color = dark_blue,
             aes(x = PC1_log, y = setback_Amyg), alpha = 0.2, width = 0.05, height = 0) + 
  theme_classic() + ylab("Amygdala response to setbacks") + 
  xlab("Cumulative ECA score")
effect_plot
ggsave(effect_plot, file = "figures/amyg_motivation_behavior/amyg_to_setbacks_by_PC1.png", 
     height = 4, width = 6)
```


## check: relationship between ECA and motivation
```{r}

motiv_mod_PC1 <- lm(motivated ~  
                        PC1_log + perceived_control + median_motor_RT_ave +
                        AGE.c + SEX.c, 
                      data =  beh_scan_ECA_wide_WSLS_setbacks)

summary(motiv_mod_PC1)

```

plot effect 
```{r}
effect_df <- data.frame(effect("PC1_log", motiv_mod_PC1), conf_int = T)

effect_plot <- ggplot(data = effect_df, aes(x = PC1_log, y = fit)) + 
  geom_line(color = dark_blue) + 
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = dark_blue, alpha = 0.2) + 
  geom_jitter(data =  beh_scan_ECA_wide_WSLS_setbacks, color = dark_blue,
             aes(x = PC1_log, y = motivated), alpha = 0.2, width = 0.05, height = 0) + 
  theme_classic() + ylab("motivation") + 
  xlab("Cumulative ECA score")
effect_plot

ggsave(effect_plot, file = "figures/amyg_motivation_behavior/motivation_by_PC1.png", 
     height = 4, width = 6)
```

## does motivation mediate effect of ECA on amygdala to setbacks? No 
not quite - not really sure why.
```{r}
# treat = X variable
motiv_mediate_PC1_amyg <- mediate(model.m = motiv_mod_PC1, model.y = amyg_mod_motiv_PC1,
                                  sims = 1000, boot = FALSE,
                                  boot.ci.type = "perc",
                                  treat = "PC1_log", mediator = "motivated")

summary(motiv_mediate_PC1_amyg)
```



# hard effort setback

## by motivation: NS 
only age is significant! 
including perceived control because related to motivation
```{r}
persist_mod_motiv <- lm(stay_shift ~  motivated + perceived_control +  
                          median_motor_RT_ave + N_trials +
                        AGE.c + SEX.c, 
                      data = filter(beh_scan_ECA_wide_WSLS2, Effort_Choice_prior == "Hard", 
                      Feedback_prior== "Setback"))

summary(persist_mod_motiv)
```

## by Amyg: NS 
only age is significant! 
```{r}
persist_hard_mod_Amyg <- lm(stay_shift ~  setback_Amyg + total_TRs_censored +
                          median_motor_RT_ave +  N_trials  +
                        AGE.c + SEX.c, 
                      data = filter(beh_scan_ECA_wide_WSLS2, Effort_Choice_prior == "Hard", 
                      Feedback_prior== "Setback"))

summary(persist_hard_mod_Amyg)
```


# persist all setbacks 

## by motivation: NS 
only age is significant! 
including perceived control because related to motivation
```{r}
persist_mod_motiv <- lm(stay_shift ~  motivated + #perceived_control +  
                          median_motor_RT_ave + N_trials + #PC1_log +
                        AGE.c + SEX.c, 
                      data =  beh_scan_ECA_wide_WSLS_setbacks)

summary(persist_mod_motiv)
```

## with more covarriates: NS 
```{r}
persist_mod_motiv <- lm(stay_shift ~  motivated + perceived_control +  
                          median_motor_RT_ave + N_trials + PC1_log +
                        AGE.c + SEX.c, 
                      data =  beh_scan_ECA_wide_WSLS_setbacks)

summary(persist_mod_motiv)
```


## by Amyg: NS

```{r}
persist_mod_Amyg <- lm(stay_shift ~  setback_Amyg + total_TRs_censored +
                          median_motor_RT_ave +  N_trials  +
                        AGE.c + SEX.c, 
                      data =  beh_scan_ECA_wide_WSLS_setbacks)

summary(persist_mod_Amyg)
```


## by Amyg: adding PC1: NS 

```{r}
persist_mod_Amyg <- lm(stay_shift ~  setback_Amyg + total_TRs_censored +
                          median_motor_RT_ave +  N_trials  +  PC1_log + 
                        AGE.c + SEX.c, 
                      data =  beh_scan_ECA_wide_WSLS_setbacks)

summary(persist_mod_Amyg)
```

## by PC1 alone: Not sig! 

```{r}
persist_mod_Amyg <- lm(stay_shift ~  #setback_Amyg + total_TRs_censored +
                          median_motor_RT_ave +  N_trials  +  PC1_log +
                        AGE.c + SEX.c, 
                      data =  beh_scan_ECA_wide_WSLS_setbacks)

summary(persist_mod_Amyg)
```


# persist after reward vs. setback 

## by motivation: NS
```{r}
persist_motiv_3way <- lm(stay_shift ~  motivated*Effort_Choice_prior*Feedback_prior +
                     total_TRs_censored +  median_motor_RT_ave +  N_trials  +
                        AGE.c + SEX.c, 
                      data = beh_scan_ECA_wide_WSLS2)

summary(persist_motiv_3way)
```


## by amyg: NS
```{r}
persist_amyg_3way <- lm(stay_shift ~  setback_Amyg*Effort_Choice_prior*Feedback_prior +
                     total_TRs_censored +  median_motor_RT_ave +  N_trials  +
                        AGE.c + SEX.c, 
                      data = beh_scan_ECA_wide_WSLS2)

summary(persist_amyg_3way)
```


# prop hard NS
## Amyg to setbacks: NS 
```{r}
choices_mod_amyg <- lm(prop_hard_choices ~ setback_Amyg +
                        total_TRs_censored + PC1_log +
                          N_trials + 
                          median_motor_RT_ave + 
                        AGE.c + SEX.c, 
                      data = beh_scan_ECA_wide2)

summary(choices_mod_amyg)
```


## by motivation: NS 
includingg perceived control and motor skills, since relte to motivation 
```{r}
choices_mod_motiv<- lm(prop_hard_choices ~ 
                          motivated + N_trials + 
                         perceived_control + median_motor_RT_ave + 
                        AGE.c + SEX.c, 
                      data = beh_scan_ECA_wide2)

summary(choices_mod_motiv)
```
