
# follow up: perceived effort on choice behavior (brms models)
Notes: looking at this from different angles: trial by trial, difference between hard and easy, average effort, and hard only.

## make some new variables 
```{r}
# add  perceived  effort by condition as a trial-by-trial measure.
beh_scan_ECA_long <- beh_scan_ECA_long %>%
  mutate(perceived_effort  = ifelse(Effort_Choice.n == 1, hard_effort_perceived, 
                                    ifelse(Effort_Choice.n == 0, easy_effort_perceived, NA)),
         perceived_effort_diff =  (hard_effort_perceived - easy_effort_perceived), 
         perceived_effort_ave = (hard_effort_perceived + easy_effort_perceived)/2, 
         # mean centered
         PC1_log.c = PC1_log - mean(PC1_log, na.rm = T),
         perceived_effort.c = perceived_effort - mean(perceived_effort, na.rm =T),
         perceived_effort_diff.c = perceived_effort_diff - mean(perceived_effort_diff, na.rm =T),
         perceived_effort_ave.c = perceived_effort_ave - mean(perceived_effort_ave, na.rm =T), 
         hard_effort_perceived.c = hard_effort_perceived - mean(hard_effort_perceived, na.rm = T))
```

## 1. perceived effort by trial 
### perceived effort is SIG and group is  also sIG!
```{r}
load("brms_models/results/perceived_effort/perceived_effort_choice_brms.Rdata")  

blm_table(perceived_effort_choice_brms)
```

### perceived effort X group: SIG!
```{r}
load("brms_models/results/perceived_effort/perceived_effort_choice_brms_gxpe.Rdata")  
blm_table(perceived_effort_choice_brms_gxpe)
```

### plot of sig group effects, when accounting for perceived effort
ECA is less likely to choose the hard task!! 
```{r}
new_df <- data.frame(expand.grid(GROUP_ECA.x = c("COMP", "ECA"),
                                 perceived_effort = mean(beh_scan_ECA_long$perceived_effort, na.rm = T),
                                 AGE.c = 0, Trial_Number.c =0, Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(perceived_effort_choice_brms, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(intercept = as.factor('intercept'), 
         Trial_Number = Trial_Number.c + max(Trial_Number.c))

effect_plot <- ggplot(effect_df, aes(x = GROUP_ECA.x, y = fit)) +
  geom_point(size = 3)  + 
 geom_errorbar(aes(ymin= lower, ymax= upper), width = 0.25) +
 geom_hline(aes(yintercept = 0.5), linetype = "dashed") + 
   theme_classic() + theme(legend.position = "none") + 
  ylab ("Likelihood to choose hard")  + xlab ("GROUP") + ylim(0, 1)
effect_plot

ggsave(effect_plot, file = "figures/perceived_effort/choice_by_GROUP_with_perceived_effort.pdf", width = 3, height = 4)
```

### plot of SIG perceived effort X GROUP effects
comparisons have a lower threshold of perceived effort to choose  hard? s
should I only use perceived effort for the hard condition? 
or shhuld I use the differrence between easy and hard? 
```{r}
new_df <- data.frame(expand.grid(GROUP_ECA.x = c("COMP", "ECA"),
                                 perceived_effort = seq(from = 1, to = 4, by  = 0.1),
                                 AGE.c = 0, Trial_Number.c =0, Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(perceived_effort_choice_brms_gxpe, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(intercept = as.factor('intercept'), 
         Trial_Number = Trial_Number.c + max(Trial_Number.c))

effect_plot <- ggplot(effect_df, aes(x = perceived_effort, y = fit)) +
  geom_line(color = dark_blue)  + facet_grid(~GROUP_ECA.x) + 
 geom_ribbon(aes(ymin= lower, ymax= upper), alpha = 0.25, fill = dark_blue) +
    #geom_point(data = perceived_df, color= dark_blue,
     #  aes(x = perceived_effort_rating, y = prop_hard_choices), 
      # alpha = 0.2, width = 0.05, height =0.0) +
 geom_hline(aes(yintercept = 0.5), linetype = "dashed") + 
   theme_classic() + theme(legend.position = "none") + 
  ylab ("Likelihood to choose hard")  + xlab ("Perceived effort") + ylim(0, 1)
effect_plot

ggsave(effect_plot, file = "figures/perceived_effort/choice_by_groupXperceived_effort.pdf", width = 3, height = 4)
```


## 2. perceived effort diff (hard-easy)
remove kids with negative values?
```{r}

hist(beh_scan_ECA_long$perceived_effort_diff.c)
```

### perceived diff is NS & group is NS
```{r}
load("brms_models/results/perceived_effort/perceived_effort_diff_choice_brms_g.Rdata")  
blm_table(perceived_effort_diff_choice_brms_g)
```


### difference in perceived effort x group: NS
```{r}
load("brms_models/results/perceived_effort/perceived_effort_diff_choice_brms_gxpe.Rdata")  
blm_table(perceived_effort_diff_choice_brms_gxpe)
```

### plot NS effects 
```{r}

new_df <- data.frame(expand.grid(GROUP_ECA.x = c("COMP", "ECA"),
                                 perceived_effort_diff.c = seq(from = -3, to = 3, by  = 0.1),
                                 AGE.c = 0, Trial_Number.c =0, Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(perceived_effort_diff_choice_brms_g, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(intercept = as.factor('intercept'), 
         Trial_Number = Trial_Number.c + max(Trial_Number.c))

effect_plot <- ggplot(effect_df, aes(x = perceived_effort_diff.c, y = fit)) +
  geom_line(color = dark_blue)  + facet_grid(~GROUP_ECA.x) + 
 geom_ribbon(aes(ymin= lower, ymax= upper), alpha = 0.25, fill = dark_blue) +
   # geom_point(data = perceived_df, color= dark_blue,
    #   aes(x = perceived_effort_diff.c, y = prop_hard_choices), 
     #  alpha = 0.2, width = 0.05, height =0.0) +
 geom_hline(aes(yintercept = 0.5), linetype = "dashed") + 
   theme_classic() + theme(legend.position = "none") + 
  ylab ("Likelihood to choose hard")  + xlab ("Perceived effort difference (Hard-Easy)") + ylim(0, 1)
effect_plot

ggsave(effect_plot, file = "figures/perceived_effort/choice_by_perceived_effort_diff_and_group.pdf", width = 3, height = 4)
```

## 3. average perceived effort (hard + easy)
### perceived average is NS & group is NS
```{r}
load("brms_models/results/perceived_effort/perceived_effort_ave_choice_brms_g.Rdata")  
blm_table(perceived_effort_ave_choice_brms_g)
```


### average perceived effort x group: NS
```{r}
load("brms_models/results/perceived_effort/perceived_effort_ave_choice_brms_gxpe.Rdata")  
blm_table(perceived_effort_ave_choice_brms_gxpe)
```


### plot NS effects 
```{r}
range(beh_scan_ECA_long$perceived_effort_ave.c, na.rm  = T)
new_df <- data.frame(expand.grid(GROUP_ECA.x = c("COMP", "ECA"),
                                 perceived_effort_ave.c = seq(from = min(beh_scan_ECA_long$perceived_effort_ave.c, na.rm  = T), to = max(beh_scan_ECA_long$perceived_effort_ave.c, na.rm  = T), by  = 0.1),
                                 AGE.c = 0, Trial_Number.c =0, Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(perceived_effort_ave_choice_brms_g, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(intercept = as.factor('intercept'), 
         Trial_Number = Trial_Number.c + max(Trial_Number.c))

effect_plot <- ggplot(effect_df, aes(x = perceived_effort_ave.c, y = fit)) +
  geom_line(color = dark_blue)  + facet_grid(~GROUP_ECA.x) + 
 geom_ribbon(aes(ymin= lower, ymax= upper), alpha = 0.25, fill = dark_blue) +
   # geom_point(data = perceived_df, color= dark_blue,
    #   aes(x = perceived_effort_diff.c, y = prop_hard_choices), 
     #  alpha = 0.2, width = 0.05, height =0.0) +
 geom_hline(aes(yintercept = 0.5), linetype = "dashed") + 
   theme_classic() + theme(legend.position = "none") + 
  ylab ("Likelihood to choose hard")  + xlab ("Average perceived effort (Hard + Easy)") + ylim(0, 1)
effect_plot

ggsave(effect_plot, file = "figures/perceived_effort/choice_by_perceived_effort_ave_and_group.pdf", width = 3, height = 4)
```

## 4. hard effort perceived
### perceived average is NS & group is NS
```{r}
load("brms_models/results/perceived_effort/hard_effort_perceived_choice_brms_g.Rdata")  
blm_table(hard_effort_perceived_choice_brms_g)
```

### average perceived effort x group: NS
```{r}
load("brms_models/results/perceived_effort/perceived_effort_ave_choice_brms_gxpe.Rdata")  
blm_table(perceived_effort_ave_choice_brms_gxpe)
```

### plot NS effects 
```{r}
range(beh_scan_ECA_long$hard_effort_perceived.c, na.rm  = T)
new_df <- data.frame(expand.grid(GROUP_ECA.x = c("COMP", "ECA"),
                                 hard_effort_perceived.c = seq(from = min(beh_scan_ECA_long$hard_effort_perceived.c, na.rm  = T), to = max(beh_scan_ECA_long$hard_effort_perceived.c, na.rm  = T), by  = 0.1),
                                 AGE.c = 0, Trial_Number.c =0, Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(hard_effort_perceived_choice_brms_g, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(intercept = as.factor('intercept'), 
         Trial_Number = Trial_Number.c + max(Trial_Number.c))

effect_plot <- ggplot(effect_df, aes(x = hard_effort_perceived.c, y = fit)) +
  geom_line(color = dark_blue)  + facet_grid(~GROUP_ECA.x) + 
 geom_ribbon(aes(ymin= lower, ymax= upper), alpha = 0.25, fill = dark_blue) +
   # geom_point(data = perceived_df, color= dark_blue,
    #   aes(x = perceived_effort_diff.c, y = prop_hard_choices), 
     #  alpha = 0.2, width = 0.05, height =0.0) +
 geom_hline(aes(yintercept = 0.5), linetype = "dashed") + 
   theme_classic() + theme(legend.position = "none") + 
  ylab ("Likelihood to choose hard")  + xlab ("Average perceived effort (Hard + Easy)") + ylim(0, 1)
effect_plot

ggsave(effect_plot, file = "figures/perceived_effort/choice_by_hard_effort_perceived_and_group.pdf", width = 3, height = 4)
```

## 5. wide version of perceived effort on prop. hard 


### hard only: NS
```{r}
perceived_choice_lm <- lm(prop_hard_choices.c ~  GROUP_ECA * hard_effort_perceived +
                             median_motor_RT_hard + 
                            AGE.c + SEX.c, 
                          data = beh_scan_ECA_wide)
summary(perceived_choice_lm)
```

### difference in perceived effort: NS
```{r}
perceived_diff_choice_lm <- lm(prop_hard_choices.c ~  GROUP_ECA * perceived_effort_diff.c + 
                            AGE.c + SEX.c + median_motor_RT_hard, 
                          data = beh_scan_ECA_wide)
summary(perceived_diff_choice_lm)
```

### average perceived effort: NS
```{r}
perceived_diff_choice_lm <- lm(prop_hard_choices.c ~  GROUP_ECA * perceived_effort_ave.c + 
                            AGE.c + SEX.c + median_motor_RT_hard, 
                          data = beh_scan_ECA_wide)
summary(perceived_diff_choice_lm)

beh_scan_ECA_wide$median_motor_RT_easy
```


# follow-up: perceived effort on choice RT? 
```{r}
```

