---
title: "Brain-Behavior associations"
author: "Michelle.VanTieghem"
date: "10/10/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---
*confound:* behavior varies by task version, so only including usable scan participants who were guaranteed to perform the task in scanner for both runs.

```{r, include = F, warnings = F, echo=FALSE, message = F}
source("../../../0_R_analysis_setup_file.R")
```


```{r}
# load all data with PCA added!
load("../1_PCA/data/all_pacct_effort_data_with_PCA.rda")

```


# effects of choice reactivity on choice behavior: NS
Testing hypothesis from COMP pre-registration, that choice-related prefrontal activity would be associated with greater proportion of hard-effort choices.\

clean data and remove outliers first! 
```{r}
beh_scan_ECA_long <- beh_scan_ECA_long %>%
  filter(!is.na(choice_choice_mPFC))

# these were calculated in Aim1_hypothesis1a
load("tables/Choice_betas_outlier_wideects.Rdata")
choice_mPFC_outliers <- choice_outlier_wideects %>% filter(ROI == "mPFC")
choice_VS_outliers <- choice_outlier_wideects %>% filter(ROI == "VS")
choice_ACC_outliers <- choice_outlier_wideects %>% filter(ROI == "ACC")


```


### mPFC and choices
```{r}
choice_mPFC_mod_long <- glmer(Effort_Choice.n ~ PC1_sqrt + choice_choice_mPFC +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c + #
                      (1 + Trial_Number.c | SUBJECTID), 
                     family = binomial,
                    data = filter(beh_scan_ECA_long, ! SUBJECTID %in% choice_mPFC_outliers$SUBJECTID),
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mPFC_mod_long)

choice_mPFC_mod_wide <- lm(prop_hard_choices ~ PC1_sqrt + choice_choice_mPFC +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c,
                    data = subset(beh_scan_ECA_wide, !SUBJECTID %in% choice_mPFC_outliers$SUBJECTID))
summary(choice_mPFC_mod_wide)

```

### ACC and choices
```{r}
choice_ACC_mod_long <- glmer(Effort_Choice.n ~ PC1_sqrt + choice_ACC +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c + #
                      (1 + Trial_Number.c | SUBJECTID), 
                     family = binomial,
                    data = filter(beh_scan_ECA_long, ! SUBJECTID %in% choice_ACC_outliers$SUBJECTID),
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_ACC_mod_long)

choice_ACC_mod_wide <- lm(prop_hard_choices ~ PC1_sqrt + choice_ACC +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c,
                    data = subset(beh_scan_ECA_wide, !SUBJECTID %in% choice_ACC_outliers$SUBJECTID))
summary(choice_ACC_mod_wide)

```



### VS and choices
```{r}
choice_VS_mod_long <- glmer(Effort_Choice.n ~ PC1_sqrt + choice_VS +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c + #
                      (1 + Trial_Number.c | SUBJECTID), 
                     family = binomial,
                    data = filter(beh_scan_ECA_long, ! SUBJECTID %in% choice_VS_outliers$SUBJECTID),
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_VS_mod_long)

choice_VS_mod_wide <- lm(prop_hard_choices ~ PC1_sqrt + choice_VS +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c,
                    data = subset(beh_scan_ECA_wide, !SUBJECTID %in% choice_VS_outliers$SUBJECTID))
summary(choice_VS_mod_wide)

```


# effects of FB ROIs on choice behavior: NS
Testing hypothesis from COMP pre-registration, that reward-related VS reactivity would be associated with greater proportion of hard-effort choices.\
clean data and remove outliers first 
## remove outliers 
```{r}
load("tables/Feedback_betas_outlier_wideects.Rdata")
reward_mPFC_outliers <- FB_outlier_wideects %>% filter(ROI == "mPFC" & contrast == "reward")
reward_vmPFC_outliers <- FB_outlier_wideects %>% filter(ROI == "vmPFC" & contrast == "reward")
reward_VS_outliers <- FB_outlier_wideects %>% filter(ROI == "VS" & contrast == "reward")
reward_Amyg_outliers <- FB_outlier_wideects %>% filter(ROI == "Amyg" & contrast == "reward")

reward_setback_mPFC_outliers <- FB_outlier_wideects %>% filter(ROI == "mPFC" & contrast == "reward_minus_setback")
reward_setback_vmPFC_outliers <- FB_outlier_wideects %>% filter(ROI == "vmPFC" & contrast == "reward_minus_setback")
reward_setback_VS_outliers <- FB_outlier_wideects %>% filter(ROI == "VS" & contrast == "reward_minus_setback")
reward_setback_Amyg_outliers <- FB_outlier_wideects %>% filter(ROI == "Amyg" & contrast == "reward_minus_setback")
```

### VS to reward and choices
```{r}
choice_VS_mod_long <- glmer(Effort_Choice.n ~ PC1_sqrt + reward_VS +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c + #
                      (1 + Trial_Number.c | SUBJECTID), 
                     family = binomial,
                    data = filter(beh_scan_ECA_long, ! SUBJECTID %in% reward_VS_outliers$SUBJECTID),
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_VS_mod_long)

choice_VS_mod_wide <- lm(prop_hard_choices ~ PC1_sqrt + reward_VS +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c,
                    data = subset(beh_scan_ECA_wide, !SUBJECTID %in% reward_VS_outliers$SUBJECTID))
summary(choice_VS_mod_wide)

```


### VS to reward-setback and choices
```{r}
choice_VS_mod_long <- glmer(Effort_Choice.n ~ PC1_sqrt + reward_setback_VS +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c + #
                      (1 + Trial_Number.c | SUBJECTID), 
                     family = binomial,
                    data = filter(beh_scan_ECA_long, ! SUBJECTID %in% reward_setback_VS_outliers$SUBJECTID),
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_VS_mod_long)

choice_VS_mod_wide <- lm(prop_hard_choices ~ PC1_sqrt + reward_setback_VS +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c,
                    data = subset(beh_scan_ECA_wide, !SUBJECTID %in% reward_setback_VS_outliers$SUBJECTID))
summary(choice_VS_mod_wide)

```


### vmPFC to reward and choices
```{r}
choice_vmPFC_mod_long <- glmer(Effort_Choice.n ~ PC1_sqrt + reward_vmPFC +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c + #
                      (1 + Trial_Number.c | SUBJECTID), 
                     family = binomial,
                    data = filter(beh_scan_ECA_long, ! SUBJECTID %in% reward_vmPFC_outliers$SUBJECTID),
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_vmPFC_mod_long)

choice_vmPFC_mod_wide <- lm(prop_hard_choices ~ PC1_sqrt + reward_vmPFC +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c,
                    data = subset(beh_scan_ECA_wide, !SUBJECTID %in% reward_vmPFC_outliers$SUBJECTID))
summary(choice_vmPFC_mod_wide)

```


### vmPFC to reward-setback and choices
```{r}
choice_vmPFC_mod_long <- glmer(Effort_Choice.n ~ PC1_sqrt + reward_setback_vmPFC +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c + #
                      (1 + Trial_Number.c | SUBJECTID), 
                     family = binomial,
                    data = filter(beh_scan_ECA_long, ! SUBJECTID %in% reward_setback_vmPFC_outliers$SUBJECTID),
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_vmPFC_mod_long)

choice_vmPFC_mod_wide <- lm(prop_hard_choices ~ PC1_sqrt + reward_setback_vmPFC +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c,
                    data = subset(beh_scan_ECA_wide, !SUBJECTID %in% reward_setback_vmPFC_outliers$SUBJECTID))
summary(choice_vmPFC_mod_wide)

```


### Amyg to reward and choices
```{r}
choice_Amyg_mod_long <- glmer(Effort_Choice.n ~ PC1_sqrt + reward_Amyg +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c + #
                      (1 + Trial_Number.c | SUBJECTID), 
                     family = binomial,
                    data = filter(beh_scan_ECA_long, ! SUBJECTID %in% reward_Amyg_outliers$SUBJECTID),
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_Amyg_mod_long)

choice_Amyg_mod_wide <- lm(prop_hard_choices ~ PC1_sqrt + reward_Amyg +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c,
                    data = subset(beh_scan_ECA_wide, !SUBJECTID %in% reward_Amyg_outliers$SUBJECTID))
summary(choice_Amyg_mod_wide)

```


### Amyg to setback and choices*
significant effect of ECA on amyg reactivity to setbacks. 
```{r}
choice_Amyg_mod_long <- glmer(Effort_Choice.n ~ PC1_sqrt + setback_Amyg +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c + #
                      (1 + Trial_Number.c | SUBJECTID), 
                     family = binomial,
                    data = filter(beh_scan_ECA_long, ! SUBJECTID %in% reward_setback_Amyg_outliers$SUBJECTID),
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_Amyg_mod_long)

choice_Amyg_mod_wide <- lm(prop_hard_choices ~ PC1_sqrt + reward_setback_Amyg +
                       AGE.c + SEX.c + Reinforce_rate.c + Trial_Number.c,
                    data = subset(beh_scan_ECA_wide, !SUBJECTID %in% reward_setback_Amyg_outliers$SUBJECTID))
summary(choice_Amyg_mod_wide)

```