---
title: "ECA effects on perceived effort"
author: "Michelle.VanTieghem"
date: "Dec 16, 2019"
output:
  html_document:
    number_sections: no
    toc: yes
    
    toc_float:
      collapsed: no
      smooth_scroll: yes
  png_document:
    toc: yes
---

# Readme 
In depth analysis of ECA effects on perceived effort \



```{r, include = F, warnings = F, echo=FALSE, message = F}
source("../../../0_R_analysis_setup_file.R")
```


```{r}
# load all data with PCA added!
load("../data/all_pacct_effort_data_with_PCA.rda")

```


## make a wide data version with perceived effort and motor skills.
```{r}
# make long version of perceived effort data
perceived_df <- beh_scan_ECA_wide %>% 
  gather(key = "condition", value = "perceived_effort_rating", 
         hard_effort_perceived, easy_effort_perceived) %>%
  mutate(condition = as.factor(ifelse(condition == "hard_effort_perceived", 
                                      "Hard", "Easy"))) %>%
      mutate( motor_speed_by_condition = ifelse(condition == "Easy", median_motor_RT_easy, median_motor_RT_hard), 
              diff_pos_affect = win_feeling - lose_feeling, 
             GROUP_ECA = as.factor(GROUP_ECA)) %>%
  filter(!is.na(perceived_effort_rating))
```


# check correlation between motor skills and perceived effort.
## hard buttons & hard perceived: SIG
```{r}
cor.test(beh_scan_ECA_wide$median_motor_RT_hard, beh_scan_ECA_wide$hard_effort_perceived)

```

## easy buttons & easy perceived: NS
```{r}
cor.test(beh_scan_ECA_wide$median_motor_RT_easy, beh_scan_ECA_wide$easy_effort_perceived)

```

## mean buttons & mean perceivd effort: weakly sig
because hard is correlated.
```{r}
cor.test(beh_scan_ECA_wide$perceived_effort_ave, beh_scan_ECA_wide$median_motor_RT_ave)

```

#  perceived effort: 

## checking distributions
```{r}
qqPlot(perceived_df$perceived_effort_rating, "norm")
qqPlot(perceived_df$perceived_effort_rating, "lnorm") # no
poisson <- fitdistr( perceived_df$perceived_effort_rating, "Poisson")
qqPlot(perceived_df$perceived_effort_rating, "pois", lambda =poisson$estimate)
```

## COMP main effects of condition.
```{r}
perceived_effort_mod_g <- glmer(perceived_effort_rating ~ condition + AGE.c + SEX.c + 
                            # Reinforce_rate.c + motor_speed_by_condition + 
                              # diff_pos_affect + perceived_reinforce + perceived_control +
                               (1 | SUBJECTID), 
                             family = "poisson",
                           data = filter(perceived_df, GROUP_ECA == "COMP"))
summary(perceived_effort_mod_g)


```

## ECA group effects 
main effect SIG, no interaction with condition or age
including/not including these covariates does not make a difference! 
```{r}
perceived_effort_mod_g <- glmer(perceived_effort_rating ~ condition + GROUP_ECA + AGE.c + SEX.c + 
                             #Reinforce_rate.c + motor_speed_by_condition + 
                              # diff_pos_affect + perceived_reinforce + perceived_control +
                               (1 | SUBJECTID), 
                             family = "poisson",
                           data = perceived_df)
summary(perceived_effort_mod_g)


perceived_effort_mod_cxg <- glmer(perceived_effort_rating ~ condition *GROUP_ECA + AGE.c + SEX.c +  
                            # Reinforce_rate.c +  motor_speed_by_condition + 
                             #  diff_pos_affect + perceived_reinforce + perceived_control +
                               (1 | SUBJECTID), 
                            family = "poisson",
                           data = perceived_df)
summary(perceived_effort_mod_cxg)


perceived_effort_mod_gxa <- glmer(perceived_effort_rating ~ condition + GROUP_ECA*AGE.c + SEX.c +  
                               #     Reinforce_rate.c +  motor_speed_by_condition + 
                              # diff_pos_affect + perceived_reinforce + perceived_control +
                               (1 | SUBJECTID), 
                                family = "poisson",
                           data = perceived_df)
summary(perceived_effort_mod_gxa)
```


### plot effect of condition
```{r}
# get effect  df tidy
effort_effect <-  as.data.frame(effect("condition", perceived_effort_mod_g, confint=TRUE))

plot_effect <- ggplot(effort_effect,aes(x = condition, y = fit)) +
 geom_point(size = 3,stat = "identity", position=position_dodge()) + theme_classic() + 
  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_jitter(data = perceived_df, aes(x = condition, y = perceived_effort_rating),
       width = 0.1, height = 0.1, pch = 21,
             alpha = 0.3, fill = dark_blue) +
  theme_classic() + ylab("Perceived Effort") + coord_cartesian(ylim=c(1,4)) +
  xlab ("condition") + theme(legend.position = "none") 
plot_effect

ggsave(plot_effect, file = "../figures/self_report/perceived_effort_by_condition.png", width = 6, height = 4)

```

### plot effect of GROUP
```{r}
# get effect  df tidy
effort_effect <-  as.data.frame(effect("condition:GROUP_ECA", perceived_effort_mod_g, confint=TRUE))

plot_effect <- ggplot(effort_effect,aes(x = GROUP_ECA, y = fit)) +
 geom_point(size = 3,stat = "identity", position=position_dodge()) + theme_classic() + 
  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_jitter(data = perceived_df, aes(x = GROUP_ECA, y = perceived_effort_rating),
       width = 0.1, height = 0.1, pch = 21,
             alpha = 0.3, fill = dark_blue) +
  theme_classic() + ylab("Perceived Effort") + coord_cartesian(ylim=c(1,4)) +
  xlab ("GROUP") + theme(legend.position = "none") + facet_grid(~condition)
plot_effect

ggsave(plot_effect, file = "../figures/perceived_effort/perceived_effort_by_GROUP.png", width = 4, height = 4)

```


## condition x age effects: TREND
```{r}
perceived_effort_mod_cxa <- glmer(perceived_effort_rating ~ condition*AGE.c + GROUP_ECA + SEX.c +
                                    Reinforce_rate.c +  motor_speed_by_condition + 
                               (1 | SUBJECTID), 
                               family = "poisson",
                           data = perceived_df)
summary(perceived_effort_mod_cxa)
```

### plot condition x age 
```{r}
# get effect  df tidy
effort_effect <-  as.data.frame(effect("condition:AGE.c", perceived_effort_mod_cxa, confint=TRUE))

plot_effect <- ggplot(effort_effect,aes(x = AGE.c, y = fit)) +
 geom_line() + theme_classic() + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.25, fill = dark_blue) +
  geom_jitter(data = perceived_df, aes(x = AGE.c, y = perceived_effort_rating),
       width = 0.2, height = 0.1, pch = 21,
             alpha = 0.3, fill = dark_blue) +
  theme_classic() + ylab("Perceived effort") + coord_cartesian(ylim=c(1,4)) +
  xlab ("Cumulative ECA Score") + theme(legend.position = "none") + facet_grid(~condition)
plot_effect

ggsave(plot_effect, file = "../figures/perceived_effort/perceived_effort_by_ageXcondition.png", width = 6, height = 4)
```


# cumulative ECA effects
main effect, no interaction with condition.
```{r}
perceived_effort_mod_PC1 <- glmer(perceived_effort_rating ~ condition + PC1_log + AGE.c + SEX.c + 
                             # Reinforce_rate.c +  motor_speed_by_condition +
                              # diff_pos_affect + perceived_reinforce + perceived_control +
                               (1 | SUBJECTID), 
                                family = "poisson",
                           data = perceived_df)
summary(perceived_effort_mod_PC1)

perceived_effort_mod_cxPC1 <- lmer(perceived_effort_rating ~ condition *PC1_log + AGE.c + SEX.c +  
                             # Reinforce_rate.c +  motor_speed_by_condition +
                              # diff_pos_affect + perceived_reinforce + perceived_control +     
                               (1 | SUBJECTID), 
                           data = perceived_df)
summary(perceived_effort_mod_cxPC1)


perceived_effort_mod_PC1xa <- lmer(perceived_effort_rating ~ condition + PC1_log*AGE.c + SEX.c + 
                             # Reinforce_rate.c +  motor_speed_by_condition +
                              # diff_pos_affect + perceived_reinforce + perceived_control +
                               (1 | SUBJECTID), 
                           data = perceived_df)
summary(perceived_effort_mod_PC1xa)
```


### plot effect of cumulative ECA 
greater perceived effort with more ECA 
just plotting both conditions for visualization purposes.
```{r}
# get effect  df tidy
effort_effect <-  as.data.frame(effect("condition:PC1_log", perceived_effort_mod_PC1, confint=TRUE))

plot_effect <- ggplot(effort_effect,aes(x = PC1_log, y = fit)) +
 geom_line() + theme_classic() + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.25, fill = dark_blue) +
  geom_jitter(data = perceived_df, aes(x = PC1_log, y = perceived_effort_rating),
       width = 0.2, height = 0.1, pch = 21,
             alpha = 0.3, fill = dark_blue) +
  theme_classic() + ylab("Perceived effort") + coord_cartesian(ylim=c(1,4)) +
  xlab ("Cumulative ECA Score") + theme(legend.position = "none") + facet_grid(~condition)
plot_effect

ggsave(plot_effect, file = "../figures/perceived_effort/perceived_effort_by_PC1_log.png", width = 6, height = 4)
```



