---
title: "Self-report data by ECA"
author: "Michelle.VanTieghem"
date: "Dec 2, 2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---
# notes:
summary of results: significant ECA effect of perceived effort: more ECA = more perceived effort for both hard and easy. \
no ECA effect on positive affect, perceived control, frustration. 


# Load data
## only behavior
from data_cleaning_for_analysis 
```{r data, message = F, warning = F}
source("../../../0_R_analysis_setup_file.R", echo=F)

load("../1_PCA/data/all_pacct_effort_data_with_PCA.rda")
```


# Effort Manipulation checks & effects of ECA 

## Self-reported affect to rewards & setbacks 
win feeling = how did you feel when you won coins \
lose feeling = how did you feel with you didn't win coins  \
(on likert scale, where 1 = very unhappy and 4 = very happy)
```{r tre}
# make long version of perceived effort data
pos_affect_df <- beh_ECA_wide %>% 
  gather(key = "condition", value = "positive_affect", 
          win_feeling,lose_feeling) %>%
  mutate(condition = as.factor(ifelse(condition == "win_feeling", 
                                      "Rewards", "Setbacks"))) %>%
  select(SUBJECTID, GROUP_ECA, PC1_log, SEX.c, AGE.c,  positive_affect, condition) %>%
  filter(!is.na(positive_affect) & !is.na(condition) & !is.na(AGE.c) & !is.na(SEX.c)) %>%
  mutate(GROUP_ECA = as.factor(GROUP_ECA))

```

### group effects? NS
```{r ert}
pos_affect_mod_g <- lmer(positive_affect ~ condition * GROUP_ECA + AGE.c + SEX.c + 
                          (1 | SUBJECTID),
   data = pos_affect_df)
summary(pos_affect_mod_g)

pos_affect_mod_PC1 <- lmer(positive_affect ~ condition * PC1_log + AGE.c + SEX.c + 
                          (1 | SUBJECTID),
   data = pos_affect_df)
summary(pos_affect_mod_PC1)
```


```{r qreeee}
# get effect  df tidy
affect_effect <-  as.data.frame(effect("condition:GROUP_ECA", pos_affect_mod_g, confint=TRUE))

plot_effect <- ggplot(affect_effect,aes(x = condition, y = fit)) +
 geom_bar(stat = "identity", position=position_dodge(),
                                 alpha = 0.25, fill = dark_blue) + theme_classic() + 
  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_jitter(data = pos_affect_df,  aes(x = condition, y = positive_affect),
              width = 0.2, height = 0.05, pch = 21,
             alpha = 0.3, fill = dark_blue) +
   theme(legend.position = "none") + facet_grid(~GROUP_ECA) +
  theme_classic() + ylab("Positive Affect") + coord_cartesian(ylim=c(1,4)) +
  xlab ("Condition") + theme(legend.position = "none")
plot_effect

ggsave(plot_effect, file = "figures/manipulation_checks/no_group_diff_pos_affect.pdf", width = 2.5, height = 4)

```

## Age x condition?
```{r}
pos_affect_mod_gxa <- lmer(positive_affect ~ condition * AGE.c + SEX.c +  GROUP_ECA +
                          (1 | SUBJECTID),
   data = pos_affect_df)
summary(pos_affect_mod_gxa)
```

## Perceived control

### main effect of age, but not group. 
perceived control declines with age - kids know that it's rigged.
```{r poi}
control_df <- beh_scan_ECA_wide %>%
  filter(!is.na(perceived_control)) %>%
  mutate(GROUP_ECA = as.factor(GROUP_ECA))

perceived_control_mod_g <-  lm(perceived_control ~ GROUP_ECA + AGE.c + SEX.c + 
                                 Reinforce_rate.c, data = control_df)

summary(perceived_control_mod_g)

perceived_control_mod_PC1 <-  lm(perceived_control ~ PC1_log + AGE.c + SEX.c + 
                                 Reinforce_rate.c, data = control_df)

summary(perceived_control_mod_PC1)
```

plot main effect of age
```{r}
control_effect <-  as.data.frame(effect("GROUP_ECA:AGE.c", perceived_control_mod_g, confint=TRUE))

plot_effect <- ggplot(control_effect, aes(x = AGE.c, y = fit)) +
 geom_line() + theme_classic() + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.25, fill = dark_blue) +
  geom_jitter(data = control_df, aes(x = AGE.c, y = perceived_control),
       width = 0.2, height = 0.1, pch = 21,
             alpha = 0.3, fill = dark_blue) +
  theme_classic() + ylab("Perceived control") + coord_cartesian(ylim=c(1,4)) +
  xlab ("Age (mean-centered)") + theme(legend.position = "none") + facet_grid(~GROUP_ECA)
plot_effect

ggsave(plot_effect, file = "figures/manipulation_checks/age_effect_perceived_control.pdf", width = 2.5, height = 4)

```

## frustration
```{r}
df <- beh_ECA_subj %>%
  filter(!is.na(frustrated)) %>%
  mutate(GROUP_ECA = as.factor(GROUP_ECA))

```

### GROUP effects? NS
```{r}
frustrated_mod_g <- lm(frustrated ~ GROUP_ECA + AGE.c + SEX.c + Reinforce_rate.c, 
                      data = df)
summary(frustrated_mod_g)


frustrated_mod_g <- lm(frustrated ~ PC1_log + AGE.c + SEX.c + Reinforce_rate.c, 
                      data = df)
summary(frustrated_mod_g)
```

## motivation
```{r}
df <- beh_ECA_subj %>%
  filter(!is.na(motivated)) %>%
  mutate(GROUP_ECA = as.factor(GROUP_ECA))

```

### GROUP effects? NS
motivation is affected by their positive affect after winning. 
when you account for that positive affect, then group influences motivation. 
but i dont know if this is legit. 
```{r}
motivated_mod_g <- lm(motivated ~ GROUP_ECA + win_feeling + AGE.c + SEX.c + Reinforce_rate.c, 
                      data = df)
summary(motivated_mod_g)


motivated_mod_PC1 <- lm(motivated ~ PC1_log + win_feeling + AGE.c + SEX.c + Reinforce_rate.c, 
                      data = df)
summary(motivated_mod_PC1)
```


## Sleepy
```{r}
df <- beh_ECA_subj %>%
  filter(!is.na(sleepy)) %>%
  mutate(GROUP_ECA = as.factor(GROUP_ECA))

```

### ECA effects? NS
motivation is affected by their positive affect after winning. 
when you account for that positive affect, then group influences motivation. 
but i dont know if this is legit. 
```{r}
sleepy_mod_g <- lm(sleepy~ GROUP_ECA + AGE.c + SEX.c + Reinforce_rate.c, 
                      data = df)
summary(sleepy_mod_g)


sleepy_mod_PC1 <- lm(sleepy ~ PC1_log + AGE.c + SEX.c + Reinforce_rate.c, 
                      data = df)
summary(sleepy_mod_PC1)
```


## Fun
```{r}
df <- beh_ECA_subj %>%
  filter(!is.na(fun)) %>%
  mutate(GROUP_ECA = as.factor(GROUP_ECA))

```

### GROUP effects? NS but sig age effects
motivation is affected by their positive affect after winning. 
when you account for that positive affect, then group influences motivation. 
but i dont know if this is legit. 
```{r}
fun_mod_g <- lm(fun ~ GROUP_ECA + AGE.c + SEX.c + Reinforce_rate.c, 
                      data = df)
summary(fun_mod_g)


fun_mod_PC1 <- lm(fun ~ PC1_log + AGE.c + SEX.c + Reinforce_rate.c, 
                      data = df)
summary(fun_mod_PC1)
```

##  Motor skills: button-pressing on pre-test (hard vs. easy)
median RT during  finger tapping pre-test
```{r stuff}
beh_ECA_motor_long <- beh_ECA_long %>%
  group_by(SUBJECTID) %>%
  mutate(motor_skills_RT = ifelse(Effort_Choice == "Easy", (motor_skills_easy*100), 
                            ifelse(Effort_Choice == "Hard", (motor_skills_hard*100), NA)),
         log_motor_skills_RT = log(motor_skills_RT))

motor_skills_RT_table <- beh_ECA_motor_long %>%
  group_by(Effort_Choice) %>%
  summarize(median(e_RT, na.rm = T),
            sd(motor_skills_RT, na.rm = T))
save(motor_skills_RT_table, file = "tables/2_manipulation_checks/motor_skills_RT_table_by_condition.Rdata")

ggplot(data = beh_comp_motor_long, aes(motor_skills_RT)) + facet_grid(version~Effort_Choice) +
  geom_density() + theme_classic()

fix <- beh_comp_long %>% filter(is.na(version))
unique(fix$SUBJECTID)
``` 

RT is not normally distributed
```{r}
shapiro.test(beh_comp_motor$motor_skills_RT)
shapiro.test(beh_comp_motor$log_motor_skills_RT)

plot(beh_comp_motor$motor_skills_RT)
plot(beh_comp_motor$log_motor_skills_RT) # beh_comp_motor$motor_skills_RT)
```

### Effort RT was slower for the hard task
```{r other stuff}
# sig using Raw RT 
motor_skills_RT <- lmer(motor_skills_RT ~ condition  + AGE.c + SEX.c + 
                (1 | SUBJECTID),
               data = beh_comp_motor)
summary(motor_skills_RT)

# same with logged RT
motor_skills_RT_lg <- lmer(log_RT ~ condition  + AGE.c + SEX.c + 
                (1 | SUBJECTID),
               data = beh_comp_motor)
summary(motor_skills_RT_lg)
```

### plot the effects by condition
```{r more stuff}
effect_df <- data.frame(effect("condition", motor_skills_RT_lg))

RT_condition_plot <- ggplot(data = effect_df, aes(x = condition, y = fit)) + 
  geom_point( color = "black", size = 1.5) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  geom_jitter(data = beh_comp_motor, aes(x = condition, y = log_RT), alpha = 0.3, size = 1, width = 0.15, color= dark_blue) +
  my_colors + my_colors2 + theme_classic() + ylab("log RT (ms)") + ylim(2.5, 3.75)

RT_condition_plot
ggsave(RT_condition_plot, file = "figures/manipulation_checks/2_manipulation_checks/motor_skills_RT_by_condition.pdf", width = 3, height = 4)
```


### no age x condition interaction
```{r ttt }
# same with logged RT
motor_skills_RT_lg_int <- lmer(log_RT ~ condition* AGE.c + SEX.c + 
                (1 | SUBJECTID),
               data = beh_comp_motor)
summary(motor_skills_RT_lg_int)
```


### plot the effects by age 
```{r bbbb}
effect_df <- data.frame(effect("condition:AGE.c", motor_skills_RT_lg))

motor_skills_RT_int_plot <- ggplot(data = effect_df, aes(x = AGE.c, y= fit)) + 
  geom_line(aes(color = condition)) + 
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = condition), alpha = 0.25) +
  geom_point(data = beh_comp_motor, aes(x = AGE.c, y = log_RT, color= condition), alpha = 0.3, width = 0.04) +
  my_colors + my_colors2 + theme_classic() + ylab("log RT (ms)") + 
  geom_line(data = beh_comp_motor, aes(x = AGE.c, y = log_RT, group = SUBJECTID))
motor_skills_RT_int_plot
ggsave(motor_skills_RT_int_plot, file = "figures/manipulation_checks/2_manipulation_checks/motor_skills_RT_by_conditionxAge.pdf")
```
