---
title: " Replicate Bhanji: vmPFC mediates role of frustration on persistence?"
author: "Michelle.VanTieghem"
date: "10/10/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# load data 
```{r}
# load all data with PCA added!
source("../../../0_R_analysis_setup_file.R", echo=F)
load("data/all_pacct_effort_data_with_PCA.rda")
library(mediation)
```

## get outliers for ROI contrasts of interest
```{r}
load("tables/Feedback_betas_outlier_subjects.Rdata")
outlier_remove <- FB_outlier_subjects %>%
  filter((ROI == "vmPFC" & contrast == "setback") |
           (ROI == "Amyg" & contrast == "setback"))

```

## reformat data and remove nas
```{r}
 
beh_scan_ECA_wide2 <- beh_scan_ECA_wide %>%
  dplyr::select(SUBJECTID, GROUP_ECA, PC1_log,  AGE.c, SEX.c, 
                Fam_inc_needs, IQ, 
         perceived_effort_ave, 
         perceived_reinforce, Reinforce_rate,
         perceived_control, 
         win_feeling, lose_feeling, 
         motivated, frustrated,
        median_motor_RT_ave, 
        setback_Amyg, reward_Amyg,
        setback_vmPFC, reward_vmPFC, 
        total_TRs_censored, 
        choice_choice_mPFC, 
        prop_hard_choices, 
        N_trials) %>%
  mutate(diff_pos_affect = win_feeling - lose_feeling) %>%
  # remove outliers! 
  filter(!SUBJECTID %in% outlier_remove$SUBJECTID) %>%
  na.omit() 

nrow(beh_scan_ECA_wide2)
```

## reformat WSLS data
```{r}
beh_scan_ECA_wide_WSLS2 <- beh_scan_ECA_wide_WSLS %>%
    dplyr::select(SUBJECTID, GROUP_ECA, PC1_log,  AGE.c, SEX.c, 
                Fam_inc_needs, IQ, 
         perceived_effort_ave, 
         perceived_reinforce, Reinforce_rate,
         perceived_control, 
         win_feeling, lose_feeling, 
         motivated, frustrated,
        median_motor_RT_ave, 
        setback_Amyg, reward_Amyg,
        setback_vmPFC, reward_vmPFC, 
        total_TRs_censored, 
        choice_choice_mPFC, 
        stay_shift, 
        N_trials, 
        Feedback_prior, Effort_Choice_prior)%>%
  mutate(diff_pos_affect = win_feeling - lose_feeling) %>%
  # remove missed feedback
  filter(Feedback_prior != "Too_slow") %>%
  
  # remove outliers! 
  filter(!SUBJECTID %in% outlier_remove$SUBJECTID) %>%
  na.omit() 
  
nrow(beh_scan_ECA_wide_WSLS2)

beh_scan_ECA_wide_WSLS2 %>%
  group_by(Effort_Choice_prior, Feedback_prior) %>%
  dplyr::summarize(mean(stay_shift))

```


## make a WSLS dataset: setbacks only, collapsed harrd & easy
need 1 row per subj
```{r}
beh_scan_ECA_wide_WSLS_FB <- beh_scan_ECA_wide_WSLS2 %>%
  group_by(SUBJECTID, Feedback_prior) %>%
    dplyr::summarize(GROUP_ECA = GROUP_ECA[1],
                     PC1_log = mean(PC1_log, na.rm = T),
                     AGE.c = AGE.c[1],
                     SEX.c = SEX.c[1], 
                Fam_inc_needs = Fam_inc_needs[1],
                IQ = IQ[1], 
         perceived_effort_ave = perceived_effort_ave[1], 
         perceived_reinforce = perceived_reinforce[1],
        Reinforce_rate = Reinforce_rate[1],
         perceived_control = perceived_control[1], 
         win_feeling = win_feeling[1],
        lose_feeling = lose_feeling[1],
         motivated = motivated[1],
        frustrated = frustrated[1],
        diff_pos_affect = diff_pos_affect[1],
        median_motor_RT_ave = median_motor_RT_ave[1],
        setback_Amyg = setback_Amyg[1],
        reward_Amyg = reward_Amyg[1],
        setback_vmPFC = setback_vmPFC[1],
        reward_vmPFC = reward_vmPFC[1], 
        total_TRs_censored = total_TRs_censored[1], 
        choice_choice_mPFC = choice_choice_mPFC[1], 
        stay_shift = mean(stay_shift, na.rm = T), 
        N_trials = mean(N_trials, na.rm = T))

beh_scan_ECA_wide_WSLS_setbacks <- beh_scan_ECA_wide_WSLS_FB %>%
  filter(Feedback_prior == "Setback")

```



## vmPFC and frustration: SIG
we know from thee specification curve analysis that's robust! 
```{r}
vmPFC_mod_frust <- lm(setback_vmPFC ~ frustrated + total_TRs_censored + 
                        AGE.c + SEX.c, 
                      data = beh_scan_ECA_wide2)

summary(vmPFC_mod_frust)
```

plot effect 
```{r}
effect_df <- data.frame(effect("frustrated", vmPFC_mod_frust), conf_int = T)

effect_plot <- ggplot(data = effect_df, aes(x = frustrated, y = fit)) + 
  geom_line(color = dark_blue) + 
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = dark_blue, alpha = 0.2) + 
  geom_jitter(data = beh_scan_ECA_wide2, color = dark_blue,
             aes(x = frustrated, y = setback_vmPFC), alpha = 0.2, width = 0.05, height = 0) + 
  theme_classic() + ylab("vmPFC response to setbacks") + 
  xlab("Self-reported frustration")

ggsave(effect_plot, file = "figures/vmPFC_frustration_behavior/vmPFC_to_setbacks_by_frustration.png", 
     height = 4, width = 6)
```

# prop hard choices

## by vmPFC to setbacks: NS 
```{r}
choices_mod_vmPFC <- lm(prop_hard_choices ~ setback_vmPFC  + total_TRs_censored +
                          N_trials + 
                          median_motor_RT_ave + 
                        AGE.c + SEX.c, 
                      data = beh_scan_ECA_wide2)

summary(choices_mod_vmPFC )
```


## by frustration: NS 
```{r}
choices_mod_vmPFC <- lm(prop_hard_choices ~ 
                          frustrated +
                          N_trials + 
                          median_motor_RT_ave + 
                        AGE.c + SEX.c, 
                      data = beh_scan_ECA_wide2)

summary(choices_mod_vmPFC )
```

# stay after hard-effort setback
##  by frustration: NS 
only age is significant! 
```{r}
persist_hard_mod_frust <- lm(stay_shift ~  frustrated + 
                          median_motor_RT_ave + N_trials +
                        AGE.c + SEX.c, 
                      data = filter(beh_scan_ECA_wide_WSLS2, Effort_Choice_prior == "Hard", 
                      Feedback_prior== "Setback"))

summary(persist_hard_mod_frust)
```




##  by vmPFC: NS 
only age is significant! 
```{r}
persist_hard_mod_vmPFC <- lm(stay_shift ~  setback_vmPFC + total_TRs_censored +
                          median_motor_RT_ave + N_trials +
                        AGE.c + SEX.c, 
                      data = filter(beh_scan_ECA_wide_WSLS2, Effort_Choice_prior == "Hard", 
                      Feedback_prior== "Setback"))

summary(persist_hard_mod_vmPFC)
```

# stay after all setbacks
## by vmPFC: TREND, or sig when control for PC1
```{r}
persist_mod_vmPFC <- lm(stay_shift ~  setback_vmPFC + total_TRs_censored +
                          median_motor_RT_ave + N_trials +
                        AGE.c + SEX.c, 
                      data = beh_scan_ECA_wide_WSLS_setbacks)

summary(persist_mod_vmPFC)
```

## vmPFC: sig when control for PC1
```{r}
persist_mod_vmPFC_PC1 <- lm(stay_shift ~  setback_vmPFC + total_TRs_censored +
                          median_motor_RT_ave + N_trials +
                          PC1_log +
                        AGE.c + SEX.c, 
                      data = beh_scan_ECA_wide_WSLS_setbacks)

summary(persist_mod_vmPFC_PC1)
```


plot effect : greater vmPFC response to setbacks predicts more persistence after setbacks
```{r}
effect_df <- data.frame(effect("setback_vmPFC", persist_mod_vmPFC))

effect_plot <- ggplot(data = effect_df, aes(x = setback_vmPFC, y = fit)) + 
  geom_line(color = dark_blue) + 
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = dark_blue, alpha = 0.2) + 
  geom_jitter(data = filter(beh_scan_ECA_wide_WSLS2, Feedback_prior == "Setback"), color = dark_blue,
             aes(x = setback_vmPFC, y = stay_shift), alpha = 0.2, width = 0.05, height = 0) + 
  theme_classic() + xlab("vmPFC response to setbacks") + 
  ylab("Prop. persistent choices after setbacks")

effect_plot
ggsave(effect_plot, file = "figures/vmPFC_frustration_behavior/Prop_stay_setbacks_by_vmPFC_to_setbacks.png", 
     height = 4, width = 6)
```


## by frustration
```{r}
persist_mod_frust <- lm(stay_shift ~  frustrated + total_TRs_censored +
                          median_motor_RT_ave + N_trials + lose_feeling + #PC1_log +
                        AGE.c + SEX.c, 
                      data = beh_scan_ECA_wide_WSLS_setbacks)

summary(persist_mod_frust)
```
