---
title: "Make onset files for effort reward"
author: "Michelle Vantieghem"
date: "Nov 26, 2019"
output:
    html_document:
        toc: yes
        toc_float:
            smooth_scroll: true
            collapsed: false
        number_sections: true
---

# NOTES 
updated: fixing some bugs, July 5, 2018 \
updating April 12, 2019: (1) combining turtles and missed choices as one confound file \
(2) making it blank if there are no confounds instead of 000 for FSL. \
updating September 2019: going back to 000 which I need for my model!! 
updating November 26, 2019 to add PA255 - was excluded at prior step before. 

```{r}
library(tidyverse)
```

# 1. get most current subject list of usable scans + behavior 
```{r}
# this was generated in the step prior
subject_list <- read.table("../5_brain_behav_inclusion/sublists/include_scan_and_beh_by_run2019-11-27.txt")
names(subject_list) <- c("SUBJECTID", "RunNumber")
nrow(subject_list) # 224 runs .
```

# 2. read files into R - only for these usable runs of usable subjects.
```{r}
# get all behavior data files
filepath <- "../../behavioral_data/3_effort_task_data/raw_scan_version/"
filelist <- list.files(filepath, pattern = "csv")

# make empty data list.
data.list <- list()  

for(i in filelist){
  file <- paste0(filepath, i)
  # GET SUBJECTID AND RUNNUM
  subjectid <- substr(i, 1, 5)
  run_num <- paste0("RUN",substr(i, 10,10))
  # only if subject in usable list...
  if (subjectid %in% subject_list$SUBJECTID){
      sub_runs_usable <- subject_list %>%
        filter(SUBJECTID == subjectid)
        # and only if this run is usable...
      if (run_num %in% sub_runs_usable$RunNumber){
         # assign data frame for each subject 
          data.file <-  tryCatch(read.csv(file, sep = ','), error=function(e) NULL)
          data.file <- data.frame(data.file)
          names(data.file)
          # add data for each subject to list of data frames 
          data.list[[i]] <- data.file
      }
  }
}
length(data.list) # 224

```

# 3. Make onset files 
For each run for each subject for each stim type, make the onset files and save them.
new directory - saving onsets in FSL_pipeline all together, instead of indiv. subj folders.
```{r}
# run a loop for each dataframe in the list
# there will be 2 dataframes for each subject (2 runs)
stim_list <- c("Choice_easy", "Choice_hard", "Choice_missed", "Feedback_easy_setback", "Feedback_hard_setback", "Feedback_easy_reward", "Feedback_hard_reward", "Feedback_too_slow", "Effort_hard", "Effort_easy")
# designate where you will save the onset files to on the server.
# note tht you are saving these into the derivatives folder, where your processed data lives

for (i in 1:length(data.list)){
  # save the dataframe 
  df <- data.list[[i]]
  SUBJECTID <- substr(names(data.list)[i], 1, 5)
  RunNumber <- paste0("run", substr(names(data.list)[i], 10, 10))
  # make a folder to save output
  output.directory <- paste0("onset_files/")
  dir.create(paste0(output.directory, SUBJECTID)) 
  dir.create(paste0(output.directory, SUBJECTID, "/", RunNumber))
  print(paste0("making onsets for ", SUBJECTID))
  
  # clean up file
  df2 <- df %>%
    # rename these to reflect feedback
      rename(Feedback_Phase_Onset = Reward_Phase_Onset, 
             Feedback_Phase_Offset = Reward_Phase_Offset) %>%
    # mark certain stim types in the dataframe
      mutate(Choice_easy = ifelse(Effort_Choice == "Easy",1,0),
             Choice_hard = ifelse(Effort_Choice == "Hard", 1, 0),
             Choice_missed = ifelse(Effort_Choice == "Miss", 1, 0),
             Effort_easy = ifelse(Effort_Choice == "Easy", 1, 0),
             Effort_hard = ifelse(Effort_Choice == "Hard", 1, 0),
             Feedback_easy_reward = ifelse(Accuracy == 1 & Reward_received == 1 & Effort_Choice == "Easy", 1,0),
             Feedback_easy_setback = ifelse(Accuracy == 1 & Reward_received == 0 & Effort_Choice == "Easy", 1,0),
             Feedback_hard_reward = ifelse(Accuracy == 1 &  Reward_received == 1 & Effort_Choice == "Hard", 1,0),
             Feedback_hard_setback = ifelse(Accuracy == 1 &  Reward_received == 0 & Effort_Choice == "Hard", 1,0),
             Feedback_too_slow = ifelse(Accuracy == 0, 1, 0))
    
    # generate onset lists...
    for (stim_type in stim_list){
      
      # get onsets and offsets names 
      phase <- strsplit(stim_type, "_")[[1]][1]
      stim_type_onset <- paste0(phase, "_Phase_Onset")
      stim_type_offset <- paste0(phase, "_Phase_Offset")
      
      # create a marker in the dataframe that represents when this stim type happened.
      df2$df_stim <- df2[grepl(stim_type, names(df2))]
      trial_numbers <- sum(df2$df_stim, na.rm = T)
      
      # if they have trials of this condition... make onsets! 
      if (trial_numbers > 0){
      onsets <- df2  %>%
        filter(df_stim == 1) %>%
        select(stim_type_onset)
      offsets <- df2 %>%
        filter(df_stim == 1) %>%
        select(stim_type_offset)
      # calculate trial duration
      duration <- offsets - onsets 
      # make 3 column format
      onset_file <- cbind(onsets, rep(duration, length(onsets)), rep(1, length(onsets)))
      # remove NAs
      onset_file2 <- onset_file %>% 
        filter(!is.na(onsets))
        
      }else{
        # if there are no onsets for this condition, make it 3 zeros.
        onset_file2 <-cbind(0,0,0)
      }
      write.table(onset_file2, paste0(output.directory, SUBJECTID, "/", RunNumber, "/", stim_type, ".txt"), col.names = FALSE, row.names =  FALSE, quote = FALSE)
  }
}

```

# combine certain sets of stim files

## first make a function that returns NAs for blank text files when you read them in. (instead of crashing)
```{r}
#
deal_with_blank_files <- function(f){
   # try to read the file 
   data <- try(read.table(f, header = F))
   # if there is an error, return NAs instead.
         if (inherits(data, "try-error")) {
         #  print ("ERROR")
           # return 3 NAs for each column of onset file.
           data <- c(NA,NA,NA)
           print ("error")
           # otherwise, return the data! 
           # otherwise, return the data! 
          } else { print ("empty!")
          }
  return(data)
}
```

```{r}

# now run loop for all subjects ! 
for (sub in subject_list$SUBJECTID){
  print(sub)
  output.directory <- paste0("onset_files/", sub, "/")
  sub_df <- subject_list %>%
    filter(SUBJECTID == sub)
  for (RunNumber in sub_df$RunNumber){
   # print(RunNumber)
      ## MISSES
      missed_choices <- deal_with_blank_files(paste0(output.directory, RunNumber, "/Choice_missed.txt"))
      too_slow <- deal_with_blank_files(paste0(output.directory, RunNumber, "/Feedback_too_slow.txt"))
     
     missed_trials <- na.omit(rbind(too_slow, missed_choices))
    # reorder these to make sure in time order! 
      if (sum(missed_trials$V3) != 0){
          missed_trials2 <- missed_trials %>% arrange(V1)  %>%
            filter(! V3 == 0)
      } else {
        missed_trials2 <- cbind(0,0,0)
      }
      write.table(missed_trials2, paste0(output.directory, RunNumber, "/missed_trials.txt"), col.names = FALSE, row.names =  FALSE, quote = FALSE)
  
      
      ## ALL CHOICES 
      hard <- deal_with_blank_files(paste0(output.directory, RunNumber, "/Choice_hard.txt"))
      easy <- deal_with_blank_files(paste0(output.directory, RunNumber, "/Choice_easy.txt"))
      choice_trials <- na.omit(rbind(hard, easy))
      if (sum(choice_trials$V3) != 0){
          choice_trials2 <- choice_trials %>% arrange(V1)  %>%
            filter(! V3 == 0)
      } else {
        choice_trials2 <- cbind(0,0,0)
      }
      write.table(choice_trials2, paste0(output.directory, RunNumber, "/Choice_trials.txt"), col.names = FALSE, row.names =  FALSE, quote = FALSE)

      
      ## ALL FEEDBACKmissed_choices <- deal_with_blank_files(paste0(output.directory, RunNumber, "/Choice_missed.txt"))
      hard_setback <- deal_with_blank_files(paste0(output.directory, RunNumber, "/Feedback_hard_setback.txt"))
      hard_reward <- deal_with_blank_files(paste0(output.directory, RunNumber, "/Feedback_hard_reward.txt"))
      easy_setback <- deal_with_blank_files(paste0(output.directory, RunNumber, "/Feedback_easy_setback.txt"))
      easy_reward <- deal_with_blank_files(paste0(output.directory, RunNumber, "/Feedback_easy_reward.txt"))

      # lots of combos to make here. 
      feedback_hard <- na.omit(rbind(hard_setback, hard_reward))
            if (sum(feedback_hard$V3) !=0) {
          feedback_hard2 <- feedback_hard %>% arrange(V1) %>%
            filter(! V3 == 0)
      } else {
        feedback_hard2 <- cbind(0,0,0)
      }
      write.table(feedback_hard2, paste0(output.directory, RunNumber, "/feedback_hard.txt"), col.names = FALSE, row.names =  FALSE, quote = FALSE)

      feedback_easy <- na.omit(rbind(easy_setback, easy_reward))
      if (sum(feedback_easy$V3) !=0) {
          feedback_easy2 <- feedback_easy %>% arrange(V1)  %>%
            filter(! V3 == 0)
      } else {
        feedback_easy2 <- cbind(0,0,0)
      }
     write.table(feedback_easy2, paste0(output.directory, RunNumber, "/feedback_easy.txt"), col.names = FALSE, row.names =  FALSE, quote = FALSE)

      feedback_reward <- na.omit(rbind(hard_reward, easy_reward))
      if (sum(feedback_reward$V3) !=0) {
          feedback_reward2 <- feedback_reward %>% arrange(V1) %>%
            filter(! V3 == 0)
      } else {
        feedback_reward2 <- cbind(0,0,0)
      }
      write.table(feedback_reward2, paste0(output.directory, RunNumber, "/feedback_reward.txt"), col.names = FALSE, row.names =  FALSE, quote = FALSE)
      
      feedback_setback <- na.omit(rbind(hard_setback, easy_setback))
      if(sum(feedback_setback$V3) !=0) {
          feedback_setback2 <- feedback_setback %>% arrange(V1) %>%
            filter(! V3 == 0)
      } else {
        feedback_setback2 <- cbind(0,0,0)
      }
      write.table(feedback_setback2, paste0(output.directory, RunNumber, "/feedback_setback.txt"), col.names = FALSE, row.names =  FALSE, quote = FALSE)

      feedback_trials <- na.omit(rbind(hard_setback, hard_reward, easy_setback, easy_reward))
      if (sum(feedback_trials$V3) != 0) {
          feedback_trials2 <- feedback_trials %>% arrange(V1) %>%
            filter(! V3 == 0)
      } else {
        feedback_trials2 <- cbind(0,0,0)
      }
      write.table(feedback_trials2, paste0(output.directory, RunNumber, "/feedback_trials.txt"), col.names = FALSE, row.names =  FALSE, quote = FALSE)
      # reorder these to make sure in time order! 
 
  }
}
```

