---
title: "level 1 template"
author: "Michelle Vantieghem"
date: "Oct 4, 2019 "
output:
    html_document:
        toc: yes
        toc_float:
            smooth_scroll: true
            collapsed: false
        df_print: paged
        number_sections: false
---
updated October 3 to create a single level1 model that can be used for all possibel contrasts
with preprocessing included, so motion regression correction will be carried out 
blank onsets were changes to 000 so warning: some contrasts will be zeros in some subjecst.

# Make your level1 fsf template in the FEAT GUI 
### Script is saved in template_lev1_fsf 
### This script will run preprocessing and level1 statistics on each run

# Lower-level analysis 
## Data
#### inputs should be your bold files 
#### check number of TRs is correct, and length of TR is correct 
#### choose output directory to save lev1_run.feat 

## Pre-stats
#### No alternative ref image 
#### Motion correction: mcflirt
#### B0 unwarping -- YES
fieldmap = PAXXX_fieldmap_rads \
fieldmap mag = PAxxx_fieldmap_mag_brain \
effective EPI echo spacing = 0.52 ms \
EPI TE = 30 ms \
unwarp direction = y \
% signal loss threshold = 10 \
#### Slice timing: none
#### BET brain extraction -yes 
#### Spatial smoothing FWHM 6 
#### Intensity normalization - no
#### Highpass filter- yes

## Registration
#### Main structural image with normal search BBR
#### standard space with normal search 12 DOF, non-linear, warp resolution 10 (default)

## Stats 
#### yes - use FILM prewhitening 
#### Standard + Extended motion 
#### include additional confound EVs - confound.txt file 

### Full Model Setup
#### EVlist:
```{r}
# create key for numbered EVs
EV_list <- c("HardChoice", "EasyChoice", "HardEffort", "EasyEffort", "HardReward", "HardSetback", "EasyReward", "EasySetback", "Missed") # all possible EVs
EV_number <- c(1:9)
EV_key <- data.frame(EV_list, EV_number)
EV_key
```


#### copes
```{r}

# get list of contrasts
cope_list <-  c("HardChoice", "EasyChoice", "HardEffort", "EasyEffort", "HardReward", "HardSetback", "EasyReward", "EasySetback", "Missed", # the 9 EVs alone
               "allChoices", "Hard-EasyChoice", "allEffort", "Hard-EasyEffort", # choice and effort contrasts
               "allFB",  "RewardFB", "SetbackFB", "Reward-SetbackFB", "HardFB", "EasyFB", "Hard-EasyFB", # FB main effects of reward/setback and easy/hard
               "HardReward-HardSetback", "EasyReward-EasySetback", "HardReward-EasyReward", "HardSetback-EasySetback") # FB interaction of reward/setback x easy/hard
cope_number <- c(1:length(cope_list))
cope_key <- data.frame(cope_list, cope_number)

cope_key
```

#### cope matrix 
```{r}
cope_mat2 <- data.frame("HardChoice" = c(1, 0, 0, 0, 0, 0, 0, 0, 0), 
                        "EasyChoice"= c(0, 1, 0, 0, 0, 0, 0, 0, 0),
                        "HardEffort"= c(0, 0, 1, 0, 0, 0, 0, 0, 0),
                        "EasyEffort"= c(0, 0, 0, 1, 0, 0, 0, 0, 0), 
                        "HardReward"= c(0, 0, 0, 0, 1, 0, 0, 0, 0), 
                        "HardSetback"= c(0, 0, 0, 0, 0, 1, 0, 0, 0),
                        "EasyReward"= c(0, 0, 0, 0, 0, 0, 1, 0, 0),
                        "EasySetback"= c(0, 0, 0, 0, 0, 0, 0, 1, 0), 
                        "Missed"= c(0, 0, 0, 0, 0, 0, 0, 0, 1), # the 9 EVs alone
                       "allChoices"= c(1, 1, 0, 0, 0, 0, 0, 0, 0),
                        "Hard-EasyChoice"= c(1, -1, 0, 0, 0, 0, 0, 0, 0),
                       "allEffort"= c(0, 0, 1, 1, 0, 0, 0, 0, 0),
                       "Hard-EasyEffort"= c(0, 0, 1, -1, 0, 0, 0, 0, 0), # choice and effort contrasts
                       "allFB"= c(0, 0, 0, 0, 1, 1, 1, 1, 0), 
                       "RewardFB"= c(0, 0, 0, 0, 1, 0, 1, 0, 0), 
                       "SetbackFB"= c(0, 0, 0, 0, 0, 1, 0, 1, 0),
                       "Reward-SetbackFB"= c(0, 0, 0, 0, 1, -1, 1, -1, 0), 
                       "HardFB"= c(0, 0, 0, 0, 1, 1,  0, 0, 0),
                       "EasyFB"= c(0, 0, 0, 0, 0, 0, 1, 1, 0), 
                       "Hard-EasyFB"= c(0, 0, 0, 0, 1, 1, -1, -1, 0), # FB main effects of reward/setback and easy/hard
                       "HardReward-HardSetback"= c(0, 0, 0, 0, 1, -1, 0, 0, 0), 
                       "EasyReward-EasySetback"= c(0, 0, 0, 0, 0, 0, 1, -1, 0),
                       "HardReward-EasyReward"= c(0, 0, 0, 0, 1, 0, -1, 0, 0),
                       "HardSetback-EasySetback"= c(0, 0, 0, 0, 0, 1, 0, -1, 0)) # FB interaction of reward/setback x easy/hard

final_cope_mat <- t(cope_mat2)
final_cope_mat
write.table(final_cope_mat, file = "level1_cope_matrix.txt", row.names = F, col.names = F)
```

# Post-stats 
### none (no thresholding needed for single subject, single run data)
