---
title: "checking_proc_lists"
author: "Michelle.VanTieghem"
date: "6/11/2019"
output: html_document
---

# Notes
check that all subjects successfully ran through level1 processing
there are 2 separate level1 models: collapsed EVs and all EVS


# 1. get included list of runs/subjects
```{r}
include <- read.table("../../Sublists/level1_sublists/sublist_include_scan_and_beh_for_level1_2019-04-30.txt", header = T)
head(include)
```


# 2. get list of successfully processed runs with collapsed EV level1 model.
```{r}
library(tidyverse)
processed <- read.table("../../Sublists/level1_sublists/sublist_lev1_collapsed_EVs.txt") %>%
  mutate(SUBJECTID = substr(V1, 1, 5),
         RunNumber = substr(V1, 25, 28)) %>%
  rename(proc_done = V1)
```

## merge 
```{r}

compare <- merge(include, processed, by = c("SUBJECTID", "RunNumber"))
head(compare)
```

## are any runs missing from the list? no!
(indicating that their processing failed)
```{r}

sum(is.na(compare$proc_done))

```

# 3. get list of successfully processed all EV model
```{r}
library(tidyverse)
processed2 <- read.table("../../Sublists/level1_sublists/sublist_lev1_all_EVs.txt") %>%
  mutate(SUBJECTID = substr(V1, 1, 5),
         RunNumber = substr(V1, 25, 28)) %>%
  rename(proc_done = V1)
head(processed2)
```

## merge 
```{r}

compare2 <- merge(include, processed2, by = c("SUBJECTID", "RunNumber"))
head(compare2)
```

## are any runs missing from the list? no!
(indicating that their processing failed)
```{r}

sum(is.na(compare2$proc_done))

```

