---
title: "specification curves for vmPFC response to reward-setbacks "
author: "Michelle.VanTieghem"
date: "1/5/2020"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# notes: 
code for specification curves from Dani Cosme
https://github.com/dcosme/specification-curves/blob/master/SCA_tutorial.Rmd
```{r, include = F, warnings = F, echo=FALSE, message = F}
source("../../../../0_R_analysis_setup_file.R")
```

# load data
```{r}
# load all data with PCA added!
load("../data/all_pacct_effort_data_with_PCA.rda")
```

## clean data
```{r} 
FB_level_order <- c("vmPFC", "mPFC", "VS", "Amyg")

# get just reward ROIs
reward_df <- beh_scan_ECA_wide %>%
  rename(Amyg = reward_Amyg,
         mPFC = reward_FB_mPFC, 
         vmPFC = reward_vmPFC, 
         VS = reward_VS) %>%
  select(-starts_with("choice"), -starts_with("setback"), 
         -starts_with("feedback"), -starts_with("reward_setback")) %>%
  gather(key = "ROI", value = "reward_beta",  vmPFC, mPFC, VS, Amyg) %>%
  filter(!is.na(reward_beta))

# check right number of subjects! 
length(unique(reward_df$SUBJECTID))

# get just setback ROIs
setback_df <- beh_scan_ECA_wide %>%
   rename(Amyg = setback_Amyg, 
          vmPFC = setback_vmPFC, 
         mPFC = setback_FB_mPFC, 
         VS = setback_VS) %>%
  select(-starts_with("choice"), -starts_with("reward"), 
         -starts_with("feedback"), -starts_with("reward_setback")) %>%
  gather(key = "ROI", value = "setback_beta",  vmPFC, mPFC, VS,  Amyg) %>%
  select(SUBJECTID, ROI, setback_beta) %>%
  filter(!is.na(setback_beta))

# combine them in long format
FB_df <- merge(reward_df, setback_df, by = c("SUBJECTID", "ROI")) %>%
  mutate(reward_minus_setback = reward_beta - setback_beta,
        ROI = factor(ROI, levels = FB_level_order),
         AGE.c = AGE.x - mean(AGE.x, na.rm = T),
         SEX.c = SEX.x - mean(SEX.x, na.rm = T), 
         IQ.c = IQ- mean(IQ, na.rm = T),
         total_TRs_censored.c = total_TRs_censored - mean(total_TRs_censored, na.rm = T),
         Reinforce_rate.c = Reinforce_rate - mean(Reinforce_rate, na.rm = T), 
         GROUP_ECA.c = ifelse(GROUP_ECA == "COMP", -1, 1), 
        PC1_log.c = PC1_log -mean(PC1_log)) %>%
  gather(key = "contrast", value = "beta", reward_beta, setback_beta, reward_minus_setback) %>%
  filter(!is.na(beta))

# rename levels of contrast factor
FB_df$contrast <- as.factor(ifelse(FB_df$contrast == "reward_beta", "reward", ifelse(FB_df$contrast == "setback_beta", "setback", FB_df$contrast)))
FB_df$diff_pos_affect <- FB_df$win_feeling - FB_df$lose_feeling

```

## remove outliers
calculated already.
```{r}
load(file = "../tables/Feedback_betas_outlier_subjects.Rdata")
setback_outliers <- FB_outlier_subjects %>% 
  filter(ROI == "vmPFC" & contrast == "reward_minus_setback")

FB_df2 <- FB_df %>%
  mutate(beta = ifelse(SUBJECTID %in% setback_outliers$SUBJECTID , NA, beta))
nrow(FB_df2)
```  

## filter only setback data 
```{r}
FB_df3 <- FB_df2 %>%
  filter(contrast == "reward_minus_setback" & ROI == "vmPFC")  %>% 
  select(beta, PC1_log.c, AGE.c, SEX.c, IQ.c, Fam_inc_needs.c, 
         total_TRs_censored.c, Reinforce_rate.c, 
         frustrated, perceived_control, motivated, perceived_effort_ave, 
         perceived_reinforce, diff_pos_affect)
nrow(FB_df3)

# omit NAs
FB_df4 = FB_df3 %>% 
  na.omit()
nrow(FB_df4)
```

# using code from Dani Cosme for sensitivity analysis 

```{r}
library(purrr)
library(cowplot)
```

## check full model run normally 
```{r}
full_test <- lm(beta ~  PC1_log.c + AGE.c  + SEX.c + IQ.c + Fam_inc_needs.c + 
                       total_TRs_censored.c +  Reinforce_rate.c  + 
                      frustrated + perceived_control +  motivated +  
                      perceived_effort_ave + perceived_reinforce + diff_pos_affect,
                 data = FB_df4)
summary(full_test)
```

## run all nested models using `dredge` from `MuMIn`
* max number of predictors = 30
```{r dredge}
# set na.action for dredge
options(na.action = "na.fail")

# run full model
full.model = full_test
# run all possible nested models
all.models = MuMIn::dredge(full.model, rank = "AIC", extra = "BIC")
```


##  PC1 

  extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "PC1_log.c") %>%
  ungroup() %>%
  select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/specification_curves/vmPFC_FB_diff_by_PC1.png", height = 8, width  = 20)
```


##  motivation  

  extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "motivated") %>%
  ungroup() %>%
  select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/specification_curves/vmPFC_FB_diff_by_motivation.png", height = 8, width  = 20)

```


## perceived effort

  extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "perceived_effort_ave") %>%
  ungroup() %>%
  select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/specification_curves/vmPFC_FB_diff_by_perceived_effort.png", height = 8, width  = 20)

```


## perceived reinforce 

extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "perceived_reinforce") %>%
  ungroup() %>%
  select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/specification_curves/vmPFC_FB_diff_by_perceived_reinforce.png", height = 8, width  = 20)

```


## frustration
extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "frustrated") %>%
  ungroup() %>%
  select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/specification_curves/vmPFC_FB_diff_by_frustration.png", height = 8, width  = 20)

```


## perceived control 

extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "perceived_control") %>%
  ungroup() %>%
  select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/specification_curves/vmPFC_FB_diff_by_perceived_control.png", height = 8, width  = 20)

```


## diff positive affect

  extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "diff_pos_affect") %>%
  ungroup() %>%
  select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/specification_curves/vmPFC_FB_diff_by_diff_pos_affect.png", height = 8, width  = 20)

```


## AGE 
  extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "AGE.c") %>%
  ungroup() %>%
  select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/specification_curves/vmPFC_FB_diff_by_AGE.png", height = 8, width  = 20)

```


##  motion confound 

  extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "total_TRs_censored.c") %>%
  ungroup() %>%
  select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/specification_curves/vmPFC_FB_diff_by_motion.png", height = 8, width  = 20)

```


## Family income to needs

extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "Fam_inc_needs.c") %>%
  ungroup() %>%
  select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/specification_curves/vmPFC_FB_diff_by_Fam_inc_needs.png", height = 8, width  = 20)

```

##  IQ 

extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "IQ.c") %>%
  ungroup() %>%
  select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/specification_curves/vmPFC_FB_diff_by_IQ.png", height = 8, width  = 20)

```


##  Actual reinforcement rate 

extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "Reinforce_rate.c") %>%
  ungroup() %>%
  select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "coefficient for actual reinforcement rate \n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/specification_curves/vmPFC_FB_diff_by_actual_reinforcement.png", height = 8, width  = 20)

```