---
title: "Demographics & data checks for COMP paper"
author: "Michelle.VanTieghem"
date: "November 27, 2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    df_print: paged
    toc_float:
      collapsed: no
      smooth_scroll: yes
---


# Load data 
## only behavior
from data_cleaning_for_analysis 
```{r,  warnings = F, message = F}
source("../../0_R_analysis_setup_file.R")

# wide version, by subject.
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_subj.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_subj_WSLS.Rdata")


# long version, by trial 
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_long.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_long_WSLS.Rdata")
```

## with scanning data 
from data_cleaning_for_analysis 
```{r}
# wide version, by subject.
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_wide.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_wide_WSLS.Rdata")

# long version, by trial 
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_long.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_long_WSLS.Rdata")

```

# DEMOGRAPHICS 

## demo table for  behavior sample
```{r}
# confirm no one has WASI < 70
#beh_comp_subj %>% filter(IQ < 70)

comp_beh_demo_table <- beh_comp_subj %>%
  summarize (N = n(), 
             mean_age = round(mean(AGE, na.rm = T), 2),
             sd_age = round(sd(AGE, na.rm = T), 2),
             min_age = round(min(AGE, na.rm =T), 2),
             max_age= round(max(AGE, na.rm = T),2),
             N_female = sum(SEX, na.rm = T),
             N_male = n() - sum(SEX, na.rm = T), 
             mean_IQ = round(mean(IQ, na.rm = T),2),
             sd_IQ = round(sd(IQ, na.rm = T),2), 
             mean_fam_inc_needs = round(mean(Fam_inc_needs, na.rm = T), 2),
             sd_fam_inc_needs = round(sd(Fam_inc_needs, na.rm = T),2),
             perc_below_poverty = sum(ifelse(Fam_inc_needs < 1, 1, 0), na.rm = T)/n())

```

## demo table for scan sample
```{r}
comp_scan_demo_table <- beh_scan_comp_wide %>%
  summarize (N = n(), 
             mean_age = round(mean(AGE, na.rm = T), 2),
             sd_age = round(sd(AGE, na.rm = T), 2),
             min_age = round(min(AGE, na.rm =T), 2),
             max_age= round(max(AGE, na.rm = T),2),
             N_female = sum(SEX, na.rm = T),
             N_male = n() - sum(SEX, na.rm = T), 
             mean_IQ = round(mean(IQ, na.rm = T),2), 
             sd_IQ = round(sd(IQ, na.rm = T),2),
             mean_fam_inc_needs = round(mean(Fam_inc_needs, na.rm = T), 2),
             sd_fam_inc_needs = round(sd(Fam_inc_needs, na.rm = T),2), 
             perc_below_poverty = round(sum(ifelse(Fam_inc_needs < 1, 1, 0), na.rm = T)/n()))
```

## combined demo table 
```{r}
# combine them! 
demo_table_pretty <- data.frame(t(rbind(comp_beh_demo_table, comp_scan_demo_table)))
names(demo_table_pretty) <- c("Behavior", "Scanning")
demo_table_pretty

save(demo_table_pretty, file= "tables/1_demographics_descriptives/Demo_comp_behavior_and_scan.Rdata")
demo_table_wide <-data.frame(t(demo_table_pretty))
write.csv(demo_table_wide, file = "tables/1_demographics_descriptives/demo_table_pretty_wide_for_poster.csv")

```

## should I test whether demographics differ in scan sample vs. full sample?

## plot age
```{r}
age_hist <- ggplot(data = beh_comp_subj, aes(x = AGE)) + 
  geom_histogram(bins = 10, fill = dark_blue, alpha = 0.5) + theme_classic() 
age_hist

ggsave(age_hist,file = "figures/1_demographics_descriptives/comp_age_histogram.pdf", width = 3, height= 4)

```

## plot SES
income to needs = total household income / poverty threshold for 2018
living below poverty threshold if < 1 
```{r}
FIN_hist <- ggplot(data = beh_comp_subj, aes(x = Fam_inc_needs)) + 
  geom_histogram(bins = 10, fill = dark_blue, alpha = 0.5) + theme_classic() +
  geom_vline(xintercept = 1, linetype = "dashed") + xlab ("Family Income to Needs Ratio")

FIN_hist
ggsave(FIN_hist,file = "figures/1_demographics_descriptives/comp_fam_inc_needs_histogram.pdf", width = 3, height= 4)

```


## Age checks: differnces in # trials? yes!
age is correlated with number of trials
```{r}

cor.test(beh_comp_subj$AGE, beh_comp_subj$N_trials)
ggplot(data = beh_comp_subj, aes(x = AGE, y = N_trials)) + 
  geom_jitter(alpha = 0.5) + geom_smooth()  + theme_classic () 

```


# Descriptive Statistics
## post-scan questions
```{r}
#names(beh_comp_subj)
mean_table <- beh_comp_subj %>% 
  summarize(perceived_reinforce = mean(as.numeric(as.character(perceived_reinforce)), na.rm = T), 
            perceived_control= mean(as.numeric(as.character(perceived_control)), na.rm = T), 
            perceived_effort_hard = mean(as.numeric(as.character(hard_effort_perceived)), na.rm = T), 
            perceived_effort_easy = mean(as.numeric(as.character(easy_effort_perceived)), na.rm = T), 
            fun = mean(as.numeric(as.character(fun)), na.rm = T), 
            motivated = mean(as.numeric(as.character(motivated)), na.rm = T), 
            frustrated = mean(as.numeric(as.character(frustrated)), na.rm = T), 
            sleepy = mean(as.numeric(as.character(sleepy)), na.rm = T), 
            win_feeling = mean(as.numeric(as.character(win_feeling)), na.rm = T), 
            lose_feeling = mean(as.numeric(as.character(lose_feeling)), na.rm = T))
mean_table <- data.frame(t(mean_table))
names(mean_table) <- "mean"

sd_table <- beh_comp_subj %>% 
  summarize(perceived_reinforce = sd(as.numeric(as.character(perceived_reinforce)), na.rm = T), 
            perceived_control= sd(as.numeric(as.character(perceived_control)), na.rm = T), 
            perceived_effort_hard = sd(as.numeric(as.character(hard_effort_perceived)), na.rm = T), 
            perceived_effort_easy = sd(as.numeric(as.character(easy_effort_perceived)), na.rm = T), 
            fun = sd(as.numeric(as.character(fun)), na.rm = T), 
            motivated = sd(as.numeric(as.character(motivated)), na.rm = T), 
            frustrated = sd(as.numeric(as.character(frustrated)), na.rm = T), 
            sleepy = sd(as.numeric(as.character(sleepy)), na.rm = T), 
            win_feeling = sd(as.numeric(as.character(win_feeling)), na.rm = T), 
            lose_feeling = sd(as.numeric(as.character(lose_feeling)), na.rm = T))
sd_table <- data.frame(t(sd_table))
names(sd_table) <- "sd"
sd_table$variable <- rownames(sd_table) 

post_test_table <- cbind(mean_table, sd_table) %>%
  select(variable, mean, sd)
post_test_table

save(post_test_table, file = "tables/1_demographics_descriptives/post_test_self_report_descriptives.Rdata")
```

## histograms of self-report data

### perceived control
```{r}
df <- beh_comp_subj %>%
  filter(!is.na(perceived_control)) %>%
group_by(perceived_control) %>%
  summarize(counts = n())

pc_plot <- ggplot(df, aes(x = factor(perceived_control), y = counts)) + 
    scale_x_discrete(labels = c("1" = "None", "2" = "Some", "3" = "Alot")) +
  geom_bar(stat = "identity", fill = dark_blue, alpha = 0.3) + theme_classic() +
  xlab ("Perceived Control")

pc_plot
ggsave(pc_plot, file = "figures/1_demographics_descriptives/comp_perceived_control_histogram.pdf", width = 2.5, height= 4)

```

### reinforcement rate... 
```{r}
df <- beh_comp_subj %>%
  filter(!is.na(perceived_reinforce)) %>%
group_by(perceived_reinforce) %>%
  summarize(counts = n())

pc_plot <- ggplot(df, aes(x = factor(perceived_reinforce), y = counts)) + 
    scale_x_discrete(labels = c("1" = "Less than half", "2" = "Half the time", "3" = "More than half")) +
  geom_bar(stat = "identity", fill = dark_blue, alpha = 0.3) + theme_classic() +
  xlab ("Perceived Reinforcement")

pc_plot
ggsave(pc_plot, file = "figures/1_demographics_descriptives/comp_perceived_reinforcement_histogram.pdf", width = 3, height= 4)
```


### motivation  
```{r}
df <- beh_comp_subj %>%
  filter(!is.na(motivated)) %>%
group_by(motivated) %>%
  summarize(counts = n())

pc_plot <- ggplot(df, aes(x = factor(motivated), y = counts)) + 
  geom_bar(stat = "identity", fill = dark_blue, alpha = 0.3) + theme_classic() +
  xlab ("Motivation")

pc_plot
ggsave(pc_plot, file = "figures/1_demographics_descriptives/comp_motivated_hist.pdf", width = 3, height= 4)

```


### frustrated  
```{r}
df <- beh_comp_subj %>%
  filter(!is.na(frustrated)) %>%
group_by(frustrated) %>%
  summarize(counts = n())

pc_plot <- ggplot(df, aes(x = factor(frustrated), y = counts)) + 
  geom_bar(stat = "identity", fill = dark_blue, alpha = 0.3) + theme_classic() +
  xlab ("frustrated")

pc_plot
ggsave(pc_plot, file = "figures/1_demographics_descriptives/comp_frustrated_hist.pdf", width = 3, height= 4)
```


### win feeling (positive affect)
```{r}
df <- beh_comp_subj %>%
  filter(!is.na(win_feeling)) %>%
group_by(win_feeling) %>%
  summarize(counts = n())

pc_plot <- ggplot(df, aes(x = factor(win_feeling), y = counts)) + 
  geom_bar(stat = "identity", fill = dark_blue, alpha = 0.3) + theme_classic() +
  xlab (" Win Feeling (positive affect)")

pc_plot
ggsave(pc_plot, file = "figures/1_demographics_descriptives/comp_win_feeling_hist.pdf", width = 3, height= 4)
```


### lose feeling (positive affect)
```{r}
df <- beh_comp_subj %>%
  filter(!is.na(lose_feeling)) %>%
group_by(lose_feeling) %>%
  summarize(counts = n())

pc_plot <- ggplot(df, aes(x = factor(lose_feeling), y = counts)) + 
  geom_bar(stat = "identity", fill = dark_blue, alpha = 0.3) + theme_classic() +
  xlab ("Lose feeling (negative affect)")

pc_plot
ggsave(pc_plot, file = "figures/1_demographics_descriptives/comp_lose_feeling_hist.pdf", width = 3, height= 4)
```


## correlations of self-report data

### perceived vs. actual reinforcement 
```{r}
# perceived reinforcement is correlated with actual reinforcement.
reinforce_vars <- beh_comp_subj %>%
  select(AGE, IQ, Reinforce_rate,  perceived_reinforce) 

cor_table <- correlation(reinforce_vars)
cor_table_reinforce <- summary(cor_table)
cor_table_reinforce
save(cor_table_reinforce, file = "tables/1_demographics_descriptives/corr_table_perceived_vs_actual_reinforcement.Rdata")

reinforce_plot <- ggplot(data = beh_comp_subj, aes(x = Reinforce_rate, y = perceived_reinforce)) + 
  geom_point(color = dark_blue, alpha = 0.3) + geom_smooth( method = "lm", color = dark_blue, fill = dark_blue) + 
  theme_classic() + ylab(" Perceived Reinforcement Rate") + xlab ("Actual Reinforcement Rate")

reinforce_plot
ggsave(reinforce_plot, file = "figures/1_demographics_descriptives/corr_reinforce_plot.pdf", width = 4, height = 4)
```

### motivation correlated with perceived control 
```{r}
control <- beh_comp_subj %>%
  filter(perceived_control <= 3) %>%
  select(AGE, IQ, perceived_control, perceived_reinforce, frustrated, motivated, 
         win_feeling, lose_feeling)
cor_table <- correlation(control)
cor_table_control <- summary(cor_table)
cor_table_control
save(cor_table_control, file = "tables/1_demographics_descriptives/corr_table_motivation_perceived_control.Rdata")

# this should actually be a bar graph!! 
beh_comp_subj <- beh_comp_subj %>%
  mutate(perceived_control.f = as.factor(ifelse(perceived_control >= 3, "3", 
                                      ifelse(perceived_control == 2, "2", "1"))))
anova_percieved <- lm(motivated ~ perceived_control.f, data = subset(beh_comp_subj, !is.na(perceived_control.f)))

effect_df <- data.frame(effect("perceived_control.f", anova_percieved))
order <- c("1", "2", "3", "")
levels(effect_df$perceived_control.f) <- order
summary(effect_df$perceived_control.f)

levels(beh_comp_subj$perceived_control.f) <- order
summary(beh_comp_subj$perceived_control.f)
control_plot <- ggplot(data = effect_df,
                       aes(x = perceived_control.f, y = fit)) + 
  geom_bar(stat = "identity", fill= dark_blue, alpha = 0.3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.5, color = dark_blue) +
  geom_jitter(data = beh_comp_subj, aes(x = perceived_control.f, y = motivated), 
              width = 0.1, height = 0.0, color = dark_blue, alpha = 0.3) + 
  theme_classic() + ylab("Self-reported motivation") + xlab ("Perceived Control")

control_plot
ggsave(control_plot, file = "figures/1_demographics_descriptives/corr_perceived_control_motivation.pdf", width = 2.5, height = 4)
```

### age isn't correlated with perceived effort, but is correlated with motor skills.
```{r}
effort_vars <- beh_comp_subj %>%
  select(AGE, IQ, motor_skills_easy, motor_skills_hard, hard_effort_perceived, easy_effort_perceived) %>%
  mutate(motor_skills_ave = (motor_skills_hard + motor_skills_easy)/2, 
        perceived_effort_ave = (hard_effort_perceived +easy_effort_perceived)/2)

cor_table <- correlation(effort_vars)
cor_table_motor <- summary(cor_table)
cor_table_motor
save(cor_table_motor, file = "tables/1_demographics_descriptives/corr_table_motor_age_perceived_effort.Rdata")


motor_plot <- ggplot(data = beh_comp_subj, aes(x = AGE, y = motor_skills_hard)) + 
  geom_point(color = dark_blue, alpha = 0.3) + geom_smooth( method = "lm", color = dark_blue, fill = dark_blue) + 
  theme_classic() + ylab("Motor skills for hard task") + xlab ("Age (years)")

motor_plot
ggsave(motor_plot, file = "figures/1_demographics_descriptives/corr_motor_age_plot.pdf", width = 4, height = 4)
```

### perceived effort correlated with motor skills 
```{r}

motor_plot <- ggplot(data = beh_comp_subj, aes( y = motor_skills_hard, hard_effort_perceived)) + 
  geom_jitter(color = dark_blue, alpha = 0.3, width = 0.1, height  = 0.1) +
  geom_smooth( method = "lm", color = dark_blue, fill = dark_blue) + 
  theme_classic() + xlab("Motor skills for hard task") + ylab ("Perceived effort on hard task")

motor_plot
ggsave(motor_plot, file = "figures/1_demographics_descriptives/corr_motor_perceived_effort_plot.pdf", width = 4, height = 4)
```

