---
title: "Manipulation checks for effort task"
author: "Michelle.VanTieghem"
date: "6/7/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

# Load data
## only behavior
from data_cleaning_for_analysis 
```{r data, message = F, warning = F}
source("../../0_R_analysis_setup_file.R", echo=F)

# wide version, by subject.
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_subj.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_subj_WSLS.Rdata")


# long version, by trial 
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_long.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_long_WSLS.Rdata")

```


# Effort Manipulation checks

## Effort RT: button-pressing between conditions? (hard vs. easy)

first check RT data, and calculate means by condition for each subject. \
note: RT from button presses was multiple per trial, so these 'motor skills easy / hard' represent the median RT from the given trial.
```{r stuff}
beh_comp_motor_long <- beh_comp_long %>%
  group_by(SUBJECTID) %>%
  mutate(effort_RT = ifelse(Effort_Choice == "Easy", (motor_skills_easy*100), 
                            ifelse(Effort_Choice == "Hard", (motor_skills_hard*100), NA)),
         log_effort_RT = log(effort_RT))

effort_RT_table <- beh_comp_motor_long %>%
  group_by(Effort_Choice) %>%
  summarize(median(effort_RT, na.rm = T),
            sd(effort_RT, na.rm = T))
save(effort_RT_table, file = "tables/2_manipulation_checks/effort_RT_table_by_condition.Rdata")

ggplot(data = beh_comp_motor_long, aes(effort_RT)) + facet_grid(version~Effort_Choice) +
  geom_density() + theme_classic()

fix <- beh_comp_long %>% filter(is.na(version))
unique(fix$SUBJECTID)
``` 

RT is not normally distributed
```{r}
shapiro.test(beh_comp_motor$effort_RT)
shapiro.test(beh_comp_motor$log_effort_RT)

plot(beh_comp_motor$effort_RT)
plot(beh_comp_motor$log_effort_RT) # beh_comp_motor$effort_RT)
```

### Effort RT was slower for the hard task
```{r other stuff}
# sig using Raw RT 
effort_RT <- lmer(effort_RT ~ condition  + AGE.c + SEX.c + 
                (1 | SUBJECTID),
               data = beh_comp_motor)
summary(effort_RT)

# same with logged RT
effort_RT_lg <- lmer(log_RT ~ condition  + AGE.c + SEX.c + 
                (1 | SUBJECTID),
               data = beh_comp_motor)
summary(effort_RT_lg)
```

### plot the effects by condition
```{r more stuff}
effect_df <- data.frame(effect("condition", effort_RT_lg))

RT_condition_plot <- ggplot(data = effect_df, aes(x = condition, y = fit)) + 
  geom_point( color = "black", size = 1.5) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  geom_jitter(data = beh_comp_motor, aes(x = condition, y = log_RT), alpha = 0.3, size = 1, width = 0.15, color= dark_blue) +
  my_colors + my_colors2 + theme_classic() + ylab("log RT (ms)") + ylim(2.5, 3.75)

RT_condition_plot
ggsave(RT_condition_plot, file = "figures/2_manipulation_checks/Effort_RT_by_condition.pdf", width = 3, height = 4)
```


### no age x condition interaction
```{r ttt }
# same with logged RT
effort_RT_lg_int <- lmer(log_RT ~ condition* AGE.c + SEX.c + 
                (1 | SUBJECTID),
               data = beh_comp_motor)
summary(effort_RT_lg_int)
```


### plot the effects by age 
```{r bbbb}
effect_df <- data.frame(effect("condition:AGE.c", effort_RT_lg))

effort_RT_int_plot <- ggplot(data = effect_df, aes(x = AGE.c, y= fit)) + 
  geom_line(aes(color = condition)) + 
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = condition), alpha = 0.25) +
  geom_point(data = beh_comp_motor, aes(x = AGE.c, y = log_RT, color= condition), alpha = 0.3, width = 0.04) +
  my_colors + my_colors2 + theme_classic() + ylab("log RT (ms)") + 
  geom_line(data = beh_comp_motor, aes(x = AGE.c, y = log_RT, group = SUBJECTID))
effort_RT_int_plot
ggsave(effort_RT_int_plot, file = "figures/2_manipulation_checks/Effort_RT_by_conditionxAge.pdf")
```

## Perceived effort: 
We expect that children overall will rate the hard task (ring finger) as more difficult than the easy task (thumb) in their post-test ratings. As a control analysis, we will follow-up to exclude subjects who rated equal or less effort for the hard task than easy task.

```{r nnnn}
# make long version of perceived effort data
perceived_df <- beh_comp_subj %>% 
  gather(key = "condition", value = "perceived_effort_rating", 
         hard_effort_perceived, easy_effort_perceived) %>%
  mutate(condition = as.factor(ifelse(condition == "hard_effort_perceived", 
                                      "Hard", "Easy"))) %>%
      mutate(motor_skills_ave= (motor_skills_easy + motor_skills_hard)/2,
             motor_skills_ave.c = motor_skills_ave - mean(motor_skills_ave, na.rm =T ),
             motor_skills_by_condition = ifelse(condition == "Easy", motor_skills_easy, motor_skills_hard))


```

### model: main effects of AGE and condition
```{r seee}
perceived_effort_mod <- lmer(perceived_effort_rating ~ condition + AGE.c + SEX.c + #IQ + Fam_inc_needs + 
                             Reinforce_rate.c + # + motor_skills_hard + motor_skills_easy + 
                               (1 | SUBJECTID), 
                           data = perceived_df)
summary(perceived_effort_mod)

```

plot effect of condition
```{r tyyy}
# get effect  df tidy
effort_effect <-  as.data.frame(effect("condition", perceived_effort_mod, confint=TRUE))

plot_effect <- ggplot(effort_effect,aes(x = condition, y = fit)) +
 geom_bar(stat = "identity", position=position_dodge(),
                                 alpha = 0.25, fill = dark_blue) + theme_classic() + 
  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_jitter(data = perceived_df, aes(x = condition, y = perceived_effort_rating),
       width = 0.2, height = 0, pch = 21,
             alpha = 0.3, fill = dark_blue) +
  theme_classic() + ylab("Perceived effort") + coord_cartesian(ylim=c(1,4)) +
  xlab ("Condition") + theme(legend.position = "none")
plot_effect

pdf("figures/Manipulation_check_perceived_effort_Hard_vs_easy.pdf", width = 2.5, height = 4)
plot_effect
dev.off()
```


plot effect of age
```{r ooooo}
# get effect  df tidy
effort_effect <-  as.data.frame(effect("AGE.c", perceived_effort_mod, confint=TRUE))

plot_effect <- ggplot(effort_effect, aes(x = AGE.c, y = fit)) +
 geom_line(color = dark_blue, size = 1) + geom_ribbon(aes(ymax = upper, ymin = lower), 
                                                         alpha = 0.2, fill= dark_blue) + 
 geom_point(data = perceived_df,  aes(x = AGE.c, y = perceived_effort_rating),
            alpha = 0.25, color = dark_blue) + theme(legend.position = "none") +
  theme_classic() + ylab("Perceived effort") + 
  xlab ("AGE (centered)") + theme(legend.position = "none")
plot_effect

pdf("figures/Manipulation_check_perceived_effort_by_Age.pdf", width = 2.5, height = 4)
plot_effect
dev.off()
```


### main effect of motor skills on effort
```{r ppp}

perceived_effort_mod <- lmer(perceived_effort_rating ~ condition + SEX.c +  #AGE.c + 
                             Reinforce_rate.c + motor_skills_ave.c + 
                               (1 | SUBJECTID), 
                           data = perceived_df)
summary(perceived_effort_mod)

```


### main effect of motor skills on effort, NS with age
```{r zzz}

perceived_effort_mod <- lmer(perceived_effort_rating ~ condition + SEX.c + AGE.c + 
                             Reinforce_rate.c + motor_skills_ave.c + 
                               (1 | SUBJECTID), 
                           data = perceived_df)
summary(perceived_effort_mod)

```

### age interact with condition? No
```{r xxx}
perceived_effort_mod <- lmer(perceived_effort_rating ~ condition * AGE.c + SEX.c +  
                             Reinforce_rate.c + 
                               (1 | SUBJECTID), 
                           data = perceived_df)
summary(perceived_effort_mod)

```






### any kids rate easy task harder than hard task? N = 2 
rerun main analyses omitting these 2 subjects
```{r eqq}
nrow(beh_comp_subj %>% filter(hard_effort_perceived < easy_effort_perceived))

```

### any kids rate easy task == hard task? yes  - 23% of kids! 
```{r qwe}
nrow(beh_comp_subj %>% filter(hard_effort_perceived == easy_effort_perceived))/ nrow(beh_comp_subj)

```

## Self-reported affect:
We expect that children will report greater positive affect in response to rewards relative to setbacks (on likert scale, where 1 = very unhappy and 4 = very happy)
```{r tre}
# make long version of perceived effort data
pos_affect_df <- beh_comp_subj %>% 
  gather(key = "condition", value = "positive_affect", 
          win_feeling,lose_feeling) %>%
  mutate(condition = as.factor(ifelse(condition == "win_feeling", 
                                      "Rewards", "Setbacks"))) %>%
  select(SUBJECTID, SEX.c, AGE.c,  positive_affect, condition) %>%
  filter(!is.na(positive_affect) & !is.na(condition) & !is.na(AGE.c) & !is.na(SEX.c))

```

### main effect of Age and Condition
```{r ert}
pos_affect_mod <- lmer(positive_affect ~ condition + AGE.c + SEX.c + 
                          (1 | SUBJECTID),
   data = pos_affect_df)
summary(pos_affect_mod)
```

### Age x condition interaction: NS
*use anova because lmer doesn't work! 
```{r ytr}
pos_affect_modb <- lmer(positive_affect ~ condition * AGE.c + SEX.c + 
                          (1 | SUBJECTID),
   data = pos_affect_df)
summary(pos_affect_modb)
```

```{r qreeee}
# get effect  df tidy
affect_effect <-  as.data.frame(effect("condition", pos_affect_mod, confint=TRUE))

plot_effect <- ggplot(affect_effect,aes(x = condition, y = fit)) +
 geom_bar(stat = "identity", position=position_dodge(),
                                 alpha = 0.25, fill = dark_blue) + theme_classic() + 
  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_jitter(data = pos_affect_df,  aes(x = condition, y = positive_affect),
              width = 0.2, height = 0, pch = 21,
             alpha = 0.3, fill = dark_blue) +
   theme(legend.position = "none") +
  theme_classic() + ylab("Positive Affect") + coord_cartesian(ylim=c(1,4)) +
  xlab ("Condition") + theme(legend.position = "none")
plot_effect

pdf("figures/Manipulation_check_positive_affect_Rewards_vs_Setbacks.pdf", width = 2.5, height = 4)
plot_effect
dev.off()
```

## Perceived control
Most children understood that they did not have full control over the task 
```{r poi}
df <- beh_comp_subj %>%
  filter(!is.na(perceived_control)) %>%
group_by(perceived_control) %>%
  summarize(counts = n())


pc_plot <- ggplot(df, aes(x = factor(perceived_control), y = counts)) + 
    scale_x_discrete(labels = c("1" = "None", "2" = "Some", "3" = "Alot")) +
  geom_bar(stat = "identity", fill = dark_blue, alpha = 0.3) + theme_classic() +
  xlab ("Perceived Control")

pc_plot

pdf("figures/comp_perceived_control_hist.pdf", width = 2.5, height= 4)
pc_plot
dev.off()
```