---
title: "Behavior modeling"
author: "Michelle.VanTieghem"
date: "6/7/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

notes: converting all models to BRMS on 11/27/2019

# Load data
## only behavior
from data_cleaning_for_analysis 
```{r, warning = F, message = F}
source("../../0_R_analysis_setup_file.R", echo=F)

# wide version, by subject.
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_subj.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_subj_WSLS.Rdata")


# long version, by trial 
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_long.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_long_WSLS.Rdata")

```

# Behavioral measures: Choice behavior
notes: lmer models displayed here, brms versions run in COMP_brms_preregistration_analyses.R 

## histogram of distribution
```{r}
#names(beh_comp_subj)
choice_hist <- ggplot(data = beh_comp_subj, aes(x = prop_hard_choices)) + 
  geom_histogram(bins = 10, fill = dark_blue, alpha = 0.3) + theme_classic() +
  xlab("Proportion Hard vs. Easy Choices")
choice_hist 

pdf("figures/comp_prop_hard_choices_hist.pdf", width = 2.5, height= 4)
choice_hist
dev.off()

```


## 1. basic model with trial number, reinforcement rate. 

```{r}
load("brms_models/preregistration_model_results/choice_mod1_brms.Rdata")
print(choice_mod1_brms, digits = 4)
```

### fitted brms model with raw data, showing intercept > 0.5 probability 
```{r}
#blm_table(choice_mod1_brms, SUBJECTID)

new_df <- data.frame(expand.grid( AGE.c = 0, Trial_Number.c = 0, Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(choice_mod1_brms, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(intercept = as.factor('intercept'))
head(effect_df)


effect_plot <- ggplot(effect_df, aes(x = intercept, y = fit)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.2, fill = dark_blue)  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
   geom_jitter(data = beh_comp_subj,color= dark_blue,
       aes(x = as.factor('intercept'), y = prop_hard_choices), 
       alpha = 0.3, width = 0.05, height =0.0) +
   theme_classic() + theme(legend.position = "none") + 
  ylab ("Likelihood to choose hard")  + xlab ("")
effect_plot

ggsave(effect_plot, file = "figures/3_basic_behavior_models/choice_intercept_different_than_0.5.pdf", height = 4, width = 2)
```


## 1b. Effect of Age X time? NS.
```{r}
load("brms_models/preregistration_model_results/choice_mod1_ageint_brms.Rdata")
print(choice_mod1_ageint, digits = 4)
```

### plot null effects of age 
```{r}
# include possible ranges of AGE and TRIAL NUMBER 
new_df <- data.frame(expand.grid(AGE.c = c(min(beh_comp_long$AGE.c), -1*sd(beh_comp_long$AGE), 0, 1*sd(beh_comp_long$AGE), max(beh_comp_long$AGE.c)),
                                Trial_Number.c = 0, 
                                Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(choice_mod1_brms, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(Trial_phase = as.factor(Trial_Number.c))

effect_plot <- ggplot(effect_df, aes(x = AGE.c, y = fit)) +
  geom_line(alpha = 0.2, color = dark_blue)  +
 geom_ribbon(aes(ymin= lower, ymax= upper), fill = dark_blue, alpha = 0.2) +
  geom_jitter(data = beh_comp_subj,color = dark_blue,
       aes(x = AGE.c, y = prop_hard_choices), 
       alpha = 0.3, width = 0.05, height =0.0) +
   theme_classic() + theme(legend.position = "none") + 
  ylab ("Likelihood to choose hard")  + xlab ("Age (mean-centered)") 
effect_plot

ggsave(effect_plot, file = "figures/3_basic_behavior_models/choice_NS_age.pdf", height = 4, width = 3)
```

## plot null effects of trial number
```{r}
# include possible ranges of AGE and TRIAL NUMBER 
new_df <- data.frame(expand.grid(AGE.c = 0,  Trial_Number.c = c(min(beh_comp_long$Trial_Number.c), -1*sd(beh_comp_long$Trial_Number),
                                                                0, 1*sd(beh_comp_long$Trial_Number), max(beh_comp_long$Trial_Number.c)),
                                Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(choice_mod1_ageint, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(Trial_phase = as.factor(Trial_Number.c))
head(effect_df)

effect_plot <- ggplot(effect_df, aes(x = Trial_Number.c, y = fit)) +
  geom_line(alpha = 0.2, color = dark_blue)  +
 geom_ribbon(aes(ymin= lower, ymax= upper), fill = dark_blue, alpha = 0.2) +
 # how to add individual brms estimates per subject? ranef... 
     theme_classic() + theme(legend.position = "none") + ylim(0, 1) +
  ylab ("Likelihood to choose hard")  + xlab ("Trial Number (mean-centered)") 
effect_plot

ggsave(effect_plot, file = "figures/3_basic_behavior_models/choice_NS_TrialNumber.pdf", height = 4, width = 3)
```

# Behavioral measures: WSLS
## clean data to exclude 'too slow' trials
```{r}
summary(beh_comp_long_WSLS$Effort_Choice_prior)
summary(beh_comp_long_WSLS$Feedback_prior)

beh_comp_long_WSLS <- beh_comp_long_WSLS %>%
  filter(Feedback_prior != "Too_slow")
```


## 1. modeling prior effort x prior feedback
model with full random effects.
main effect of effort choice, age, and proportion hard.
```{r}
load("brms_models/preregistration_model_results/WSLS_mod2_brms.Rdata")
print(WSLS_mod2_brms, digits = 3)

```

### Figure from brms fitted model with raw data 
showing all 4 conditions, but really only a main effect of prior effort.
```{r}
# load single-subj data 
load("../../2_cleaning_QC/cleaned_data/WSLS_by_subj_condition.Rdata")

new_df <- data.frame(expand.grid(Effort_Choice_prior = c("Hard", "Easy"),
                                  Feedback_prior = c("Reward","Setback"),
                                  AGE.c = 0, Trial_Number.c = 0, Reinforce_rate.c = 0, SEX.c = 0, proportion_hard.c = 0))

WSLS_effect<- fitted(WSLS_mod2_brms, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate)
WSLS_hard_effect <- filter(WSLS_effect, Effort_Choice_prior == "Hard")
WSLS_easy_effect <- filter(WSLS_effect, Effort_Choice_prior == "Easy")

WSLS_hard_plot <- ggplot(WSLS_hard_effect, aes(x = Feedback_prior, y = fit, fill= Feedback_prior)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.2)  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
   geom_jitter(data = subset(beh_comp_subj_WSLS, Feedback_prior != "Too_slow" & Effort_Choice_prior == "Hard"),
       aes(x = Feedback_prior, y = stay_shift, color = Feedback_prior), 
       alpha = 0.3, width = 0.05, height =0.0) + #stackratio = 1, stackdir = "center", binaxis = "y", binwidth = .01, dotsize = 1) + 
   theme_classic() + my_colors + my_colors2 +   theme(legend.position = "none") + 
  ylab ("Likelihood to choose hard again") + xlab ("Feedback on prior trial") + ggtitle("Behavior after a hard trial") 

WSLS_easy_plot <- ggplot(WSLS_easy_effect, aes(x = Feedback_prior, y = fit, fill= Feedback_prior)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.2)  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
   geom_jitter(data = subset(beh_comp_subj_WSLS, Feedback_prior != "Too_slow" & Effort_Choice_prior == "Hard"),
       aes(x = Feedback_prior, y = stay_shift, color = Feedback_prior), 
       alpha = 0.3, width = 0.05, height =0.0) + #stackratio = 1, stackdir = "center", binaxis = "y", binwidth = .01, dotsize = 1) + 
   theme_classic() + my_colors + my_colors2 +   theme(legend.position = "none") + 
  ylab ("Likelihood to choose easy again") + xlab ("Feedback on prior trial") + ggtitle("Behavior after an easy trial") 
combined2 <- grid.arrange(WSLS_easy_plot, WSLS_hard_plot, nrow = 1)


ggsave(combined2, height = 4, width = 6, file = "figures/3_basic_behavior_models/WSLS_by_prior_effort_prior_feedback_brms.pdf")
```


## 1b. AGE x Prior effort choice: SIG
main effect of effort choice, age, proportion hard, and effort choice x age
```{r}
load("brms_models/preregistration_model_results/WSLS_mod2b_brms_age_int.Rdata")

print(WSLS_mod2b_brms_age_int, digits = 4)
```

### plot the interaction
```{r}

new_df <- data.frame(expand.grid(AGE.c = c(min(beh_comp_long$AGE.c), -1*sd(beh_comp_long$AGE), 0, 1*sd(beh_comp_long$AGE), max(beh_comp_long$AGE.c)),
                     Effort_Choice_prior = c("Hard", "Easy"),
                     Feedback_prior = c("Reward","Setback"),
                      Trial_Number.c = 0, Reinforce_rate.c = 0, SEX.c = 0, proportion_hard.c = 0))

WSLS_effect <- fitted(WSLS_mod2b_brms_age_int, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate)
WSLS_hard_effect <- WSLS_effect %>% filter(Effort_Choice_prior == "Hard")
WSLS_easy_effect <- WSLS_effect %>% filter(Effort_Choice_prior == "Easy")
# fix this age variable.
beh_comp_subj_WSLS$AGE.c <- beh_comp_subj_WSLS$AGE - mean(beh_comp_subj_WSLS$AGE)

WSLS_hard_plot <- ggplot(WSLS_hard_effect, aes(x = AGE.c, y = fit)) +
  geom_line(aes(color = Feedback_prior)) + 
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = Feedback_prior), alpha = 0.3) +
  geom_point(data = filter(beh_comp_subj_WSLS, Effort_Choice_prior == "Hard" & Feedback_prior != "Too_slow"),
      aes(x = AGE.c, y = stay_shift, color = Feedback_prior), alpha = 0.3) +
   theme_classic() + my_colors + my_colors2 + ylim(0,1) +
  ylab ("Likelihood to choose hard again") + xlab ("Age (mean-centered)") +
   theme(legend.position = "none") + ggtitle("Behavior after a hard trial") +
   geom_hline(aes(yintercept = 0.5), linetype = "dashed")  

WSLS_easy_plot <- ggplot(WSLS_easy_effect, aes(x = AGE.c, y = fit)) +
  geom_line(aes(color = Feedback_prior)) + 
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = Feedback_prior), alpha = 0.3) +
  geom_point(data = filter(beh_comp_subj_WSLS, Effort_Choice_prior == "Easy" & Feedback_prior != "Too_slow"),
      aes(x = AGE.c, y = stay_shift, color = Feedback_prior), alpha = 0.3) +
   theme_classic() + my_colors + my_colors2 + ylim(0,1) +
  ylab ("Likelihood to choose easy again") + xlab ("Age (mean-centered)") +
   theme(legend.position = "none") + ggtitle("Behavior after an easy trial") +
   geom_hline(aes(yintercept = 0.5), linetype = "dashed")  

combined <- grid.arrange(WSLS_easy_plot, WSLS_hard_plot, nrow = 1)

ggsave(combined, file = "figures/3_basic_behavior_models/WSLS_by_prior_effort_X_Age.pdf", width = 6, height = 4)

```


## prior effort x Trial N: SIG
```{r}
load("brms_models/preregistration_model_results/WSLS_mod2c_brms_trial_int.Rdata")
print(WSLS_mod2c_brms_trial_int, digits = 4)
```


### plot the interaction effect
```{r}
new_df <- data.frame(expand.grid(Trial_Number.c = c(min(beh_comp_long$Trial_Number.c), -1*sd(beh_comp_long$Trial_Number), 0, 1*sd(beh_comp_long$Trial_Number), max(beh_comp_long$Trial_Number.c)),
                     Effort_Choice_prior = c("Hard", "Easy"),
                     Feedback_prior = c("Reward","Setback"),
                     AGE.c = 0, Reinforce_rate.c = 0, SEX.c = 0, proportion_hard.c = 0))

WSLS_effect <- fitted(WSLS_mod2c_brms_trial_int, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate)
WSLS_hard_effect <- WSLS_effect %>% filter(Effort_Choice_prior == "Hard")
WSLS_easy_effect <- WSLS_effect %>% filter(Effort_Choice_prior == "Easy")

WSLS_hard_plot <- ggplot(WSLS_hard_effect, aes(x = Trial_Number.c, y = fit)) +
  geom_line(aes(color = Feedback_prior)) + 
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = Feedback_prior), alpha = 0.3) +
    theme_classic() + my_colors + my_colors2 + ylim(0,1) +
  ylab ("Likelihood to choose hard again") + xlab ("Trial (mean-centered)") +
   theme(legend.position = "none") + ggtitle("Behavior after a hard trial") +
   geom_hline(aes(yintercept = 0.5), linetype = "dashed")  

WSLS_easy_plot <- ggplot(WSLS_easy_effect, aes(x = Trial_Number.c, y = fit)) +
  geom_line(aes(color = Feedback_prior)) + 
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = Feedback_prior), alpha = 0.3) +
  # need to get random slopes from brms model to plot for each subj.
    theme_classic() + my_colors + my_colors2 + ylim(0,1) +
  ylab ("Likelihood to choose easy again") + xlab ("Trial (mean-centered)") +
   theme(legend.position = "none") + ggtitle("Behavior after an easy trial") +
   geom_hline(aes(yintercept = 0.5), linetype = "dashed")  

combined <- grid.arrange(WSLS_easy_plot, WSLS_hard_plot, nrow = 1)
ggsave(combined, file = "figures/3_basic_behavior_models/WSLS_by_trialN_X_effort_choice.pdf", width = 6, height = 4)


```