---
title: "Aim 1 Hypothesis 1 choice phase"
author: "Michelle.VanTieghem"
date: "6/7/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---


# Load data
## only behavior
from data_cleaning_for_analysis 
```{r}
source("../../0_R_analysis_setup_file.R", echo=F)

# wide version, by subject.
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_subj.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_subj_WSLS.Rdata")


# long version, by trial 
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_long.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_long_WSLS.Rdata")

```


## with scanning data 
from data_cleaning_for_analysis 
```{r}
# wide version, by subject.
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_wide.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_wide_WSLS.Rdata")

# long version, by trial 
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_long.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_long_WSLS.Rdata")

```




# Aim 1: Identify neural substrates that support effort-based persistence behavior. 
Parameter estimates (copes) will be extracted at the subject level from each ROI and conditions of interest (Choice Phase, Feedback Phase). Linear models in R will model the effects of conditions on reactivity, controlling for between-subject covariates.
Covariates: For all analyses, we will include between-subject effects of age and sex in primary analyses. For other covariates, in the event that these variables meaningfully influence the outcome of interest, we will keep them in the final models, otherwise they will be removed from final models. These include motor skills (from finger tapping), motion confounds, and IQ.


## Hypothesis 1: Effort-based decisions will involve activation of (a) prefrontal regions (vmPFC and ACC) implicated in decision-making and (b) striatal regions (VS) implicated in choice valuation.

### set up & clean data
```{r} 
choice_level_order <- c('ACC', 'mPFC',  "VS")
#organize data for choice phase.
choice_df <- beh_scan_comp_wide %>%
  # combine left and right accumbens betas into bilateral! 
  select(-starts_with("feedback"), -starts_with("setback"), -starts_with("reward")) %>%
  gather(key = "ROI", value = "beta", allChoices_ACC, allChoices_choice_mPFC,  allChoices_VS) %>%
  mutate( ROI = ifelse(grepl("ACC", ROI), "ACC", 
          ifelse(grepl("mPFC", ROI), "mPFC", ifelse(grepl("VS", ROI), "VS", "fix"))),
      ROI = factor(ROI, levels = choice_level_order), 
         AGE.c = AGE - mean(AGE, na.rm = T),
         SEX.c = SEX - mean(SEX, na.rm = T), 
         IQ.c = IQ- mean(IQ, na.rm = T),
         total_TRs_censored.c = total_TRs_censored - mean(total_TRs_censored, na.rm = T),
         Reinforce_rate.c = Reinforce_rate - mean(Reinforce_rate, na.rm = T))
summary(as.factor(choice_df$ROI))
summary(choice_df$beta)

```


```{r}
ggplot(data = choice_df, aes(x = ROI, y = beta)) + 
  geom_boxplot() + geom_jitter(alpha = 0.2, width = 0.05, color = dark_blue) + theme_classic() 

```

### clean data: remove beta outliers
```{r}
# calculate limits fo routliers at 3SD from mean
choice_outliers <- choice_df %>%
  group_by(ROI) %>%
  summarize(outlier_upper = mean(beta) + 3*sd(beta), 
            outlier_lower = mean(beta) - 3*sd(beta))

# mark outliers for each ROI
choice_df2 <- data.frame()
for (region in choice_outliers$ROI){
    check <- choice_df %>% filter(ROI == region) %>%
    mutate(choice_outlier = ifelse(beta > choice_outliers$outlier_upper[choice_outliers$ROI == region] | 
                               beta < choice_outliers$outlier_lower[choice_outliers$ROI == region], 1, 0))
    choice_df2 <- rbind(choice_df2, check)
}

# look at outlier #
outlier_table <- choice_df2 %>%
  group_by(ROI) %>%
  summarize(n = n(), 
            n_outlier = sum(choice_outlier))

outlier_table

# remove data of outliers, mark as NA. 
choice_df2 <- choice_df2 %>% 
  mutate(beta = ifelse(choice_outlier == 1, NA, beta)) 

sum(is.na(choice_df2$beta))
# get subjects for outliers for long analyses 
choice_outlier_subjects <- choice_df2 %>% 
  filter(choice_outlier == 1) %>% select (ROI, SUBJECTID)
save(choice_outlier_subjects, file = "tables/Choice_betas_outlier_subjects.Rdata")

levels(choice_df2$ROI) <- choice_level_order

```

### Model 1 with ACC 
```{r}
mod1_ACC <- lm(beta ~  AGE.c + SEX.c + 
                   total_TRs_censored.c + Reinforce_rate.c, 
           data = subset(choice_df2, ROI == "ACC"))

choice_effect_ACC <- summary(mod1_ACC)$coefficients[1,]

```

### model 1 with mPFC 
```{r}
mod1_mPFC <- lm(beta ~  AGE.c + SEX.c + 
                   total_TRs_censored.c + Reinforce_rate.c, 
           data = subset(choice_df2, ROI == "mPFC"))

choice_effect_mPFC <- summary(mod1_mPFC)$coefficients[1,]

```

### model 1 with VS 
```{r}
mod1_VS <- lm(beta ~  AGE.c + SEX.c + #IQ.c +
                   total_TRs_censored.c + Reinforce_rate.c, 
           data = subset(choice_df2, ROI == "VS"))

choice_effect_VS <- summary(mod1_VS)$coefficients[1,]

```


### table of all ROIs 

```{r}
table_choice_activation <- data.frame(rbind(choice_effect_ACC, choice_effect_mPFC, choice_effect_VS)) %>%
  rename(p_value = "Pr...t..", 
         SE = "Std..Error", 
         t_value = "t.value")
table_choice_activation$ROI <- c("ACC", "mPFC", "VS")
table_choice_activation$df <- 40

table_choice_activation <- table_choice_activation %>% 
        mutate(sig =  ifelse(p_value < 0.001, "***", ifelse(p_value < 0.01, "**", 
                                         ifelse(p_value < 0.05, "*", "")))) %>%
  select(ROI, Estimate, SE, df, t_value, p_value, sig)
table_choice_activation
save(table_choice_activation, file = "model_results/choice_activation_model_results.Rdata")
```

### plot of all ROIs

```{r}
# model together just for the sake of plots. 
mod1 <- lm(beta ~ ROI + AGE.c + SEX.c + #IQ.c +
                   total_TRs_censored.c + Reinforce_rate.c, 
           data = choice_df2)
summary(mod1)
effect_df <- data.frame(effect("ROI", mod1, confint = T))

plot_effect <- ggplot(data = effect_df,
                      aes(x = factor(ROI, level = choice_level_order), y = fit)) + 
                        geom_bar(stat = "identity", position=position_dodge(),
                                 alpha = 0.2, fill = dark_blue) + theme_classic() + 
  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_point(data = choice_df2,  aes(x = factor(ROI, level = choice_level_order), y = beta), 
             position = position_dodge(.9), alpha = 0.25, color = dark_blue) + 
  theme(legend.position = "none") + ylim(-200, 200)+ 
  ylab("Reactivity during Choice Phase") + xlab ("ROI") + my_colors2 + my_colors + 
 geom_hline(yintercept=0, linetype="dashed",  size=.5)
plot_effect

pdf("figures/All_ROIs_Choice_Phase_CORRECTED.pdf", width = 3, height = 4)
plot_effect
dev.off()

```

## Hypothesis 1 Follow-up model: How do fronto-striatal regions respond differently for hard vs. easy effort choices?

### set up & clean data
```{r} 
names(beh_scan_comp_wide)

#organize data for choice phase.
choice_contrast_df <- beh_scan_comp_wide %>%
  # combine left and right accumbens betas into bilateral! 
  select(-starts_with("feedback"), -contains ("FB"), -contains("Setback"), -contains("Reward"), -starts_with("allChoice")) %>%
  # converting this because i forgot to pull easy choices alone
 # mutate(easy_choice_ACC = -(hard_easy_choice_ACC - HardChoice_ACC), 
  #       easy_choice_mPFC = -(hard_easy_choice_ACC - HardChoice_ACC), 
   #      easy_VS = -(hard_easy_VS - hard_VS)) %>%
  gather(key = "ROI", value = "beta", HardChoice_ACC, HardChoice_choice_mPFC, HardChoice_VS,
         EasyChoice_ACC, EasyChoice_choice_mPFC, EasyChoice_VS, 
         Hard_EasyChoice_ACC, Hard_EasyChoice_choice_mPFC, Hard_EasyChoice_VS) %>%
  mutate(contrast = as.factor(ifelse(grepl("Hard_Easy", ROI), "Hard_Easy",
                           ifelse(grepl("Hard", ROI), "Hard", "Easy"))),
           ROI = as.factor(ifelse(grepl("ACC", ROI), "ACC", 
                        ifelse(grepl("mPFC", ROI), "mPFC", "VS"))),
           AGE.c = AGE - mean(AGE, na.rm = T),
         SEX.c = SEX - mean(SEX, na.rm = T), 
         IQ.c = IQ- mean(IQ, na.rm = T),
         total_TRs_censored.c = total_TRs_censored - mean(total_TRs_censored, na.rm = T),
         Reinforce_rate.c = Reinforce_rate - mean(Reinforce_rate, na.rm = T))
summary(as.factor(choice_contrast_df$ROI))
summary(as.factor(choice_contrast_df$contrast))


#sanity check for easy contrast calculation 
hard_easy_df <- choice_contrast_df %>% filter(contrast == "Hard_Easy")
hard_df <- choice_contrast_df %>%filter (contrast =="Hard")
easy_df <- choice_contrast_df %>% filter(contrast == "Easy")

easy_ACC_check <- easy_df$beta[easy_df$ROI == "ACC"]
hard_ACC_check <- hard_df$beta[hard_df$ROI == "ACC"]

hard_easy_ACC_check <- hard_ACC_check - easy_ACC_check
hard_easy_ACC_check2 <- hard_easy_df$beta[hard_easy_df$ROI == "ACC"]
plot(hard_easy_ACC_check, hard_easy_ACC_check2)

```


```{r}
ggplot(data = choice_contrast_df, aes(x = ROI, y = beta)) + facet_grid(~contrast) +
  geom_boxplot() + geom_jitter(alpha = 0.2, width = 0.05, color = dark_blue) + theme_classic() 

```

### clean data: remove beta outliers
```{r}
 #calculate limits fo routliers at 3SD from mean
choice_contrast_outliers <- choice_contrast_df %>%
  # remove NAs because not all subjects have these betas! 
  filter(!is.na(beta) & contrast != "Hard_easy") %>%
  group_by(ROI, contrast) %>%
  summarize(outlier_upper = mean(beta, na.rm = T) + 3*sd(beta, na.rm = T), 
            outlier_lower = mean(beta, na.rm = T)- 3*sd(beta, na.rm = T))

# mark outliers for each ROI
choice_contrast_df2 <- data.frame()
for (region in unique(choice_contrast_outliers$ROI)){
  #region = "choice_mPFC"
  #print(region)
  for (cope in unique(choice_contrast_outliers$contrast)){
   # print(cope)
      #cope = "reward_minus_setback"
      check <- choice_contrast_df %>% filter(ROI == region & contrast == cope) %>%
      mutate(choice_contrast_outlier =
               ifelse(beta > choice_contrast_outliers$outlier_upper[choice_contrast_outliers$ROI == region & choice_contrast_outliers$contrast == cope] | 
                                 beta < choice_contrast_outliers$outlier_lower[choice_contrast_outliers$ROI == region & choice_contrast_outliers$contrast == cope], 1, 0))
      choice_contrast_df2 <- rbind(choice_contrast_df2, check)
  }
}

# look at outlier #
outlier_table <- choice_contrast_df2 %>%
  group_by(ROI, contrast) %>%
  summarize(n = n(), 
            n_outlier = sum(choice_contrast_outlier, na.rm = T))
# idk why i ahve to do thsi!! 
outlier_table$n <- outlier_table$n 
outlier_table$n_outlier <- outlier_table$n_outlier

outlier_table
# remove data of outliers 
choice_contrast_df2 <- choice_contrast_df2 %>% 
  filter(!is.na(beta)) %>%
  mutate(beta = ifelse(choice_contrast_outlier > 0 , NA, beta))
sum(is.na(choice_contrast_df2$beta))
choice_contrast_outlier_subjects <- choice_contrast_df2 %>% 
  filter(choice_contrast_outlier == 1) %>% select(SUBJECTID, ROI, contrast)

choice_contrast_outlier_subjects
save(choice_contrast_outlier_subjects, file = "tables/choice_contrast_betas_outlier_subjects.Rdata")

# check that these 5 outlier values were removed
sum(is.na(choice_contrast_df2$beta))
```

### Model 1b for ACC 
```{r}
# repeated measures, with reward and setback as contrasts
mod1b_ACC <- lmer(beta ~ contrast + #IQ.c + 
                     AGE.c + SEX.c + total_TRs_censored.c + Reinforce_rate.c + #Fam_inc_needs +
                  (1 | SUBJECTID),
                data = subset(choice_contrast_df2, ROI == "ACC" & contrast != "Hard_Easy"))
summary(mod1b_ACC)

```

### Model 1B for mPFC 
```{r}
# repeated measures, with reward and setback as contrasts
mod1b_mPFC <- lmer(beta ~ contrast + #IQ.c + 
                     AGE.c + SEX.c + total_TRs_censored.c + Reinforce_rate.c + #Fam_inc_needs +
                  (1 | SUBJECTID),
                data = subset(choice_contrast_df2, ROI == "mPFC"& contrast != "Hard_Easy"))
summary(mod1b_mPFC)

```

### Model 1b for VS 
```{r}
# repeated measures, with reward and setback as contrasts
mod1b_VS  <- lmer(beta ~ contrast + #IQ.c + 
                     AGE.c + SEX.c + total_TRs_censored.c + Reinforce_rate.c + #Fam_inc_needs +
                  (1 | SUBJECTID),
                data = subset(choice_contrast_df2, ROI == "VS"& contrast != "Hard_Easy"))
summary(mod1b_VS)

```


### Model 1b plot for all ROIs

```{r}
choice_level_order <- c("ACC", "mPFC", "VS")

effect_ACC <- data.frame(ROI = "ACC", effect("contrast", mod1b_ACC, confint = T))
effect_mPFC  <- data.frame(ROI = "mPFC",effect("contrast", mod1b_mPFC, confint = T))
effect_VS <- data.frame(ROI = "VS", effect("contrast", mod1b_VS, confint = T))
# merge them all together into one df
effect_df <- rbind(effect_ACC, effect_mPFC, effect_VS)
# so we can plot! 
plot_effect <- ggplot(data = effect_df, aes(x = contrast, y = fit, fill = contrast)) + 
                        geom_bar(stat = "identity", position=position_dodge(),
alpha = 0.5) + theme_classic() + facet_grid (~ ROI) +
  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_point(data = subset(choice_contrast_df2, contrast != "Hard_Easy"),
            aes(x = contrast, y = beta, color = contrast), position = position_dodge(.9),
             alpha = 0.25) + theme(legend.position = "none") +
  
  ylab("Reactivity during Choice Phase") + xlab ("Choice") + my_colors2 + my_colors + 
 geom_hline(yintercept=0, linetype="dashed",  size=.5)
plot_effect

pdf("figures/All_ROIs_Hard_vs_Easy_Choice.pdf", width = 6, height = 3)
plot_effect
dev.off()

```



re-level ROIs to get results for each ROI
```{r}
choice_contrast_df2 <- choice_contrast_df2 %>%
  mutate(ROI_ACC = relevel(ROI, "ACC"),
         ROI_mPFC = relevel(ROI, "mPFC"),
         ROI_VS = relevel(ROI, "VS"),
         contrast_hard = relevel(contrast, "Hard"), 
         contrast_easy = relevel(contrast, "Easy"))
 
# ACC
mod1b_ACC_h <- lmer(beta ~ contrast_hard + AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(choice_contrast_df2, ROI == "ACC"))
hard_effect_ACC <- summary(mod1b_ACC_h)$coefficients[1,]

mod1b_ACC_e <- lmer(beta ~ contrast_easy + AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(choice_contrast_df2, ROI == "ACC"))
easy_effect_ACC <- summary(mod1b_ACC_e)$coefficients[1,]
hard_minus_easy_effect_ACC <- summary(mod1b_ACC_e)$coefficients[2,]

# MPFC
mod1b_mPFC_h <- lmer(beta ~ contrast_hard + AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(choice_contrast_df2, ROI == "mPFC"))
hard_effect_mPFC <- summary(mod1b_mPFC_h)$coefficients[1,]

mod1b_mPFC_e <- lmer(beta ~ contrast_easy + AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(choice_contrast_df2, ROI == "mPFC"))
easy_effect_mPFC <- summary(mod1b_mPFC_e)$coefficients[1,]
hard_minus_easy_effect_mPFC <- summary(mod1b_mPFC_e)$coefficients[2,]

# VS  
mod1b_VS_h <- lmer(beta ~ contrast_hard + AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(choice_contrast_df2, ROI == "VS"))
hard_effect_VS <- summary(mod1b_VS_h)$coefficients[1,]

mod1b_VS_e <- lmer(beta ~ contrast_easy + AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(choice_contrast_df2, ROI == "VS"))
easy_effect_VS <- summary(mod1b_VS_e)$coefficients[1,]
hard_minus_easy_effect_VS <- summary(mod1b_VS_e)$coefficients[2,]

# combine tables 
table_choice_contrast_activation <- data.frame(rbind(
    hard_effect_ACC, easy_effect_ACC, hard_minus_easy_effect_ACC,
                       hard_effect_mPFC,  easy_effect_mPFC, hard_minus_easy_effect_mPFC,
  hard_effect_VS, easy_effect_VS, hard_minus_easy_effect_VS)) 
table_choice_contrast_activation$level <- rownames(table_choice_contrast_activation)

table_choice_contrast_activation <- table_choice_contrast_activation %>%
  rename(p_value = "Pr...t..", 
         SE = "Std..Error", 
         t_value = "t.value") %>%
  mutate( sig =  ifelse(p_value < 0.001, "***", ifelse(p_value < 0.01, "**", 
                                         ifelse(p_value< 0.05, "*", "")))) %>%
  select(level, Estimate, SE, df, t_value, p_value, sig)
table_choice_contrast_activation
save(table_choice_contrast_activation, file = "model_results/choice_contrast_activation_model_results.Rdata")
```


### Model 1c difference scores between easy & hard.  
```{r}
effect_df <- table_choice_contrast_activation %>%
  filter(grepl("Hard_minus_easy", level)) %>%
  mutate(ROI = ifelse(grepl("ACC", level), "ACC", 
                      ifelse(grepl("mPFC", level), "mPFC", "VS")))

# make subject by ROI df
names(choice_contrast_df2)
choice_contrast_diff_scores <- choice_contrast_df2 %>%
  group_by(SUBJECTID) %>%
  summarize(mPFC = mean(easy_hard_choice_mPFC),
           ACC = mean(easy_hard_choice_ACC), 
            VS = mean(easy_hard_VS)) %>%
  gather(key = ROI, value = easy_hard, mPFC, ACC, VS)



# so we can plot! 
plot_effect <- ggplot(data = effect_df, aes(x = ROI, y =Estimate)) + 
                        geom_bar(stat = "identity", position=position_dodge(),
fill = dark_blue, alpha = 0.25) + theme_classic() + ylim(-200, 200) + 
  geom_errorbar(aes(ymin = Estimate - 2*SE, ymax = Estimate + 2*SE),color = dark_blue, position=position_dodge(.9), width = 0.25) +
  geom_point(data =choice_contrast_diff_scores,  
            aes(x = ROI, y = easy_hard), position = position_dodge(.9),
             alpha = 0.25, color = dark_blue) + theme(legend.position = "none") +
  ylab("Reactivity for Easy vs. Hard Choices") + xlab ("ROI") + my_colors2 + my_colors + 
 geom_hline(yintercept=0, linetype="dashed",  size=.5)
plot_effect

pdf("figures/All_ROIs_Hard-Easy_Choice_diff_scores.pdf", width = 3, height = 4)
plot_effect
dev.off()

```