---
title: "Aim 1 Hypothesis 2 feedback phase"
author: "Michelle.VanTieghem"
date: "6/7/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

# Load data
## only behavior
from data_cleaning_for_analysis 
```{r}
source("../../0_R_analysis_setup_file.R", echo=F)

# wide version, by subject.
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_subj.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_subj_WSLS.Rdata")


# long version, by trial 
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_long.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_long_WSLS.Rdata")

```


## with scanning data 
from data_cleaning_for_analysis 
```{r}
# wide version, by subject.
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_wide.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_wide_WSLS.Rdata")

# long version, by trial 
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_long.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_long_WSLS.Rdata")

```


## Hypothesis 2:  Processing of positive and negative feedback will involve prefrontal regions (vmPFC, mPFC) and subcortical regions (amygdala, striatum).
In particular, we hypothesize that (a) ventral striatum response will be greater to rewards vs. setbacks and (b) amygdala response will be greater to setbacks vs. rewards and (c) differential responses in prefrontal regions to setbacks vs. rewards. Follow-up analyses will examine differences in feedback responses following Hard vs. Easy effort allocations.


### set up & clean data
```{r} 
FB_level_order <- c("vmPFC", "mPFC", "VS", "Amyg")

# get just reward ROIs
reward_df <- beh_scan_comp_wide %>%
  rename(Amyg = reward_Amyg,
         mPFC = reward_mPFC, 
         vmPFC = reward_vmPFC, 
         VS = reward_VS) %>%
  select(-starts_with("choice"), -starts_with("setback"), 
         -starts_with("feedback"), -starts_with("reward_setback")) %>%
  gather(key = "ROI", value = "reward_beta",  vmPFC, mPFC, VS, Amyg)

# get just setback ROIs
setback_df <- beh_scan_comp_wide %>%
   rename(Amyg = setback_Amyg, 
          vmPFC = setback_vmPFC, 
         mPFC = setback_mPFC, 
         VS = setback_VS) %>%
  select(-starts_with("choice"), -starts_with("setback"), 
         -starts_with("feedback"), -starts_with("setback_setback")) %>%
  gather(key = "ROI", value = "setback_beta",  vmPFC, mPFC, VS,  Amyg) %>%
  select(SUBJECTID, ROI, setback_beta)

# combine them in long format
FB_df <- merge(reward_df, setback_df, by = c("SUBJECTID", "ROI")) %>%
  mutate(reward_minus_setback = reward_beta - setback_beta,
  ROI = factor(ROI, levels = FB_level_order),
         AGE.c = AGE - mean(AGE, na.rm = T),
         SEX.c = SEX - mean(SEX, na.rm = T), 
         IQ.c = IQ- mean(IQ, na.rm = T),
         total_TRs_censored.c = total_TRs_censored - mean(total_TRs_censored, na.rm = T),
         Reinforce_rate.c = Reinforce_rate - mean(Reinforce_rate, na.rm = T)) %>%
  gather(key = "contrast", value = "beta", reward_beta, setback_beta, reward_minus_setback)

# rename levels of contrast factor
FB_df$contrast <- as.factor(ifelse(FB_df$contrast == "reward_beta", "reward", ifelse(FB_df$contrast == "setback_beta", "setback", FB_df$contrast)))
```

### plot before removing outliers
```{r}
ggplot(data = FB_df, aes(x = contrast, y = beta, color = contrast)) + 
  geom_point(position = position_dodge(.9),
             alpha = 0.25) + theme(legend.position = "none") +
    theme_bw() + facet_grid(~ROI) + my_colors + my_colors2 

```

### clean data
```{r}
# calculate limits fo routliers at 3SD from mean
FB_outliers <- FB_df %>%
  group_by(ROI, contrast) %>%
  summarize(outlier_upper = mean(beta) + 3*sd(beta), 
            outlier_lower = mean(beta)- 3*sd(beta))

# mark outliers for each ROI
FB_df2 <- data.frame()
for (region in unique(FB_outliers$ROI)){
  #region = "choice_mPFC"
  #print(region)
  for (cope in unique(FB_outliers$contrast)){
   # print(cope)
      #cope = "reward_minus_setback"
      check <- FB_df %>% filter(ROI == region & contrast == cope) %>%
      mutate(FB_outlier = ifelse(beta > FB_outliers$outlier_upper[FB_outliers$ROI == region & FB_outliers$contrast == cope] | 
                                 beta < FB_outliers$outlier_lower[FB_outliers$ROI == region & FB_outliers$contrast == cope], 1, 0))
      FB_df2 <- rbind(FB_df2, check)
  }
}

# look at outlier #
outlier_table <- FB_df2 %>%
  group_by(ROI, contrast) %>%
  summarize(n = n(), 
            n_outlier = sum(FB_outlier))
# idk why i ahve to do thsi!! 
outlier_table$n <- outlier_table$n 
outlier_table$n_outlier <- outlier_table$n_outlier

outlier_table
# remove data of outliers 
FB_df2 <- FB_df2 %>% 
  mutate(beta = ifelse(FB_outlier > 0 , NA, beta))
sum(is.na(FB_df2$beta))
FB_outlier_subjects <- FB_df2 %>% 
  filter(FB_outlier == 1) %>% select(SUBJECTID, ROI, contrast)

FB_outlier_subjects
save(FB_outlier_subjects, file = "tables/Feedback_betas_outlier_subjects.Rdata")
```


### Model 2 for vmPFC
```{r}
# repeated measures, with reward and setback as contrasts
mod2_vmPFC <- lmer(beta ~ contrast + #IQ.c + 
                     AGE.c + SEX.c + total_TRs_censored.c + Reinforce_rate.c + #Fam_inc_needs +
                  (1 | SUBJECTID),
                data = subset(FB_df2, contrast != "reward_minus_setback" & ROI == "vmPFC"))
summary(mod2_vmPFC)

```

### Model 2 for mPFC

```{r}
# repeated measures, with reward and setback as contrasts
mod2_mPFC <- lmer(beta ~ contrast + #IQ.c +
                    AGE.c + SEX.c + total_TRs_censored.c + Reinforce_rate.c + #Fam_inc_needs +
                  (1 | SUBJECTID),
                data = subset(FB_df2, contrast != "reward_minus_setback" & ROI == "mPFC"))
summary(mod2_mPFC)

```

### Model 2 for VS

```{r}
# repeated measures, with reward and setback as contrasts
mod2_VS <- lmer(beta ~ contrast + #IQ.c +
                    AGE.c + SEX.c + total_TRs_censored.c + Reinforce_rate.c + #Fam_inc_needs +
                  (1 | SUBJECTID),
                data = subset(FB_df2, contrast != "reward_minus_setback" & ROI == "VS"))
summary(mod2_VS)

```


### Model 2 for Amyg

```{r}
# repeated measures, with reward and setback as contrasts
mod2_amyg <- lmer(beta ~ contrast + #IQ.c +
                    AGE.c + SEX.c + total_TRs_censored.c + Reinforce_rate.c + #Fam_inc_needs +
                  (1 | SUBJECTID),
                data = subset(FB_df2, contrast != "reward_minus_setback" & ROI == "Amyg"))
summary(mod2_amyg)

```


### Model 2 plot for all ROIs

```{r}
FB_level_order <- c("vmPFC", "mPFC", "VS","Nacc", "Amyg")

effect_vmPFC <- data.frame(ROI = "vmPFC", effect("contrast", mod2_vmPFC, confint = T))
effect_mPFC  <- data.frame(ROI = "mPFC",effect("contrast", mod2_mPFC, confint = T))
effect_VS <- data.frame(ROI = "VS", effect("contrast", mod2_VS, confint = T))
effect_amyg <- data.frame(ROI = "Amyg",effect("contrast", mod2_amyg, confint = T))
# merge them all together into one df
effect_df <- rbind(effect_vmPFC, effect_mPFC, effect_VS,  effect_amyg)
# so we can plot! 
plot_effect <- ggplot(data = effect_df, aes(x = contrast, y = fit, fill = contrast)) + 
                        geom_bar(stat = "identity", position=position_dodge(),
alpha = 0.5) + theme_classic() + facet_grid (~ ROI) +
  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_point(data = subset(FB_df2, contrast != "reward_minus_setback"), 
            aes(x = contrast, y = beta, color = contrast), position = position_dodge(.9),
             alpha = 0.25) + theme(legend.position = "none") +
  
 # geom_line(data =subset(FB_df, contrast != "reward_minus_setback"), 
  #          aes(x = contrast, y = beta, color = contrast, group = SUBJECTID), alpha = 0.2) + 
  ylab("Reactivity during Feedback Phase") + xlab ("Feedback") + my_colors2 + my_colors + 
 geom_hline(yintercept=0, linetype="dashed",  size=.5)
plot_effect

pdf("figures/All_ROIs_Reward_Setback.pdf", width = 6, height = 3)
plot_effect
dev.off()

```

### Model 2 table for all ROIs

re-level ROIs to get results for each ROI
```{r}
FB_df2 <- FB_df2 %>%
  mutate(ROI_vmPFC = relevel(ROI, "vmPFC"),
         ROI_mPFC = relevel(ROI, "mPFC"),
         ROI_VS = relevel(ROI, "VS"),
         ROI_Amyg = relevel(ROI, "Amyg"), 
         contrast_reward = relevel(contrast, "reward"), 
         contrast_setback = relevel(contrast, "setback"))
 
# vmPFC
mod2_vmPFC_r <- lmer(beta ~ contrast_reward + AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(FB_df2, contrast != "reward_minus_setback" & ROI == "vmPFC"))
reward_effect_vmPFC <- summary(mod2_vmPFC_r)$coefficients[1,]

mod2_vmPFC_s <- lmer(beta ~ contrast_setback + AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(FB_df2, contrast != "reward_minus_setback" & ROI == "vmPFC"))
setback_effect_vmPFC <- summary(mod2_vmPFC_s)$coefficients[1,]
reward_minus_setback_effect_vmPFC <- summary(mod2_vmPFC_s)$coefficients[2,]

# MPFC
mod2_mPFC_r <- lmer(beta ~ contrast_reward + AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(FB_df2, contrast != "reward_minus_setback" & ROI == "mPFC"))
reward_effect_mPFC <- summary(mod2_mPFC_r)$coefficients[1,]

mod2_mPFC_s <- lmer(beta ~ contrast_setback +  AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(FB_df2, contrast != "reward_minus_setback" & ROI == "mPFC"))
setback_effect_mPFC <- summary(mod2_mPFC_s)$coefficients[1,]
reward_minus_setback_effect_mPFC <- summary(mod2_mPFC_s)$coefficients[2,]

# AMYGDALA
mod2_Amyg_r <- lmer(beta ~ contrast_reward + AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(FB_df2, contrast != "reward_minus_setback" & ROI == "Amyg"))
reward_effect_Amyg <- summary(mod2_Amyg_r)$coefficients[1,]
# get effect when Amyg is reference ROI and setback is reference contrast
mod2_Amyg_s <- lmer(beta ~ contrast_setback +  AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(FB_df2, contrast != "reward_minus_setback" & ROI == "Amyg"))
setback_effect_Amyg <- summary(mod2_Amyg_s)$coefficients[1,]
reward_minus_setback_effect_Amyg <- summary(mod2_Amyg_s)$coefficients[2,]

# VS  
mod2_VS_r <- lmer(beta ~ contrast_reward+  AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(FB_df2, contrast != "reward_minus_setback"& ROI == "VS"))
reward_effect_VS <- summary(mod2_VS_r)$coefficients[1,]
# get effect when VS is reference ROI and setback is reference contrast
mod2_VS_s <- lmer(beta ~ contrast_setback +  AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(FB_df2, contrast != "reward_minus_setback" & ROI == "VS"))
setback_effect_VS <- summary(mod2_VS_s)$coefficients[1,]
reward_minus_setback_effect_VS <- summary(mod2_VS_s)$coefficients[2,]

table_FB_activation <- data.frame(rbind(
  reward_effect_vmPFC,  setback_effect_vmPFC, reward_minus_setback_effect_vmPFC,
                       reward_effect_mPFC,  setback_effect_mPFC, reward_minus_setback_effect_mPFC,
  reward_effect_VS,setback_effect_VS,reward_minus_setback_effect_VS,
                                        reward_effect_Amyg,setback_effect_Amyg,reward_minus_setback_effect_Amyg)) 
table_FB_activation$level <- rownames(table_FB_activation)

table_FB_activation <- table_FB_activation %>%
  rename(p_value = "Pr...t..", 
         SE = "Std..Error", 
         t_value = "t.value") %>%
  mutate( sig =  ifelse(p_value < 0.001, "***", ifelse(p_value < 0.01, "**", 
                                         ifelse(p_value< 0.05, "*", "")))) %>%
  select(level, Estimate, SE, df, t_value, p_value, sig)
table_FB_activation
save(table_FB_activation, file = "model_results/feedback_activation_model_results.Rdata")
```

## Hypothesis 2 Follow-up model: reactivity to hard setbacks vs. hard rewards 

### set up & clean data
```{r} 
names(beh_scan_comp_wide %>% select(contains("Hard")))

#organize data for choice phase.
hard_FB_contrast_df <- beh_scan_comp_wide %>%
  # combine left and right accumbens betas into bilateral! 
  select(-starts_with("feedback"),  -contains("easy"), -contains("choice")) %>%
  gather(key = "ROI", value = "beta", 
         hard_reward_FB_vmPFC, hard_setback_FB_vmPFC, hard_reward_setback_FB_vmPFC,
         hard_reward_FB_mPFC, hard_setback_FB_mPFC, hard_reward_setback_FB_mPFC,
         hard_reward_VS, hard_setback_VS, hard_reward_setback_VS,
                  hard_reward_Amyg, hard_setback_Amyg, hard_reward_setback_Amyg) %>%
  mutate(
           contrast = as.factor(ifelse(grepl("reward_setback", ROI), "reward_setback",
                           ifelse(grepl("reward", ROI), "reward", "setback"))),
           ROI = as.factor(ifelse(grepl("vmPFC", ROI), "vmPFC", 
                        ifelse(grepl("mPFC", ROI), "mPFC",
                               ifelse(grepl("VS", ROI), "VS", "Amyg")))),
           AGE.c = AGE - mean(AGE, na.rm = T),
         SEX.c = SEX - mean(SEX, na.rm = T), 
         IQ.c = IQ- mean(IQ, na.rm = T),
         total_TRs_censored.c = total_TRs_censored - mean(total_TRs_censored, na.rm = T),
         Reinforce_rate.c = Reinforce_rate - mean(Reinforce_rate, na.rm = T))
summary(as.factor(hard_FB_contrast_df$ROI))
summary(as.factor(hard_FB_contrast_df$contrast))
nrow(hard_FB_contrast_df)

# number of subjects
length(unique(hard_FB_contrast_df$SUBJECTID[!is.na(hard_FB_contrast_df$hard_setback_reward_FB_mPFC)]))

```

### plot before removing outliers
```{r}
ggplot(data = hard_FB_contrast_df, aes(x = contrast, y = beta, color = contrast)) + 
  geom_point(position = position_dodge(.9),
             alpha = 0.25) + theme(legend.position = "none") +
    theme_bw() + facet_grid(~ROI) + my_colors + my_colors2 

```

### clean data
```{r}
# calculate limits fo routliers at 3SD from mean
hard_FB_outliers <- hard_FB_contrast_df %>%
  filter(!is.na(beta)) %>%
  group_by(ROI, contrast) %>%
  summarize(outlier_upper = mean(beta) + 3*sd(beta), 
            outlier_lower = mean(beta)- 3*sd(beta))

# mark outliers for each ROI
hard_FB_contrast_df2 <- data.frame()
for (region in unique(FB_outliers$ROI)){
  #region = "choice_mPFC"
  #print(region)
  for (cope in unique(FB_outliers$contrast)){
   # print(cope)
      #cope = "reward_minus_setback"
      check <- hard_FB_contrast_df %>% filter(ROI == region & contrast == cope) %>%
      mutate(FB_outlier = ifelse(beta > FB_outliers$outlier_upper[FB_outliers$ROI == region & FB_outliers$contrast == cope] | 
                                 beta < FB_outliers$outlier_lower[FB_outliers$ROI == region & FB_outliers$contrast == cope], 1, 0))
      hard_FB_contrast_df2 <- rbind(hard_FB_contrast_df2, check)
  }
}

# look at outlier #
hard_FB_outlier_table <- hard_FB_contrast_df2 %>%
  filter(!is.na(beta)) %>%
  group_by(ROI, contrast) %>%
  summarize(n = n(), 
            n_outlier = sum(FB_outlier))
# idk why i ahve to do thsi!! 
hard_FB_outlier_table$n <- hard_FB_outlier_table$n 
hard_FB_outlier_table$n_outlier <- hard_FB_outlier_table$n_outlier

hard_FB_outlier_table
# remove data of outliers 
hard_FB_contrast_df2 <- hard_FB_contrast_df2 %>% 
  filter(!is.na(beta)) %>%
  mutate(beta = ifelse(FB_outlier > 0 , NA, beta))
sum(is.na(hard_FB_contrast_df2$beta))
hard_FB_outlier_subjects <- hard_FB_contrast_df2 %>% 
  filter(FB_outlier == 1) %>% select(SUBJECTID, ROI, contrast)

hard_FB_outlier_subjects
save(hard_FB_outlier_subjects, file = "tables/hard_FB_contrast_betas_outlier_subjects.Rdata")
```


### Model 2b for vmPFC 

```{r}
summary(hard_FB_contrast_df2$contrast)
# repeated measures, with reward and setback as contrasts
mod2b_vmPFC <- lmer(beta ~ contrast + #IQ.c +
                    AGE.c + SEX.c + total_TRs_censored.c + Reinforce_rate.c + #Fam_inc_needs +
                  (1 | SUBJECTID),
                data = subset(hard_FB_contrast_df2, contrast != "reward_setback" & ROI == "vmPFC"))
summary(mod2b_vmPFC)

```

### Model 2b for mPFC 

```{r}
summary(hard_FB_contrast_df2$contrast)
# repeated measures, with reward and setback as contrasts
mod2b_mPFC <- lmer(beta ~ contrast + #IQ.c +
                    AGE.c + SEX.c + total_TRs_censored.c + Reinforce_rate.c + #Fam_inc_needs +
                  (1 | SUBJECTID),
                data = subset(hard_FB_contrast_df2, contrast != "reward_setback" & ROI == "mPFC"))
summary(mod2b_mPFC)
```

```{r}
# repeated measures, with reward and setback as contrasts
mod2b_VS <- lmer(beta ~ contrast + #IQ.c +
                    AGE.c + SEX.c + total_TRs_censored.c + Reinforce_rate.c + #Fam_inc_needs +
                  (1 | SUBJECTID),
                data = subset(hard_FB_contrast_df2,contrast != "reward_setback" &  ROI == "VS"))
summary(mod2b_VS)
```

### Model 2b for Amyg
```{r}
# repeated measures, with reward and setback as contrasts
mod2b_Amyg <- lmer(beta ~ contrast + #IQ.c +
                    AGE.c + SEX.c + total_TRs_censored.c + Reinforce_rate.c + #Fam_inc_needs +
                  (1 | SUBJECTID),
                data = subset(hard_FB_contrast_df2, contrast != "reward_setback" &  ROI == "Amyg"))
summary(mod2b_Amyg)
```


### Model 2 plot for all ROIs

```{r}
FB_level_order <- c("vmPFC", "mPFC", "VS", "Amyg")

effect_vmPFC <- data.frame(ROI = "vmPFC", effect("contrast", mod2b_vmPFC, confint = T))
effect_mPFC  <- data.frame(ROI = "mPFC",effect("contrast", mod2b_mPFC, confint = T))
effect_VS <- data.frame(ROI = "VS", effect("contrast", mod2b_VS, confint = T))
effect_amyg <- data.frame(ROI = "Amyg",effect("contrast", mod2b_Amyg, confint = T))
# merge them all together into one df
effect_df <- rbind(effect_vmPFC, effect_mPFC, effect_VS,  effect_amyg)
# so we can plot! 
plot_effect <- ggplot(data = effect_df, aes(x = contrast, y = fit, fill = contrast)) + 
                        geom_bar(stat = "identity", position=position_dodge(),
alpha = 0.5) + theme_classic() + facet_grid (~ ROI) +
  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_point(data = subset(hard_FB_contrast_df2, contrast != "reward_setback"), 
            aes(x = contrast, y = beta, color = contrast), position = position_dodge(.9),
             alpha = 0.25) + theme(legend.position = "none") +
  ylab("Reactivity to hard trial feedback") + xlab ("Feedback") + my_colors2 + my_colors + 
 geom_hline(yintercept=0, linetype="dashed",  size=.5)
plot_effect

pdf("figures/All_ROIs_Hard_Reward_Setback.pdf", width = 6, height = 4)
plot_effect
dev.off()

```

### Model 2 table for all ROIs

re-level ROIs to get results for each ROI
```{r}
hard_FB_contrast_df2 <- hard_FB_contrast_df2 %>%
  mutate(ROI_vmPFC = relevel(ROI, "vmPFC"),
         ROI_mPFC = relevel(ROI, "mPFC"),
         ROI_VS = relevel(ROI, "VS"),
         ROI_Amyg = relevel(ROI, "Amyg"), 
         contrast_reward = relevel(contrast, "reward"), 
         contrast_setback = relevel(contrast, "setback"))
 
# vmPFC
mod2_hard_FB_vmPFC_r <- lmer(beta ~ contrast_reward + AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(hard_FB_contrast_df2, contrast != "reward_minus_setback" & ROI == "vmPFC"))
reward_effect_vmPFC <- summary(mod2_hard_FB_vmPFC_r)$coefficients[1,]

mod2_hard_FB_vmPFC_s <- lmer(beta ~ contrast_setback + AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(hard_FB_contrast_df2, contrast != "reward_minus_setback" & ROI == "vmPFC"))
setback_effect_vmPFC <- summary(mod2_hard_FB_vmPFC_s)$coefficients[1,]
reward_minus_setback_effect_vmPFC <- summary(mod2_hard_FB_vmPFC_s)$coefficients[2,]

# MPFC
mod2_hard_FB_mPFC_r <- lmer(beta ~ contrast_reward + AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(hard_FB_contrast_df2, contrast != "reward_minus_setback" & ROI == "mPFC"))
reward_effect_mPFC <- summary(mod2_hard_FB_mPFC_r)$coefficients[1,]

mod2_hard_FB_mPFC_s <- lmer(beta ~ contrast_setback +  AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(hard_FB_contrast_df2, contrast != "reward_minus_setback" & ROI == "mPFC"))
setback_effect_mPFC <- summary(mod2_hard_FB_mPFC_s)$coefficients[1,]
reward_minus_setback_effect_mPFC <- summary(mod2_hard_FB_mPFC_s)$coefficients[2,]

# AMYGDALA
mod2_hard_FB_Amyg_r <- lmer(beta ~ contrast_reward + AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(hard_FB_contrast_df2, contrast != "reward_minus_setback" & ROI == "Amyg"))
reward_effect_Amyg <- summary(mod2_hard_FB_Amyg_r)$coefficients[1,]
# get effect when Amyg is reference ROI and setback is reference contrast
mod2_hard_FB_Amyg_s <- lmer(beta ~ contrast_setback +  AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(hard_FB_contrast_df2, contrast != "reward_minus_setback" & ROI == "Amyg"))
setback_effect_Amyg <- summary(mod2_hard_FB_Amyg_s)$coefficients[1,]
reward_minus_setback_effect_Amyg <- summary(mod2_hard_FB_Amyg_s)$coefficients[2,]

# VS  
mod2_hard_FB_VS_r <- lmer(beta ~ contrast_reward+  AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(hard_FB_contrast_df2, contrast != "reward_minus_setback"& ROI == "VS"))
reward_effect_VS <- summary(mod2_hard_FB_VS_r)$coefficients[1,]
# get effect when VS is reference ROI and setback is reference contrast
mod2_hard_FB_VS_s <- lmer(beta ~ contrast_setback +  AGE.c + SEX.c + 
                       total_TRs_censored.c + Reinforce_rate.c + 
                  (1 | SUBJECTID),
                data = subset(hard_FB_contrast_df2, contrast != "reward_minus_setback" & ROI == "VS"))
setback_effect_VS <- summary(mod2_hard_FB_VS_s)$coefficients[1,]
reward_minus_setback_effect_VS <- summary(mod2_hard_FB_VS_s)$coefficients[2,]

table_hard_FB_activation <- data.frame(rbind(
  reward_effect_vmPFC,  setback_effect_vmPFC, reward_minus_setback_effect_vmPFC,
                       reward_effect_mPFC,  setback_effect_mPFC, reward_minus_setback_effect_mPFC,
  reward_effect_VS,setback_effect_VS,reward_minus_setback_effect_VS,
                                        reward_effect_Amyg,setback_effect_Amyg,reward_minus_setback_effect_Amyg)) 
table_hard_FB_activation$level <- rownames(table_hard_FB_activation)

table_hard_FB_activation <- table_hard_FB_activation %>%
  rename(p_value = "Pr...t..", 
         SE = "Std..Error", 
         t_value = "t.value") %>%
  mutate( sig =  ifelse(p_value < 0.001, "***", ifelse(p_value < 0.01, "**", 
                                         ifelse(p_value< 0.05, "*", "")))) %>%
  select(level, Estimate, SE, df, t_value, p_value, sig)
table_hard_FB_activation
save(table_hard_FB_activation, file = "model_results/hard_FB_activation_model_results.Rdata")
```

