---
title: "Aim2 Hypothesis 3 choice phase"
author: "Michelle.VanTieghem"
date: "6/7/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---


# Load data
## only behavior
from data_cleaning_for_analysis 
```{r}
source("../../0_R_analysis_setup_file.R", echo=F)

# wide version, by subject.
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_subj.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_subj_WSLS.Rdata")


# long version, by trial 
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_long.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_long_WSLS.Rdata")

```


## with scanning data 
from data_cleaning_for_analysis 
```{r}
# wide version, by subject.
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_wide.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_wide_WSLS.Rdata")

# long version, by trial 
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_long.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_long_WSLS.Rdata")

```

# Aim 2: Brain-behavior relationships
We will examine how neural circuitry relates to behavior in the task at the between- subject level. \
Aim 2a: First, we will examine whether children’s effort based motivation differs as a function of fronto-striatal circuitry during decision-making. \
Aim 2b: Second, we will examine how reactivity to feedback (reward, setback) is associated with children’s effort-based decision-making. \

### remove outliers from this data first! 
removing entire subjects from data frame
```{r}

beh_scan_comp_wide <- beh_scan_comp_wide %>%
  filter(! SUBJECTID %in% choice_outlier_subjects$SUBJECTID) %>%
  filter(! SUBJECTID %in% FB_outlier_subjects$SUBJECTID)
nrow(beh_scan_comp_wide)
```


## Hypothesis 3: Greater fronto- striatal modulation during the choice phase will be associated with a greater proportion of hard- effort choices

### mod 3 wide version 

#### ACC: NS

```{r}
mod3_ACC <- lm(prop_hard_choices ~ choice_ACC  +# IQ + Fam_inc_needs +  
            AGE.c + SEX.c + total_TRs_censored + Reinforce_rate.c,
           data = beh_scan_comp_wide)
summary(mod3_ACC)
```


#### mPFC : NS
```{r}
mod3_mPFC <- lm(prop_hard_choices ~ choice_mPFC  + #IQ +Fam_inc_needs + 
            AGE + SEX + total_TRs_censored + Reinforce_rate,
           data = beh_scan_comp_wide)
summary(mod3_mPFC)
```

#### VS: NS
```{r}
mod3_VS <- lm(prop_hard_choices ~ choice_VS + #+ IQ +Fam_inc_needs + 
            AGE + SEX, # + total_TRs_censored + Reinforce_rate,
           data = beh_scan_comp_wide)
summary(mod3_VS)
```


### include all ROIs, controlling for others?  all NS.
```{r}
mod3_all <- lm(prop_hard_choices ~ choice_VS + choice_mPFC + choice_ACC + #IQ + Fam_inc_needs + 
            AGE + SEX + total_TRs_censored + Reinforce_rate,
           data = beh_scan_comp_wide)
summary(mod3_all)

```

### long versions run with brms:
run in "COMP_prereg_brms_part1.R"
```{r}

load("brms_models/preregistration_model_results/mod3_ACC_long_brms.Rdata")
load("brms_models/preregistration_model_results/mod3_mPFC_long_brms.Rdata")
load("brms_models/preregistration_model_results/mod3_VS_long_brms.Rdata")
```

model output loaded here.

#### ACC: NS
```{r}
print(mod3_ACC_long_brms, digits = 4)
```


#### mPFC: NS
```{r}
print(mod3_mPFC_long_brms, digits = 4)
```


#### VS: NS
```{r}
print(mod3_VS_long_brms, digits = 4)
```

