---
title: "Aim 2 Hypothesis 4 - reward and beahvior"
author: "Michelle.VanTieghem"
date: "6/7/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---


# Load data
## only behavior
from data_cleaning_for_analysis 
```{r}
source("../../0_R_analysis_setup_file.R", echo=F)

# wide version, by subject.
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_subj.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_subj_WSLS.Rdata")


# long version, by trial 
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_long.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_long_WSLS.Rdata")

```


## with scanning data 
from data_cleaning_for_analysis 
```{r}
# wide version, by subject.
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_wide.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_wide_WSLS.Rdata")

# long version, by trial 
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_long.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_long_WSLS.Rdata")

```
### remove outliers from this data first! 
removing entire subjects from data frame
```{r}

beh_scan_comp_wide <- beh_scan_comp_wide %>%
  filter(! SUBJECTID %in% choice_outlier_subjects$SUBJECTID) %>%
  filter(! SUBJECTID %in% FB_outlier_subjects$SUBJECTID)
nrow(beh_scan_comp_wide)
```


## Hypothesis 4: Greater striatal response to rewards will be associated with a greater proportion of hard-effort choices.
Do between subject differences in reactivity to rewards relate to proportion of hard- effort choices? 

### Model 4 wide version
#### VS: NS
```{r}
mod4_VS <- lm(prop_hard_choices ~ reward_setback_VS + # + IQ + Fam_inc_needs +
            AGE + SEX + total_TRs_censored + Reinforce_rate,
           data = beh_scan_comp_wide)
summary(mod4_VS)

```


### VS reward vs. setback all trials, long version brms: NS
loaded from COMP_brms_preregistration_analyses2.R 

```{r}
### Reward vs. setbacks all trials
load("brms_models/preregistration_model_results/mod4_VS_long_brms.Rdata")
print(mod4_VS_long_brms, digits = 4)
```

### VS rewards vs. hard setbacks - hard only
```{r}
load("brms_models/preregistration_model_results/mod4_hard_VS_long_brms.Rdata")
print(mod4_hard_VS_long_brms, digits = 4)
```


### VS hard rewards only 
```{r}
load("brms_models/preregistration_model_results/mod4_hard_reward_VS_long_brms.Rdata")
print(mod4_hard_reward_VS_long_brms, digits = 4)
```


### VS hard setbacks only
```{r}
load("brms_models/preregistration_model_results/mod4_hard_setback_VS_long_brms.Rdata")
print(mod4_hard_setback_VS_long_brms, digits = 4)
```

### Follow-ups with other regions: NS
vmPFC: NS
```{r}
load("brms_models/preregistration_model_results/mod4_vmPFC_long_brms.Rdata")
print(mod4_vmPFC_long_brms, digits = 4)
```

mPFC: NS
```{r}
load("brms_models/preregistration_model_results/mod4_mPFC_long_brms.Rdata")
print(mod4_mPFC_long_brms, digits = 4)
```

Amyg: NS
```{r}
load("brms_models/preregistration_model_results/mod4_amyg_long_brms.Rdata")
print(mod4_Amyg_long_brms, digits = 4)
```

