---
title: "Aim 2 Hypothesis 5 - setback and behavior"
author: "Michelle.VanTieghem"
date: "6/7/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---


# Load data
## only behavior
from data_cleaning_for_analysis 
```{r}
source("../../0_R_analysis_setup_file.R", echo=F)

# wide version, by subject.
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_subj.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_subj_WSLS.Rdata")


# long version, by trial 
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_long.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_comp_long_WSLS.Rdata")

```


## with scanning data 
from data_cleaning_for_analysis 
```{r}
# wide version, by subject.
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_wide.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_wide_WSLS.Rdata")

# long version, by trial 
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_long.Rdata")
load("../../2_cleaning_QC/cleaned_data/COMPS_ONLY/beh_scan_comp_long_WSLS.Rdata")

```

## Hypothesis 5: The degree of prefrontal modulation in response to setbacks will correspond to lose-stay decision- making strategies 
(i.e. choosing hard again immediately following a hard setback).
Does prefrontal modulation to hard-effort setbacks predict whether subjects show more lose-stay behavior? 
(i.e. subjects who pick hard again after a hard-effort setback)

###  remove outliers 
```{r}
# long version, by trial for WSLS
beh_scan_comp_long_WSLS <- beh_scan_comp_long_WSLS %>%
  filter(SUBJECTID != "PA067") %>%
# choice outlier subjects
    mutate(choice_ACC = ifelse(SUBJECTID %in% choice_outlier_subjects$SUBJECTID[choice_outlier_subjects$ROI == "ACC"], NA, choice_ACC), 
         choice_VS = ifelse(SUBJECTID %in% choice_outlier_subjects$SUBJECTID[choice_outlier_subjects$ROI == "VS"], NA, choice_VS),
         choice_mPFC = ifelse(SUBJECTID %in% choice_outlier_subjects$SUBJECTID[choice_outlier_subjects$ROI == "mPFC"], NA, choice_mPFC),
         
         # FB outlier subjects
         reward_vmPFC = ifelse(SUBJECTID %in% FB_outlier_subjects$SUBJECTID[FB_outlier_subjects$ROI == "vmPFC"], NA, reward_vmPFC),
         reward_setback_vmPFC = ifelse(SUBJECTID %in% FB_outlier_subjects$SUBJECTID[FB_outlier_subjects$ROI == "vmPFC"], NA, reward_setback_vmPFC),
         
         reward_mPFC = ifelse(SUBJECTID %in% FB_outlier_subjects$SUBJECTID[FB_outlier_subjects$ROI == "mPFC"], NA, reward_mPFC),
         reward_setback_mPFC = ifelse(SUBJECTID %in% FB_outlier_subjects$SUBJECTID[FB_outlier_subjects$ROI == "mPFC"], NA, reward_setback_mPFC),
         
         reward_VS = ifelse(SUBJECTID %in% FB_outlier_subjects$SUBJECTID[FB_outlier_subjects$ROI == "VS"], NA, reward_VS),
         reward_setback_VS = ifelse(SUBJECTID %in% FB_outlier_subjects$SUBJECTID[FB_outlier_subjects$ROI == "VS"], NA, reward_setback_VS),
         
         reward_Amyg  = ifelse(SUBJECTID %in% FB_outlier_subjects$SUBJECTID[FB_outlier_subjects$ROI == "Amyg"], NA, reward_Amyg),
         reward_setback_Amyg = ifelse(SUBJECTID %in% FB_outlier_subjects$SUBJECTID[FB_outlier_subjects$ROI == "Amyg"], NA, reward_setback_Amyg))
```


### make wide version of data 
```{r, include = F}

WSLS_by_subj_condition <- beh_scan_comp_long_WSLS %>%
                # removing PA067 becayse they are outlier for all feedback phase beh_scan_comp_long <- beh_scan_comp_long %>%
  # removing PA067 becayse they are outlier for all feedback phase 
  filter(SUBJECTID != "PA067") %>%
# choice outlier subjects
    mutate(choice_ACC = ifelse(SUBJECTID %in% choice_outlier_subjects$SUBJECTID[choice_outlier_subjects$ROI == "ACC"], NA, choice_ACC), 
         choice_VS = ifelse(SUBJECTID %in% choice_outlier_subjects$SUBJECTID[choice_outlier_subjects$ROI == "VS"], NA, choice_VS),
         choice_mPFC = ifelse(SUBJECTID %in% choice_outlier_subjects$SUBJECTID[choice_outlier_subjects$ROI == "mPFC"], NA, choice_mPFC),
         
         # FB outlier subjects
         reward_vmPFC = ifelse(SUBJECTID %in% FB_outlier_subjects$SUBJECTID[FB_outlier_subjects$ROI == "vmPFC"], NA, reward_vmPFC),
         reward_setback_vmPFC = ifelse(SUBJECTID %in% FB_outlier_subjects$SUBJECTID[FB_outlier_subjects$ROI == "vmPFC"], NA, reward_setback_vmPFC),
         
         reward_mPFC = ifelse(SUBJECTID %in% FB_outlier_subjects$SUBJECTID[FB_outlier_subjects$ROI == "mPFC"], NA, reward_mPFC),
         reward_setback_mPFC = ifelse(SUBJECTID %in% FB_outlier_subjects$SUBJECTID[FB_outlier_subjects$ROI == "mPFC"], NA, reward_setback_mPFC),
         
         reward_VS = ifelse(SUBJECTID %in% FB_outlier_subjects$SUBJECTID[FB_outlier_subjects$ROI == "VS"], NA, reward_VS),
         reward_setback_VS = ifelse(SUBJECTID %in% FB_outlier_subjects$SUBJECTID[FB_outlier_subjects$ROI == "VS"], NA, reward_setback_VS),
         
         reward_Amyg  = ifelse(SUBJECTID %in% FB_outlier_subjects$SUBJECTID[FB_outlier_subjects$ROI == "Amyg"], NA, reward_Amyg),
         reward_setback_Amyg = ifelse(SUBJECTID %in% FB_outlier_subjects$SUBJECTID[FB_outlier_subjects$ROI == "Amyg"], NA, reward_setback_Amyg),
         
         # hard FB contrast outlier subjects
         hard_setback_vmPFC  = ifelse(SUBJECTID %in% hard_FB_outlier_subjects$SUBJECTID[hard_FB_outlier_subjects$ROI == "vmPFC"], NA, hard_setback_FB_vmPFC),
         hard_reward_mPFC = ifelse(SUBJECTID %in% hard_FB_outlier_subjects$SUBJECTID[hard_FB_outlier_subjects$ROI == "mPFC"], NA, hard_reward_FB_mPFC)) %>%
# now make 4 rows per subject for each WSLS condition
  group_by(SUBJECTID, Effort_Choice_prior, Feedback_prior) %>%
  summarize(N_trials_per_cond = n(),
             prop_stay = mean(stay_shift, na.rm= T), 
            Reinforce_hard = mean(Reinforce_hard),
            prop_hard_choices = mean(proportion_hard),
            reward_Amyg = mean(reward_Amyg), 
            reward_VS = mean(reward_VS), 
            reward_mPFC = mean(reward_mPFC), 
            reward_vmPFC = mean(reward_vmPFC),
            setback_Amyg = mean(setback_Amyg), 
            setback_VS = mean(setback_VS), 
            setback_mPFC = mean(setback_mPFC), 
            setback_vmPFC = mean(setback_vmPFC),
            reward_setback_Amyg = mean(reward_setback_Amyg), 
            reward_setback_VS = mean(reward_setback_VS), 
            reward_setback_mPFC = mean(reward_setback_mPFC), 
            reward_setback_vmPFC = mean(reward_setback_vmPFC),
            # hard choices only
            hard_reward_Amyg = mean(hard_reward_Amyg), 
            hard_reward_VS = mean(hard_reward_VS), 
            hard_reward_mPFC = mean(hard_reward_FB_mPFC), 
            hard_reward_vmPFC = mean(hard_reward_FB_vmPFC),
            hard_setback_Amyg = mean(hard_setback_Amyg), 
            hard_setback_VS = mean(hard_setback_VS), 
            hard_setback_mPFC = mean(hard_setback_FB_mPFC), 
            hard_setback_vmPFC = mean(hard_setback_FB_vmPFC),
            hard_reward_setback_Amyg = mean(hard_reward_setback_Amyg), 
            hard_reward_setback_VS = mean(hard_reward_setback_VS), 
            hard_reward_setback_mPFC = mean(hard_reward_setback_FB_mPFC), 
            hard_reward_setback_vmPFC = mean(hard_reward_setback_FB_vmPFC),
            # covariates
            IQ.c = mean(IQ.c), 
            SEX.c = mean(SEX.c), 
            AGE.c = mean(AGE.c), 
            Reinforce_rate.c = mean(Reinforce_rate), 
            perceived_control = mean(perceived_control), 
            frustrated = mean(frustrated), 
            motivated = mean(motivated), 
            win_feeling = mean(win_feeling), 
            lose_feeling = mean(lose_feeling), 
            perceived_reinforce = mean(perceived_reinforce)) 

save(WSLS_by_subj_condition, file= "../../2_cleaning_QC/cleaned_data//WSLS_by_subj_condition.Rdata")

WSLS_summary_hard_setback <- subset(WSLS_by_subj_condition, Feedback_prior == "Setback" & Effort_Choice_prior == "Hard")
nrow(WSLS_summary_hard_setback)

```

## Hypothesis 5: with hard setback only [subset of participants!!].
### wide version

#### mPFC: NS
```{r}
WSLS_mPFC_hard_setbacks <- lm(prop_stay ~ hard_setback_mPFC + N_trials_per_cond + Reinforce_rate.c + 
                                        SEX.c + AGE.c, 
                              data = WSLS_summary_hard_setback)
summary(WSLS_mPFC_hard_setbacks)
```


### long version with brms: NS
```{r}
load("brms_models/preregistration_model_results/mod5_WSLS_mPFC_long_hard_setbacks.Rdata")
print(WSLS_mPFC_long_brms_hard_setbacks, digits = 5)

```


#### vmPFC: NS 
```{r}
WSLS_vmPFC_hard_setbacks <- lm(prop_stay ~ hard_setback_vmPFC + N_trials_per_cond + Reinforce_rate.c +  
                                         SEX.c + AGE.c, 
                              data = WSLS_summary_hard_setback)
summary(WSLS_vmPFC_hard_setbacks)
```


### long version with brms: NS
```{r}
load("brms_models/preregistration_model_results/mod5_WSLS_vmPFC_long_hard_setbacks.Rdata")
print(WSLS_vmPFC_long_brms_hard_setbacks, digits = 5)

```


## Hypothesis 5: with hard reward-setback contrast 

#### mPFC: NS 
```{r}
WSLS_mPFC_hard_reward_setbacks <- lm(prop_stay ~ hard_reward_setback_mPFC + N_trials_per_cond + Reinforce_rate.c +  
                                         SEX.c + AGE.c, 
                              data = WSLS_summary_hard_setback)
summary(WSLS_mPFC_hard_reward_setbacks)
```

#### brms long version
```{r}
load("brms_models/preregistration_model_results/mod5_WSLS_mPFC_long_hard_reward_setback.Rdata")
print(WSLS_mPFC_long_brms_hard_reward_setback, digits = 5)
```

#### vmPFC: NS 
```{r}
WSLS_vmPFC_hard_reward_setbacks <- lm(prop_stay ~ hard_reward_setback_vmPFC + N_trials_per_cond + Reinforce_rate.c +  
                                         SEX.c + AGE.c, 
                              data = WSLS_summary_hard_setback)
summary(WSLS_vmPFC_hard_reward_setbacks)
```

#### brms long version
```{r}
load("brms_models/preregistration_model_results/mod5_WSLS_vmPFC_long_hard_reward_setback.Rdata")
print(WSLS_vmPFC_long_brms_hard_reward_setback, digits = 5)
```


## Hypothesis 5: all setback trials (hard + easy)
### wide version

#### mPFC: TREND
```{r}
WSLS_mPFC_all_setbacks <- lm(prop_stay ~ setback_mPFC + N_trials_per_cond + Reinforce_rate.c, #+
                              # SEX.c + AGE.c,
                              data = WSLS_summary_hard_setback)
summary(WSLS_mPFC_all_setbacks)
```

#### brms version
```{r}
load("brms_models/preregistration_model_results/mod5_WSLS_mPFC_long_all_setbacks.Rdata")
print(WSLS_mPFC_long_brms_all_setbacks, digits = 5)
```

#### vmPFC: NS
```{r}
WSLS_vmPFC_all_setbacks <- lm(prop_stay ~ setback_vmPFC + N_trials_per_cond + Reinforce_rate.c + 
                                          SEX.c + AGE.c, 
                              data = WSLS_summary_hard_setback)
summary(WSLS_vmPFC_all_setbacks)
```

#### long version with brms
```{r}
load("brms_models/preregistration_model_results/mod5_WSLS_vmPFC_long_all_setbacks.Rdata")
print(WSLS_vmPFC_long_brms_all_setbacks, digits = 4)
```



## Hypothesis 5: with reward-setback contrast (hard + easy)
### wide version

#### mPFC: 
```{r}
WSLS_mPFC_hard_setbacks_contrast <- lm(prop_stay ~ reward_setback_mPFC + N_trials_per_cond + Reinforce_rate.c +
                                            SEX.c + AGE.c, 
                                       data = WSLS_summary_hard_setback)

summary(WSLS_mPFC_hard_setbacks_contrast)

```


### long version with brms 
```{r}

load("brms_models/preregistration_model_results/mod5_WSLS_mPFC_long_all_reward_setback.Rdata")
print(WSLS_mPFC_long_brms_all_reward_setback, digits = 4)
```


#### vmPFC: NS
```{r}
WSLS_vmPFC_hard_setbacks_contrast <- lm(prop_stay ~ reward_setback_vmPFC + N_trials_per_cond + Reinforce_rate.c +
                                             SEX.c + AGE.c, 
                                        data = WSLS_summary_hard_setback)

summary(WSLS_vmPFC_hard_setbacks_contrast)

```

### long version with brms 
```{r}
load("brms_models/preregistration_model_results/mod5_WSLS_vmPFC_long_all_reward_setback.Rdata")
print(WSLS_vmPFC_long_brms_all_reward_setback, digits = 4)
```


