---
title: "Data cleaning for analysis for COMPS"
author: "Michelle.VanTieghem"
date: "7/9/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# notes
level1 models for subjects with 1 run: must already be registered intoo standard space! 

```{r, echo = F, message = F, warning = F}
library(tidyverse)
```

## load sublist that we want to extract ROIs from
```{r}
usable_subj <- read.table("../5_brain_behav_inclusion/sublists/include_scan_and_beh_by_run2019-11-27.txt", header = F)
names(usable_subj) <- c("SUBJECTID", "RunNumber")

sublist <- usable_subj %>%
  group_by(SUBJECTID) %>%
  summarize(n = n())
nrow(sublist) # 126

subs_with_1_run <- usable_subj %>%
  group_by(SUBJECTID) %>%
  summarize(n = n() ) %>%
  filter(n < 2)
subs_with_1_run <- usable_subj %>%
  filter(SUBJECTID %in% subs_with_1_run$SUBJECTID) %>%
  mutate(RunNumber == ifelse("RUN1", 1, 2))

```

## designate groupings of contrasts...
```{r}
study_dir <- "/danl/PACCT/subject_data/derivatives/effort_reward/"

# get cope model key for complete EV model with 24 copes
load("../6_brain_preproc_level1_by_run/complete_EV_model_cope_key.Rdata")
cope_key <- cope_key %>%
  rename(contrast = cope_list)

basic_cope_key <- cope_key %>%
  filter(contrast %in% c("allChoices", "allEffort", "RewardFB", "SetbackFB", "Reward-SetbackFB"))

choice_contrast_cope_key <- cope_key %>%
  filter(contrast %in% c("EasyChoice", "HardChoice",  "Hard-EasyChoice"))

hard_FB_contrast_cope_key <- cope_key %>%
  filter(contrast %in% c("HardReward", "HardSetback", "HardReward-HardSetback"))

# there aren't enough subjects to do beta pulls with these 2...
# but getting a sublist to take count anyway.
reward_FB_contrast_cope_key <- cope_key %>%
  filter(contrast %in% c("HardReward", "EasyReward", "HardReward-EasyReward"))
setback_FB_contrast_cope_key <- cope_key %>%
  filter(contrast %in% c("HardSetback", "EasySetback", "HardSetback-EasySetback"))
```

## make input file for basic contrasts
```{r}

for (copeN in basic_cope_key$cope_number){
# reset for each cope 
  input_files <- data.frame(SUBJECTID = NA, file = NA)
  # get the contrast 
  contrast <- as.character(basic_cope_key$contrast[basic_cope_key$cope_number == copeN])
  
  # for each subject in the dataframe, get their input file!
  for (sub in sublist$SUBJECTID){
    N_runs <- sublist %>% filter(SUBJECTID == sub) %>% select(n)
   
        # if they has 2 runs....
    if (N_runs == 2){
        subfile <- data.frame(SUBJECTID = sub, file= paste0(study_dir, sub, "/effort/model/lev2_complete.gfeat/cope", copeN, ".feat/stats/cope1.nii.gz"))
        input_files <- rbind(input_files, subfile)

    } else {
        # if they have 1 run....
      RunNumber <- subs_with_1_run %>% filter(SUBJECTID == sub) %>% select(RunNumber)
      subfile <- data.frame(SUBJECTID = sub, file = paste0(study_dir, sub, "/effort/model/preproc_lev1_run", RunNumber, ".feat/stats/cope", copeN, "_standard.nii.gz"))
      input_files <- rbind(input_files, subfile)
      
    }
    # write the input files!
    input_files <-na.omit(input_files)
   
  # save file for ROI beta pulls (all subjects)
      write.table(input_files, file = paste0("cope_input_files/cope", copeN,contrast,  "_input_files.txt"), quote = F, row.names = F, col.names = F)

  }
}


nrow(input_files)

```

## for choice contrast EVs 
### make sublist 
must have at least 8 trials per hard & easy
```{r}
# load behavior data in long format
load("../../behavioral_data/3_effort_task_data/compiled/compiled_long_format_all_data.Rdata")

choice_contrast_subs <- behavior_long_data %>%
  # only do this for subjects with usable scanning 
  filter(SUB %in% sublist$SUBJECTID) %>%
  # count number of trials per condition and filter out
  group_by(SUB, Effort_Choice) %>%
  summarize(N_trials =n()) %>%
  spread(Effort_Choice, N_trials) %>%
  filter(Easy >= 8 & Hard >= 8)

# keep this sublist for later. 
nrow(choice_contrast_subs)
choice_contrast_sublist <- choice_contrast_subs$SUB
save(choice_contrast_sublist, file = "sublists/subs_with_8_trials_for_choice_contrast_EVs.Rdata")

```

### make input files 
```{r}

for (copeN in choice_contrast_cope_key$cope_number){
# reset for each cope 
  input_files <- data.frame(SUBJECTID = NA, file = NA)
  # get the contrast 
  contrast <- as.character(choice_contrast_cope_key$contrast[choice_contrast_cope_key$cope_number == copeN])
  
  # for each subject in the dataframe, get their input file!
  for (sub in choice_contrast_sublist){
    N_runs <- sublist %>% filter(SUBJECTID == sub) %>% select(n)
   
        # if they has 2 runs....
    if (N_runs == 2){
        subfile <- data.frame(SUBJECTID = sub, file= paste0(study_dir, sub, "/effort/model/lev2_complete.gfeat/cope", copeN, ".feat/stats/cope1.nii.gz"))
        input_files <- rbind(input_files, subfile)

    } else {
        # if they have 1 run....
      RunNumber <- subs_with_1_run %>% filter(SUBJECTID == sub) %>% select(RunNumber)
      subfile <- data.frame(SUBJECTID = sub, file = paste0(study_dir, sub, "/effort/model/preproc_lev1_run", RunNumber, ".feat/stats/cope", copeN, "_standard.nii.gz"))
      input_files <- rbind(input_files, subfile)
      
    }
    # write the input files!
    input_files <-na.omit(input_files)
   
  # save file for ROI beta pulls (all subjects)
      write.table(input_files, file = paste0("cope_input_files/cope", copeN,contrast,  "_input_files.txt"), quote = F, row.names = F, col.names = F)

  }
}

nrow(input_files)

```


## hard FB contrast
### make sublist
must have at least 8 trials per the 4 conditions. 
```{r}
hard_FB_contrast_subs <- behavior_long_data %>%
  # clean up the feedback condition info 
  mutate(Feedback = ifelse(Reward_received == 1, "Reward", 
                           ifelse(Reward_received == 0, "Setback", "Missed"))) %>%
  
  # only do this for subjects with usable scanning 
  filter(SUB %in% sublist$SUBJECTID) %>%
  # count number of trials per condition and filter out
  group_by(SUB, Effort_Choice, Feedback) %>%
  summarize(N_trials =n()) %>%
  filter(Effort_Choice == "Hard" & !is.na(Feedback)) %>%
  spread(Feedback, N_trials) %>%
  filter(Reward >= 8 & Setback >= 8)
nrow(hard_FB_contrast_subs)

# save the sublist for later
hard_FB_contrast_sublist <- hard_FB_contrast_subs$SUB
save(hard_FB_contrast_sublist, file = "sublists/subs_with_8_trials_for_hard_FB_contrast_EVs.Rdata")
```

### make input files 
```{r}

for (copeN in hard_FB_contrast_cope_key$cope_number){
# reset for each cope 
  input_files <- data.frame(SUBJECTID = NA, file = NA)
  # get the contrast 
  contrast <- as.character(hard_FB_contrast_cope_key$contrast[hard_FB_contrast_cope_key$cope_number == copeN])
  
  # for each subject in the dataframe, get their input file!
  for (sub in hard_FB_contrast_sublist){
    N_runs <- sublist %>% filter(SUBJECTID == sub) %>% select(n)
   
        # if they has 2 runs....
    if (N_runs == 2){
        subfile <- data.frame(SUBJECTID = sub, file= paste0(study_dir, sub, "/effort/model/lev2_complete.gfeat/cope", copeN, ".feat/stats/cope1.nii.gz"))
        input_files <- rbind(input_files, subfile)

    } else {
        # if they have 1 run....
      RunNumber <- subs_with_1_run %>% filter(SUBJECTID == sub) %>% select(RunNumber)
      subfile <- data.frame(SUBJECTID = sub, file = paste0(study_dir, sub, "/effort/model/preproc_lev1_run", RunNumber, ".feat/stats/cope", copeN, "_standard.nii.gz"))
      input_files <- rbind(input_files, subfile)
      
    }
    # write the input files!
    input_files <-na.omit(input_files)
   
  # save file for ROI beta pulls (all subjects)
      write.table(input_files, file = paste0("cope_input_files/cope", copeN,contrast,  "_input_files.txt"), quote = F, row.names = F, col.names = F)

  }
}

nrow(input_files)

```


## Setback FB contrast
### make sublist
must have at least 8 trials per the 4 conditions. \
there are not many subjects here!...
```{r}
setback_FB_contrast_subs <- behavior_long_data %>%
  # clean up the feedback condition info 
  mutate(Feedback = ifelse(Reward_received == 1, "Reward", 
                           ifelse(Reward_received == 0, "Setback", "Missed"))) %>%
  
  # only do this for subjects with usable scanning 
  filter(SUB %in% sublist$SUBJECTID) %>%
  # count number of trials per condition and filter out
  group_by(SUB, Effort_Choice, Feedback) %>%
  summarize(N_trials =n()) %>%
  filter(Feedback == "Setback" & !is.na(Effort_Choice)) %>%
  spread(Effort_Choice, N_trials) %>%
  filter(Hard >= 8 & Easy >= 8)
nrow(setback_FB_contrast_subs)

# save the sublist for later
setback_FB_contrast_sublist <- setback_FB_contrast_subs$SUB
save(setback_FB_contrast_sublist, file = "sublists/subs_with_8_trials_for_setback_FB_contrast_EVs.Rdata")
```

## Reward FB contrast
### make sublist
must have at least 8 trials per the 4 conditions. \
there are not many subjects here!...not enough for beta pulls.
```{r}
reward_FB_contrast_subs <- behavior_long_data %>%
  # clean up the feedback condition info 
  mutate(Feedback = ifelse(Reward_received == 1, "Reward", 
                           ifelse(Reward_received == 0, "Setback", "Missed"))) %>%
  
  # only do this for subjects with usable scanning 
  filter(SUB %in% sublist$SUBJECTID) %>%
  # count number of trials per condition and filter out
  group_by(SUB, Effort_Choice, Feedback) %>%
  summarize(N_trials =n()) %>%
  filter(Feedback == "Reward" & !is.na(Effort_Choice)) %>%
  spread(Effort_Choice, N_trials) %>%
  filter(Hard >= 8 & Easy >= 8)
nrow(reward_FB_contrast_subs)

# save the sublist for later
reward_FB_contrast_sublist <- reward_FB_contrast_subs$SUB
save(reward_FB_contrast_sublist, file = "sublists/subs_with_8_trials_for_reward_FB_contrast_EVs.Rdata")
```
