---
title: "specification curves for ACC response to had-easy choices "
author: "Michelle.VanTieghem"
date: "1/5/2020"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# notes: 
code for specification curves from Dani Cosme
https://github.com/dcosme/specification-curves/blob/master/SCA_tutorial.Rmd
```{r, include = F, warnings = F, echo=FALSE, message = F}
source("../../../../0_R_analysis_setup_file.R")
require(tidyverse)

# using code from Dani Cosme for sensitivity analysis 
library(purrr)
library(cowplot)

```

# load data
```{r}
# load all data with PCA added!
load("../data/all_pacct_effort_data_with_PCA.rda")
```


## clean data
## set up & clean data
```{r} 
choice_level_order <- c('ACC', 'mPFC',  "VS")
#organize data for choice phase.
choice_contrast_df <- beh_scan_ECA_wide %>%
  # combine left and right accumbens betas into bilateral! 
  dplyr::select(-starts_with("feedback"), -starts_with("setback"), -starts_with("reward")) %>%
  gather(key = "ROI", value = "beta", hard_easy_choice_ACC, hard_easy_choice_choice_mPFC, 
         hard_easy_choice_ACC) %>%
  filter(!is.na(beta) & !is.na(PC1)) %>%
  mutate(ROI = ifelse(ROI == "hard_easy_choice_ACC", "ACC",
                      ifelse(ROI == "hard_easy_choice_choice_mPFC", "mPFC",  "VS")),
            ROI = factor(ROI, levels = choice_level_order),
         AGE.c = AGE - mean(AGE, na.rm = T),
         SEX.c = SEX - mean(SEX, na.rm = T), 
         IQ.c = IQ- mean(IQ, na.rm = T),
         total_TRs_censored.c = total_TRs_censored - mean(total_TRs_censored, na.rm = T),
         Reinforce_rate.c = Reinforce_rate - mean(Reinforce_rate, na.rm = T), 
         GROUP_ECA.c = ifelse(GROUP_ECA == "COMP", -1, 1), 
         PC1_log.c = PC1_log - mean(PC1_log, na.rm = T))

# check right number of subjects! 
length(unique(choice_contrast_df$SUBJECTID))

```

## remove outliers
calculated already.
```{r}
load(file = "../tables/choice_contrast_betas_outlier_subjects.Rdata")
choice_outliers <- choice_contrast_outlier_subjects %>% 
  filter(ROI == "ACC") # & contrast ==  "hard_easy")
choice_outliers

choice_df2 <- choice_contrast_df %>%
  mutate(beta = ifelse(SUBJECTID %in% choice_outliers$SUBJECTID , NA, beta), 
         diff_pos_affect = win_feeling-lose_feeling) %>%
  dplyr::select(ROI, beta, PC1_log.c, AGE.c, SEX.c, IQ.c, Fam_inc_needs.c, 
         total_TRs_censored.c, Reinforce_rate.c, 
         frustrated, perceived_control, motivated, perceived_effort_ave, 
         perceived_reinforce, diff_pos_affect, 
         win_feeling, lose_feeling, median_motor_RT_ave) %>%
  filter(ROI == "ACC") %>%
  na.omit() 

nrow(choice_df2)
```

## model with evey covariate possible. 
frustrated is sig! and trend PC1 
```{r}
full_test <- lm(beta ~  PC1_log.c + AGE.c  + SEX.c + IQ.c + Fam_inc_needs.c + 
                       total_TRs_censored.c +  Reinforce_rate.c  + 
                       frustrated + perceived_control +  motivated +  
                       perceived_effort_ave + perceived_reinforce + 
                      win_feeling +  lose_feeling + median_motor_RT_ave , 
                 data = choice_df2)
summary(full_test)
```

## correlation tests for frustrated 
```{r}
# sig 
with(choice_df2, cor.test(frustrated, AGE.c))
with(choice_df2, cor.test(frustrated, perceived_reinforce))

with(choice_df2, cor.test(frustrated, Reinforce_rate.c))
with(choice_df2, cor.test(frustrated, perceived_control))
with(choice_df2, cor.test(frustrated, total_TRs_censored.c))
with(choice_df2, cor.test(frustrated, median_motor_RT_ave))
with(choice_df2, cor.test(frustrated, perceived_effort_ave))
with(choice_df2, cor.test(frustrated, motivated))
with(choice_df2, cor.test(frustrated, win_feeling))
with(choice_df2, cor.test(frustrated, lose_feeling))
```


## make list of models to test
removing Sex, IQ, and fam inc from all models, not of interest! 
including perceived reinforcement
omitting everything else! 
```{r}
# specify models
full_test <- lm(beta ~  PC1_log.c + frustrated + 
                         perceived_reinforce + 
                        AGE.c  + total_TRs_censored.c +  Reinforce_rate.c, 
              data = choice_df2)
summary(full_test)
```


## run all nested models using `dredge` from `MuMIn`
* max number of predictors = 30
```{r dredge}
# set na.action for dredge
options(na.action = "na.fail")

# run full model
full.model = full_test
# run all possible nested models
all.models = MuMIn::dredge(full.model, rank = "AIC", extra = "BIC")
```


## frustrated 
extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "frustrated") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(ACC)1", "ACC", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(ACC)1", "ACC", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/targeted_SCA/ACC_hard-easy_choice_by_frustrated.png", height = 6, width = 8)
```


##  PC1 

  extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "PC1_log.c") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(ACC)1", "ACC", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(ACC)1", "ACC", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/targeted_SCA/ACC_hard-easy_choice_by_PC1.png", height = 6, width = 8)
```

## perceived reinforcement
extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "perceived_reinforce") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(ACC)1", "ACC", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(ACC)1", "ACC", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/targeted_SCA/ACC_hard-easy_choice_by_perceived_reinforce.png", height = 6, width = 8)

```


## AGE 
  extract coefficients and p-values
```{r}
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "AGE.c") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(ACC)1", "ACC", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(ACC)1", "ACC", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/targeted_SCA/ACC_hard-easy_choice_by_AGE.png", height = 6, width = 8)

```


##  motion confound 

  extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "total_TRs_censored.c") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(ACC)1", "ACC", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(ACC)1", "ACC", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/targeted_SCA/ACC_hard-easy_choice_by_motion.png", height = 6, width = 8)

```

##  Actual reinforcement rate 

extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "Reinforce_rate.c") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(ACC)1", "ACC", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "coefficient for actual reinforcement rate \n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(ACC)1", "ACC", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/targeted_SCA/ACC_hard-easy_choice_by_actual_reinforcement.png", height = 6, width = 8)

```



# plot effect of frustration on ACC to hard-easy choices
```{r}
ACC_hard_Easy_choice_mod_pe <- lm(beta ~  PC1_log.c + frustrated +
                        perceived_reinforce + 
                        AGE.c  + total_TRs_censored.c +  Reinforce_rate.c, 
              data = choice_df2)
summary(ACC_hard_Easy_choice_mod_pe)
```

plot effect
```{r}
effect_df <- data.frame(effect("frustrated",ACC_hard_Easy_choice_mod_pe))

effect_plot <- ggplot(data = effect_df, aes(x = frustrated, y = fit)) + 
  geom_line(color = dark_blue) + 
  geom_ribbon(aes(ymin = lower, ymax  = upper),alpha = 0.2, fill = dark_blue) + 
  geom_jitter(data = choice_df2, aes(x = perceived_effort_ave, y = beta), 
              width = 0.05, height = 0, alpha = 0.2, color = dark_blue) + 
  ylab("ACC recruitment for Hard > Easy ") + xlab("frustrated")

effect_plot
ggsave(effect_plot, file = "../figures/targeted_SCA/ACC_hard-easy_choice_by_frustration_effect_plot.png", 
       height = 4, width = 4)
```
