---
title: "ECA effects on actual effort"
author: "Michelle.VanTieghem"
date: "Dec 16, 2019"
output:
  html_document:
    number_sections: no
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# Readme
specification curve analysis for actual effort (button preses, contrrlling for max keys). \
No effects of effort choice because it's nearly identical to max keys!! but max keys is taking into account the fact that the exact button press requirements might vary by subject. 


```{r, include = F, warnings = F, echo=FALSE, message = F}
source("../../../../0_R_analysis_setup_file.R")
```


```{r}
# load all data with PCA added!
load("../../data/all_pacct_effort_data_with_PCA.rda")

```

# clean data first 
```{r}

#remove outliers from RT calculations first! 
# and also filter out trials where they didn't reach the top! 
button_RT_df <- beh_scan_ECA_long %>%
  filter(Accuracy == 1 & Effort_Choice != "Miss") %>%
  # just making these to find outliers 
  mutate(mean_easy = mean(median_RT_easy_button_press, na.rm = T),
          sd_easy = sd(median_RT_easy_button_press, na.rm = T),
         mean_hard = mean(median_RT_hard_button_press, na.rm = T), 
         sd_hard = sd(median_RT_hard_button_press, na.rm = T),
    # redoing nvariables omitting outliers (marked as NA)
          median_RT_easy_button_press = ifelse(median_RT_easy_button_press < mean_easy + 3*sd_easy, median_RT_easy_button_press, NA), 
         median_RT_hard_button_press = ifelse(median_RT_hard_button_press < mean_hard + 3*sd_hard, median_RT_hard_button_press, NA),
         median_RT_button_press = ifelse(Effort_Choice.n == 0, median_RT_easy_button_press, 
                                         ifelse(Effort_Choice.n == 1, median_RT_hard_button_press, NA)), 
         # add perceived effort by trial. 
         perceived_effort_by_trial = ifelse(Effort_Choice.n == 1, hard_effort_perceived, 
                                            easy_effort_perceived)) %>%
  dplyr::select(SUBJECTID, Effort_Choice.n, Effort_Choice, 
                GROUP_ECA.x, PC1_log, AGE.c, SEX.c, IQ.c, 
         total_censored_TRs, Reinforce_rate.c, 
         Trial_Number, max_keys,
         frustrated, perceived_control, motivated,
         perceived_effort_ave, perceived_effort_by_trial,
         effort_key_count, median_RT_button_press,
         perceived_reinforce, median_motor_RT_ave, 
         win_feeling, lose_feeling, 
         hard_easy_choice_choice_mPFC)  %>%
  na.omit() 

N_subs <- length(unique(button_RT_df$SUBJECTID))
N_subs


save(button_RT_df, file = "../../data/button_RT_df.Rdata")
```


# check data 

```{r}
key_press_table <- button_RT_df %>%
  group_by(Effort_Choice) %>%
  dplyr::summarize(effort_key_count = mean(effort_key_count, na.rm = T), 
                   sd_key_count = sd(effort_key_count, na.rm = T), 
                   upper = effort_key_count + 2*sd_key_count, 
                   lower = effort_key_count - 2*sd_key_count)
key_press_table 
```

```{r}

ggplot(data = button_RT_df, aes(x = Effort_Choice, y = effort_key_count)) + 
  geom_jitter(color = dark_blue, alpha = 0.1, width = 0.1) + 
  geom_boxplot() + 
  geom_point(data = key_press_table, aes(x = Effort_Choice, y = effort_key_count), 
             size = 3) + ylim (0, 16)

sd(button_RT_df$effort_key_count[button_RT_df$Effort_Choice == "Hard"])
```

# actual effort - button presses

## basic model with covariates 
main effects of Trrial N, max keys, motor speed. Effort Choice is not significant! 
```{r}

key_count_full <- lmer(effort_key_count ~ PC1_log + Effort_Choice.n +
                            AGE.c + SEX.c +  Trial_Number +
                         max_keys +  median_motor_RT_ave +
                         (1 + Effort_Choice.n | SUBJECTID),
                       # can't include trial number random effects with lmer. 
                           # (1 + Effort_Choice.n + Trial_Number.c | SUBJECTID),
                          data = button_RT_df)
summary(key_count_full)
```

## full model with self-report data
AGE, perceived reinforce, perceived effort, perceived control. 
```{r}

key_count_full <- lmer(effort_key_count ~ PC1_log + Effort_Choice.n +
                            AGE.c + SEX.c +  Trial_Number+ 
                         max_keys +  median_motor_RT_ave +
                         perceived_reinforce + perceived_control + 
                              lose_feeling + win_feeling + 
                              frustrated + motivated + 
                           #   perceived_effort_ave.c +
                         perceived_effort_by_trial+
                         (1 + Effort_Choice.n | SUBJECTID),
                       # can't include trial number random effects with lmer. 
                           # (1 + Effort_Choice.n + Trial_Number.c | SUBJECTID),
                          data = filter(button_RT_df, Effort_Choice != "Miss"))
summary(key_count_full)

```


## test model with significant effects and necessary covariates
```{r}
key_count_test <- lmer(effort_key_count ~ PC1_log + Effort_Choice.n +
                            AGE.c +  Trial_Number + 
                         max_keys +  median_motor_RT_ave +
                         perceived_reinforce + perceived_control + 
                           #   perceived_effort_ave.c +
                         perceived_effort_by_trial*Effort_Choicen +
                         (1 + Effort_Choice.n | SUBJECTID),
                       # can't include trial number random effects with lmer. 
                           # (1 + Effort_Choice.n + Trial_Number.c | SUBJECTID),
                          data = button_RT_df)
summary(key_count_test)
```

                  
## run all nested models using `dredge` from `MuMIn`
* max number of predictors = 30
```{r dredge}
# set na.action for dredge
options(na.action = "na.fail")

# run full model
full.model = key_count_test
# run all possible nested models
all.models = MuMIn::dredge(full.model, rank = "AIC", extra = "BIC")

model_table = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom.mixed::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() 
```



## PC1_log
extract coefficients and p-values
```{r  }
# extract p-values for the term of interest! 
model_ps = model_table %>%
  filter(term == "PC1_log") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)

  # extract estimates for the term of interest!
model_params <- model_table %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../../figures/targeted_SCA/actual_effort_button_press_by_PC1_log.png",  height = 6, width  = 8)
```

if you perceive it as harder, you press more! 
```{r}
effect_df <- data.frame(effect("PC1_log", key_count_test))

effect_plot <- ggplot(data = effect_df, aes(x = PC1_log, y = fit)) + 
  geom_line(color = dark_blue) + 
  geom_ribbon(aes(ymin = lower, ymax  = upper),alpha = 0.2, fill = dark_blue) + 
  ##geom_jitter(data = button_RT_df, aes(x = perceived_effort_by_trial, y = effort_key_count), 
    #          width = 0.05, height = 0, alpha = 0.2, color = dark_blue) + 
  ylab("Key Count") + xlab("PC1_log")

effect_plot
ggsave(effect_plot, file = "../../figures/targeted_SCA/actual_effort_button_press_by_PC1_log.png", 
       height = 4, width = 6)
```


##  perceived_reinforce
extract coefficients and p-values
```{r  }
# extract p-values for the term of interest! 
model_ps = model_table %>%
  filter(term == "perceived_reinforce") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)

  # extract estimates for the term of interest!
model_params <- model_table %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../../figures/targeted_SCA/actual_effort_button_press_by_perceived_reinforce.png",  height = 6, width  = 8)
```


##  perceived_reinforce
extract coefficients and p-values
```{r  }
# extract p-values for the term of interest! 
model_ps = model_table %>%
  filter(term == "perceived_reinforce") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)

  # extract estimates for the term of interest!
model_params <- model_table %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../../figures/targeted_SCA/actual_effort_button_press_by_perceived_reinforce.png",  height = 6, width  = 8)
```


##  perceived effort by trial
extract coefficients and p-values
```{r}
# extract p-values for the term of interest! 
model_ps = model_table %>%
  filter(term == "perceived_effort_by_trial") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)

  # extract estimates for the term of interest!
model_params <- model_table %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../../figures/targeted_SCA/actual_effort_button_press_by_perceived_effort_trials.png",  height = 6, width  = 8)
```

if you perceive it as harder, you press more! 
```{r}
effect_df <- data.frame(effect("perceived_effort_by_trial", key_count_test))

effect_plot <- ggplot(data = effect_df, aes(x = perceived_effort_by_trial, y = fit)) + 
  geom_line(color = dark_blue) + 
  geom_ribbon(aes(ymin = lower, ymax  = upper),alpha = 0.2, fill = dark_blue) + 
  ##geom_jitter(data = button_RT_df, aes(x = perceived_effort_by_trial, y = effort_key_count), 
    #          width = 0.05, height = 0, alpha = 0.2, color = dark_blue) + 
  ylab("Key Count") + xlab("Perceived effort")

effect_plot
ggsave(effect_plot, file = "../../figures/targeted_SCA/actual_effort_button_press_by_perceived_effort.png", 
       height = 4, width = 6)
```



## AGE
extract coefficients and p-values
```{r}
# extract p-values for the term of interest! 
model_ps = model_table %>%
  filter(term == "AGE.c") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)

  # extract estimates for the term of interest!
model_params <- model_table %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../../figures/targeted_SCA/actual_effort_button_press_by_AGE.png",  height = 6, width  = 8)
```
            
effect
```{r}
effect_df <- data.frame(effect("AGE.c",key_count_test))

effect_plot <- ggplot(data = effect_df, aes(x = AGE.c, y = fit)) + 
  geom_line(color = dark_blue) + 
  geom_ribbon(aes(ymin = lower, ymax  = upper),alpha = 0.2, fill = dark_blue) + 
  #geom_jitter(data = button_RT_df, aes(x = AGE.c, y = effort_key_count), 
   #           width = 0.05, height = 0, alpha = 0.2, color = dark_blue) + 
  ylab("Key Count") + xlab("Age (mean-centered)")

effect_plot
ggsave(effect_plot, file = "../../figures/targeted_SCA/actual_effort_key_count_by_age.png", 
       height = 4, width = 6)
```

## Motor speed
extract coefficients and p-values
```{r}
# extract p-values for the term of interest! 
model_ps = model_table %>%
  filter(term == "median_motor_RT_ave") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)

  # extract estimates for the term of interest!
model_params <- model_table %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = as.factor(ifelse(p.value < .05, 1, 0))) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))

# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = as.numeric(as.character(significant.p))) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c( "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../../figures/targeted_SCA/actual_effort_button_press_by_motor_speed.png",  height = 6, width  = 8)
```

# test role of mPFC to hard>easy given effects of perceived effort
## first, include mPFC and take out perceived effort. NS
```{r}
key_count_test_mPFC <- lmer(effort_key_count ~ PC1_log + Effort_Choice.n +
                            AGE.c +  Trial_Number + 
                        median_motor_RT_ave + max_keys + 
                        #perceived_reinforce + perceived_control + 
                           #   perceived_effort_ave.c +
                        # perceived_effort_by_trial + 
                           hard_easy_choice_choice_mPFC + 
                         (1 + Effort_Choice.n | SUBJECTID),
                       # can't include trial number random effects with lmer. 
                           # (1 + Effort_Choice.n + Trial_Number.c | SUBJECTID),
                          data = button_RT_df)
summary(key_count_test_mPFC)

```


## including mPFC and perceievd effort: NS.
```{r}
key_count_test_mPFC <- lmer(effort_key_count ~ PC1_log + Effort_Choice.n +
                            AGE.c +  Trial_Number + 
                        median_motor_RT_ave + max_keys + 
                        #perceived_reinforce + perceived_control + 
                            #  perceived_effort_ave.c +
                        perceived_effort_by_trial + 
                           hard_easy_choice_choice_mPFC +  
                         (1 + Effort_Choice.n | SUBJECTID),
                       # can't include trial number random effects with lmer. 
                           # (1 + Effort_Choice.n + Trial_Number.c | SUBJECTID),
                          data = button_RT_df)
summary(key_count_test_mPFC)

```