---
title: "specification curves for VS Reward-Setback respones"
author: "Michelle.VanTieghem"
date: "1/5/2020"

output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# notes: 
code for specification curves from Dani Cosme
https://github.com/dcosme/specification-curves/blob/master/SCA_tutorial.Rmd
```{r, include = F, warnings = F, echo=FALSE, message = F}
source("../../../../0_R_analysis_setup_file.R")
require(tidyverse)

# using code from Dani Cosme for sensitivity analysis 
library(purrr)
library(cowplot)

```

# load data
```{r}
# load all data with PCA added!
load("../data/all_pacct_effort_data_with_PCA.rda")
```

## clean data
```{r} 
FB_level_order <- c("vmPFC", "mPFC", "VS", "Amyg")

# get just reward ROIs
reward_df <- beh_scan_ECA_wide %>%
  rename(Amyg = reward_Amyg,
         mPFC = reward_FB_mPFC, 
         vmPFC = reward_vmPFC, 
         VS = reward_VS) %>%
  dplyr::select(-starts_with("choice"), -starts_with("setback"), 
         -starts_with("feedback"), -starts_with("reward_setback")) %>%
  gather(key = "ROI", value = "reward_beta",  vmPFC, mPFC, VS, Amyg) %>%
  filter(!is.na(reward_beta))

# check right number of subjects! 
length(unique(reward_df$SUBJECTID))

# get just setback ROIs
setback_df <- beh_scan_ECA_wide %>%
   rename(Amyg = setback_Amyg, 
          vmPFC = setback_vmPFC, 
         mPFC = setback_FB_mPFC, 
         VS = setback_VS) %>%
  dplyr::select(-starts_with("choice"), -starts_with("reward"), 
         -starts_with("feedback"), -starts_with("reward_setback")) %>%
  gather(key = "ROI", value = "setback_beta",  vmPFC, mPFC, VS,  Amyg) %>%
  dplyr::select(SUBJECTID, ROI, setback_beta) %>%
  filter(!is.na(setback_beta))

# combine them in long format
FB_df <- merge(reward_df, setback_df, by = c("SUBJECTID", "ROI")) %>%
  mutate(reward_minus_setback = reward_beta - setback_beta,
        ROI = factor(ROI, levels = FB_level_order),
         AGE.c = AGE - mean(AGE, na.rm = T),
         SEX.c = SEX - mean(SEX, na.rm = T), 
         IQ.c = IQ- mean(IQ, na.rm = T),
         total_TRs_censored.c = total_TRs_censored - mean(total_TRs_censored, na.rm = T),
         Reinforce_rate.c = Reinforce_rate - mean(Reinforce_rate, na.rm = T), 
         GROUP_ECA.c = ifelse(GROUP_ECA == "COMP", -1, 1), 
        PC1_log.c = PC1_log -mean(PC1_log)) %>%
  gather(key = "contrast", value = "beta", reward_beta, setback_beta, reward_minus_setback) %>%
  filter(!is.na(beta))

# rename levels of contrast factor
FB_df$contrast <- as.factor(ifelse(FB_df$contrast == "reward_beta", "reward", ifelse(FB_df$contrast == "setback_beta", "setback", FB_df$contrast)))
FB_df$diff_pos_affect <- FB_df$win_feeling - FB_df$lose_feeling

```

## remove outliers
calculated already.
```{r}
load(file = "../tables/Feedback_betas_outlier_subjects.Rdata")
setback_outliers <- FB_outlier_subjects %>% 
  filter(ROI == "Amyg" & contrast == "reward_minus_setback")

FB_df2 <- FB_df %>%
  mutate(beta = ifelse(SUBJECTID %in% setback_outliers$SUBJECTID , NA, beta))
nrow(FB_df2)

```  

## filter only setback data 
```{r}
FB_df3 <- FB_df2 %>%
  filter(contrast == "reward_minus_setback" & ROI == "Amyg")  %>% 
  dplyr::select(beta, PC1_log.c, AGE.c, SEX.c, IQ.c, Fam_inc_needs.c, 
         total_TRs_censored.c, Reinforce_rate.c, 
         frustrated, perceived_control, motivated, perceived_effort_ave, 
         perceived_reinforce, diff_pos_affect, 
         win_feeling, lose_feeling, 
         median_motor_RT_ave)
nrow(FB_df3)

# omit NAs
FB_df4 = FB_df3 %>% 
  na.omit()
nrow(FB_df4)
```


## model with evey covariate possible. 
```{r}
full_test <- lm(beta ~  PC1_log.c + AGE.c  + SEX.c + IQ.c + Fam_inc_needs.c + 
                       total_TRs_censored.c +  Reinforce_rate.c  + 
                       frustrated + perceived_control +  motivated +  
                       perceived_effort_ave + perceived_reinforce + 
                      win_feeling +  lose_feeling + median_motor_RT_ave, 
                 data = FB_df4)
summary(full_test)
```

## correlation tests for PC1 
```{r}

#  sig
with(FB_df4, cor.test(PC1_log.c, win_feeling))
with(FB_df4, cor.test(PC1_log.c, perceived_control))
with(FB_df4, cor.test(PC1_log.c, total_TRs_censored.c))
with(FB_df4, cor.test(PC1_log.c, lose_feeling))
with(FB_df4, cor.test(PC1_log.c, perceived_effort_ave))

# not 
with(FB_df4, cor.test(PC1_log.c, perceived_reinforce))
with(FB_df4, cor.test(PC1_log.c, Reinforce_rate.c))
with(FB_df4, cor.test(PC1_log.c, AGE.c))
with(FB_df4, cor.test(PC1_log.c, frustrated))
with(FB_df4, cor.test(PC1_log.c, median_motor_RT_ave))

```


## make list of models to test
removing Sex, IQ and fam income from all models, not of interest! 
must include  age and motion.
motivated is correlated with win feeling, perceived control and median motor RT ave.
omitting everything else! 
```{r}
# specify models
full_test <- lm(beta ~  PC1_log.c + AGE.c + 
                  IQ.c + Fam_inc_needs.c + 
                  perceived_control +  total_TRs_censored.c + 
                  lose_feeling +  perceived_effort_ave,
              data = FB_df4)
summary(full_test)
```


## run all nested models using `dredge` from `MuMIn`
* max number of predictors = 30
```{r dredge}
# set na.action for dredge
options(na.action = "na.fail")

# run full model
full.model = full_test
# run all possible nested models
all.models = MuMIn::dredge(full.model, rank = "AIC", extra = "BIC")
```



##  PC1 

  extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "PC1_log.c") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/targeted_SCA/VS_reward_by_PC1.png", height = 6, width = 8)
```


## Fam income to needs
extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "Fam_inc_needs.c") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/targeted_SCA/VS_reward_by_family_income_to_needs.png", height = 6, width = 8)

```


## perceived contrrol
extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "perceived_control") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/targeted_SCA/VS_reward_by_perceived_control.png", height = 6, width = 8)
```


## AGE 
  extract coefficients and p-values
```{r}
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "AGE.c") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/targeted_SCA/VS_reward_by_AGE.png", height = 6, width = 8)

```


##  motion confound 

  extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "total_TRs_censored.c") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/targeted_SCA/VS_reward_by_motion.png", height = 6, width = 8)

```


##  IQ

  extract coefficients and p-values
```{r  }
# extract parameter estimate 
model_params = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  dplyr::select(model_num, term, estimate) %>%
  spread(term, estimate) %>%
  dplyr::select(-starts_with("sd"))
# extract p-values for the term of interest! 
model_ps = MuMIn::get.models(all.models, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  dplyr::select(model_num, tidied) %>%
  unnest() %>%
  filter(term == "IQ.c") %>%
  ungroup() %>%
  dplyr::select(model_num, estimate, std.error, p.value)
```

  plot specification curve
* red = statistically significant values at p < .05
* black = p > .05
```{r , fig.width=10, fig.height=6}
# merge and tidy for plotting
plot.data = left_join(model_ps, model_params, by = "model_num") %>%
  arrange(estimate) %>%
  mutate(specification = row_number(),
         significant.p = ifelse(p.value < .05, "yes", "no")) %>%
  gather(variable, value, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p) %>% 
  mutate(variable = gsub("[()]", "", variable),
         variable = gsub("Intercept", "intercept", variable),
         variable = gsub("as.factor(vs)1", "vs", variable)) %>%
  spread(variable, value)  
# get names of variables included in model
variable.names = names(dplyr::select(plot.data, -estimate, -specification, -model_num, -std.error, -p.value, -significant.p))
# plot top panel
top = plot.data %>%
  ggplot(aes(specification, estimate, color = significant.p)) +
    geom_point(shape = "|", size = 4) +
    #geom_hline(yintercept = null.df$AIC, linetype = "dashed", color = "lightblue") +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "", y = "regression coefficient\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# set plotting order for variables based on number of times it's included in better fitting models
order = plot.data %>%
  arrange(estimate) %>%
  mutate(significant.p.num = ifelse(significant.p == "yes", 1, 0)) %>%
  gather(variable, value, eval(variable.names)) %>% 
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  mutate(order = sum(significant.p.num)) %>%
  dplyr::select(variable, order) %>%
  unique()
# rename variables and plot bottom panel
bottom = plot.data %>%
  gather(variable, value, eval(variable.names)) %>% 
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = ifelse(variable == "(Intercept)", "intercept",
                    ifelse(variable == "as.factor(vs)1", "vs", variable))) %>%
  left_join(., order, by = "variable") %>%
  ggplot(aes(specification, reorder(variable, order), color = significant.p)) +
    geom_text(aes(label = value)) +
    scale_color_manual(values = c("black", "red")) +
    labs(x = "\nspecification number", y = "variables\n") + 
    theme_minimal(base_size = 11) +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 9),
          axis.text = element_text(color = "black"),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
# join panels
(wt = cowplot::plot_grid(top, bottom, ncol = 1, align = "v", labels = c('A', 'B')))
ggsave(wt, file = "../figures/targeted_SCA/VS_reward_by_IQ.png", height = 6, width = 8)

```

