---
title: "WSLS specification curve analysis"
author: "Michelle.VanTieghem"
date: "10/10/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# notes
Dec 1 2019: updated with new MICM variables and using PC1_log instead of sqrt.\
need to re-run brms models!!  and only use brms for plots. \
also only using scan sample since behavior differs!! 

```{r, include = F, warnings = F, echo=FALSE, message = F}
source("../../../../0_R_analysis_setup_file.R")
```

```{r}
# load all data with PCA added!
load("../data/all_pacct_effort_data_with_PCA.rda")
```

## set up data
```{r}

beh_scan_ECA_long <- beh_scan_ECA_long %>%
  dplyr::select(SUBJECTID, GROUP_ECA.x, Effort_Choice, Effort_Choice.n, 
                PC1_log , Trial_Number.c , IQ.c,
                          AGE.c , SEX.c , Reinforce_rate.c , perceived_effort_ave.c , 
                         motivated , perceived_reinforce , frustrated ,
                        lose_feeling , win_feeling , perceived_control , 
                         key_resp_choice.rt,
                          median_motor_RT_ave) %>%
  na.omit() 

beh_scan_ECA_wide <- beh_scan_ECA_wide %>%
  dplyr::select(SUBJECTID, GROUP_ECA, prop_hard_choices, PC1_log , IQ.c, 
                          AGE.c , SEX.c , Reinforce_rate , perceived_effort_ave , 
                         motivated , perceived_reinforce , frustrated ,
                        lose_feeling , win_feeling , perceived_control , 
                          median_motor_RT_ave) %>%
  na.omit()
```

# Set full models 

## full model with all covariates
```{r}
full_mod <- lmer(Effort_Choice.n ~ AGE.c +  PC1_log +
                   Reinforce_rate + 
                SEX.c +  median_motor_RT_ave + Trial_Number.c + IQ.c +
                (1 | SUBJECTID),
              data = beh_scan_ECA_long)
summary(full_mod)
```


## full model with all self-report measures
none of them are significant! maybe winfeeling
```{r}
full_mod_all <- lmer(Effort_Choice.n ~ AGE.c +  PC1_log +
                perceived_reinforce + Reinforce_rate.c +
                  perceived_effort_ave + perceived_control + 
                frustrated + motivated + win_feeling + lose_feeling +
                SEX.c +  median_motor_RT_ave + Trial_Number.c + IQ.c +
                (1 | SUBJECTID),
              data = beh_scan_ECA_long)
summary(full_mod_all)
```


## test model with only significant stuff or necessary covariates 
then run all combos of that model. 
```{r}
test_mod <- lmer(Effort_Choice.n ~ AGE.c +  PC1_log +
                 Reinforce_rate.c +
                  win_feeling + 
                 median_motor_RT_ave + Trial_Number.c +
                (1 | SUBJECTID),
              data = beh_scan_ECA_long)
summary(test_mod)
```

## add brain measures 
```{r}
test_mod <- lmer(Effort_Choice.n ~ AGE.c +  PC1_log +
                 Reinforce_rate.c +
                  win_feeling + 
                 median_motor_RT_ave + Trial_Number.c +
                  setback_Amyg + reward_vmPFC + reward_VS + reward_Amyg +
                (1 | SUBJECTID),
              data = beh_scan_ECA_long)
summary(test_mod)
```

## run all model iterations 

## see how strong 


# brain measures (hard-easy choice subsample)
```{r}

load("../data/all_pacct_effort_data_with_PCA.rda")

# need to make sub-sample 
beh_scan_ECA_long_ss <- beh_scan_ECA_long %>%
  dplyr::select(SUBJECTID, GROUP_ECA.x, Effort_Choice, Effort_Choice.n, 
                PC1_log , Trial_Number.c , IQ.c,
                          AGE.c , SEX.c , Reinforce_rate.c , perceived_effort_ave.c , 
                         motivated , perceived_reinforce , frustrated ,
                        lose_feeling , win_feeling , perceived_control , 
                         key_resp_choice.rt,
                          median_motor_RT_ave,
                hard_easy_choice_choice_mPFC, hard_easy_choice_VS, hard_easy_choice_ACC) %>%
  na.omit() 
```

## establish same effects replicate in sub-sample 
 now PC1 is a trend?! 
```{r}
test_mod_ss <- lmer(Effort_Choice.n ~ AGE.c +  PC1_log +
                 Reinforce_rate.c +
                  win_feeling + 
                 median_motor_RT_ave + Trial_Number.c +
                (1 | SUBJECTID),
              data = beh_scan_ECA_long_ss)
summary(test_mod_ss)
```


## full model with all choice brain measures of interest
now PC1 is significant!!! not helpful. 
```{r}

test_mod_ss_brain <- lmer(Effort_Choice.n ~ AGE.c +  PC1_log +
                 Reinforce_rate.c +
                  win_feeling + 
                 median_motor_RT_ave + Trial_Number.c +
                   hard_easy_choice_choice_mPFC + hard_easy_choice_VS + hard_easy_choice_ACC +
                (1 | SUBJECTID),
              data = beh_scan_ECA_long_ss)
summary(test_mod_ss_brain)                
                

```
