---
title: "ECA effects on key press overshoots"
author: "Michelle.VanTieghem"
date: "Dec 16, 2019"
output:
  html_document:
    number_sections: no
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# Readme
check with overshoots. no specification curve necessary because the same as actual effort (N button press) \
1) Should we control for max keys or not in this analysis?  \
No effects of effort choice because it's nearly identical to max keys!! but max keys is taking into account the fact that the exact button press requirements might vary by subject. \
2) should we include or exclude subjects who didn't make it to the top?



```{r, include = F, warnings = F, echo=FALSE, message = F}
source("../../../../0_R_analysis_setup_file.R")
```

# load data
```{r}
# load all data with PCA added!
load("../../data/all_pacct_effort_data_with_PCA.rda")

```

## clean data first 
```{r}

#remove outliers from RT calculations first! 
# and also filter out trials where they didn't reach the top! 
button_RT_df <- beh_scan_ECA_long %>%
  filter( Effort_Choice != "Miss") %>%
  # just making these to find outliers 
  mutate(mean_easy = mean(median_RT_easy_button_press, na.rm = T),
          sd_easy = sd(median_RT_easy_button_press, na.rm = T),
         mean_hard = mean(median_RT_hard_button_press, na.rm = T), 
         sd_hard = sd(median_RT_hard_button_press, na.rm = T),
    # redoing nvariables omitting outliers (marked as NA)
          median_RT_easy_button_press = ifelse(median_RT_easy_button_press < mean_easy + 3*sd_easy, median_RT_easy_button_press, NA), 
         median_RT_hard_button_press = ifelse(median_RT_hard_button_press < mean_hard + 3*sd_hard, median_RT_hard_button_press, NA),
         median_RT_button_press = ifelse(Effort_Choice.n == 0, median_RT_easy_button_press, 
                                         ifelse(Effort_Choice.n == 1, median_RT_hard_button_press, NA)), 
         # add perceived effort by trial. 
         perceived_effort_by_trial = ifelse(Effort_Choice.n == 1, hard_effort_perceived, 
                                            easy_effort_perceived)) %>%
  dplyr::select(SUBJECTID, Effort_Choice.n, Effort_Choice, 
                GROUP_ECA.x, PC1_log, AGE.c, SEX.c, IQ.c, 
         total_censored_TRs, Reinforce_rate.c, 
         Trial_Number, max_keys,
         frustrated, perceived_control, motivated,
         perceived_effort_ave, perceived_effort_by_trial,
         effort_key_count, median_RT_button_press,
         perceived_reinforce, median_motor_RT_ave, 
         win_feeling, lose_feeling)  %>%
  mutate(effort_key_overshoot = effort_key_count -max_keys) %>%
  na.omit() 

N_subs <- length(unique(button_RT_df$SUBJECTID))
N_subs


range(button_RT_df$effort_key_overshoot, na.rm = T) # so why would this not = 0?
```

## check data 

```{r}
key_press_table <- button_RT_df %>%
  group_by(Effort_Choice) %>%
  dplyr::summarize(effort_key_overshoot = mean(effort_key_overshoot, na.rm = T), 
                   sd_key_overshoot = sd(effort_key_overshoot, na.rm = T), 
                   upper = effort_key_overshoot + 2*sd_key_overshoot, 
                   lower = effort_key_overshoot - 2*sd_key_overshoot)
key_press_table 
```

```{r}

ggplot(data = button_RT_df, aes(x = Effort_Choice, y = effort_key_overshoot)) + 
  geom_jitter(color = dark_blue, alpha = 0.1, width = 0.1) + 
  geom_boxplot() + 
  geom_point(data = key_press_table, aes(x = Effort_Choice, y = effort_key_overshoot), 
             size = 3) 

```

# overshoots in button presses 

## basic model with covariates 
motor speed and effort choice
```{r}

key_overshoot_full <- lmer(effort_key_overshoot ~ PC1_log + Effort_Choice.n +
                            AGE.c + SEX.c +  Trial_Number +
                           median_motor_RT_ave + max_keys + 
                         (1 + Effort_Choice.n | SUBJECTID),
                       # can't include trial number random effects with lmer. 
                           # (1 + Effort_Choice.n + Trial_Number.c | SUBJECTID),
                          data = filter(button_RT_df, Accuracy == 1))
summary(key_overshoot_full)
```

## full model with self-report data
AGE, perceived effort, in addition to motor and choice
```{r}

key_overshoot_full <- lmer(effort_key_overshoot ~ PC1_log + Effort_Choice.n +
                            AGE.c + SEX.c +  Trial_Number +
                           median_motor_RT_ave + max_keys +
                         perceived_reinforce + perceived_control + 
                              lose_feeling + win_feeling + 
                              frustrated + motivated + 
                           #   perceived_effort_ave.c +
                         perceived_effort_by_trial+
                         (1 + Effort_Choice.n | SUBJECTID),
                       # can't include trial number random effects with lmer. 
                           # (1 + Effort_Choice.n + Trial_Number.c | SUBJECTID),
                         data = filter(button_RT_df, Accuracy == 1))
summary(key_overshoot_full)

```


## test model with significant effects and necessary covariates
sig effect of perceived effort, motor, max keys, trial N
```{r}
key_overshoot_test <- lmer(effort_key_overshoot ~ PC1_log + Effort_Choice.n +
                            AGE.c +  Trial_Number +  max_keys + 
                         median_motor_RT_ave +
                           #   perceived_effort_ave.c +
                         perceived_effort_by_trial +
                         (1 + Effort_Choice.n | SUBJECTID),
                       # can't include trial number random effects with lmer. 
                           # (1 + Effort_Choice.n + Trial_Number.c | SUBJECTID),
                        data = filter(button_RT_df, Accuracy == 1))
summary(key_overshoot_test)
```



## test without max keys 
sig effect of perceived effort, motor, choice
```{r}
key_overshoot_test <- lmer(effort_key_overshoot ~ PC1_log + Effort_Choice.n +
                            AGE.c +  Trial_Number + 
                         median_motor_RT_ave +
                           #   perceived_effort_ave.c +
                         perceived_effort_by_trial +
                         (1 + Effort_Choice.n | SUBJECTID),
                       # can't include trial number random effects with lmer. 
                           # (1 + Effort_Choice.n + Trial_Number.c | SUBJECTID),
                        data = filter(button_RT_df, Accuracy == 1))
summary(key_overshoot_test)
```

## test without filtering for accuracy 
including trials that didn't get to top of green bar \
 
sig effect of effort, motor, age, choice
```{r}
key_overshoot_test <- lmer(effort_key_overshoot ~ PC1_log + Effort_Choice.n +
                            AGE.c +  Trial_Number + 
                         median_motor_RT_ave +
                           #   perceived_effort_ave.c +
                         perceived_effort_by_trial +
                         (1 + Effort_Choice.n | SUBJECTID),
                       # can't include trial number random effects with lmer. 
                           # (1 + Effort_Choice.n + Trial_Number.c | SUBJECTID),
                        data = button_RT_df)
summary(key_overshoot_test)
```       