---
title: "organizing effort task data"
author: "Michelle.VanTieghem"
date: "Nov 26, 2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# notes
 updated on Jan 29, 2019 to calculate % actual reinforcement per subject for pos vs neg \
updated on March 25, 2019 to include ALL DATA COLLECTED EVER \
 updated April 3, 2019 to make sure reinforcement rate is based on only effort trials that were successful! \
updated November 26, 2019 to record version of task (inside or out of scanner) based on naming of file \
this is an imperfect measure, but better than nothing. \
updated on Dec 16, 2019 to include button press counts and RT.

```{r}
library(stringr)
library(tidyverse)
library(ggplot2)
```

## read files into R 
```{r}
filepath <- "../../behavioral_data/3_effort_task_data/raw_scan_version/"
filelist <- list.files(filepath, pattern = "csv")
length(filelist) # 

data.list <- list()  

for(i in filelist){
  file <- paste0(filepath, i)
  # assign data frame for each subject 
  data.file <-  tryCatch(read.csv(file, sep = ','), error=function(e) NULL)
 data.file <- data.frame(data.file)
  # add data for each subject to list of data frames 
  data.list[[i]] <- data.file
}
length(data.list) # 367 after removing all duplicate runs! 

```

# Make a dataframe with data collapsed by run 
```{r}
cumulative_data <- data.frame()
for (m in 1:length(data.list)){
  df <- data.frame(data.list[[m]])
  # GET RUN NUMBER AND SUBJECTID FROM FILE NAME - NOT FILE CONTENTS
  # BECAUSE FILE NAMES WERE FIXED FOR TYPOS
  filename <- names(data.list)[m]
  # GET VERSION based on name of file...
  keyboard_version <- ifelse(grepl("external_keyboard_handedness", filename), "outside scanner external keyboard", "inside scanner")

  SUBJECTID <- substr(filename, 1, 5)
  filename2 <- unlist(strsplit(filename, "_"))
  Run_number <- filename2[2]
  # GET REST OF INFO FROM ACTUAL DATA
   date <- df$date[1]
   N_trials <- nrow(df)  
    choices <- ifelse(df$Effort_Choice == "Easy", 0, 
                      ifelse(df$Effort_Choice == "Hard", 1, NA))
    # Response rate
    N_choices_missed <-  sum(is.na(choices))
    N_choices_resp <-  N_trials - N_choices_missed
    
    # hard vs. easy overall 
    N_choices_hard <- sum(choices, na.rm = T)
    N_choices_easy <- N_choices_resp - N_choices_hard
    N_prop_hard <- N_choices_hard/ N_choices_resp
    
    # Effort task successful? accuracy on effort tasks.
    N_accurate <- sum(df$Accuracy, na.rm = T)
    Prop_accurate <- N_accurate/N_choices_resp
    N_accurate_hard <- sum(df$Accuracy[df$Effort_Choice == "Hard"], na.rm = T)
    N_accurate_easy <- sum(df$Accuracy[df$Effort_Choice == "Easy"], na.rm = T)
    Prop_accurate_hard <- N_accurate_hard / N_choices_hard
    Prop_accurate_easy <-  N_accurate_easy / N_choices_easy
    
    N_tooslow <- sum(ifelse(df$Accuracy == 0, 1, 0), na.rm = T)
    Prop_tooslow <- N_tooslow/ N_choices_resp
    N_tooslow_hard <- sum(ifelse(df$Accuracy[df$Effort_Choice == "Hard"] == 0, 1, 0), na.rm = T)
    N_tooslow_easy <- sum(ifelse(df$Accuracy[df$Effort_Choice == "Easy"] == 0, 1, 0), na.rm = T)
    Prop_tooslow_hard <- N_tooslow_hard / N_choices_hard
    Prop_tooslow_easy <- N_tooslow_easy / N_choices_easy 
      
    # reinforcement by effort and overall 
    N_reward_trials <- sum(df$Reward_received, na.rm = T)
    N_setback_trials <- N_accurate - N_reward_trials
    # reinforcement only occured for trials where they were accurate! 
    Reinforce_rate <- N_reward_trials/N_accurate
    
    N_hard_reward <- sum(df$Reward_received[df$Effort_Choice == "Hard"], na.rm = T)
    N_hard_setback <- N_accurate_hard - N_hard_reward
    Reinforce_hard <- N_hard_reward / N_accurate_hard
    
    N_easy_reward <- sum(df$Reward_received[df$Effort_Choice == "Easy"], na.rm = T)
    N_easy_setback <- N_accurate_easy - N_easy_reward 
    Reinforce_easy <- N_easy_reward/ N_accurate_easy
    
  
    # cumulate average data for the subject. 
    subdata <- data.frame(SUBJECTID, keyboard_version, date, Run_number,
                          N_trials, N_choices_missed, N_choices_resp,
                          N_choices_hard, N_choices_easy, N_prop_hard,
                          N_accurate, N_accurate_hard, N_accurate_easy,
                          Prop_accurate, Prop_accurate_hard, Prop_accurate_easy,
                          N_tooslow, N_tooslow_hard, N_tooslow_easy,
                          Prop_tooslow, Prop_tooslow_hard, Prop_tooslow_easy,
                          N_reward_trials, N_setback_trials, Reinforce_rate, 
                          N_hard_reward, N_hard_setback, Reinforce_hard, 
                          N_easy_reward, N_easy_setback, Reinforce_easy)
                  
 cumulative_data <- rbind(cumulative_data, subdata)

}
 
head(cumulative_data)
behavior_run_data <- cumulative_data
```

## check for repeated runs - none! 
```{r}

check_runs <- behavior_run_data %>%
  group_by(SUBJECTID) %>%
  dplyr::summarize(N_runs = n()) %>%
  filter(N_runs > 2)
nrow(check_runs)  
check_runs
```  
  

```{r}
save(behavior_run_data, file = "../../behavioral_data/3_effort_task_data/compiled/compiled_effort_scan_version_all_runs.Rdata")
```



# make dataframe in long format for behavior analysis.
only with subjects who should be included.
```{r}

# make an empty dataframe.
data.long <- data.frame()
for(filename in filelist){
  #print (i)
 # filename <- filelist[101]
  file <- paste0(filepath, filename)
  # assign data frame for each subject and read it into R
  data.file <-  tryCatch(read.csv(file, sep = ','), error=function(e) NULL)
  data.file <- data.frame(data.file)
  keyboard_version <- ifelse(grepl("external_keyboard_handedness", filename), "outside scanner external keyboard", "inside scanner")
  # get the subject ID and run number.
  SUB <- substr(filename, 1, 5)
  filename2 <- unlist(strsplit(filename, "_"))
  Run_number <- filename2[2]
  # select items to save for long df 
  sub_df <- data.file %>%
      select(date, Trial_Number, Effort_Choice, 
            key_resp_choice.keys, key_resp_choice.rt,
            Trial_Number_Easy, Trial_Number_Hard, Choice_Number_Miss, 
            max_keys, key_count,  Accuracy, Reward_received) 
  ### GET BUTTON PRESS INFO ### 
  # if they made both hard and easy choices 
    if ('key_resp_effort.rt' %in% names(data.file) & 'key_resp_hard_effort.rt' %in% names(data.file)){
        RT_df <- data.file %>%
            select(date, Trial_Number, key_resp_hard_effort.rt, key_resp_effort.rt ) %>%
             # the easy condition isn't marked as such, only hard is. rename to be more intuitive . 
            rename(cumulative_RT_hard_effort = key_resp_hard_effort.rt, 
                   cumulative_RT_easy_effort = key_resp_effort.rt)
   # if they only had easy choices
  } else if ('key_resp_effort.rt' %in% names(data.file) & !'key_resp_hard_effort.rt' %in% names(data.file)){
        RT_df <- data.file %>%
            select(date, Trial_Number, key_resp_effort.rt) %>%
            rename(cumulative_RT_easy_effort = key_resp_effort.rt) %>%
          # make a variable placeholder and mark NA for hard task RT.
            mutate(cumulative_RT_hard_effort = NA)
    # if they only had hard choices 
    } else if (!'key_resp_effort.rt' %in% names(data.file) & 'key_resp_hard_effort.rt' %in% names(data.file)){
              RT_df <- data.file %>%
            select(date, Trial_Number, key_resp_hard_effort.rt) %>%
            rename(cumulative_RT_hard_effort = key_resp_hard_effort.rt) %>%
          # make a variable placeholder and mark NA for easy task RT.
            mutate(cumulative_RT_easy_effort = NA)
    } 

    #GET THE NUMBER OF PRESSES & mean RT VARIABLES.
   ## EASY 
     RT_df$cumulative_RT_easy_effort <-  as.character(RT_df$cumulative_RT_easy_effort)
     RT_df$cumulative_RT_easy_effort[RT_df$cumulative_RT_easy_effort == ""] <- NA
      easy_buttons <- strsplit(RT_df$cumulative_RT_easy_effort, ",")
      for (i in 1:length(easy_buttons)){
      # only move forward if this isn't an NA for this trial.
        if (!is.na(easy_buttons[[i]])){
             # count number of presses in this trial
            RT_df$N_easy_button_press[i] <- length(easy_buttons[[i]])
            # get mean RT for presses in this trial
            RT_easy_button_press_temp <- as.numeric(cbind(str_extract(easy_buttons[[i]], "[0-9.]+")))
            # they are cumulative, so need to subtract from the button press before to get actual RT for each press.
            # this formula is going to depend on how many presses there are for a given trial.
             RT_easy_button_press_temp2 <- NA
            for (k in 1:length(RT_easy_button_press_temp)){
               if (k == 1){
                 RT_easy_button_press_temp2[k] <- RT_easy_button_press_temp[k]
               } else {
                  RT_easy_button_press_temp2[k] <- RT_easy_button_press_temp[k] - RT_easy_button_press_temp[k-1]
               }
            } # take the average
            RT_df$mean_RT_easy_button_press[i] <- mean(RT_easy_button_press_temp2)
            RT_df$median_RT_easy_button_press[i] <- median(RT_easy_button_press_temp2)
        } else {
          # just mark as NA.
        RT_df$N_easy_button_press[i] <- NA
        RT_df$mean_RT_easy_button_press[i] <- NA
        RT_df$median_RT_easy_button_press[i] <- NA

        }
      }
    ## HARD 
    RT_df$cumulative_RT_hard_effort <-  as.character(RT_df$cumulative_RT_hard_effort)
    RT_df$cumulative_RT_hard_effort[RT_df$cumulative_RT_hard_effort == ""] <- NA
      hard_buttons <- strsplit(RT_df$cumulative_RT_hard_effort, ",")
     # hard_buttons %>% str_match("[0-9]+") %>%  as.numeric()
      for (i in 1:length(hard_buttons)){
      # only move forward if this isn't an NA for this trial.
        if (!is.na(hard_buttons[[i]])){
            # count number of presses in this trial
            RT_df$N_hard_button_press[i] <- length(hard_buttons[[i]])
            # get RT for presses in this trial

            RT_hard_button_press_temp <- as.numeric(cbind(str_extract(hard_buttons[[i]], "[0-9.]+")))
            # they are cumulative, so need to subtract from the button press before to get actual RT for each press.
            # this formula is going to depend on how many presses there are for a given trial.
            RT_hard_button_press_temp2 <- NA
            for (k in 1:length(RT_hard_button_press_temp)){
               if (k == 1){
                 RT_hard_button_press_temp2[k] <- RT_hard_button_press_temp[k]
               } else {
                  RT_hard_button_press_temp2[k] <- RT_hard_button_press_temp[k] - RT_hard_button_press_temp[k-1]
               }
            }
            RT_df$mean_RT_hard_button_press[i] <- mean(RT_hard_button_press_temp2)
            RT_df$median_RT_hard_button_press[i] <- median(RT_hard_button_press_temp2)

        } else {
            # just mark as NA.
            RT_df$N_hard_button_press[i] <- NA
            RT_df$mean_RT_hard_button_press[i] <- NA
            RT_df$median_RT_hard_button_press[i] <- NA

        }
      }
     sub_df2 <- data.frame(SUB, Run_number, keyboard_version, sub_df)
     sub_df3 <- left_join(sub_df2, RT_df, by = c("date", "Trial_Number")) 
        # add data for each subject to list of data frames 
        data.long <- rbind(data.long, sub_df3)
}

#head(data.long)

behavior_long_data <- data.long
save(behavior_long_data, file = "../../behavioral_data/3_effort_task_data/compiled/compiled_long_format_all_data_with_buttonpress.Rdata")
```
