---
title: "post-test behavior"
author: "Michelle Vantieghem"
date: "Nov 26, 2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

This file is not fun, first we match all of the different backups to find the most amount of data. 

# load in cleaned behavior task data, so we know which subjects to pull post-test data
```{r}
library(tidyverse)
load("../../behavioral_data/3_effort_task_data/compiled/compiled_effort_scan_version_filtered_usable_with_demo.Rdata")

sublist_task <- unique(df_by_run_usable_beh$SUBJECTID)
length(sublist_task) # 178 subjects actually have usable effort data.
```

# get post-test data from multiple possible locations

1. my backup that i stopped updating.
```{r}
pt_files1 <- list.files(path = "../../behavioral_data/4_post_test_data/raw_data/", pattern = "csv")
length(pt_files1)

sublist_pt1 <- paste0("PA", substr(pt_files1, 1, 3))
```

2. Lisa's task data folder
```{r}
pt_files2 <- list.files(path = "../../behavioral_data/LG_backups/effort_4_post/", pattern = "csv")
length(pt_files2)

sublist_pt2 <- paste0("PA", substr(pt_files2, 1, 3))
head(sublist_pt2)

```

3. dropbox (checking raw backup, but not needed)
```{r, eval = F, include = F, echo = F}
pt_files3 <- list.files(path = "/Users/michellevantieghem2/Dropbox/Effort_Reward_Game/data/4_effort_reward_post_test/PACCT/", pattern = "csv")
length(pt_files3)

sublist_pt3 <- paste0("PA", substr(pt_files3, 1, 3))
head(sublist_pt3)
```

## find matching files 
```{r}
# 173 files match between Lisa's backup and mine. 
in_pt2_list <- sublist_task[sublist_task %in% sublist_pt2]
length(in_pt2_list)

# there are 5 additional files in Lisa's folder that aren't in mine. 
#These subjects all have effort data data, were not backed up from dropbox but the data were backed up by Lisa! 
not_in_pt2_list <- sublist_task[!sublist_task %in% sublist_pt2]
not_in_pt2_list
length(not_in_pt2_list)

# There are no files in my folder that aren't in Lisa's
in_my_list <- not_in_pt2_list[not_in_pt2_list %in% sublist_pt1]
length(in_my_list)

#in_dropbox_list <- not_in_pt2_list[not_in_pt2_list %in% sublist_pt3]
#length(in_dropbox_list)
```

# read in post-test data
using lisa's folder since it has 173 out of 178
assuming remaining 5 subbjects never completed the post-test questionnaire. 
```{r}
filepath <- "../../behavioral_data/LG_backups/effort_4_post/"

pt_files2 <- list.files(path = filepath, pattern = "csv")

pt.data.list <- list() 
for(i in pt_files2){
  file <- paste0(filepath, i)
  # assign data frame for each subject 
  data.file <-  tryCatch(read.csv(file, sep = ','), error=function(e) NULL)
  data.file <- data.frame(data.file)
  # add data for each subject to list of data frames 
  pt.data.list[[i]] <- data.file
}

#head(pt.data.list)
length(pt.data.list)
save(pt.data.list, file = "../../behavioral_data/4_post_test_data/compiled/compiled_post_test_data_long_format_list.Rdata")
```


# now load this..
1] How much fun did you have playing the game?                                         
[2] How sleepy did you feel during the game?                                            
[3] How motivated did you feel during the game?                                         
[4] How frustrated did you feel during the game?                                        
[5] During the Hard Task:  how much effort did it take ? (how hard did you have to work)
[6] During the Easy Task: how much effort did it take ? (how hard did you have to work)?
[7] how did you feel when you won a lot of coins?                                       
[8] how  did you feel when you did not win a lot of coins that you earned?      
[9] Sometimes, even when you filled up the green bar, you didn't get coins. How often did this happen?
[10] How much control did you feel like you had over winning the coins?                                

```{r}

cumulative_data <- data.frame()

for (m in 1:length(pt.data.list)){

  filename <- names(pt.data.list)[m]
  SUBJECTID <- paste0("PA", substr(filename, 1, 3))
  # get data frame out...
  df <- data.frame(pt.data.list[[m]])
  # only keep post-test if their data is usable
#  if (SUBJECTID %in% sublist_task){
      print(SUBJECTID)
      if(nrow(df) == 8){
        df <- df %>% 
        dplyr::select(Questions, rating.response)
        # for all subjects, we got these 8 measures
        fun <- df$rating.response[1]
        sleepy <- df$rating.response[2]
        motivated <- df$rating.response[3]
        frustrated <- df$rating.response[4]
        hard_effort <- df$rating.response[5]
        easy_effort <- df$rating.response[6]
        win_feeling <- df$rating.response[7]
        lose_feeling <- df$rating.response[8]
          perceived_reinforce <- NA
        perceived_control <- NA
    } else if (nrow(df) > 8){
          if("rating3.response" %in% names(df)){
              df <- df %>% 
              dplyr::select(Questions, rating.response, rating3.response)
              # for all subjects, we got these 8 measures
              fun <- df$rating.response[1]
              sleepy <- df$rating.response[2]
              motivated <- df$rating.response[3]
              frustrated <- df$rating.response[4]
              hard_effort <- df$rating.response[5]
              easy_effort <- df$rating.response[6]
              win_feeling <- df$rating.response[7]
              lose_feeling <- df$rating.response[8]
              perceived_reinforce <- df$rating3.response[9]
              perceived_control <- df$rating3.response[10]
          } else {
               df <- df %>% 
                    dplyr::select(Questions, rating.response)
                # for all subjects, we got these 8 measures
                fun <- df$rating.response[1]
                sleepy <- df$rating.response[2]
                motivated <- df$rating.response[3]
                frustrated <- df$rating.response[4]
                hard_effort <- df$rating.response[5]
                easy_effort <- df$rating.response[6]
                win_feeling <- df$rating.response[7]
                lose_feeling <- df$rating.response[8]
                perceived_reinforce <- df$rating.response[9]
                perceived_control <- df$rating.response[10]
          }
    } 
     # cumulate average data for the subject. 
      subdata <- data.frame(SUBJECTID, fun, sleepy, motivated, frustrated, hard_effort, easy_effort, win_feeling, lose_feeling, perceived_reinforce, perceived_control)
      cumulative_data <- rbind(cumulative_data, subdata)
}

 
head(cumulative_data)
nrow(cumulative_data)
# there are several duplicates.
length(unique(cumulative_data$SUBJECTID))
list_duplicates <- which(duplicated(cumulative_data[,1]),)
# now remove them
cumulative_data2 <- cumulative_data[-c(list_duplicates),]
nrow(cumulative_data2)
length(unique(cumulative_data2$SUBJECTID))
```

```{r}
# rename and save
post_test_df <- cumulative_data2
save(post_test_df, file = "../../behavioral_data/4_post_test_data/compiled/compiled_cleaned_post_test_data.Rdata")

```
