---
title: "cleaning and recoding and feature selection"
author: "Michelle VanTieghem"
date: "October 29, 2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

# notes 
originally done in October 29, 2019  \
Re-doing on Dec 1, 2019 with updated MICM_DV variables 

```{r setup, message = F, echo = F}
source("../../../0_R_analysis_setup_file.R")
```

# Get Raw data 
## Notes:
PULLING RAW DATA FROM MASTER  & NEW TESI CODED SHEET \
copied from danlab server on 10/29 \
if you don't have server access this won't work! 

## get variables from master.
```{r}
pacct_master <- read_excel("../../../../subj_demo/masters/MASTER_20191118_updated_MICM.xlsx") 

TESI_vars <- names(pacct_master)[grepl("TESI", names(pacct_master)) & grepl("CG", names(pacct_master)) 
                    & !grepl("NCG", names(pacct_master)) & !grepl("EARLY", names(pacct_master)) 
                    & !grepl("LATE", names(pacct_master)) & !grepl("ADV", names(pacct_master))]

pacct <- pacct_master %>%
        select(IDENT_SUBID, GROUP, DEM_3_GENDER_CHILD,
         MICM_LOS, MICM_FTP, MICM_EMON, MICM_DV, MICM_EMOA_WO_DV, MICM_PHYSA,MICM_SEXA,
         KSADS_PTSD_J, KSADS_PTSD_K, KSADS_PTSD_L, CGH_SUM_SWITCH, TESI_vars)

```

# cleaning 
## Add better variable names for TESI and KSADS! 

```{r}
# get data dictionary with better labels for each variable name
dictionary <- readxl::read_excel('../../../../../PACCT-CMI-Hackathon/rawData/variableLabels/PACCT_DATA_DICTIONARY_10.25.19.xlsx') %>%
  select(Variable_Name, Variable_Label) %>%
  filter(Variable_Name %in% names(pacct)[grepl("TESI", names(pacct))])

# replacing numbered TESI variable names with better names from data dictionary
TESI_pacct_names <- names(pacct)[grepl("TESI", names(pacct))] 

# 2 of these appeared in the November 2019 version ofo the master. not in data dictionary.
not_including <- TESI_pacct_names[! TESI_pacct_names %in% dictionary$Variable_Name]

# get rid of them for now. 
pacct <- pacct %>%
  select(-not_including)

# have a systematic way to change variables, make sure matching up correctly.
for (variable in TESI_pacct_names){
  if (variable %in% dictionary$Variable_Name){
    # save the matching label
    new_label <- dictionary %>%
      filter(Variable_Name == variable) %>%
      select(Variable_Label) %>%
      as.character()
    # change the column name to the new label in the master.
    names(pacct)[names(pacct) == variable] <- new_label 
  }
}

# update labels for KSADS 
names(pacct)[grepl("KSADS_PTSD_J", names(pacct))] <- "KSADS_PTSD_DV" #KSADS_PTSD_J	Witness to Domestic Violence \
names(pacct)[grepl("KSADS_PTSD_K", names(pacct))] <- "KSADS_PTSD_PA" #KSADS_PTSD_K	Physical Abuse \
names(pacct)[grepl("KSADS_PTSD_L", names(pacct))] <- "KSADS_PTSD_SA" #KSADS_PTSD_L	Sexual Abuse \

```

## Recoding variables 
KSADS: original coding: 0 = unknown, 1 = no diagnosis , 2 = yes diagnosis \
changed to: 0 = not exposed, 1 = exposed \
TESI_family_mental_illness: change 0.25 to 0 
```{r table for KSADS}
pacct_cleaned <- pacct %>%
  # recoding the variables so that 0 = no diagnosis and 1 = diagnosis 
  mutate(KSADS_PTSD_DV = ifelse(KSADS_PTSD_DV  == 0, NA, 
                               ifelse (KSADS_PTSD_DV  == 1, 0, 
                               ifelse(KSADS_PTSD_DV  == 2, 1, NA))),
  KSADS_PTSD_PA = ifelse(KSADS_PTSD_PA == 0, NA, 
                               ifelse (KSADS_PTSD_PA == 1, 0, 
                               ifelse(KSADS_PTSD_PA == 2, 1, NA))),
  KSADS_PTSD_SA = ifelse(KSADS_PTSD_SA == 0, NA, 
                               ifelse (KSADS_PTSD_SA == 1, 0, 
                               ifelse(KSADS_PTSD_SA == 2, 1, NA))), 
  TESI_MENTAL_ILLNESS_CG= ifelse(TESI_MENTAL_ILLNESS_CG == 0.25, 0, TESI_MENTAL_ILLNESS_CG))

```

# Feature selection
## check variable colinearity 

```{r, echo = F}

# note: at this point we are not yet filtering for missing cases
# so there are NAs in the data!

var_cor <- pacct_cleaned %>%
  select(-IDENT_SUBID, -GROUP, -DEM_3_GENDER_CHILD) %>% # remove labels
  as.matrix() %>% # convert to matrix
  rcorr() # calculate correlations


# visualize correlations
corrplot(var_cor$r, method = "color", type = "lower")

# save
pdf("figures/PCA/Caregiving_adversity_variables_corrplot.pdf")
corrplot(var_cor$r, method = "color", type = "lower")
dev.off()

```

## check specific variable correlations

### physical abuse
```{r, echo = F}
 PA_cor <- pacct_cleaned %>%
  select(-IDENT_SUBID, -GROUP, -DEM_3_GENDER_CHILD) %>% # remove labels
  select(contains("PHYS"), contains("PA"), -TESI_SEPARATION_CG) %>%
  as.matrix() %>% # convert to matrix
  rcorr()  #calculate correlations 

PA_cor$r

```


### sexual abuse 
MICM and KSADS highly correlated, TESI not as much
```{r, echo = F}
SA_cor <- pacct_cleaned %>%
  select(-IDENT_SUBID, -GROUP, -DEM_3_GENDER_CHILD) %>% # remove labels
  select(contains("_SA"), contains("SEXA")) %>%
  as.matrix() %>% # convert to matrix
  rcorr()  #calculate correlations 

SA_cor$r
```

###  domestic violence
MICM and KSADS highly correlated, TESI not as much.
```{r, echo = F}
DV_cor <- pacct_cleaned %>%
  select(-IDENT_SUBID, -GROUP, -DEM_3_GENDER_CHILD) %>% # remove labels
  select(contains("DV"), -contains("WO")) %>%
  as.matrix() %>% # convert to matrix
  rcorr()  #calculate correlations 

DV_cor$r
```

## emotional abuse 
REALLY not correlated between TESI and MICM 
```{r, echo = F}
EMOA_cor <- pacct_cleaned %>%
  select(-IDENT_SUBID, -GROUP, -DEM_3_GENDER_CHILD) %>% # remove labels
  select(contains("EMOA")) %>%
  as.matrix() %>% # convert to matrix
  rcorr()  #calculate correlations 

EMOA_cor$r
```


## neglect 
looked at this subset of variables because based on corrplot, they looked correlated.
```{r, echo = F}

Neg_cor <- pacct_cleaned %>%
  select(-IDENT_SUBID, -GROUP, -DEM_3_GENDER_CHILD) %>% # remove labels
  select(contains("LOS"), contains("NEGLECT"), contains("FTP"), CGH_SUM_SWITCH) %>%
  as.matrix() %>% # convert to matrix
  rcorr()  #calculate correlations 

Neg_cor$r
```

## updating variables 
group decided to remove MICM DV because KSADS DV is a better measure \
KSADS PTSD PA is less-specific to caregiving, so remove \
TESI_SEXABUSE WITNESS combined with SEXABUSE because infrequent \
TESI_FAMDV_THREAT combined with TESI_FAM_DV because infrequent \
```{r}
# find concerningly high correlations
any(var_cor$r > 0.8 & var_cor$r < 1.0)

# make changes to the data 
pacct_cleaned <- pacct_cleaned %>%
  select( -MICM_DV, -KSADS_PTSD_PA)  %>% 
  mutate(TESI_SEXABUSE_CG = ifelse(TESI_SEXABUSE_CG == 1, 1, 
                                ifelse(TESI_SEXABUSE_WITNESS_CG == 1, 1, 0)), 
         TESI_FAMDV_CG = ifelse(TESI_FAMDV_CG == 1, 1, 
                                ifelse(TESI_FAMDVTHREAT_CG == 1, 1, 0))) %>%
  select(-TESI_SEXABUSE_WITNESS_CG, -TESI_FAMDVTHREAT_CG)

# set up matrix for correlations
var_cor2 <- pacct_cleaned %>%
  select(-IDENT_SUBID, -GROUP, -DEM_3_GENDER_CHILD) %>% 
  as.matrix() %>% # convert to matrix
  rcorr() # calculate correlations

# removed the too highly correlated variables! 
which(var_cor2$r > 0.8 & var_cor2$r < 1.0)

```

# finish cleaning data:
SAVE DATA.
```{r}

# save
save(pacct_cleaned, file = "data/pacct_all_cleaned_ELV.Rdata")
```
