---
title: "Bootstrap PCA"
author: "Michelle VanTieghem"
date: "October 29, 2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

#Notes:
re-doing on Nov 7, 2019 with Paul's updated PCA pipeline with absolute value loadings instead of squared loadings. \
redoing on Dec 1, 2019 with updated MICM variables. \
updating on Dec 5, 2019 to include non-absolute value loadings.


```{r, echo = F, message = F, warning = F}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(PCAmixdata)
```

# Load in cleaned & standardized & unlabeled data.data

```{r}
load("../data/cleaned_ELV_for_dim_reduction.Rdata")
```

# Bootstrap the PCA

```{r}
# Setup: number of bootstraps and output dataframe
nBoots = 1000
bootFrame = data.frame(eigMat = rep(NA, nBoots), loadings = rep(NA, nBoots))

# start loop to run PCA 1000 times with random sampling
for (i in 1:nBoots){
  blah = FALSE
  while (blah == FALSE){
    # get a sample of data
    ind = sample(1:nrow(pacctNoLabelsCleaned), size = nrow(pacctNoLabelsCleaned), replace = TRUE)
    bootSamples = pacctNoLabelsCleaned[ind, ]
    # only proceed if the current bootstrap sample is usable: 
    # must not have any variables that are all 0 or 1 (correlation would be NA)
     if (!any(is.na(cor(bootSamples)))){
      blah = TRUE # proceed with PCA!
      }
  } 
  # end while loop, continue to run PCA
  
  # run the PCA
  pcaMix1 = bootSamples %>%
    PCAmix(., graph=FALSE, ndim = ncol(bootSamples))
  
  # Extract eigenvalue matrix, loadings, and subject-level predictions
  bootFrame$eigMat[i] = list(pcaMix1$eig)
  bootFrame$loadings[i] = list(abs(pcaMix1$quanti$coord))
  bootFrame$subPreds[i] = list(pcaMix1$scores)
  
}


save(bootFrame, file = '../PCA_output/pcaBootstrap.rda')
```

# PCA on full sample as 'template'

```{r}
pcaFull = PCAmix(pacctNoLabelsCleaned, graph = FALSE, ndim = ncol(pacctNoLabelsCleaned))
pcaFullSample = list(pcaFull$eig, abs(pcaFull$quanti$coord))

save(pcaFull, file = '../PCA_output/pcaFullSampleModel.rda')
save(pcaFullSample, file = '../PCA_output/pcaFullSample.rda')

# create a *key* linking subject numbers in the model with PACCT subject numbers
pcaFullScores = data.frame(pcaFull$scores)
pcaFullScores$subject= row.names(pcaFullScores)

# add SUBIDS from original labeled data
load("../data/pacct_effort_w_labels.Rdata")
# first confirm that identical dataset lengths
identical(nrow(pcaFullScores), nrow(pacct_effort_w_labels))
# now add the subids to the pca output 
pcaFullScores$IDENT_SUBID = pacct_effort_w_labels$IDENT_SUBID

save(pcaFullScores, file = '../PCA_output/pcaFullScoresKey.rda')
```


# How do we get the absolute value loadings?
The way PCAmix calculates loadings (saved in the quanti.cor object) for a given component is to correlate the raw scores of a variable for each subject with the subject's predicted score (scores object) on that same component

The sqload object is the squares of these loadings

See: https://www.rdocumentation.org/packages/PCAmixdata/versions/3.1/topics/PCAmix
```{r}
# absolute value of the loading for MICM_LOS from teh fullsubject sample, for dimension 1
abs(pcaFull$quanti$coord)[1]

pcaFull$quanti$coord[1]

# Just a demonstration of how loadings are calculated -- this should be the same as cell [1,1]
# subject's MICM_LOS score for dimension 1 x their actual value for MICM_LOS
cor(pcaFull$scores[,1], pacct_effort_w_labels$MICM_LOS)
```

# How do we get the non-absolute value loadings? (raw)
```{r}
regularLoadings = pcaFull$quanti$coord[, 1:5] %>%
  as.data.frame() %>%
  mutate(., vars = row.names(.)) %>%
  tidyr::gather(., key = 'dimensions', value = 'loading', contains('dim'))

save(regularLoadings, file = '../PCA_output/pcaFullLoadingsNotAbsVal.rda')

ggplot(regularLoadings, aes(x = vars, y = loading)) +
  geom_hline(yintercept = 0) +
  geom_point() + 
  facet_grid(~dimensions) + 
  coord_flip() + 
  theme_bw()

```