---
title: "Adding PCA to effort data"
author: "Michelle.VanTieghem"
date: "6/7/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

#TO DO:
use tidy(model) as the output printing! 
add invlogit() to your coefficients to get predicted probabilities of the choices. 
check whether the effect package is correctly displaying probability vs. logit thing.
could use predict() instead, like the brms version.

# Notes 
## group coding explanations:
PI_DA = self-created variable for adopted vs. not: used for COMP paper as sample \
Recruitment_group = 6 updated groups from master in August 2019
GROUP = COMP = C from recruitment group, ECA = any adversity (DC, IFC, DA, PI)
IDENT_SUBTYPE_CODED = old GROUP from master in June, don't use it.



```{r, include = F, warning = F, echo=FALSE, message = F}
source("../../../0_R_analysis_setup_file.R", echo=F)
```

# Load data 
```{r}
load("../../../9_combine_brain_beh_data/cleaned_data/COMP_ECA/all_pacct_effort_data.Rda")
```


## add most updated cruitment group designations from october 2019
```{r}
master <- read_excel("../../../../subj_demo/masters/MASTER_W1_20200309.xlsx") 

demo <- master %>%
  dplyr::select(IDENT_SUBID, GROUP) %>%
  mutate(SUBJECTID = substr(IDENT_SUBID, 1, 5), 
         GROUP_ECA = as.factor(ifelse(GROUP == "C", "COMP", "ECA")))
```

## add full sample PC1 scores to datasets
check missing data, because PCA scores noto available for some subjects
```{r}
#load('model_results/PCA/bootstrapPCASubjectLoadings.Rdata') # not using bootstrappeds cores for now.
load("../PCA_output/pcaFullSampleScoresWithLabels.rda")

nrow(pacctPCAscores) 
names(pacctPCAscores)

# 10 subjects have scan but don't have PCA - because they don't have TESI. 
sum(!beh_scan_ECA_wide$SUBJECTID %in% pacctPCAscores$SUBJECTID)

# 45 subjects have PCA but don't have scan  
sum(!pacctPCAscores$SUBJECTID %in% beh_scan_ECA_wide$SUBJECTID)


```


## PC1 & PC 2 
check normality.
```{r}

min_boot <- min(pacctPCAscores$BootstrapPC1)
hist(pacctPCAscores$BootstrapPC1)
hist(pacctPCAscores$BootstrapPC1)
hist(sqrt(pacctPCAscores$BootstrapPC1 - min_boot))
# log version needs to add a positive value, because all of the COMPS = 0
hist(log(pacctPCAscores$BootstrapPC1 - min_boot + 1))
```


```{r}
min_boot <- min(pacctPCAscores$BootstrapPC2)
hist(pacctPCAscores$BootstrapPC2)
hist(sqrt(pacctPCAscores$BootstrapPC2 - min_boot + 1))
#log(sqrt(pacctPCAscores$BootstrapPC2 - min_boot + 1))

shapiro.test(pacctPCAscores$BootstrapPC2)
shapiro.test(sqrt(pacctPCAscores$BootstrapPC2))
```


### transform variable
no matter what you do,never going to be normal.
```{r}

shapiro.test(pacctPCAscores$BootstrapPC1)
# these are both bad, but better.
shapiro.test(log(pacctPCAscores$BootstrapPC1 - min_boot + 1))
shapiro.test(sqrt(pacctPCAscores$BootstrapPC1- min_boot + 1))

PCA_scores <- pacctPCAscores %>%
  dplyr::select(SUBJECTID, BootstrapPC1, BootstrapPC2, starts_with("CBCL")) %>%
  rename(PC1 = BootstrapPC1,
         PC2 = BootstrapPC2) %>%
  mutate(PC1_sqrt = sqrt(PC1 - min_boot), 
         PC1_log = log(PC1 - min_boot + 1), 
         PC2_sqrt = sqrt(PC2 - min_boot), 
         PC2_log = log(PC2 - min_boot + 1))

```

```{r}
# merge with all the data 
beh_ECA_wide <- merge(beh_ECA_wide, PCA_scores, by = "SUBJECTID", all = T)  %>%
  merge(., demo, by = "SUBJECTID")

beh_ECA_wide_WSLS <- merge(beh_ECA_wide_WSLS, PCA_scores, by = "SUBJECTID") %>%
  merge(., demo, by = "SUBJECTID")

beh_ECA_long <- merge(beh_ECA_long, PCA_scores, by = "SUBJECTID") %>%
  merge(., demo, by = "SUBJECTID")

beh_ECA_long_WSLS <- merge(beh_ECA_long_WSLS, PCA_scores, by = "SUBJECTID")%>%
  merge(., demo, by = "SUBJECTID")

# scanning data 
beh_scan_ECA_wide <- merge(beh_scan_ECA_wide, PCA_scores, by = "SUBJECTID") %>%
  merge(., demo, by = "SUBJECTID")
nrow(beh_scan_ECA_wide)

beh_scan_ECA_wide_WSLS <- merge(beh_scan_ECA_wide_WSLS, PCA_scores, by = "SUBJECTID") %>%
  merge(., demo, by = "SUBJECTID")

beh_scan_ECA_long <- merge(beh_scan_ECA_long, PCA_scores, by = "SUBJECTID") %>%
  merge(.,
        demo, by = "SUBJECTID")
beh_scan_ECA_long_WSLS <- merge(beh_scan_ECA_long_WSLS, PCA_scores, by = "SUBJECTID")%>%
  merge(., demo, by = "SUBJECTID")

## save all of it as rda file!! 
save(beh_ECA_wide, beh_ECA_wide_WSLS, beh_ECA_long, beh_ECA_long_WSLS, 
     beh_scan_ECA_wide, beh_scan_ECA_wide_WSLS, beh_scan_ECA_long, beh_scan_ECA_long_WSLS, 
     file = "../data/all_pacct_effort_data_with_PCA.rda")
```


## compare GROUPS with PC1
### calculate missing PC1 by recruitment group.
these are subjects who are missing TESI variables. 
```{r}

PC1_table <- beh_ECA_wide %>%
  filter(!is.na(Recruitment_group)) %>%
  group_by(Recruitment_group) %>%
  dplyr::summarize(total_n = n(),
            has_PC1 = sum(!is.na(PC1_sqrt)),
            no_PC1 = sum(is.na(PC1_sqrt)))

PC1_table

# now remove the people who don't have PC1
beh_ECA_wide <- beh_ECA_wide %>%
  filter(!is.na(PC1_sqrt))
```


# Plots of PC1 and group(s)
COMP vs. any adversity 
```{r}

ggplot(beh_ECA_wide, aes(x = GROUP_ECA, y = PC1_log)) + 
  geom_boxplot() + theme_classic()+ geom_jitter(alpha = 0.5, width = 0.05)

```

with bio parent vs. adopted 
```{r}
ggplot(beh_ECA_wide, aes(x = as.factor(PI_DA), y = PC1_log)) + 
  geom_boxplot() + theme_classic() + geom_jitter(alpha = 0.5, width = 0.05)

```

recruitment groups 
```{r}
ggplot(beh_ECA_wide, aes(x = Recruitment_group, y = PC1_log)) + 
  geom_boxplot() + theme_classic()+ geom_jitter(alpha = 0.5, width = 0.05)

```

## plots of PC2 

COMP vs. any adversity 
```{r}

ggplot(beh_ECA_wide, aes(x = GROUP_ECA, y = PC2)) + 
  geom_boxplot() + theme_classic()+ geom_jitter(alpha = 0.5, width = 0.05)

```



with bio parent vs. adopted 
```{r}
ggplot(beh_ECA_wide, aes(x = as.factor(PI_DA), y = PC2)) + 
  geom_boxplot() + theme_classic() + geom_jitter(alpha = 0.5, width = 0.05)

```


```{r}
ggplot(beh_ECA_wide, aes(x = Recruitment_group, y = PC2)) + 
  geom_boxplot() + theme_classic()+ geom_jitter(alpha = 0.5, width = 0.05)

```