---
title: "Demographics & data checks for ECA paper"
author: "Michelle.VanTieghem"
date: "6/7/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    df_print: paged
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r, include = F, warnings = F, echo=FALSE}
library(tidyverse)
library(lmerTest)
library(ggplot2)
library(effects)
library(corrplot) # for pretty correlation plots 
library(psycho) # for pretty correlation tables.

# color scheme 
my_colors <-  scale_color_manual(values=c("#0006CC", "#CC0000", "black", "black"))
my_colors2 <- scale_fill_manual(values=c("#0006CC", "#CC0000","black", "black"))
dark_blue = "#0006CC"
dark_Red = "#CC0000"
```


# Load data 
```{r}
# load all data with PCA added!
load("data/all_pacct_effort_data_with_PCA.rda")
```


# DEMOGRAPHICS 

## everyone by recruitment group
```{r}
nrow(beh_ECA_wide)
sum(is.na(beh_ECA_wide$PC1))

ECA_detailed_demo_table <- beh_ECA_wide %>%
  filter(!is.na(PC1)) %>%
  mutate(Recruitment_group = ifelse(Recruitment_group == "IFC" | Recruitment_group == "PI", "IA", Recruitment_group)) %>%
  group_by(Recruitment_group) %>%
  dplyr::summarize (N = n(), 
             mean_age = round(mean(AGE, na.rm = T), 2),
             sd_age = round(sd(AGE, na.rm = T), 2),
             min_age = round(min(AGE, na.rm =T), 2),
             max_age= round(max(AGE, na.rm = T),2),
             N_female = sum(SEX, na.rm = T),
             N_male = n() - sum(SEX, na.rm = T), 
             mean_IQ = round(mean(IQ, na.rm = T),2),
             sd_IQ = round(sd(IQ, na.rm = T),2), 
             mean_fam_inc_needs = round(mean(Fam_inc_needs, na.rm = T), 2),
             sd_fam_inc_needs = round(sd(Fam_inc_needs, na.rm = T),2),
             perc_below_poverty = round(sum(ifelse(Fam_inc_needs < 1, 1, 0), na.rm = T)/n(),2))
stuff <- t(ECA_detailed_demo_table)
stuff 
write.csv(stuff, file = "tables/ECA_detailed_demo_table.csv", row.names = T)

```

## demo table for  behavior sample
```{r}
# confirm no one has WASI < 70
#beh_ECA_wide %>% filter(IQ < 70)

ECA_beh_demo_table <- beh_ECA_wide %>%
  filter(!is.na(PC1)) %>%
  dplyr::summarize (N = n(), 
             Prop_female = round(sum(SEX, na.rm = T)/n(),2),
             mean_age = round(mean(AGE, na.rm = T), 2),
             sd_age = round(sd(AGE, na.rm = T), 2),
             min_age = round(min(AGE, na.rm =T), 2),
             max_age= round(max(AGE, na.rm = T),2))
ECA_beh_demo_table

```

## demo table for scan sample
```{r}
ECA_scan_demo_table <- beh_scan_ECA_wide %>%
  dplyr::summarize (N = n(), 
             Prop_female = round(sum(SEX.x, na.rm = T)/n(),2),
             mean_age = round(mean(AGE.x, na.rm = T), 2),
             sd_age = round(sd(AGE.x, na.rm = T), 2),
             min_age = round(min(AGE.x, na.rm =T), 2),
             max_age= round(max(AGE.x, na.rm = T),2))
ECA_scan_demo_table
```

## combined demo table 
```{r}
# combine them! 
demo_table_pretty <- data.frame(t(rbind(ECA_beh_demo_table, ECA_scan_demo_table)))
names(demo_table_pretty) <- c("Behavior", "Scanning")
#demo_table_pretty

save(demo_table_pretty, file= "tables/Demo_ECA_behavior_and_scan.Rdata")
wide_table <- t(demo_table_pretty) 
wide_table 
write.csv(wide_table, file = "tables/demo_table_pretty_wide_for_poster.csv")

```

## plot age
```{r}
age_hist <- ggplot(data = beh_ECA_wide, aes(x = AGE)) + 
  geom_histogram(bins = 12, fill = dark_blue, alpha = 0.5) + theme_classic() 
#pdf("figures/manipulation_checks/ECA_age_hist.pdf", width = 8, height= 4)
age_hist
#dev.off()
```

## plot SES
income to needs = total household income / poverty threshold for 2018
living below poverty threshold if < 1 
```{r}
 ggplot(data = beh_ECA_wide, aes(x = Fam_inc_needs)) + 
  geom_histogram(bins = 10, fill = dark_blue, alpha = 0.5) + theme_classic() 

```


## Age checks: differnces in # trials? yes!
age is correlated with number of trials
```{r}

cor.test(beh_ECA_wide$AGE, beh_ECA_wide$N_trials)
ggplot(data = beh_ECA_wide, aes(x = AGE, y = N_trials)) + 
  geom_jitter(alpha = 0.5) + geom_smooth()  + theme_classic () 

# no more duplicated data!
check <- beh_ECA_wide %>%
  filter(N_trials > 42)
check
```


# Aim 1: Manipulation checks
## post-scan questions
```{r}
#names(beh_ECA_wide)
mean_table <- beh_ECA_wide %>% 
  dplyr::summarize(perceived_reinforce = mean(as.numeric(as.character(perceived_reinforce)), na.rm = T), 
            perceived_control= mean(as.numeric(as.character(perceived_control)), na.rm = T), 
            perceived_effort_hard = mean(as.numeric(as.character(hard_effort_perceived)), na.rm = T), 
            perceived_effort_easy = mean(as.numeric(as.character(easy_effort_perceived)), na.rm = T), 
            fun = mean(as.numeric(as.character(fun)), na.rm = T), 
            motivated = mean(as.numeric(as.character(motivated)), na.rm = T), 
            frustrated = mean(as.numeric(as.character(frustrated)), na.rm = T), 
            sleepy = mean(as.numeric(as.character(sleepy)), na.rm = T), 
            win_feeling = mean(as.numeric(as.character(win_feeling)), na.rm = T), 
            lose_feeling = mean(as.numeric(as.character(lose_feeling)), na.rm = T))
mean_table <- data.frame(t(mean_table))
names(mean_table) <- "mean"

sd_table <- beh_ECA_wide %>% 
  dplyr::summarize(perceived_reinforce = sd(as.numeric(as.character(perceived_reinforce)), na.rm = T), 
            perceived_control= sd(as.numeric(as.character(perceived_control)), na.rm = T), 
            perceived_effort_hard = sd(as.numeric(as.character(hard_effort_perceived)), na.rm = T), 
            perceived_effort_easy = sd(as.numeric(as.character(easy_effort_perceived)), na.rm = T), 
            fun = sd(as.numeric(as.character(fun)), na.rm = T), 
            motivated = sd(as.numeric(as.character(motivated)), na.rm = T), 
            frustrated = sd(as.numeric(as.character(frustrated)), na.rm = T), 
            sleepy = sd(as.numeric(as.character(sleepy)), na.rm = T), 
            win_feeling = sd(as.numeric(as.character(win_feeling)), na.rm = T), 
            lose_feeling = sd(as.numeric(as.character(lose_feeling)), na.rm = T))
sd_table <- data.frame(t(sd_table))
names(sd_table) <- "sd"
sd_table$variable <- rownames(sd_table) 

post_test_table <- cbind(mean_table, sd_table) %>%
  select(variable, mean, sd)
post_test_table

save(post_test_table, file = "tables/post_test_self_report_descriptives.Rdata")
```

## histograms of self-report data

### perceived control
```{r}
df <- beh_ECA_wide %>%
  filter(!is.na(perceived_control)) %>%
group_by(perceived_control) %>%
  dplyr::summarize(counts = n())


pc_plot <- ggplot(df, aes(x = factor(perceived_control), y = counts)) + 
    scale_x_discrete(labels = c("1" = "None", "2" = "Some", "3" = "Alot")) +
  geom_bar(stat = "identity", fill = dark_blue, alpha = 0.3) + theme_classic() +
  xlab ("Perceived Control")

pc_plot

pdf("figures/manipulation_checks/ECA_perceived_control_hist.pdf", width = 2.5, height= 4)
pc_plot
dev.off()
```

### reinforcement rate... 
```{r}
df <- beh_ECA_wide %>%
  filter(!is.na(perceived_reinforce)) %>%
group_by(perceived_reinforce) %>%
  dplyr::summarize(counts = n())


pc_plot <- ggplot(df, aes(x = factor(perceived_reinforce), y = counts)) + 
    scale_x_discrete(labels = c("1" = "Less than half", "2" = "Half the time", "3" = "More than half")) +
  geom_bar(stat = "identity", fill = dark_blue, alpha = 0.3) + theme_classic() +
  xlab ("Perceived Reinforcement (Reward Rate)")

pc_plot

pdf("figures/manipulation_checks/ECA_perceived_reinforcement_hist.pdf", width = 3, height= 4)
pc_plot
dev.off()

```


### motivation  
```{r}
df <- beh_ECA_wide %>%
  filter(!is.na(motivated)) %>%
group_by(motivated) %>%
  dplyr::summarize(counts = n())


pc_plot <- ggplot(df, aes(x = factor(motivated), y = counts)) + 
  geom_bar(stat = "identity", fill = dark_blue, alpha = 0.3) + theme_classic() +
  xlab ("Motivation")

pc_plot

pdf("figures/manipulation_checks/ECA_motivated_hist.pdf", width = 3, height= 4)
pc_plot
dev.off()

```


### frustrated  
```{r}
df <- beh_ECA_wide %>%
  filter(!is.na(frustrated)) %>%
group_by(frustrated) %>%
  dplyr::summarize(counts = n())


pc_plot <- ggplot(df, aes(x = factor(frustrated), y = counts)) + 
  geom_bar(stat = "identity", fill = dark_blue, alpha = 0.3) + theme_classic() +
  xlab ("frustrated")

pc_plot

pdf("figures/manipulation_checks/ECA_frustrated_hist.pdf", width = 3, height= 4)
pc_plot
dev.off()

```


### win feeling (positive affect)
```{r}
df <- beh_ECA_wide %>%
  filter(!is.na(win_feeling)) %>%
group_by(win_feeling) %>%
  dplyr::summarize(counts = n())


pc_plot <- ggplot(df, aes(x = factor(win_feeling), y = counts)) + 
  geom_bar(stat = "identity", fill = dark_blue, alpha = 0.3) + theme_classic() +
  xlab (" Win Feeling (positive affect)")

pc_plot

pdf("figures/manipulation_checks/ECA_win_feeling_hist.pdf", width = 3, height= 4)
pc_plot
dev.off()

```


### lose feeling (positive affect)
```{r}
df <- beh_ECA_wide %>%
  filter(!is.na(lose_feeling)) %>%
group_by(lose_feeling) %>%
  dplyr::summarize(counts = n())


pc_plot <- ggplot(df, aes(x = factor(lose_feeling), y = counts)) + 
  geom_bar(stat = "identity", fill = dark_blue, alpha = 0.3) + theme_classic() +
  xlab ("Lose feeling (negative affect)")

pc_plot

pdf("figures/manipulation_checks/ECA_lose_feeling_hist.pdf", width = 3, height= 4)
pc_plot
dev.off()

```


## correlations of self-report data

### perceived vs. actual reinforcement 
```{r}

#names(beh_ECA_wide)
# perceived reinforcement is correlated with actual reinforcement.
reinforce_vars <- beh_ECA_wide %>%
  select(AGE, IQ, Reinforce_rate,  perceived_reinforce) 

cor_table <- correlation(reinforce_vars)
cor_table_reinforce <- summary(cor_table)
cor_table_reinforce
save(cor_table_reinforce, file = "tables/corr_table_perceived_vs_actual_reinforcement.Rdata")

reinforce_plot <- ggplot(data = beh_ECA_wide, aes(x = Reinforce_rate, y = perceived_reinforce)) + 
  geom_point(color = dark_blue, alpha = 0.3) + geom_smooth( method = "lm", color = dark_blue, fill = dark_blue) + 
  theme_classic() + ylab(" Perceived Reinforcement Rate") + xlab ("Actual Reinforcement Rate")

reinforce_plot

pdf("figures/manipulation_checks/corr_reinforce_plot.pdf", width = 4, height = 4)
reinforce_plot
dev.off()
```



### motivation correlated with perceived control 
```{r}
control <- beh_ECA_wide %>%
  filter(perceived_control <= 3) %>%
  select(AGE, IQ, perceived_control, perceived_reinforce, frustrated, motivated, 
         win_feeling, lose_feeling)
cor_table <- correlation(control)
cor_table_control <- summary(cor_table)
cor_table_control
save(cor_table_control, file = "tables/corr_table_motivation_perceived_control.Rdata")

# this should actually be a bar graph!! 
beh_ECA_wide <- beh_ECA_wide %>%
  mutate(perceived_control.f = as.factor(ifelse(perceived_control >= 3, "3", 
                                      ifelse(perceived_control == 2, "2", "1"))))
anova_percieved <- lm(motivated ~ perceived_control.f, data = subset(beh_ECA_wide, !is.na(perceived_control.f)))

effect_df <- data.frame(effect("perceived_control.f", anova_percieved))
order <- c("1", "2", "3", "")
levels(effect_df$perceived_control.f) <- order
summary(effect_df$perceived_control.f)

levels(beh_ECA_wide$perceived_control.f) <- order
summary(beh_ECA_wide$perceived_control.f)
control_plot <- ggplot(data = effect_df,
                       aes(x = perceived_control.f, y = fit)) + 
  geom_bar(stat = "identity", fill= dark_blue, alpha = 0.3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.5, color = dark_blue) +
  geom_jitter(data = beh_ECA_wide, aes(x = perceived_control.f, y = motivated), 
              width = 0.1, height = 0.0, color = dark_blue, alpha = 0.3) + 
  theme_classic() + ylab("Self-reported motivation") + xlab ("Perceived Control")

control_plot

pdf("figures/manipulation_checks/corr_perceived_control_motivation.pdf", width = 2.5, height = 4)
control_plot
dev.off()
```

### age isn't correlated with perceived effort, but is correlated with motor skills.
```{r}
effort_vars <- beh_ECA_wide %>%
  select(AGE, IQ, motor_skills_easy, motor_skills_hard, hard_effort_perceived, easy_effort_perceived) %>%
  mutate(motor_skills_ave = (motor_skills_hard + motor_skills_easy)/2, 
        perceived_effort_ave = (hard_effort_perceived +easy_effort_perceived)/2)

cor_table <- correlation(effort_vars)
cor_table_motor <- summary(cor_table)
cor_table_motor
save(cor_table_motor, file = "tables/corr_table_motor_age_perceived_effort.Rdata")


motor_plot <- ggplot(data = beh_ECA_wide, aes(x = AGE, y = motor_skills_hard)) + 
  geom_point(color = dark_blue, alpha = 0.3) + geom_smooth( method = "lm", color = dark_blue, fill = dark_blue) + 
  theme_classic() + ylab("Motor skills for hard task") + xlab ("Age (years)")

motor_plot

pdf("figures/manipulation_checks/corr_motor_age_plot.pdf", width = 4, height = 4)
motor_plot
dev.off()
```

### perceived effort correlated with motor skills 
```{r}

motor_plot <- ggplot(data = beh_ECA_wide, aes( y = motor_skills_hard, hard_effort_perceived)) + 
  geom_jitter(color = dark_blue, alpha = 0.3, width = 0.1, height  = 0.1) +
  geom_smooth( method = "lm", color = dark_blue, fill = dark_blue) + 
  theme_classic() + xlab("Motor skills for hard task") + ylab ("Perceived effort on hard task")

motor_plot

pdf("figures/manipulation_checks/corr_motor_perceived_effort_plot.pdf", width = 4, height = 4)
motor_plot
dev.off()
```

