---
title: "ECA effects on actual effort"
author: "Michelle.VanTieghem"
date: "Dec 16, 2019"
output:
  html_document:
    number_sections: no
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# notes 
Need to re-do with bmrs models and random effects to see if over-shoot pressing is accounted for.


```{r, include = F, warnings = F, echo=FALSE, message = F}
source("../../../0_R_analysis_setup_file.R")
```


```{r}
# load all data with PCA added!
load("data/all_pacct_effort_data_with_PCA.rda")

```

# clean data first 
```{r}

#remove outliers from RT calculations first! 
# and also filter out trials where they didn't reach the top! 
button_RT_df <- beh_scan_ECA_long %>%
  filter(Accuracy == 1) %>%
  mutate(mean_easy <- mean(median_RT_easy_button_press, na.rm = T),
          sd_easy <- sd(median_RT_easy_button_press, na.rm = T),
         mean_hard <- mean(median_RT_hard_button_press, na.rm = T), 
         sd_hard <- sd(median_RT_hard_button_press, na.rm = T),
          median_RT_easy_button_press = ifelse(median_RT_easy_button_press < mean_easy + 3*sd_easy, median_RT_easy_button_press, NA), 
         median_RT_hard_button_press = ifelse(median_RT_hard_button_press < mean_hard + 3*sd_hard, median_RT_hard_button_press, NA),
         median_RT_button_press = ifelse(Effort_Choice.n == 0, median_RT_easy_button_press, 
                                         ifelse(Effort_Choice.n == 1, median_RT_hard_button_press, NA)))

save(button_RT_df, file = "data/button_RT_df.Rdata")
```


# check data 

```{r}
key_press_table <- button_RT_df %>%
  group_by(Effort_Choice) %>%
  dplyr::summarize(effort_key_count = mean(effort_key_count, na.rm = T), 
                   sd_key_count = sd(effort_key_count, na.rm = T), 
                   upper = effort_key_count + 2*sd_key_count, 
                   lower = effort_key_count - 2*sd_key_count)
key_press_table 


ggplot(data = button_RT_df, aes(x = Effort_Choice, y = effort_key_count)) + 
  geom_jitter(color = dark_blue, alpha = 0.1, width = 0.1) + 
  geom_boxplot() + 
  geom_point(data = key_press_table, aes(x = Effort_Choice, y = effort_key_count), 
             size = 3) + ylim (0, 16)

sd(button_RT_df$effort_key_count[button_RT_df$Effort_Choice == "Hard"])
```

# 1. ECA effects on number of button presses during hard/easy tasks

## main effects of Effort Choice, max keys (titration) and motor speed (RT) and trial Number
all expected  effects. 

```{r}

load("brms_models/results/actual_effort/effort_key_count_main_effects.Rdata")  

blm_table(key_count_mod_brms)
```



## PC1 x effort choice: NS
```{r}
load("brms_models/results/actual_effort/effort_key_count_PC1xe.Rdata")
blm_table(key_count_mod_brms_PC1xe)

```

### PC1 log x  perceived effort ave: NS 
```{r}

load("brms_models/results/actual_effort/effort_key_count_PC1xpe.Rdata")
blm_table(key_count_mod_PC1xpe)

```


# 2. Check with overshoots (button press - max keys)

note: overshoot represents #presses vs. #required for the task
important to use this, since hard task buttons were titrated 
also controlling for perceived effort and median motor RT.

```{r}
# make a wide df for plotting 

actual_effort_df <- button_RT_df %>%
  gather(key = Effort_Choice, value = effort_key_overshoot, effort_key_overshoot_hard, effort_key_overshoot_easy) %>%
  mutate(Effort_Choice = ifelse(Effort_Choice == "effort_key_overshoot_hard", "Hard", "Easy"))

range(button_RT_df$effort_key_overshoot) # so why would this not = 0?
range(button_RT_df$Accuracy) # everyone "reached the green bar"
```

## full model with self-report covariates 
perceived effort and motor skills! and choices.
```{r}
load("../model_results/brms/actual_effort/overshoot_mod_full.Rdata")
blm_table(overshoot_mod_full)
```

## main effect of Choice & motor speed 
```{r}
load("brms_models/results/actual_effort/overshoot_main_effects.Rdata")
blm_table(overshoot_mod)
```

### plot modeled effects of EFfort Choice 
```{r}
new_df <- data.frame(expand.grid(PC1_log = mean(button_RT_df$PC1_log), 
                                 perceived_effort_ave = mean(button_RT_df$perceived_effort, na.rm = T),
                                 median_motor_RT_ave = mean(button_RT_df$median_motor_RT_ave, na.rm = T),
                                 Effort_Choice.n = c(0, 1), 
                                 AGE.c = 0, Trial_Number.c =0, Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(overshoot_mod, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(intercept = as.factor('intercept'), 
         Trial_Number = Trial_Number.c + max(Trial_Number.c), 
         Effort_Choice = as.factor(ifelse(Effort_Choice.n == 0, "Easy", "Hard")))

effect_plot <- ggplot(effect_df, aes(x = Effort_Choice, y = fit)) +
  geom_point(color = dark_blue)  + 
 geom_errorbar(aes(ymin= lower, ymax= upper), color = dark_blue,  width = 0.25) +
   theme_classic() + theme(legend.position = "none") + 
  ylab ("Key Press Overshoots")  + xlab ("Effort Choice") 
effect_plot

ggsave(effect_plot, file = "figures/actual_effort/effort_key_overshoot_by_condition.pdf", width = 2.5, height = 4)

```


## PC1 X Effort effects on overshoot: NS 
same as above.
```{r}

load("brms_models/results/actual_effort/overshoot_PC1xe.Rdata")
blm_table(overshoot_mod_PC1xe)
```


## PC1 X perceived_Effort effects on overshoot: NS
```{r}

load("brms_models/results/actual_effort/overshoot_PC1xpe.Rdata")
blm_table(overshoot_mod_PC1xpe)
```


# 3.  RT during hard/easy tasks:
notes: using median RT and removing outliers first! 
outliers are prbably also trials where they didn't reach the top.
```{r}
hist(button_RT_df$median_RT_hard_button_press)
hist(button_RT_df$median_RT_easy_button_press)

```

## no main effects of ECA or perceived effort.
just motor speed, age, and choice
```{r}
load("brms_models/results/actual_effort/key_press_RT_main_effects.Rdata")
blm_table(press_RT_mod)
```

### plot main effects of age and condition
```{r}
#ggsave(plot_effect, file = "figures/actual_effort/key_press_RT_by_age_and_choice.pdf", width = 2.5, height = 4)

```

##  age x choice interaction on press RT: NS
```{r}
load("brms_models/results/actual_effort/key_press_RT_axe.Rdata")
blm_table(press_RT_mod_axe)
```

## PC1 x effort choice effect on pressing RT: almost trend. but NS. 
```{r}
load("brms_models/results/actual_effort/key_press_RT_PC1xc.Rdata")
blm_table(press_RT_mod_PC1xe)
```

## PC1 x perceived effort effect on pressing RT: NS
```{r}
load("brms_models/results/actual_effort/key_press_RT_PC1xpe.Rdata")
blm_table(press_RT_mod_PC1xpe)
```



# ECA effects on motor speed (RT) during pre-test 
median_motor_RT_hard/easy reprseents the MEDIAN RT from the button presses \
Not using BRMS because this is not trial-wise data. \


## make a wide data version with perceived effort and motor skills.

```{r}
# there is only one score per participant, so use wide data!! 

# only include participants who successfully completed both finger tapping tests. 
motor_df <- beh_scan_ECA_wide %>%
   filter(motor_key_count_hard > 0 & motor_key_count_easy > 0) %>%
  gather(key = condition, value = motor_key_count, motor_key_count_hard, motor_key_count_easy) %>%
  mutate(condition = as.factor(ifelse(condition == "motor_key_count_hard", "Hard", "Easy")), 
         # also add perceived effort by condition and motor RT by condition
         median_motor_RT = ifelse(condition == "Hard", median_motor_RT_hard, median_motor_RT_easy),
         perceived_effort = ifelse(condition == "Hard", hard_effort_perceived, easy_effort_perceived))
nrow(motor_df)
# making sure no zeros.
range(motor_df$motor_key_count)
hist(motor_df$median_motor_RT)
```


## No group differences in RT, main effects of age and condition 
```{r}
motor_speed_mod <- lmer(median_motor_RT ~ condition + PC1_log + 
                    perceived_effort + 
                   AGE.c +  SEX.c +
                 (1 | SUBJECTID), 
                 data = motor_df)

summary(motor_speed_mod)
```


## age x condition  effect: NS
```{r}
motor_mod_cxa <-  lmer(median_motor_RT ~ condition*AGE.c + PC1_log + 
                    perceived_effort + 
                   AGE.c +  SEX.c +
                 (1 | SUBJECTID), 
                 data = motor_df)

summary(motor_mod_cxa)
```


## PC1 x condition interaction: NS
```{r}
motor_mod_PC1xc <- lmer(median_motor_RT ~ condition *PC1_log + perceived_effort + 
                   AGE.c +  SEX.c +
                 (1 | SUBJECTID), 
                 data = motor_df)

summary(motor_mod_PC1xc)
```

## plot main effect of condition and age on motor RT 
```{r}
# get effect  df tidy
effort_effect <-  as.data.frame(effect("condition:AGE.c", motor_speed_mod, confint=TRUE))

plot_effect <- ggplot(effort_effect,aes(x = AGE.c, y = fit)) +
 geom_line(color = dark_blue) + theme_classic() + facet_grid(~condition) + 
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = dark_blue, alpha = 0.2) +
  geom_jitter(data = motor_df, aes(x = AGE.c, y = median_motor_RT),
       width = 0.1, height = 0.1, pch = 21,
             alpha = 0.3, fill = dark_blue) +
  theme_classic() + ylab("Motor skills on pre-test (median RT)") +
  xlab ("Age (mean-centered)") + theme(legend.position = "none") 
plot_effect

ggsave(plot_effect, file = "figures/actual_effort/motor_skills_by_condition_and_age.pdf", width = 3, height = 4)
```



