---
title: "Do self-report measures predict ECA-related symptoms?"
author: "Michelle.VanTieghem"
date: "10/10/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# notes: 
removed covariates fam income to needs and IQ, which were not related to symptoms in initial models. 

# load original data 
```{r, warning = F, message = F, include = F, echo = F}
# load all data with PCA added!
source("../../../0_R_analysis_setup_file.R", echo=F)
library(mediation)

```

```{r}
load("data/all_pacct_effort_data_with_PCA.rda")
```


## get outliers for ROI contrasts of interest
```{r}
load("tables/Feedback_betas_outlier_subjects.Rdata")
outlier_remove <- FB_outlier_subjects %>%
  filter((ROI == "vmPFC" & contrast == "setback") |
           (ROI == "Amyg" & contrast == "setback"))

```

## reformat data and remove nas
```{r}
beh_scan_ECA_wide2 <- beh_scan_ECA_wide %>%
  dplyr::select(SUBJECTID, GROUP_ECA, PC1_log,  AGE.c, SEX.c, 
                Fam_inc_needs, IQ, 
         starts_with('CBCL'), 
         perceived_effort_ave, 
         perceived_reinforce, Reinforce_rate,
         perceived_control, 
         win_feeling, lose_feeling, 
         motivated, frustrated,
        median_motor_RT_ave, 
        setback_Amyg, reward_Amyg,
        setback_vmPFC, reward_vmPFC, 
        total_TRs_censored, 
        choice_choice_mPFC, 
        prop_hard_choices, 
        N_trials) %>%
  mutate(diff_pos_affect = win_feeling - lose_feeling) %>%
  # remove outliers! 
  filter(!SUBJECTID %in% outlier_remove$SUBJECTID) %>%
  na.omit() 

```


## reformat WSLS data
```{r}
beh_scan_ECA_wide_WSLS2 <- beh_scan_ECA_wide_WSLS %>%
    dplyr::select(SUBJECTID, GROUP_ECA, PC1_log,  AGE.c, SEX.c, 
                Fam_inc_needs, IQ, 
         perceived_effort_ave, 
         perceived_reinforce, Reinforce_rate,
         perceived_control, 
         win_feeling, lose_feeling, 
         motivated, frustrated,
        median_motor_RT_ave, 
        setback_Amyg, reward_Amyg,
        setback_vmPFC, reward_vmPFC, 
        total_TRs_censored, 
        choice_choice_mPFC, 
        stay_shift, 
        N_trials, 
        Feedback_prior, Effort_Choice_prior, 
        CBCL_4_INTERNPROB_T) %>%
  mutate(diff_pos_affect = win_feeling - lose_feeling) %>%
  # remove missed feedback
  filter(Feedback_prior != "Too_slow") %>%
  
  # remove outliers! 
  filter(!SUBJECTID %in% outlier_remove$SUBJECTID) %>%
  na.omit() 
  
nrow(beh_scan_ECA_wide_WSLS2)

beh_scan_ECA_wide_WSLS2 %>%
  group_by(Effort_Choice_prior, Feedback_prior) %>%
  dplyr::summarize(mean(stay_shift))

```


## make a WSLS dataset: setbacks only, collapsed harrd & easy
need 1 row per subj
```{r}
beh_scan_ECA_wide_WSLS_FB <- beh_scan_ECA_wide_WSLS2 %>%
  group_by(SUBJECTID, Feedback_prior) %>%
    dplyr::summarize(GROUP_ECA = GROUP_ECA[1],
                     PC1_log = mean(PC1_log, na.rm = T),
                     AGE.c = AGE.c[1],
                     SEX.c = SEX.c[1], 
                Fam_inc_needs = Fam_inc_needs[1],
                IQ = IQ[1], 
         perceived_effort_ave = perceived_effort_ave[1], 
         perceived_reinforce = perceived_reinforce[1],
        Reinforce_rate = Reinforce_rate[1],
         perceived_control = perceived_control[1], 
         win_feeling = win_feeling[1],
        lose_feeling = lose_feeling[1],
         motivated = motivated[1],
        frustrated = frustrated[1],
        diff_pos_affect = diff_pos_affect[1],
        median_motor_RT_ave = median_motor_RT_ave[1],
        setback_Amyg = setback_Amyg[1],
        reward_Amyg = reward_Amyg[1],
        setback_vmPFC = setback_vmPFC[1],
        reward_vmPFC = reward_vmPFC[1], 
        total_TRs_censored = total_TRs_censored[1], 
        choice_choice_mPFC = choice_choice_mPFC[1], 
        stay_shift = mean(stay_shift, na.rm = T), 
        N_trials = mean(N_trials, na.rm = T), 
        CBCL_4_INTERNPROB_T = mean(CBCL_4_INTERNPROB_T, na.rm = T))

beh_scan_ECA_wide_WSLS_setbacks <- beh_scan_ECA_wide_WSLS_FB %>%
  filter(Feedback_prior == "Setback")

```


# ECA effects on symptoms alone 

## main effect of PC1 and age 
```{r}
CBCL_mod_PC1 <- lm(CBCL_4_INTERNPROB_T ~  PC1_log +
                   AGE.c + SEX.c + Fam_inc_needs + IQ ,
                      data = beh_scan_ECA_wide2)
summary(CBCL_mod_PC1)
```


## Age x PC1 interaction.
this is notable, but only relevant for mediation if PC1*age predicts motivation, which it doesn't! 
```{r}
CBCL_mod_PC1 <- lm(CBCL_4_INTERNPROB_T ~  PC1_log*AGE.c +
                   AGE.c + SEX.c + Fam_inc_needs + IQ ,
                      data = beh_scan_ECA_wide2)
summary(CBCL_mod_PC1)
```

plot effect: effects of ECA on symptoms declines with age.
```{r}
effect_df <- data.frame(effect( 'PC1_log:AGE.c', CBCL_mod_PC1)) %>%
  mutate(AGE = as.factor(AGE.c + 9))

effect_plot <- ggplot(data = effect_df, aes(x = PC1_log, y = fit)) + 
  geom_line(color = dark_blue) + facet_grid(~AGE) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = dark_blue) + 
  geom_point(data = beh_scan_ECA_wide2, aes(x = PC1_log, y = CBCL_4_INTERNPROB_T), 
             color = dark_blue, alpha = 0.2) + 
  ylab("CBCL Total Internalizing T Score") + xlab("Cumulative ECA Score")
effect_plot

ggsave(effect_plot, file = "figures/symptoms/CBCL_internalizing_by_PC1xage.png", height = 4, width = 6)
```

omitting fam inc to needs and IQ because don't influence outcome variable. 

# Explore: All self-report and behavior without PC1 
## SIG: motivation and perceived control. 
including actual reinforce rate as covarriate 
```{r}
CBCL_mod_all <- lm(CBCL_4_INTERNPROB_T ~  perceived_effort_ave +
                   perceived_control + win_feeling + lose_feeling + 
                   perceived_reinforce + Reinforce_rate +
                   motivated + frustrated +
                   AGE.c + SEX.c +  median_motor_RT_ave,
                      data = beh_scan_ECA_wide2)
summary(CBCL_mod_all)
```

# motivation and symptoms

## motivation alone 
covarying for peceived control and motor speed
```{r}
CBCL_mod_motivated <- lm(CBCL_4_INTERNPROB_T ~  motivated + 
                           perceived_control + median_motor_RT_ave + #win_feeling + 
                   AGE.c + SEX.c,
                      data = beh_scan_ECA_wide2)
summary(CBCL_mod_motivated)
```

## motivation x age: NS
```{r}
CBCL_mod_mxa<- lm(CBCL_4_INTERNPROB_T ~  motivated *AGE.c +
                    perceived_control + median_motor_RT_ave + #win_feeling + s
                   AGE.c + SEX.c,
                      data = beh_scan_ECA_wide2)
summary(CBCL_mod_mxa)
```

## retest with PC1 : motivation effect is weak, still SIG
```{r}
CBCL_mod_motiv_PC1 <- lm(CBCL_4_INTERNPROB_T ~ PC1_log + motivated +
                    perceived_control + median_motor_RT_ave + #win_feeling + 
                   AGE.c + SEX.c,
                      data = beh_scan_ECA_wide2)
summary(CBCL_mod_motiv_PC1)
```

plot effect: motivation negatively predicts symptoms.
```{r}
effect_df <- data.frame(effect( 'motivated', CBCL_mod_motiv_PC1)) 

effect_plot <- ggplot(data = effect_df, aes(x = motivated, y = fit)) + 
  geom_line(color = dark_blue) + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = dark_blue) + 
  geom_jitter(data = beh_scan_ECA_wide2, aes(x = motivated, y = CBCL_4_INTERNPROB_T), 
             color = dark_blue, alpha = 0.2, width= 0.1, height = 0) + 
  ylab("CBCL Total Internalizing T Score") + xlab("Self-reported Motivation")
effect_plot

ggsave(effect_plot, file = "figures/symptoms/CBCL_internalizing_by_motivation.png", height = 4, width = 6)

```


plot effect: PC1 positively predicts symptoms
```{r}
effect_df <- data.frame(effect( 'PC1_log', CBCL_mod_motiv_PC1)) 

effect_plot <- ggplot(data = effect_df, aes(x = PC1_log, y = fit)) + 
  geom_line(color = dark_blue) + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = dark_blue) + 
  geom_jitter(data = beh_scan_ECA_wide2, aes(x = PC1_log, y = CBCL_4_INTERNPROB_T), 
             color = dark_blue, alpha = 0.2, width= 0.1, height = 0) + 
  ylab("CBCL Total Internalizing T Score") + xlab("Cumulative ECA Score")
effect_plot

ggsave(effect_plot, file = "figures/symptoms/CBCL_internalizing_by_PC1.png", height = 4, width = 6)

```


## mediation1: motivation mediates effect of ECA on symptoms!!
only when controlling for perceived control and contribution of motor speed
```{r}
model_direct <- lm(CBCL_4_INTERNPROB_T ~ PC1_log + 
                perceived_control +  median_motor_RT_ave + 
                win_feeling + prop_hard_choices +
                 AGE.c + SEX.c,
                      data = beh_scan_ECA_wide2)
summary(model_direct)
model.m <- lm(motivated ~ PC1_log + 
                perceived_control + median_motor_RT_ave + 
                win_feeling + prop_hard_choices +
                 AGE.c + SEX.c,
                      data = beh_scan_ECA_wide2)
summary(model.m)
model.y <- lm(CBCL_4_INTERNPROB_T ~ PC1_log + motivated +
                # impt self-report covariates to control for. 
                perceived_control +  median_motor_RT_ave + 
                win_feeling + prop_hard_choices +
                 AGE.c + SEX.c,
                      data = beh_scan_ECA_wide2)
summary(model.y)
  
# ONLY RUN ONCE: because p-values will be different each time! 

motiv_mediation1 <- mediate(model.m, model.y, sims = 2000, boot = FALSE,
boot.ci.type = "perc", treat = "PC1_log", mediator = "motivated")
save(motiv_mediation1, file = "model_results/symptoms/motivation_mediates_ECA_symptoms.Rdata")

load("model_results/symptoms/motivation_mediates_ECA_symptoms.Rdata")
summary(motiv_mediation1)
```


## mediation2: ECA mediates effect of motivation on symptoms. SIG
so the directionality here is challenged...
```{r}
# remember that PC1 onl ypredicts motivation when we also account for 
# effects of motor ability and perceived control on motivation. 
model.m <- lm(PC1_log  ~ motivated +  
                 perceived_control + median_motor_RT_ave +
                  win_feeling + prop_hard_choices +
                 AGE.c + SEX.c,
                      data = beh_scan_ECA_wide2)

model.y <- lm(CBCL_4_INTERNPROB_T ~ motivated + PC1_log +
                 perceived_control + median_motor_RT_ave + 
                win_feeling + prop_hard_choices +
                AGE.c + SEX.c,
                      data = beh_scan_ECA_wide2)

# treat = X variable
motiv_mediation2 <- mediate(model.m, model.y, sims = 2000, boot = FALSE,
boot.ci.type = "perc", treat = "motivated", mediator = "PC1_log")
save(motiv_mediation2, file = "model_results/symptoms/ECA_mediates_motivation_symptoms.Rdata")

load( "model_results/symptoms/ECA_mediates_motivation_symptoms.Rdata")
# nothing is mediated!! 
summary(motiv_mediation2)
```


## moderation? NS
```{r}
CBCL_mod_motiv_PC1 <- lm(CBCL_4_INTERNPROB_T ~ PC1_log * motivated +
                           perceived_control + median_motor_RT_ave +
                           #w#in_feeling + prop_hard_choices +
                   AGE.c + SEX.c,
                      data = beh_scan_ECA_wide2)
summary(CBCL_mod_motiv_PC1)
```



# prop hard choice behavior and symptoms

## prop hard, alone...
```{r}
CBCL_mod_prop <- lm(CBCL_4_INTERNPROB_T ~ prop_hard_choices ,
                      data = beh_scan_ECA_wide2)
summary(CBCL_mod_prop)
```

plot effect: really beacuse of outlier!! 
```{r}
effect_df <- data.frame(effect( 'prop_hard_choices', CBCL_mod_prop))

effect_plot <- ggplot(data = effect_df, aes(x = prop_hard_choices, y = fit)) + 
  geom_line(color = dark_blue) + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = dark_blue) + 
  geom_point(data = beh_scan_ECA_wide2, aes(x = prop_hard_choices, y = CBCL_4_INTERNPROB_T), 
             color = dark_blue, alpha = 0.2) + 
  ylab("CBCL Total Internalizing T Score") + xlab("Proportion of Hard Choices")
effect_plot

```

## check for outliers in prop hard
```{r}
prop_hard_table <- beh_scan_ECA_wide2 %>%
  dplyr::summarize( prop_hard_mean = mean(prop_hard_choices), 
                   prop_hard_sd = sd(prop_hard_choices), 
                   upper = prop_hard_mean + 3*prop_hard_sd, 
                   lower = prop_hard_mean - 3*prop_hard_sd)

beh_scan_ECA_wide3 <- beh_scan_ECA_wide2 %>%
  mutate(prop_hard_choices = ifelse(prop_hard_choices > prop_hard_table$upper | 
                            prop_hard_choices < prop_hard_table$lower, NA, prop_hard_choices)) %>%
  na.omit()

```


## prop hard, alone: NS 
aftere removing outlier.
```{r}
CBCL_mod_prop <- lm(CBCL_4_INTERNPROB_T ~ prop_hard_choices ,
                      data = beh_scan_ECA_wide3)
summary(CBCL_mod_prop)
```

## full model, without PC1 : TREND
including all covariates that were used above.
it's really because of N trials, which is impt for prop hard.
```{r}
CBCL_mod_all <- lm(CBCL_4_INTERNPROB_T ~ prop_hard_choices + motivated + 
                    perceived_control + median_motor_RT_ave + N_trials + 
                   AGE.c + SEX.c,
                      data = beh_scan_ECA_wide3)
summary(CBCL_mod_all)
```



## full with PC1: NS
```{r}
CBCL_mod_choice_all <- lm(CBCL_4_INTERNPROB_T ~ PC1_log *AGE.c + prop_hard_choices + motivated + 
                    perceived_control + median_motor_RT_ave + N_trials + 
                   AGE.c + SEX.c,
                      data = beh_scan_ECA_wide3)
summary(CBCL_mod_choice_all)

CBCL_mod_choice_all <- lm(CBCL_4_INTERNPROB_T ~ PC1_log + prop_hard_choices + motivated + 
                    perceived_control + median_motor_RT_ave + N_trials +
                   AGE.c + SEX.c,
                      data = beh_scan_ECA_wide3)
summary(CBCL_mod_choice_all)
```


## does PC1 predict prop hard choices? NS
so no reason to test mediation.
```{r}
prop_hard_mod_PC1 <- lm(prop_hard_choices ~  PC1_log + motivated + N_trials +
                    perceived_control + median_motor_RT_ave +
                   AGE.c + SEX.c,
                      data = beh_scan_ECA_wide2)
summary(prop_hard_mod_PC1)

```


# Explore: WSLS behavior and symptoms 
## stay after all setbacks 
```{r}
CBCL_mod_persist <- lm(CBCL_4_INTERNPROB_T ~  stay_shift + PC1_log + motivated + N_trials +
                    perceived_control + median_motor_RT_ave +
                   AGE.c + SEX.c,
                      data = beh_scan_ECA_wide_WSLS_setbacks)
summary(CBCL_mod_persist)

CBCL_mod_persistxPC1 <- lm(CBCL_4_INTERNPROB_T ~  stay_shift + PC1_log + motivated + N_trials +
                    perceived_control + median_motor_RT_ave +
                   AGE.c + SEX.c,
                      data = beh_scan_ECA_wide_WSLS_setbacks)
summary(CBCL_mod_persistxPC1)
```



## stay-shift after hard setback only: NS
```{r}
CBCL_mod_persist <- lm(CBCL_4_INTERNPROB_T ~  stay_shift + 
                         PC1_log + motivated + N_trials +
                    perceived_control + median_motor_RT_ave +
                   AGE.c + SEX.c,
                      data = filter(beh_scan_ECA_wide_WSLS2, Effort_Choice_prior == "Hard" &
                                      Feedback_prior == "Setback"))
summary(CBCL_mod_persist)

```

## stay-shift  x feedback x effort
i don't know if this model makes sense.
```{r}
CBCL_mod_persist <- lmer(CBCL_4_INTERNPROB_T ~  stay_shift + Effort_Choice_prior 
                       + Feedback_prior +
                         + PC1_log + motivated + N_trials +
                    perceived_control + median_motor_RT_ave +
                   AGE.c + SEX.c + 
                     (1 | SUBJECTID),
                      data = beh_scan_ECA_wide_WSLS2)
summary(CBCL_mod_persist)

```





# Brain: testing ROIs that are related to ECA or self-report measures
## Amygdala setbacks alone: NS
controlling for motion, age and sex 
```{r}
CBCL_mod_amyg <- lm(CBCL_4_INTERNPROB_T ~ setback_Amyg + total_TRs_censored + 
                      AGE.c  + SEX.c,
                      data = beh_scan_ECA_wide2)
summary(CBCL_mod_amyg)

```

## Amygdala setbacks with self-report covariates: TREND
```{r}
CBCL_mod_amyg <- lm(CBCL_4_INTERNPROB_T ~ setback_Amyg + total_TRs_censored + 
                       motivated + 
                          perceived_control + median_motor_RT_ave + 
                           AGE.c + SEX.c,
                      data = beh_scan_ECA_wide2)
summary(CBCL_mod_amyg)

```


## Amygdala with self-report covariates and PC1: NS
```{r}
CBCL_mod_amyg <- lm(CBCL_4_INTERNPROB_T ~ setback_Amyg + total_TRs_censored + 
                       motivated + PC1_log +
                          perceived_control + median_motor_RT_ave + 
                           AGE.c + SEX.c,
                      data = beh_scan_ECA_wide2)
summary(CBCL_mod_amyg)

```



## vmPFC rewards on symptoms, alone: NS
controlling for motion, age and sex 

```{r}
CBCL_mod_vmPFC <- lm(CBCL_4_INTERNPROB_T ~ reward_vmPFC + total_TRs_censored + 
                      AGE.c + SEX.c ,
                      data = beh_scan_ECA_wide2)
summary(CBCL_mod_vmPFC)

```

## full model with PC1: NS
including frustrated because it's correlated with reward vmPFC 
including motivated, motor, perceived contorl because related to outcome.
```{r}
CBCL_mod_vmPFC <- lm(CBCL_4_INTERNPROB_T ~ reward_vmPFC + total_TRs_censored + 
                        PC1_log + 
                       frustrated + motivated +
                       perceived_control + median_motor_RT_ave +
                     AGE.c + SEX.c ,
                      data = beh_scan_ECA_wide2)
summary(CBCL_mod_vmPFC)

```

## vmPFC x PC1: NS
```{r}
CBCL_mod_vmPFC <- lm(CBCL_4_INTERNPROB_T ~ reward_vmPFC * PC1_log +
                      total_TRs_censored + 
                       frustrated + motivated +
                       perceived_control + median_motor_RT_ave +
                           AGE.c + SEX.c,
                      data = beh_scan_ECA_wide2)
summary(CBCL_mod_vmPFC)

```

