---
title: "Self report measures by ECA "
author: "Michelle.VanTieghem"
date: "10/10/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  png_document:
    toc: yes
---

# Readme

First, we examined relationships between self-reported variables in a correlation table with the entire sample. 
Next, examined influence of potential covariates (age, sex, motor skills, reinforcement rate) on self-reported variables in the comparison sample only (N = 33). Then, we tested the role of cumulative ECA score on self-reported variables, controlling for relevant covariates. 


```{r, include = F, warnings = F, echo=FALSE, message = F}
source("../../../0_R_analysis_setup_file.R")
```

# load and clean data
```{r}
# load all data with PCA added!
load("../data/all_pacct_effort_data_with_PCA.rda")
```

 data cleaning 
```{r}

# add difference score
beh_scan_ECA_wide <- beh_scan_ECA_wide %>%
  mutate(diff_pos_affect = win_feeling - lose_feeling)

# make comparison subset
beh_scan_comps_wide <- beh_scan_ECA_wide %>%
  filter(GROUP_ECA == "COMP")
nrow(beh_scan_comps_wide) # there are only 33 comps

```

# descriptives 
## check correlations

win feeling, motivated, fun, perceived control all correlated.
frustated correlated with perceived reinforce & age 

```{r}
self_report_cor_df <- beh_scan_ECA_wide %>% 
  dplyr::select(PC1_log, prop_hard_choices, 
        AGE, perceived_control, perceived_effort_ave, 
         median_motor_RT_ave,
         perceived_reinforce, Reinforce_rate,
         lose_feeling, win_feeling, 
         frustrated, motivated, 
         fun, sleepy) %>%
  # reformatting for future table/figure use.
  rename('Prop Hard Choices' = prop_hard_choices, 
          'Age (years)' = AGE, 
         'ECA score' = PC1_log, 
         'Affect to setbacks' = lose_feeling, 
         'Affect to rewards' = win_feeling, 
         'Perceived reinforcement' = perceived_reinforce, 
         'Frustration' = frustrated, 
         'Motivation' = motivated, 
         'Perceived Control' = perceived_control,
         'Perceived effort' = perceived_effort_ave, 
         'Motor speed' = median_motor_RT_ave,
         'Actual Reinforcement' = Reinforce_rate, 
         'Amount of Fun' = fun, 
         'Sleepiness' = sleepy) 
# save to make table later.
save(self_report_cor_df, file = "../tables/corr_table_self_report_data.Rdata")

```

## visualize correlations
```{r}
# reformat for corrplot
var_cor <- self_report_cor_df %>%
  as.matrix() %>% # convert to matrix
  rcorr() # calculate correlations

corrplot(var_cor$r, method = "color", type = "lower")

# save plot
png("../figures/self_report/self_report_variables_corrplot.png", res = 300, units = "in",  height = 6, width = 6)
corrplot(var_cor$r, method = "color", type = "lower")
dev.off()
```


# Percieved Effort
## make a wide data version with perceived effort and motor skills.
```{r}
# make long version of perceived effort data
perceived_df <- beh_scan_ECA_wide %>% 
  gather(key = "condition", value = "perceived_effort_rating", 
         hard_effort_perceived, easy_effort_perceived) %>%
  mutate(condition = as.factor(ifelse(condition == "hard_effort_perceived", 
                                      "Hard", "Easy"))) %>%
      mutate( motor_speed_by_condition = ifelse(condition == "Easy", median_motor_RT_easy, median_motor_RT_hard), 
              diff_pos_affect = win_feeling - lose_feeling, 
             GROUP_ECA = as.factor(GROUP_ECA)) %>%
  filter(!is.na(perceived_effort_rating))
```


## COMP main effects of condition.
```{r}
perceived_effort_mod_comp <- lmer(perceived_effort_rating ~ condition + AGE.c + SEX.c + 
                            Reinforce_rate.c + median_motor_RT_ave + 
                               (1 | SUBJECTID), 
                           data = filter(perceived_df, GROUP_ECA == "COMP"))
summary(perceived_effort_mod_comp)
```

## comp: no age x condition interaction
```{r}
perceived_effort_mod_comp <- lmer(perceived_effort_rating ~ condition * AGE.c + SEX.c + 
                            Reinforce_rate.c + median_motor_RT_ave + 
                               (1 | SUBJECTID), 
                           data = filter(perceived_df, GROUP_ECA == "COMP"))
summary(perceived_effort_mod_comp)
```



### plot effect of condition
```{r}
# get effect  df tidy
effort_effect <-  as.data.frame(effect("condition", perceived_effort_mod_comp, confint=TRUE))

plot_effect <- ggplot(effort_effect,aes(x = condition, y = fit)) +
 geom_point(size = 3,stat = "identity", position=position_dodge()) + theme_classic() + 
  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_jitter(data = filter(perceived_df, GROUP_ECA == "COMP"), aes(x = condition, y = perceived_effort_rating),
       width = 0.1, height = 0.1, pch = 21,
             alpha = 0.3, fill = dark_blue) +
  theme_classic() + ylab("Perceived Effort") + coord_cartesian(ylim=c(1,4)) +
  xlab ("condition") + theme(legend.position = "none") 
plot_effect

ggsave(plot_effect, file = "../figures/self_report/perceived_effort_comp_by_condition.png", width = 6, height = 4)

```



## ECA group effects 
main effect SIG, no interaction with condition or age
including/not including these covariates does not make a difference! 
```{r}
perceived_effort_mod_g <- lmer(perceived_effort_rating ~ condition + GROUP_ECA + AGE.c + SEX.c + 
                            Reinforce_rate.c + median_motor_RT_ave + 
                               (1 | SUBJECTID), 
                           data = perceived_df)
summary(perceived_effort_mod_g)


perceived_effort_mod_cxg <- lmer(perceived_effort_rating ~ condition *GROUP_ECA + AGE.c + SEX.c + 
                            Reinforce_rate.c + median_motor_RT_ave + 
                               (1 | SUBJECTID),  data = perceived_df)
summary(perceived_effort_mod_cxg)
```


### plot effect of GROUP
```{r}
# get effect  df tidy
effort_effect <-  as.data.frame(effect("condition:GROUP_ECA", perceived_effort_mod_g, confint=TRUE))

plot_effect <- ggplot(effort_effect,aes(x = GROUP_ECA, y = fit)) +
 geom_point(size = 3,stat = "identity", position=position_dodge()) + theme_classic() + 
  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_jitter(data = perceived_df, aes(x = GROUP_ECA, y = perceived_effort_rating),
       width = 0.1, height = 0.1, pch = 21,
             alpha = 0.3, fill = dark_blue) +
  theme_classic() + ylab("Perceived Effort") + coord_cartesian(ylim=c(1,4)) +
  xlab ("GROUP") + theme(legend.position = "none") + facet_grid(~condition)
plot_effect

ggsave(plot_effect, file = "../figures/self_report/perceived_effort_by_GROUP.png", width = 4, height = 4)

```


## cumulative ECA effects
main effect, no interaction with condition.
```{r}
perceived_effort_mod_PC1 <- lmer(perceived_effort_rating ~ condition + PC1_log + AGE.c + SEX.c + 
                            Reinforce_rate.c + median_motor_RT_ave + 
                               (1 | SUBJECTID), 
                           data = perceived_df)
summary(perceived_effort_mod_PC1)

perceived_effort_mod_cxPC1 <- lmer(perceived_effort_rating ~ condition *PC1_log + AGE.c + SEX.c + 
                            Reinforce_rate.c + median_motor_RT_ave + 
                             (1 | SUBJECTID), 
                           data = perceived_df)
summary(perceived_effort_mod_cxPC1)

```


```{r}
# get effect  df tidy
effort_effect <-  as.data.frame(effect("condition:PC1_log", perceived_effort_mod_PC1, confint=TRUE))

plot_effect <- ggplot(effort_effect,aes(x = PC1_log, y = fit)) +
 geom_line() + theme_classic() + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.25, fill = dark_blue) +
  geom_jitter(data = perceived_df, aes(x = PC1_log, y = perceived_effort_rating),
       width = 0.2, height = 0.1, pch = 21,
             alpha = 0.3, fill = dark_blue) +
  theme_classic() + ylab("Perceived effort") + coord_cartesian(ylim=c(1,4)) +
  xlab ("Cumulative ECA Score") + theme(legend.position = "none") + facet_grid(~condition)
plot_effect

ggsave(plot_effect, file = "../figures/self_report/perceived_effort_by_PC1_log.png", width = 6, height = 4)
```


# Perceived reinforcement

## COMPS: main effect of actual reinforcement rate. 
```{r}
perceived_reinforce_mod1_comps <- lm(perceived_reinforce ~ 
                                   AGE.c  + SEX.c  + Reinforce_rate + 
                      median_motor_RT_ave, 
                 data = beh_scan_comps_wide)
summary(perceived_reinforce_mod1_comps)
```


## Group effect on perceived reinforcemennt: NS
when using the appropriate model...
```{r}
perceived_reinforce_mod1_g <- lm(perceived_reinforce ~ GROUP_ECA +  
                                   AGE.c  + SEX.c  + Reinforce_rate +
                      median_motor_RT_ave, 
                 data = beh_scan_ECA_wide)
summary(perceived_reinforce_mod1_g)
```


plot of group effect
```{r }
# get effect  df tidy
affect_effect <-  as.data.frame(effect("GROUP_ECA", perceived_reinforce_mod1_g, confint=TRUE))

plot_effect <- ggplot(affect_effect,aes(x = GROUP_ECA, y = fit)) +
 geom_point(size = 3, color = "black") + theme_classic() + 
  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_jitter(data = beh_scan_ECA_wide,  aes(x = GROUP_ECA, y = perceived_reinforce),
              width = 0.2, height = 0.05, pch = 21,
             alpha = 0.2, fill = dark_blue) +
   theme(legend.position = "none") + 
  theme_classic() + ylab("Perceived Reinforcemment") + coord_cartesian(ylim=c(1,3)) +
  xlab ("GROUP") + theme(legend.position = "none")
plot_effect

ggsave(plot_effect, file = "../figures/self_report/perceived_reinforce_by_group.png", width = 2.5, height = 4)

```

## PC1 effect on perceived reinforcement: SIG. 
```{r}
perceived_reinforce_mod1_PC1 <- lm(perceived_reinforce ~  PC1_log + 
                                   AGE.c  + SEX.c  + Reinforce_rate +
                    median_motor_RT_ave, 
                 data = beh_scan_ECA_wide)
summary(perceived_reinforce_mod1_PC1)
```


## plot of cumulative ECA effect for perceived reinforcement
```{r}
summary(beh_scan_ECA_wide$perceived_reinforce)
# get effect  df tidy
affect_effect <-  as.data.frame(effect("PC1_log", perceived_reinforce_mod1_PC1, confint=TRUE))

plot_effect <- ggplot(affect_effect, aes(x = PC1_log, y = fit)) +
 geom_line(color = dark_blue) + theme_classic() + 
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = dark_blue, alpha = 0.3) +
  geom_jitter(data = beh_scan_ECA_wide,  aes(x = PC1_log, y = perceived_reinforce),
              width = 0.2, height = 0.05, pch = 21,
             alpha = 0.2, fill = dark_blue) +
   theme(legend.position = "none") + 
  theme_classic() + ylab("Fewer setbacks <---------> More setbacks") + coord_cartesian(ylim=c(1,3)) +
  xlab ("Cumulative ECA score") + theme(legend.position = "none")
plot_effect

ggsave(plot_effect, file = "../figures/self_report/perceived_reinforce_by_PC1.png", width = 6, height = 4)

```


## Group effect on actual reinforcement rate rate: no, good because random! 
```{r}
reinforce_mod1_g <- lm(Reinforce_rate ~ GROUP_ECA ,
                 data = beh_scan_ECA_wide)
summary(reinforce_mod1_g)
```

## PC1 effect on actual reinforcement: no.
```{r}
reinforce_mod1_PC1 <- lm(Reinforce_rate ~  PC1_log ,
                 data = beh_scan_ECA_wide)
summary(reinforce_mod1_PC1)
```


# perceived control 

## COMPS: no effect of age, motor skills, reinforcement on perceived control
```{r}
control_mod1_comps <- lm(perceived_control ~  AGE.c  + SEX.c + 
                      Reinforce_rate + perceived_reinforce + 
                       median_motor_RT_ave, 
                 data = beh_scan_comps_wide)
summary(control_mod1_comps)
```

## Group effect on perceived control: NS
```{r}
control_mod1_g <- lm(perceived_control ~ GROUP_ECA +  AGE.c  + SEX.c  +
                  Reinforce_rate +
                       median_motor_RT_ave, 
                 data = beh_scan_ECA_wide)
summary(control_mod1_g)
```

### PC1 effect on perceived control: NS
```{r}
control_mod1_PC1 <- lm(perceived_control ~  PC1_log +  AGE.c  + SEX.c  +
                      Reinforce_rate + 
                       median_motor_RT_ave, 
                 data = beh_scan_ECA_wide)
summary(control_mod1_PC1)
```

```{r}
# get effect  df tidy
affect_effect <-  as.data.frame(effect("PC1_log", control_mod1_PC1, confint=TRUE))

plot_effect <- ggplot(affect_effect, aes(x = PC1_log, y = fit)) +
 geom_line(color = dark_blue) + theme_classic() + 
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = dark_blue, alpha = 0.3) +
  geom_jitter(data = beh_scan_ECA_wide,  aes(x = PC1_log, y = perceived_control),
              width = 0.2, height = 0.05, pch = 21,
             alpha = 0.2, fill = dark_blue) +
   theme(legend.position = "none") + 
  theme_classic() + ylab("Less Control <--------> More Control") + coord_cartesian(ylim=c(1,3)) +
  xlab ("Cumulative ECA score") + theme(legend.position = "none")
plot_effect

ggsave(plot_effect, file = "../figures/self_report/perceived_control_by_PC1.png", width = 6, height = 4)

```



# positive/ negative affect

```{r}

# make long version of perceived effort data
pos_affect_df <- beh_scan_ECA_wide %>% 
  gather(key = "condition", value = "positive_affect", 
          win_feeling,lose_feeling) %>%
  mutate(condition = as.factor(ifelse(condition == "win_feeling", 
                                      "Rewards", "Setbacks"))) %>%
  dplyr::select(SUBJECTID, GROUP_ECA, PC1_log, SEX.c, AGE.c,  positive_affect, condition, 
         setback_Amyg, reward_Amyg, setback_VS, reward_VS, 
         perceived_effort_ave, Reinforce_rate.c, perceived_reinforce,
         perceived_control, median_motor_RT_ave) %>%
  filter(!is.na(positive_affect) & !is.na(condition) & !is.na(AGE.c) & !is.na(SEX.c)) %>%
  mutate(GROUP_ECA = as.factor(GROUP_ECA))

# make comparison subset
pos_affect_comps <- pos_affect_df %>%
  filter(GROUP_ECA == "COMP")
nrow(pos_affect_comps)
length(unique(pos_affect_comps$SUBJECTID))


```


## COMPS: Age x condition: SIG
`
```{r}

pos_affect_mod_comps <- lmer(positive_affect ~ condition * AGE.c + SEX.c + 
                           Reinforce_rate.c + median_motor_RT_ave + 
                          (1 | SUBJECTID),
   data = pos_affect_comps)
summary(pos_affect_mod_comps)

```

```{r}
# get effect  df tidy
affect_effect <-  as.data.frame(effect("condition:AGE.c", pos_affect_mod_comps, confint=TRUE))

plot_effect <- ggplot(affect_effect, aes(x = AGE.c, y = fit)) +
 geom_line(size = 1, color = dark_blue) + theme_classic() + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = dark_blue) +
  geom_jitter(data = pos_affect_comps,  aes(x = AGE.c, y = positive_affect),
              width = 0.2, height = 0.1, pch = 21,
             alpha = 0.2, fill = dark_blue) + facet_grid(~ condition) +
   theme(legend.position = "none") + 
  theme_classic() + ylab("Self-reported Positive Affect") + coord_cartesian(ylim=c(1,4)) +
  xlab ("Age (mean-centered)") + theme(legend.position = "none")
plot_effect

ggsave(plot_effect, file = "../figures/self_report/positive_affect_COMPS.png", units = "in", width = 6, height = 4)

```

## group x condition: SIG
controlling for all relevant variables !
```{r ert}
pos_affect_mod_g <- lmer(positive_affect ~ condition * GROUP_ECA + AGE.c + SEX.c + 
                           #condition * AGE.c +
                           Reinforce_rate.c + median_motor_RT_ave + 
                          (1 | SUBJECTID),
                          
                          data = pos_affect_df)
summary(pos_affect_mod_g)
```

## PC1 x condition : SIG 
```{r}
pos_affect_mod_PC1 <- lmer(positive_affect ~ condition * PC1_log + AGE.c + SEX.c +
                            # condition * AGE.c +
                          Reinforce_rate.c + median_motor_RT_ave + 
                          (1 | SUBJECTID),
                          data = pos_affect_df)

summary(pos_affect_mod_PC1)
```

plot of group effect
```{r}
# get effect  df tidy
affect_effect <-  as.data.frame(effect("condition:GROUP_ECA", pos_affect_mod_g, confint=TRUE))

plot_effect <- ggplot(affect_effect,aes(x = GROUP_ECA, y = fit)) +
 geom_point(size = 3, color = "black") + theme_classic() + 
  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_jitter(data = pos_affect_df,  aes(x = GROUP_ECA, y = positive_affect),
              width = 0.2, height = 0.05, pch = 21,
             alpha = 0.2, fill = dark_blue) +
   theme(legend.position = "none") + facet_grid(~condition) +
  theme_classic() + ylab("Self-reported Positive Affect") + coord_cartesian(ylim=c(1,4)) +
  xlab ("GROUP") + theme(legend.position = "none")
plot_effect

ggsave(plot_effect, file = "../figures/self_report/positive_affect_by_group.png", width = 6, height = 4)

```


plot of cumulative ECA effect
```{r}
# get effect  df tidy
affect_effect <-  as.data.frame(effect("condition:PC1_log", pos_affect_mod_PC1, confint=TRUE))

plot_effect <- ggplot(affect_effect, aes(x = PC1_log, y = fit)) +
 geom_line(color = dark_blue) + theme_classic() + 
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = dark_blue, alpha = 0.3) +
  geom_jitter(data = pos_affect_df,  aes(x = PC1_log, y = positive_affect),
              width = 0.2, height = 0.05, pch = 21,
             alpha = 0.2, fill = dark_blue) +
   theme(legend.position = "none") + facet_grid(~condition) +
  theme_classic() + ylab("Positive Affect") + coord_cartesian(ylim=c(1,4)) +
  xlab ("Cumulative ECA score") + theme(legend.position = "none")
plot_effect

ggsave(plot_effect, file = "../figures/self_report/positive_affect_by_PC1.png", width = 6, height = 4)

```

## difference in reward-setback

## COMPS: Age effect sig
```{r}
diff_affect_mod_comps <- lm(diff_pos_affect ~ AGE.c + SEX.c +
                          Reinforce_rate.c + median_motor_RT_ave, 
   data = beh_scan_comps_wide)

summary(diff_affect_mod_comps)
```


## GROUP on difference scores: SIG
```{r}
diff_affect_mod_group <- lm(diff_pos_affect ~ GROUP_ECA + AGE.c + SEX.c +
                          Reinforce_rate.c + median_motor_RT_ave, 
   data = beh_scan_ECA_wide)

summary(diff_affect_mod_group)
```

## PC1 on difference scores: trend. 
```{r}
diff_affect_mod_PC1 <- lm(diff_pos_affect ~ PC1_log + AGE.c + SEX.c +
                          Reinforce_rate.c + median_motor_RT_ave, 
   data = beh_scan_ECA_wide)

summary(diff_affect_mod_PC1)
```


```{r}
# get effect  df tidy
affect_effect <-  as.data.frame(effect("PC1_log", diff_affect_mod_PC1, confint=TRUE))

plot_effect <- ggplot(affect_effect, aes(x = PC1_log, y = fit)) +
 geom_line(color = dark_blue) + theme_classic() + 
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = dark_blue, alpha = 0.3) +
  geom_jitter(data =  beh_scan_ECA_wide, aes(x = PC1_log, y = diff_pos_affect),
              width = 0.2, height = 0.05, pch = 21,
             alpha = 0.2, fill = dark_blue) +
   theme(legend.position = "none") + #facet_grid(~condition) +
  theme_classic() + ylab("Difference in Positive Affect (Reward-Setback)") + coord_cartesian(ylim=c(1,4)) +
  xlab ("Cumulative ECA score") + theme(legend.position = "none")
plot_effect

ggsave(plot_effect, file = "../figures/self_report/diff_pos_affect_by_PC1.png", width = 6, height = 4)
```


# Motivation 

## Comps:
```{r}
motivate_mod1_comps <- lm(motivated ~ AGE.c + SEX.c + perceived_control + 
                          Reinforce_rate.c + median_motor_RT_ave, 
                 data = beh_scan_comps_wide)
summary(motivate_mod1_comps)
```


```{r}
affect_effect <-  as.data.frame(effect("perceived_control", motivate_mod1_comps, confint=TRUE))

plot_effect <- ggplot(affect_effect, aes(x = perceived_control, y = fit)) +
 geom_line(color = dark_blue) + theme_classic() + 
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = dark_blue, alpha = 0.3) +
  geom_jitter(data = beh_scan_comps_wide,  aes(x = perceived_control, y = motivated),
              width = 0.1, height = 0.05, pch = 21,
             alpha = 0.2, fill = dark_blue) +
   theme(legend.position = "none") + 
  theme_classic() + ylab("Self-reported motivation") + #coord_cartesian(ylim=c(1,3)) +
  xlab ("Perceived Control") + theme(legend.position = "none")
plot_effect

ggsave(plot_effect, file = "../figures/self_report/motivation_COMPS_by_perceived_control.png", width = 6, height = 4)
```


## Group effect on motivation: SIG 
only when account for  effects of perceived control and motor speed! 
HUGE EFFECT OF PERCEIVED CONTROL. 
```{r}
motivate_mod1_g <- lm(motivated ~ GROUP_ECA + AGE.c + SEX.c + perceived_control + 
                          Reinforce_rate.c + median_motor_RT_ave, 
                 data = beh_scan_ECA_wide)
summary(motivate_mod1_g)
```

### PC1 effect on motivation: SIG when accounting for perceived control and motor speed! 
```{r}
motivate_mod1_PC1 <- lm(motivated ~  PC1_log +  AGE.c + SEX.c + perceived_control + 
                          Reinforce_rate.c + median_motor_RT_ave, 
                 data = beh_scan_ECA_wide)
summary(motivate_mod1_PC1)

```

```{r}
affect_effect <-  as.data.frame(effect("PC1_log", motivate_mod1_PC1, confint=TRUE))

plot_effect <- ggplot(affect_effect, aes(x = PC1_log, y = fit)) +
 geom_line(color = dark_blue) + theme_classic() + 
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = dark_blue, alpha = 0.3) +
  geom_jitter(data = beh_scan_ECA_wide,  aes(x = PC1_log, y = motivated),
              width = 0.2, height = 0.05, pch = 21,
             alpha = 0.2, fill = dark_blue) +
   theme(legend.position = "none") + 
  theme_classic() + ylab("Self-reported motivation") + #coord_cartesian(ylim=c(1,3)) +
  xlab ("Cumulative ECA score") + theme(legend.position = "none")
plot_effect

ggsave(plot_effect, file = "../figures/self_report/motivation_by_PC1.png", width = 6, height = 4)
```


# Frustration 

## COMPS: motor, but not age effects

```{r}
frust_mod1_comps <- lm(frustrated ~ AGE.c  + SEX.c  + 
                      median_motor_RT_ave + Reinforce_rate,
                 data = beh_scan_comps_wide)
summary(frust_mod1_comps)
```

```{r}
affect_effect <-  as.data.frame(effect("median_motor_RT_ave", frust_mod1_comps, confint=TRUE))

plot_effect <- ggplot(affect_effect, aes(x = median_motor_RT_ave, y = fit)) +
 geom_line(color = dark_blue) + theme_classic() + 
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = dark_blue, alpha = 0.3) +
  geom_jitter(data = beh_scan_comps_wide,  aes(x = median_motor_RT_ave, y = frustrated),
              width = 0, height = 0, pch = 21,
             alpha = 0.2, fill = dark_blue) +
   theme(legend.position = "none") + xlim(0.1, 0.3) +
  theme_classic() + ylab("Self-reported frustration") + #coord_cartesian(ylim=c(1,3)) +
  xlab ("Motor Speed") + theme(legend.position = "none")
plot_effect

ggsave(plot_effect, file = "../figures/self_report/frustrated_COMPS_by_motor_speed.png", width = 6, height = 4)
```

## ECA group effect on frustration: NS
```{r}
frust_mod1_g <- lm(frustrated ~ GROUP_ECA + AGE.c + SEX.c + perceived_control +
                          Reinforce_rate.c + median_motor_RT_ave, 
                 data = beh_scan_ECA_wide)
summary(frust_mod1_g)
```

## PC1 effect on frustration : NS
```{r}
frust_mod1_PC1 <- lm(frustrated ~ PC1_log + AGE.c + SEX.c + perceived_control + 
                          Reinforce_rate.c + median_motor_RT_ave, 
                 data = beh_scan_ECA_wide)
summary(frust_mod1_PC1)
```

```{r}
affect_effect <-  as.data.frame(effect("PC1_log", frust_mod1_PC1, confint=TRUE))

plot_effect <- ggplot(affect_effect, aes(x = PC1_log, y = fit)) +
 geom_line(color = dark_blue) + theme_classic() + 
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = dark_blue, alpha = 0.3) +
  geom_jitter(data = beh_scan_ECA_wide,  aes(x = PC1_log, y = frustrated),
              width = 0.2, height = 0.05, pch = 21,
             alpha = 0.2, fill = dark_blue) +
   theme(legend.position = "none") + 
  theme_classic() + ylab("Self-reported frustration") + #coord_cartesian(ylim=c(1,3)) +
  xlab ("Cumulative ECA score") + theme(legend.position = "none")
plot_effect

ggsave(plot_effect, file = "../figures/self_report/frustrated_by_PC1.png", width = 6, height = 4)
```

# Fun 

## COMP:main effects of nothing!!! 
```{r}
fun_mod1_comp <- lm(fun ~ AGE.c + SEX.c +
                          Reinforce_rate.c + median_motor_RT_ave, 
                 data = beh_scan_comps_wide)
summary(fun_mod1_comp)
```

## Group effects on fun: NS
```{r}
fun_mod1_g <- lm(fun ~ GROUP_ECA + AGE.c + SEX.c +
                          Reinforce_rate.c + median_motor_RT_ave, 
                 data = beh_scan_ECA_wide)
summary(fun_mod1_g)
```

## PC1 effects on fun: NS
```{r}
fun_mod1_g <- lm(fun ~ PC1_log + AGE.c + SEX.c +
                          Reinforce_rate.c + median_motor_RT_ave, 
                 data = beh_scan_ECA_wide)
summary(fun_mod1_g)
```


# Sleepy 

## COMP: main effects of nothing!!! 
```{r}
sleep_mod1_comp <- lm(sleepy ~ AGE.c + SEX.c +
                          Reinforce_rate.c + median_motor_RT_ave, 
                 data = beh_scan_comps_wide)
summary(sleep_mod1_comp)
```

## Group effects on sleepiness: NS
```{r}
sleep_mod1_g <- lm(sleepy ~ GROUP_ECA + AGE.c + SEX.c +
                          Reinforce_rate.c + median_motor_RT_ave, 
                 data = beh_scan_ECA_wide)
summary(sleep_mod1_g)
```

## PC1 effects on sleepiness: NS
```{r}
sleep_mod1_PC1 <- lm(sleepy ~ PC1_log + AGE.c + SEX.c +
                          Reinforce_rate.c + median_motor_RT_ave, 
                 data = beh_scan_ECA_wide)
summary(sleep_mod1_PC1)
```

