---
title: "Task version effects on behavior and RT"
author: "Michelle.VanTieghem"
date: "Dec 4, 2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---
# notes 
Dec 1 2019: updated with new MICM variables and using PC1_log instead of sqrt.

# confound: 
behavior varies by task version, so only including usable scan participants who were guaranteed to perform the task in scanner for both runs.

```{r, include = F, warnings = F, echo=FALSE, message = F}
source("../../../0_R_analysis_setup_file.R")
```


```{r}
# load all data with PCA added!
load("../1_PCA/data/all_pacct_effort_data_with_PCA.rda")
``` 

# Figuring out versions

## who did which run in the scanner vs. outside the scanner...
```{r}
scanner_sublist <- beh_scan_ECA_long %>%
  select(SUBJECTID, RunNumber)
# check that PA255 is added once you add it! 
sum(scanner_sublist$SUBJECTID =="PA255")
beh_ECA_long$scanner <- NA

beh_ECA_long <- beh_ECA_long %>% 
 mutate(scanner = as.factor(ifelse(SUBJECTID %in% scanner_sublist$SUBJECTID & 
                                      RunNumber %in% scanner_sublist$RunNumber, "inside", "outside")))
summary(beh_ECA_long$scanner)

beh_ECA_wide <- beh_ECA_wide %>% 
 mutate(scanner = as.factor(ifelse(SUBJECTID %in% scanner_sublist$SUBJECTID, "inside", "outside")))
summary(beh_ECA_wide$scanner)

```

less useful: whether the task version had "external keyboard" in the name
which applies to some, but not all, subjects who did the task in the mock scan room computer.
```{r}

beh_ECA_long <- beh_ECA_long %>%
  mutate(computer = as.factor(ifelse(computer == "inside scanner", "scanner", "mock")))
summary(beh_ECA_long$computer)

beh_ECA_wide <- beh_ECA_wide %>%
  mutate(computer = as.factor(ifelse(computer == "inside scanner", "scanner", "mock")))
summary(beh_ECA_wide$computer)

```

## logical assumption: combine computer variable with scanner
if not in completed scanner, and not on external keyboard, completed with regular computer keyboard on scanner laptop. so we have 3 different behavior version types, 
BUT really not *positive* if people who didn't use external keyboard version culd have still plugged external keyboard into the scanner laptop. 
```{r}
beh_ECA_long <- beh_ECA_long %>%
  mutate(keyboard_version = as.factor(ifelse(scanner == "inside", "scanner buttonbox", 
                                   ifelse(scanner == "outside" & computer == "mock", 
                                          "external keyboard", "computer keyboard"))))

summary(beh_ECA_long$keyboard_version)

beh_ECA_wide <- beh_ECA_wide %>%
  mutate(keyboard_version = as.factor(ifelse(scanner == "inside", "scanner buttonbox", 
                                   ifelse(scanner == "outside" & computer == "mock", 
                                          "external keyboard", "computer keyboard"))))

summary(beh_ECA_wide$keyboard_version)
```

## SAVE THIS OUT  FORR USING IN ANALYESS
```{r}

task_confound_df <- beh_ECA_wide %>%
  select(SUBJECTID, keyboard_version, computer, scanner)
save(task_confound_df, file = "data/task_confound_df.Rdata")

```

# Effort choice behavior 

## keyboard version: VERY sig effects
```{r}
choice_mod_keyversion <- glmer(Effort_Choice.n ~ keyboard_version + Trial_Number.c +
                       AGE.c + SEX.c + Reinforce_rate.c + 
                      (1 + Trial_Number.c | SUBJECTID), 
                     family = binomial,
                    data = beh_ECA_long,
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod_keyversion)
library(car)
Anova(choice_mod_keyversion, type = "III")

```

```{r}
effect_df <- data.frame(effect("keyboard_version", choice_mod_keyversion))

effect_plot<- ggplot(effect_df, aes(x = keyboard_version, y = fit)) + 
  geom_point(color = "red", size = 2) + 
  geom_errorbar(aes(ymin = lower, ymax= upper), width = .3) + 
  geom_jitter(data = beh_ECA_wide, aes(x = keyboard_version, y = prop_hard_choices),
             alpha = 0.5, width = .1, height = 0.05) + 
   theme_classic() + ylab("Proportion of Hard Choices") + ylim(0, 1.3)
effect_plot

ggsave(effect_plot, file = "figures/Task_version_confound/keyboard_effects_on_effort_choices.pdf")
```

## check differences by scanner only - inside vs. outisde

```{r}

choice_mod_scanner <- glmer(Effort_Choice.n ~ scanner + Trial_Number.c +
                       AGE.c + SEX.c + Reinforce_rate.c + 
                      (1 + Trial_Number.c | SUBJECTID), 
                     family = binomial,
                    data = beh_ECA_long,
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod_scanner)

```


```{r}
effect_df <- data.frame(effect("scanner", choice_mod_scanner))

effect_plot<- ggplot(effect_df, aes(x = scanner, y = fit)) + 
  geom_point(color = "red", size = 2) + 
  geom_errorbar(aes(ymin = lower, ymax= upper), width = .3) + 
  geom_jitter(data = beh_ECA_wide, aes(x = scanner, y = prop_hard_choices),
             alpha = 0.5, width = .1, height = 0.05) + 
   theme_classic() + ylab("Proportion of Hard Choices") + ylim(0, 1.3)
effect_plot

ggsave(effect_plot, file = "figures/task_version_confound/Scanner_effects_on_effort_choice.pdf")
```

# Choice Reaction Time 

## keyboard version: SIG effects! 
```{r}

beh_ECA_long$Effort_Choice.n <- as.factor(beh_ECA_long$Effort_Choice.n)

choice_RT_mod_keyversion <- lmer(key_resp_choice.rt ~ keyboard_version * Effort_Choice.n +
                                 Trial_Number.c + AGE.c + SEX.c + Reinforce_rate.c +  #
                      (1 | SUBJECTID), 
                    data = beh_ECA_long)
summary(choice_RT_mod_keyversion)
Anova(choice_RT_mod_keyversion, type = "III")
```

the effect of hard vs. easy is WAY more obvious in the scanner.
```{r}
effect_df <- data.frame(effect("keyboard_version:Effort_Choice.n", choice_RT_mod_keyversion))

effect_plot<- ggplot(effect_df, aes(x = Effort_Choice.n, y = fit)) + 
  geom_point(color = "red", size = 2) + 
  geom_errorbar(aes(ymin = lower, ymax= upper), width = .3) +
   theme_classic() + ylab("Choice Reaction Time") + facet_grid(~keyboard_version) + 
  xlab("Effort Choice, 0 = Easy, 1 = Hard")
effect_plot

ggsave(effect_plot, file = "figures/task_version_confound/keyboard_version_effects_on_choice_RT.pdf")
```


## significant scanner x effort choice RT 
```{r}
choice_RT_mod_scanner <- lmer(key_resp_choice.rt ~ scanner*Effort_Choice.n +
                             Trial_Number.c +
                       AGE.c + SEX.c + Reinforce_rate.c +  #
                      (1 | SUBJECTID), 
                    data = beh_ECA_long)
summary(choice_RT_mod_scanner)
```


opposite effects for hard task... slower inside scanner, faster outside scanner.
```{r}
effect_df <- data.frame(effect("scanner:Effort_Choice.n", choice_RT_mod_scanner))

effect_plot<- ggplot(effect_df, aes(x = Effort_Choice.n, y = fit)) + 
  geom_point(color = "red", size = 2) + 
  geom_errorbar(aes(ymin = lower, ymax= upper), width = .3) +
   theme_classic() + ylab("Choice Reaction Time") + facet_grid(~scanner) + 
  xlab("Effort Choice, 0 = Easy, 1 = Hard")
effect_plot

ggsave(effect_plot, file = "figures/Task_version_confound/keyboard_version_effects_on_choice_RT.pdf")


ggsave(effect_plot, file = "figures/task_version_confound/Scanner_effects_on_choice_RT.pdf")
```
