---
author: "Michelle.VanTieghem"
date: "Dec 1, 2019"
title: "prep data for PCA/FA"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

# Notes 
redoing on Dec 1 with updated MICM variables. \
updating on Dec 5 to add more iterations for stable parallel analysis.

```{r setup, include=FALSE, echo = F, warning = F}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(viridis)
library(readxl)
library(REdaS) # for diagnostic data checks before FA
library(psych)# need for factor analysis
library(GPArotation) # need for factor analysis
library(PCAmixdata)

```

## load cleaned data
```{r}
load("data/pacct_all_cleaned_ELV.Rdata")
nrow(pacct_cleaned)

pacct_cleaned <- pacct_cleaned %>%
  mutate(SUBJECTID = as.factor(substr(IDENT_SUBID, 1, 5)))

```

## cleaned behavioral effort data 
```{r}
## use behavioral data, so calculating on as many subs as possible.
load("../../../9_combine_brain_beh_data/cleaned_data/COMP_ECA/all_pacct_effort_data.Rda")
effort_sublist <- beh_ECA_wide$SUBJECTID
length(effort_sublist)

elv_sublist <- pacct_cleaned$SUBJECTID

pacct_effort <-  pacct_cleaned %>%
  filter(SUBJECTID %in% effort_sublist)
nrow(pacct_effort) 

```


## Check for how many subs don't have complete cases.
```{r}
# remove subs without full cases.
pacct_effort_w_labels <- pacct_effort  %>%  
  dplyr::filter(., complete.cases(.))
nrow(pacct_effort_w_labels) 

# how many incomplete cases?
N_incomplete_cases <- nrow(pacct_effort) - nrow(pacct_effort_w_labels)
N_incomplete_cases

  # make a key for subject, by row number...for matching later.
pacct_effort_w_labels <- pacct_effort_w_labels %>%
  mutate(subject = as.numeric(rownames(pacct_effort_w_labels)))

# KEEP THIS SUBLIST TO MATCH WITH PCA RESULTS LATER!
save(pacct_effort_w_labels, file = "data/pacct_effort_w_labels.Rdata")

```


## Remove labels 
```{r}
pacctNoLabels <- pacct_effort %>%
  select(-SUBJECTID, -IDENT_SUBID, -GROUP, -DEM_3_GENDER_CHILD) %>%
  dplyr::filter(., complete.cases(.))

nrow(pacctNoLabels)
```



## Test assumptions 
Bartlett’s test of sphericity checks whether or not the observed variables 
intercorrelate at all using the observed correlation matrix against the 
identity matrix. If the test found statistically insignificant, 
you should not employ a factor analysis.
```{r}
# test is significant! 
bart_spher(pacctNoLabels)
```

Kaiser-Meyer-Olkin (KMO) Test measures the suitability of data for factor analysis. 
It determines the adequacy for each observed variable and for the complete model. 
KMO estimates the proportion of variance among all the observed variable. 
Lower proportion is more suitable for factor analysis. KMO values range between 0 and 1. 
Value of KMO less than 0.6 is considered inadequate.

```{r}
# results here for this sample are different than the entire PACCT sample! 

KMO_pacct <- data.frame(KMO(pacctNoLabels)$MSAi) %>%
  mutate(variable = rownames(data.frame(KMO(pacctNoLabels)$MSAi))) %>%
  rename(KMO_value = KMO.pacctNoLabels..MSAi)

hist(KMO_pacct$KMO_value)
vars_omit <- KMO_pacct %>%
  filter(KMO_value < .6) 
vars_omit 

```

## remove these variables
```{r}
pacctNoLabelsCleaned <- data.frame(pacctNoLabels) %>% 
  select(-c(vars_omit$variable))
```


## standardize, convert to matrix, and save data
```{r}

scale <- function(variable){
  (variable - mean(variable))/sd(variable)
}

pacctNoLabelsCleaned <- pacctNoLabelsCleaned %>%
  mutate_all(scale) 

save(pacctNoLabelsCleaned, file = "data/cleaned_ELV_for_dim_reduction.Rdata")

```

## parallel analysis 
fa.parallel The parallel factors technique compares the observed eigen values of a corelation matrix with those from random data.
```{r}
# make a correlation matrix.
pacct_cor <- cor(pacctNoLabelsCleaned) 

# iterations increased to get a more stable estimate! 
par_analysis <- fa.parallel(pacct_cor, n.obs = nrow(pacctNoLabelsCleaned), n.iter = 1000, error.bars = TRUE)

par_analysis$nfact
#Number of factors with eigen values > eigen values of random data

par_analysis$ncomp
#Number of components with eigen values > eigen values of random data

save(par_analysis, file = "output/parallel_analysis_results.Rdata")
```


Parallel analysis suggests that the number of factors =  `r par_analysis$nfact`  and the number of components = `r par_analysis$ncomp` ... results are differrernt than non-comp PCA, which only needs 2 PCs




