---
title: "Aim 1 Hypothesis 1a: Choice Reactivity"
author: "Michelle.VanTieghem"
date: "10/10/2019"
output:
  html_document:
    number_sections: no 
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---


# Notes: 
Nov 7, 2019 - updated PCA with TESI CG variables \
That also means that not all subjects have PC results \
Missing N = 10, so also excluding those from group models. N = 116 (not 126) \
Dec 1 2019: updated with new MICM variables and using PC1_log instead of sqrt.
Dec 8, 2019: updated with PA255 so N=127 for ROIs ... but ends up being 117 because of 10 kids missing questionnaires for the PCA. \
Jan 6, 2020: adding self-report covariates 




```{r, include = F, warnings = F, echo=FALSE, message = F}
source("../../../0_R_analysis_setup_file.R")
```


```{r}
# load all data with PCA added!
load("../1_PCA/data/all_pacct_effort_data_with_PCA.rda")
```

# Aim 1: Characterize effects of ECA exposure on neurobehavioral phenotype of persistence.

## Hypothesis 1a: Neural resopnse to choices
At the group-level, children with ECA exposure will show weaker fronto-striatal recruitment during effort-choices

## Results summary 
PC1-choice: no associations \
PC1-hard vs easy choice: mPFC is only trend, regardless of no IQ, with IQ, or no IQ excluding missing IQ subs

GROUP-choice: no associations \
GROUP- hard vs easy choice: mPFC is significant! 

## set up & clean data
```{r} 
choice_level_order <- c('ACC', 'mPFC',  "VS")
#organize data for choice phase.
choice_df <- beh_scan_ECA_wide %>%
  # combine left and right accumbens betas into bilateral! 
  select(-starts_with("feedback"), -starts_with("setback"), -starts_with("reward")) %>%
  gather(key = "ROI", value = "beta", choice_ACC, choice_choice_mPFC,  choice_VS) %>%
  filter(!is.na(beta) & !is.na(PC1)) %>%
  mutate(ROI = ifelse(ROI == "choice_ACC", "ACC",
                      ifelse(ROI == "choice_choice_mPFC", "mPFC",  "VS")),
            ROI = factor(ROI, levels = choice_level_order),
         AGE.c = AGE.x - mean(AGE.x, na.rm = T),
         SEX.c = SEX.x - mean(SEX.x, na.rm = T), 
         IQ.c = IQ- mean(IQ, na.rm = T),
         total_TRs_censored.c = total_TRs_censored - mean(total_TRs_censored, na.rm = T),
         Reinforce_rate.c = Reinforce_rate - mean(Reinforce_rate, na.rm = T), 
         GROUP_ECA.c = ifelse(GROUP_ECA == "COMP", -1, 1), 
         PC1_log.c = PC1_log - mean(PC1_log, na.rm = T))

# check right number of subjects! 
length(unique(choice_df$SUBJECTID))

```

## clean data: remove beta outliers
```{r}
# calculate limits of routliers at 3SD from mean
choice_outliers <- choice_df %>%
  group_by(ROI) %>%
  dplyr::summarize(outlier_upper = mean(beta) + 3*sd(beta), 
            outlier_lower = mean(beta) - 3*sd(beta))

# mark outliers for each ROI
choice_df2 <- data.frame()
for (region in choice_outliers$ROI){
    check <- choice_df %>% filter(ROI == region) %>%
    mutate(choice_outlier = ifelse(beta > choice_outliers$outlier_upper[choice_outliers$ROI == region] | 
                               beta < choice_outliers$outlier_lower[choice_outliers$ROI == region], 1, 0))
    choice_df2 <- rbind(choice_df2, check)
}

# look at outlier #
outlier_table <- choice_df2 %>%
  group_by(ROI) %>%
  dplyr::summarize(n = n(), 
            n_outlier = sum(choice_outlier))

outlier_table

# remove data of outliers, mark as NA. 
choice_df2 <- choice_df2 %>% 
  mutate(beta = ifelse(choice_outlier == 1, NA, beta)) 

sum(is.na(choice_df2$beta))
# get subjects for outliers for long analyses 
choice_outlier_subjects <- choice_df2 %>% 
  filter(choice_outlier == 1) %>% select (ROI, SUBJECTID)
save(choice_outlier_subjects, file = "tables/Choice_betas_outlier_subjects.Rdata")

levels(choice_df2$ROI) <- choice_level_order
length(unique(choice_df2$SUBJECTID))

```

## choice reactivity
All significant main effects (negative) but no group differences.
```{r}
mod1_ACC <- lm(beta ~ GROUP_ECA.c + AGE.c + SEX.c + #IQ.c +  
                   total_TRs_censored.c + Reinforce_rate.c, 
           data = subset(choice_df2, ROI == "ACC"))
main_effect_ACC <- summary(mod1_ACC)$coefficients[1,]
choice_effect_ACC <- summary(mod1_ACC)$coefficients[2,]

mod1_mPFC <- lm(beta ~ GROUP_ECA.c + AGE.c + SEX.c + #IQ.c + 
                   total_TRs_censored.c + Reinforce_rate.c, 
           data = subset(choice_df2, ROI == "mPFC"))
main_effect_mPFC<- summary(mod1_mPFC)$coefficients[1,]
choice_effect_mPFC <- summary(mod1_mPFC)$coefficients[2,]

mod1_VS <- lm(beta ~  GROUP_ECA.c +AGE.c + SEX.c + #IQ.c + 
                   total_TRs_censored.c + Reinforce_rate.c, 
           data = subset(choice_df2, ROI == "VS"))
main_effect_VS <- summary(mod1_VS)$coefficients[1,]
choice_effect_VS <- summary(mod1_VS)$coefficients[2,]
```

### table of main effects
```{r}

table_choice_activation <- data.frame(rbind(main_effect_ACC, main_effect_mPFC, main_effect_VS)) %>%
  rename(p_value = "Pr...t..", 
         SE = "Std..Error", 
         t_value = "t.value")
table_choice_activation$ROI <- c("ACC", "mPFC", "VS")
table_choice_activation$df <- mod1_ACC$df.residual

table_choice_activation <- table_choice_activation %>% 
        mutate(sig =  ifelse(p_value < 0.001, "***", ifelse(p_value < 0.01, "**", 
                                         ifelse(p_value < 0.05, "*", "")))) %>%
  select(ROI, Estimate, SE, df, t_value, p_value, sig)
table_choice_activation
save(table_choice_activation, file = "model_results/Aim1_hypothesis1a/choice_activation_main_effect_model_results.Rdata")

```

### table of group effects

```{rr}
table_choice_activation_GROUP <- data.frame(rbind(choice_effect_ACC, choice_effect_mPFC, choice_effect_VS)) %>%
  rename(p_value = "Pr...t..", 
         SE = "Std..Error", 
         t_value = "t.value")
table_choice_activation_GROUP$level <- "GROUP"
table_choice_activation_GROUP$ROI <- c("ACC", "mPFC", "VS")
table_choice_activation_GROUP$df <- mod1_ACC$df.residual

table_choice_activation_GROUP <- table_choice_activation_GROUP %>% 
        mutate(sig =  ifelse(p_value < 0.001, "***", ifelse(p_value < 0.01, "**", 
                                         ifelse(p_value < 0.05, "*", ""))),
                         upper = Estimate + 2*SE, 
          lower = Estimate  - 2*SE) %>%
  select(level, Estimate, lower, upper, SE, df, t_value, p_value, sig)
table_choice_activation_GROUP
save(table_choice_activation_GROUP, file = "model_results/Aim1_hypothesis1a/choice_activation_GROUP_model_results.Rdata")
```

### plot of main effects 
```{r}
# model together just for the sake of plots. 
mod1 <- lm(beta ~ ROI + AGE.c + SEX.c + #IQ.c +
                   total_TRs_censored.c + Reinforce_rate.c, 
           data = choice_df2)
summary(mod1)
effect_df <- data.frame(effect("ROI", mod1, confint = T))

plot_effect <- ggplot(data = effect_df,
                      aes(x = factor(ROI, level = choice_level_order), y = fit)) + 
                        geom_bar(stat = "identity", position=position_dodge(),
                                 alpha = 0.2, fill = dark_blue) + theme_classic() + 
  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_point(data = choice_df2,  aes(x = factor(ROI, level = choice_level_order), y = beta), 
             position = position_dodge(.9), alpha = 0.25, color = dark_blue) + 
  theme(legend.position = "none") + ylim(-200, 200)+ 
  ylab("Reactivity during Choice Phase") + xlab ("ROI") + my_colors2 + my_colors + 
 geom_hline(yintercept=0, linetype="dashed",  size=.5)
plot_effect

ggsave(plot_effect, file = "figures/Aim1_hypothesis1a/All_ROIs_Choice_Phase_main_effects.pdf", width = 3, height = 4)

```

### plot of group effects
```{r}
effect_VS <- data.frame(ROI = "VS", effect("GROUP_ECA.c", mod1_VS))
effect_ACC <- data.frame(ROI = "ACC", effect("GROUP_ECA.c", mod1_ACC))
effect_mPFC <- data.frame(ROI = "mPFC", effect("GROUP_ECA.c", mod1_mPFC))
effect_df <- rbind(effect_ACC, effect_mPFC, effect_VS) %>%
  mutate(GROUP_ECA = ifelse(GROUP_ECA.c == -1, "COMP",
                        ifelse(GROUP_ECA.c == 1, "ECA", NA))) %>%
  filter(!is.na(GROUP_ECA))

plot_effect <- ggplot(data = effect_df, aes(x = GROUP_ECA, y = fit)) +  
           geom_bar(aes(fill = GROUP_ECA),stat = "identity", position=position_dodge(),
                    alpha = 0.2) + 
  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_point(data = choice_df2, aes(x = GROUP_ECA, y = beta, color = GROUP_ECA), 
            alpha = 0.25) + my_colors + my_colors2 +
  theme(legend.position = "none") + ylim(-200, 200)+ 
  ylab("Activation during Choice Phase") + xlab ("GROUP") +
  my_colors2 + my_colors + theme_classic() + facet_grid(~ROI) +
 geom_hline(yintercept=0, linetype="dashed",  size=.5) +
  theme(legend.position = "none")
plot_effect

ggsave(plot_effect, file = "figures/Aim1_hypothesis1a/All_ROIs_Choice_Phase_by_GROUP.pdf", width = 6, height = 4)
```

##  PC1 and choice reactivity

```{r}

mod1_ACC <- lm(beta ~  PC1_log.c +AGE.c + SEX.c + #IQ.c + 
                   total_TRs_censored.c + Reinforce_rate.c, 
           data = subset(choice_df2, ROI == "ACC"))
main_effect_ACC <- summary(mod1_ACC)$coefficients[1,]
choice_effect_ACC <- summary(mod1_ACC)$coefficients[2,]


mod1_mPFC <- lm(beta ~ PC1_log.c + AGE.c + SEX.c + #IQ.c + 
                   total_TRs_censored.c + Reinforce_rate.c, 
           data = subset(choice_df2, ROI == "mPFC"))
main_effect_mPFC <- summary(mod1_mPFC)$coefficients[1,]
choice_effect_mPFC <- summary(mod1_mPFC)$coefficients[2,]

mod1_VS <- lm(beta ~ PC1_log.c + AGE.c + SEX.c + #IQ.c + 
                   total_TRs_censored.c + Reinforce_rate.c, 
           data = subset(choice_df2, ROI == "VS"))
main_effect_VS <- summary(mod1_VS)$coefficients[1,]
choice_effect_VS <- summary(mod1_VS)$coefficients[2,]


### table of main effects
table_choice_activation_PC1 <- data.frame(rbind(main_effect_ACC, main_effect_mPFC, main_effect_VS)) %>%
  rename(p_value = "Pr...t..", 
         SE = "Std..Error", 
         t_value = "t.value")
table_choice_activation_PC1$ROI <- c("ACC", "mPFC", "VS")
table_choice_activation_PC1$df <- mod1_ACC$df.residual

table_choice_activation_PC1 <- table_choice_activation_PC1 %>% 
        mutate(sig =  ifelse(p_value < 0.001, "***", ifelse(p_value < 0.01, "**", 
                                         ifelse(p_value < 0.05, "*", "")))) %>%
  select(ROI, Estimate, SE, df, t_value, p_value, sig)
#table_choice_activation_PC1
#save(table_choice_activation_PC1, file = "model_results/Aim1_hypothesis1a/choice_activation_main_effect_model_results.Rdata")

```

### table of continuous ECA effects
```{r}
### table of group effects
table_choice_activation_PC1 <- data.frame(rbind(choice_effect_ACC, choice_effect_mPFC, choice_effect_VS)) %>%
  rename(p_value = "Pr...t..", 
         SE = "Std..Error", 
         t_value = "t.value")
table_choice_activation_PC1$ROI <- c("ACC", "mPFC", "VS")
table_choice_activation_PC1$df <- mod1_ACC$df.residual
table_choice_activation_PC1$level <- "PC1"

table_choice_activation_PC1 <- table_choice_activation_PC1 %>% 
        mutate(sig =  ifelse(p_value < 0.001, "***", ifelse(p_value < 0.01, "**", 
                                         ifelse(p_value < 0.05, "*", ""))),
                         upper = Estimate + 2*SE, 
          lower = Estimate  - 2*SE) %>%
  select(level, Estimate, lower, upper, SE, df, t_value, p_value, sig) 
table_choice_activation_PC1
save(table_choice_activation_PC1, file = "model_results/Aim1_hypothesis1a/choice_activation_PC1_model_results.Rdata")
```

### plot of continuous ECA effects 
```{r}
min_PC1_log.c <- min(choice_df2$PC1_log.c)
max_PC1_log.c <- max(choice_df2$PC1_log.c)
effect_VS <- data.frame(ROI = "VS", effect("PC1_log.c", mod1_VS, xlevels = list(PC1_log.c = seq(min_PC1_log.c, max_PC1_log.c, .5))))
effect_ACC <- data.frame(ROI = "ACC", effect("PC1_log.c", mod1_ACC, xlevels = list(PC1_log.c = seq(min_PC1_log.c, max_PC1_log.c, .5))))
effect_mPFC <- data.frame(ROI = "mPFC", effect("PC1_log.c", mod1_mPFC, xlevels = list(PC1_log.c = seq(min_PC1_log.c, max_PC1_log.c, .5))))
effect_df <- rbind(effect_ACC, effect_mPFC, effect_VS)

plot_effect <- ggplot(data = effect_df, aes(x = PC1_log.c, y = fit)) +  
  geom_line(color= dark_blue) +
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = dark_blue, alpha = 0.3) +
                  #      geom_bar(stat = "identity", position=position_dodge(),
                   #              alpha = 0.2, fill = dark_blue) + 
#  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_point(data =choice_df2, aes(x = PC1_log.c, y = beta), 
            alpha = 0.25, color = dark_blue) + 
  theme(legend.position = "none") + ylim(-200, 200)+ 
  ylab("Activation during Choice Phase") + xlab ("Cumulative ECA Score") +
  my_colors2 + my_colors + theme_classic() + facet_grid(~ ROI) +
 geom_hline(yintercept=0, linetype="dashed",  size=.5) 
plot_effect

pdf("figures/Aim1_hypothesis1a/All_ROIs_Choice_Phase_by_PC1.pdf", width = 6, height = 3)
plot_effect
dev.off()

```



# Hypothesis 1 Follow-up model: ECA Effects on Hard vs. Easy choice activation (N=73)
I'm not really sure how informative this is. don't have hypothesized questions about why there would e different reactivity to hard vs. easy, if there is no differences in choices to hard vs. easy

## clean data 
```{r} 

#organize data for choice phase.
choice_contrast_df <- beh_scan_ECA_wide %>%
  # combine left and right accumbens betas into bilateral! 
  select(-starts_with("feedback"), -contains ("FB"), -contains("setback"), -contains("reward"), -starts_with("choice")) %>%
  # converting this because i forgot to pull easy choices alone
    gather(key = "ROI", value = "beta", hard_choice_ACC, hard_choice_choice_mPFC, hard_choice_VS,
         easy_choice_ACC, easy_choice_choice_mPFC, easy_choice_VS, 
         hard_easy_choice_ACC, hard_easy_choice_choice_mPFC, hard_easy_choice_VS) %>%
  filter(!is.na(beta) & !is.na(PC1)) %>%
  mutate(contrast = as.factor(ifelse(grepl("hard_easy", ROI), "hard_easy",
                           ifelse(grepl("hard_", ROI), "hard", "easy"))),
           ROI = as.factor(ifelse(grepl("ACC", ROI), "ACC", 
                        ifelse(grepl("mPFC", ROI), "mPFC", "VS"))),
           AGE.c = AGE.x - mean(AGE.x, na.rm = T),
         SEX.c = SEX.x - mean(SEX.x, na.rm = T), 
         IQ.c = IQ- mean(IQ, na.rm = T),
         total_TRs_censored.c = total_TRs_censored - mean(total_TRs_censored, na.rm = T),
         Reinforce_rate.c = Reinforce_rate - mean(Reinforce_rate, na.rm = T), 
         GROUP_ECA.c = ifelse(GROUP_ECA == "COMP", -1, 1), 
         PC1_log.c = PC1_log -mean(PC1_log))
summary(as.factor(choice_contrast_df$ROI))
summary(as.factor(choice_contrast_df$contrast))

# check correct number of subjects! 
length(unique(choice_contrast_df$SUBJECTID))

#sanity check for easy contrast calculation 
hard_easy_df <- choice_contrast_df %>% filter(contrast == "hard_easy")
hard_df <- choice_contrast_df %>%filter (contrast =="hard")
easy_df <- choice_contrast_df %>% filter(contrast == "easy")

easy_ACC_check <- easy_df$beta[easy_df$ROI == "ACC"]
hard_ACC_check <- hard_df$beta[hard_df$ROI == "ACC"]

hard_easy_ACC_check <- hard_ACC_check - easy_ACC_check
hard_easy_ACC_check2 <- hard_easy_df$beta[hard_easy_df$ROI == "ACC"]
plot(hard_easy_ACC_check, hard_easy_ACC_check2)
```


### clean data: remove beta outliers
```{r}
 #calculate limits fo routliers at 3SD from mean
choice_contrast_outliers <- choice_contrast_df %>%
  # remove NAs because not all subjects have these betas! 
  filter(!is.na(beta)) %>%
  group_by(ROI, contrast) %>%
  dplyr::summarize(outlier_upper = mean(beta, na.rm = T) + 3*sd(beta, na.rm = T), 
            outlier_lower = mean(beta, na.rm = T)- 3*sd(beta, na.rm = T))

# mark outliers for each ROI
choice_contrast_df2 <- data.frame()
for (region in unique(choice_contrast_outliers$ROI)){
  #region = "choice_mPFC"
  #print(region)
  for (cope in unique(choice_contrast_outliers$contrast)){
   # print(cope)
      #cope = "reward_minus_setback"
      check <- choice_contrast_df %>% filter(ROI == region & contrast == cope) %>%
      mutate(choice_contrast_outlier =
               ifelse(beta > choice_contrast_outliers$outlier_upper[choice_contrast_outliers$ROI == region & choice_contrast_outliers$contrast == cope] | 
                                 beta < choice_contrast_outliers$outlier_lower[choice_contrast_outliers$ROI == region & choice_contrast_outliers$contrast == cope], 1, 0))
      choice_contrast_df2 <- rbind(choice_contrast_df2, check)
  }
}

# look at outlier #
outlier_table <- choice_contrast_df2 %>%
  group_by(ROI, contrast) %>%
  dplyr::summarize(n = n(), 
            n_outlier = sum(choice_contrast_outlier, na.rm = T))
# idk why i ahve to do thsi!! 
outlier_table$n <- outlier_table$n 
outlier_table$n_outlier <- outlier_table$n_outlier

outlier_table
# remove data of outliers 
choice_contrast_df2 <- choice_contrast_df2 %>% 
  filter(!is.na(beta)) %>%
  mutate(beta = ifelse(choice_contrast_outlier > 0 , NA, beta))
sum(is.na(choice_contrast_df2$beta))
choice_contrast_outlier_subjects <- choice_contrast_df2 %>% 
  filter(choice_contrast_outlier == 1) %>% select(SUBJECTID, ROI, contrast)

choice_contrast_outlier_subjects
save(choice_contrast_outlier_subjects, file = "tables/choice_contrast_betas_outlier_subjects.Rdata")

# check that these 5 outlier values were removed
sum(is.na(choice_contrast_df2$beta))
```

## GROUP on hard vs. easy choices 
full models 
```{r}

mod1_ACC <- lm(beta ~ GROUP_ECA.c + AGE.c + SEX.c + #IQ.c + 
                       total_TRs_censored.c + Reinforce_rate.c,
                data = subset(choice_contrast_df2, ROI == "ACC" & contrast == "hard_easy" ))
choice_contrast_effect_ACC <- summary(mod1_ACC)$coefficients[1,]
choiceXgroup_effect_ACC <- summary(mod1_ACC)$coefficients[2,]

mod1_mPFC <- lm(beta ~ GROUP_ECA.c + AGE.c + SEX.c + #IQ.c + 
                       total_TRs_censored.c + Reinforce_rate.c,
                data = subset(choice_contrast_df2, ROI == "mPFC"& contrast == "hard_easy" ))
choice_contrast_effect_mPFC <- summary(mod1_mPFC)$coefficients[1,]
choiceXgroup_effect_mPFC <- summary(mod1_mPFC)$coefficients[2,]

mod1_VS <- lm(beta ~GROUP_ECA.c + AGE.c + SEX.c + #IQ.c + 
                       total_TRs_censored.c + Reinforce_rate.c,
                data = subset(choice_contrast_df2, ROI == "VS"& contrast == "hard_easy" ))
choice_contrast_effect_VS <- summary(mod1_VS)$coefficients[1,]
choiceXgroup_effect_VS <- summary(mod1_VS)$coefficients[2,]
```

### tables of main effects
```{r}
# combine tables 
table_choice_contrast_activation <- data.frame(rbind(
    choice_contrast_effect_ACC,  choice_contrast_effect_mPFC, choice_contrast_effect_VS)) 
table_choice_contrast_activation$level <- rownames(table_choice_contrast_activation)

table_choice_contrast_activation <- table_choice_contrast_activation %>%
  rename(p_value = "Pr...t..", 
         SE = "Std..Error", 
         t_value = "t.value") %>%
  mutate( sig =  ifelse(p_value < 0.001, "***", ifelse(p_value < 0.01, "**", 
                                         ifelse(p_value< 0.05, "*", ""))), 
          df = mod1_VS$df.residual) %>%
  select(level, Estimate, SE, df, t_value, p_value, sig)
table_choice_contrast_activation
save(table_choice_contrast_activation, file = "model_results/Aim1_hypothesis1a/choice_contrast_activation_model_results.Rdata")
```

### tables of ECA effects 
```{r}
# combine tables 
table_choiceXgroup_contrast_activation <- data.frame(rbind(
    choiceXgroup_effect_ACC,  choiceXgroup_effect_mPFC, choiceXgroup_effect_VS)) 
table_choiceXgroup_contrast_activation$level <- rownames(table_choiceXgroup_contrast_activation)

table_choiceXgroup_contrast_activation <- table_choiceXgroup_contrast_activation %>%
  rename(p_value = "Pr...t..", 
         SE = "Std..Error", 
         t_value = "t.value") %>%
  mutate( sig =  ifelse(p_value < 0.001, "***", ifelse(p_value < 0.01, "**", 
                                         ifelse(p_value< 0.05, "*", ""))), 
          df = mod1_VS$df.residual,
                    upper = Estimate + 2*SE, 
          lower = Estimate  - 2*SE) %>%
  select(level, Estimate, lower, upper, SE, df, t_value, p_value, sig)
table_choiceXgroup_contrast_activation
save(table_choiceXgroup_contrast_activation, file = "model_results/Aim1_hypothesis1a/choiceXgroup_contrast_activation_model_results.Rdata")
```

### plot of main effects 
```{r}

effect_df <- table_choice_contrast_activation %>%
  mutate(ROI = ifelse(grepl("ACC", level), "ACC", 
                      ifelse(grepl("mPFC", level), "mPFC", "VS")))

# so we can plot! 
plot_effect <- ggplot(data = effect_df, aes(x = ROI, y =Estimate)) + 
                        geom_bar(stat = "identity", position=position_dodge(),
fill = dark_blue, alpha = 0.25) + theme_classic() +# ylim(-200, 200) + 
  geom_errorbar(aes(ymin = Estimate - 2*SE, ymax = Estimate + 2*SE),
               position=position_dodge(.9), width = 0.25) +
  geom_point(data = subset(choice_contrast_df2,  contrast == "hard_easy"),
            aes(x = ROI, y = beta), position = position_dodge(.9),
             alpha = 0.25, color = dark_blue) + theme(legend.position = "none") +
  ylab("Reactivity for Easy vs. Hard Choices") + xlab ("ROI") + my_colors2 + my_colors + 
 geom_hline(yintercept=0, linetype="dashed",  size=.5)
plot_effect

ggsave(plot_effect, file = "figures/Aim1_hypothesis1a/All_ROIs_Hard-Easy_Choice_diff_scores.pdf", width = 3, height = 4)
```


### plot of ECA effects 
```{r}
choice_level_order <- c("ACC", "mPFC", "VS") 
effect_ACC <- data.frame(ROI = "ACC", effect("GROUP_ECA.c", mod1_ACC, confint = T))
effect_mPFC  <- data.frame(ROI = "mPFC",effect("GROUP_ECA.c", mod1_mPFC, confint = T))
effect_VS <- data.frame(ROI = "VS", effect("GROUP_ECA.c", mod1_VS, confint = T))

effect_df <- rbind(effect_ACC, effect_mPFC, effect_VS) %>%
  mutate(GROUP_ECA = ifelse(GROUP_ECA.c == -1, "COMP",
                        ifelse(GROUP_ECA.c == 1, "ECA", NA))) %>%
  filter(!is.na(GROUP_ECA))
# so we can plot! 
plot_effect <- ggplot(data = effect_df, aes(x = GROUP_ECA, y = fit, fill = GROUP_ECA)) + 
                        geom_bar(stat = "identity", position=position_dodge(),
alpha = 0.5) + theme_classic() + facet_grid (~ ROI) +
  geom_errorbar(aes(ymin = lower, ymax = upper),position=position_dodge(.9), width = 0.25) +
  geom_point(data = subset(choice_contrast_df2), 
            aes(x = GROUP_ECA, y = beta, color = GROUP_ECA), position = position_dodge(.9),
             alpha = 0.25) + theme(legend.position = "none") +
  ylab("Hard-Easy Choice Activation") + xlab ("GROUP") + my_colors2 + my_colors + 
 geom_hline(yintercept=0, linetype="dashed",  size=.5)
plot_effect

pdf("figures/Aim1_hypothesis1a/All_ROIs_Hard_vs_Easy_ChoiceXgroup.pdf", width = 6, height = 3)
plot_effect
dev.off()

```

## PC1 on Hard vs. easy choies 

```{r}

mod1_ACC <- lm(beta ~ PC1_log.c + AGE.c + SEX.c + #IQ.c + 
                       total_TRs_censored.c + Reinforce_rate.c,
                data = subset(choice_contrast_df2, ROI == "ACC" & contrast == "hard_easy" ))

choiceXPC1_log_effect_ACC <- summary(mod1_ACC)$coefficients[2,]

mod1_mPFC <- lm(beta ~ PC1_log.c + AGE.c + SEX.c + #IQ.c + 
                       total_TRs_censored.c + Reinforce_rate.c,
                data = subset(choice_contrast_df2, ROI == "mPFC"& contrast == "hard_easy" ))

choiceXPC1_log_effect_mPFC <- summary(mod1_mPFC)$coefficients[2,]

mod1_VS <- lm(beta ~ PC1_log.c + AGE.c + SEX.c + #IQ.c + 
                       total_TRs_censored.c + Reinforce_rate.c,
                data = subset(choice_contrast_df2, ROI == "VS"& contrast == "hard_easy" ))

choiceXPC1_log_effect_VS <- summary(mod1_VS)$coefficients[2,]
```

### table of continuous ECA effects
```{r}
# combine tables 
table_choice_contrast_activation <- data.frame(rbind(
    choiceXPC1_log_effect_ACC,  choiceXPC1_log_effect_mPFC, choiceXPC1_log_effect_VS)) 
table_choice_contrast_activation$level <- rownames(table_choice_contrast_activation)

table_choice_contrast_activation <- table_choice_contrast_activation %>%
  rename(p_value = "Pr...t..", 
         SE = "Std..Error", 
         t_value = "t.value") %>%
  mutate( sig =  ifelse(p_value < 0.001, "***", ifelse(p_value < 0.01, "**", 
                                         ifelse(p_value< 0.05, "*", ""))), 
          df = mod1_VS$df.residual, 
          upper = Estimate + 2*SE, 
          lower = Estimate  - 2*SE) %>%
  select(level, Estimate, lower, upper, SE, df, t_value, p_value, sig)
table_choiceXPC1_log_contrast_activation <- table_choice_contrast_activation
table_choiceXPC1_log_contrast_activation
save(table_choiceXPC1_log_contrast_activation, file = "model_results/Aim1_hypothesis1a/choiceXPC1_log_contrast_activation_PC1_log_model_results.Rdata")
```

### plot of continuous ECA effects
```{r, warning= F}

min_PC1_log.c <- min(choice_df2$PC1_log.c)
max_PC1_log.c <- max(choice_df2$PC1_log.c)
effect_VS <- data.frame(ROI = "VS", effect("PC1_log.c", mod1_VS, xlevels = list(PC1_log.c = seq(min_PC1_log.c, max_PC1_log.c, .5))))
effect_ACC <- data.frame(ROI = "ACC", effect("PC1_log.c", mod1_ACC, xlevels = list(PC1_log.c = seq(min_PC1_log.c, max_PC1_log.c, .5))))
effect_mPFC <- data.frame(ROI = "mPFC", effect("PC1_log.c", mod1_mPFC, xlevels = list(PC1_log.c = seq(min_PC1_log.c, max_PC1_log.c, .5))))
effect_df <- rbind(effect_ACC, effect_mPFC, effect_VS)


effect_df <- rbind(effect_ACC, effect_mPFC, effect_VS)
# so we can plot! 
plot_effect <- ggplot(data = effect_df, aes(x = PC1_log.c, y = fit)) + 
                    geom_line(color = dark_blue) + geom_ribbon(aes(ymin = lower, ymax = upper), fill = dark_blue,alpha = 0.3) +
  geom_point(data = subset(choice_contrast_df2), 
            aes(x = PC1_log.c, y = beta), color = dark_blue, position = position_dodge(.9),
             alpha = 0.25) + theme(legend.position = "none") +
  ylab("Hard-Easy Choice Activation") + xlab ("Cumulative Adversity Score") + my_colors2 + my_colors + 
 geom_hline(yintercept=0, linetype="dashed",  size=.5) + facet_grid(~ROI) + theme_classic()
plot_effect

pdf("figures/Aim1_hypothesis1a/All_ROIs_Hard_vs_Easy_ChoiceXPC1_log.pdf", width = 6, height = 3)
plot_effect
dev.off()

```




