---
title: "Aim1, hypothesis 2b"
author: "Michelle.VanTieghem"
date: "10/10/2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# notes
Dec 1 2019: updated with new MICM variables and using PC1_log instead of sqrt.\
need to re-run brms models!!  and only use brms for plots. \
also only using scan sample since behavior differs!! 

```{r, include = F, warnings = F, echo=FALSE, message = F}
source("../../../0_R_analysis_setup_file.R")
```

```{r}
# load all data with PCA added!
load("../1_PCA/data/all_pacct_effort_data_with_PCA.rda")
```

# Aim 1: Characterize effects of ECA exposure on neurobehavioral phenotype of persistence.

# Hypothesis 2b: WSLS behavior
At the group-level, ECA-exposed children will show  greater behavioral sensitivity to setbacks (indexed by lose-shift decision-making strategies).


## clean data to exclude 'too slow' trials
```{r}

beh_scan_ECA_long_WSLS <- beh_scan_ECA_long_WSLS %>%
  filter(Feedback_prior != "Too_slow")
```


## GROUP effects: SIG main effect
GROUP: sig 
AGE: SIG
Trial N: SIG 
prop hard: SIG 
Effort x age: NS
Feedback X Effort: SIG 
Effort X trial N: SIG 
```{r}
load(file = "brms_models/results/aim1_hypothesis2b/WSLS_mod1_g.Rdata")    
blm_table(WSLS_mod1_g)
```

### group x effort x feedback: NS 
```{r}
load(file = "brms_models/results/aim1_hypothesis2b/WSLS_mod1_gxexf.Rdata")    
blm_table(WSLS_mod1_gxexf)
```

### Group x effort : NS
```{r}

load(file = "brms_models/results/aim1_hypothesis2b/WSLS_mod1_gxe.Rdata")    
blm_table(WSLS_mod1_gxe)
```

### Group x age: NS
```{r}

load(file = "brms_models/results/aim1_hypothesis2b/WSLS_mod1_gxa.Rdata")    
blm_table(WSLS_mod1_gxa)
```


### Group x trial: NS
```{r}

load(file = "brms_models/results/aim1_hypothesis2b/WSLS_mod1_gxt.Rdata")    
blm_table(WSLS_mod1_gxt)
```




### plot main effects of GROUP
```{r}

new_df <- data.frame(expand.grid(GROUP_ECA.x = c(rep("COMP",4),rep("ECA", 4)),
                     Effort_Choice_prior = rep(c("Hard", "Easy"), 4),
                     Feedback_prior = c("Reward", "Reward", "Setback", "Setback", "Reward", "Reward", "Setback", "Setback"),
                     AGE.c = 0, Trial_Number.c = 0, Reinforce_rate.c = 0, SEX.c = 0, proportion_hard.c = 0))

WSLS_effect<- fitted(WSLS_mod1_g, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(GROUP_ECA = as.factor(GROUP_ECA.x))

summary(WSLS_effect$GROUP_ECA.x)
summary(beh_scan_ECA_wide_WSLS$GROUP_ECA)

WSLS_hard_setback_effect <- filter(WSLS_effect, Effort_Choice_prior == "Hard" & Feedback_prior == "Setback")
WSLS_easy_setback_effect <- filter(WSLS_effect, Effort_Choice_prior == "Easy" & Feedback_prior == "Setback")
WSLS_hard_reward_effect <- filter(WSLS_effect, Effort_Choice_prior == "Hard" & Feedback_prior == "Reward")
WSLS_easy_reward_effect <- filter(WSLS_effect, Effort_Choice_prior == "Easy" & Feedback_prior == "Reward")

WSLS_easy_setback_plot <- ggplot(WSLS_easy_setback_effect, aes(x = GROUP_ECA, y = fit)) +
  geom_point(aes(fill = GROUP_ECA), stat = "identity", position = "dodge", alpha = 0.2)  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
   geom_jitter(data = filter(beh_scan_ECA_wide_WSLS, Effort_Choice_prior == "Easy" & Feedback_prior == "Setback"),
       aes(x = GROUP_ECA, y = stay_shift, color = GROUP_ECA), 
       alpha = 0.3, width = 0.05, height =0.0) + 
  theme_classic() + my_colors + my_colors2 +  ggtitle('Behavior after an easy setback') +
  ylab ("Likelihood to choose easy again") + xlab ("GROUP") + 
  theme(legend.position = "none") + 
  geom_hline(aes(yintercept = 0.5), linetype = "dashed")

WSLS_hard_setback_plot <- ggplot(WSLS_hard_setback_effect, aes(x = GROUP_ECA, y = fit)) +
  geom_point(aes(fill = GROUP_ECA), stat = "identity", position = "dodge", alpha = 0.2)  +
 geom_errorbar(aes(ymin = lower, ymax = upper), position= position_dodge(.9), width = .2) +
  geom_jitter(data = filter(beh_scan_ECA_wide_WSLS, Effort_Choice_prior == "Hard" & Feedback_prior == "Setback"),
       aes(x = GROUP_ECA, y = stay_shift, color = GROUP_ECA), 
       alpha = 0.3, width = 0.05, height =0.0) +
   theme_classic() + my_colors + my_colors2 +  ggtitle('Behavior after a hard setback') +
  ylab ("Likelihood to choose hard again") + xlab ("GROUP") + 
  theme(legend.position = "none")+ 
  geom_hline(aes(yintercept = 0.5), linetype = "dashed")

WSLS_easy_reward_plot <- ggplot(WSLS_easy_reward_effect, aes(x = GROUP_ECA, y = fit)) +
  geom_point(aes(fill = GROUP_ECA), stat = "identity", position = "dodge", alpha = 0.2)  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
   geom_jitter(data = filter(beh_scan_ECA_wide_WSLS, Effort_Choice_prior == "Easy" & Feedback_prior == "Reward"),
       aes(x = GROUP_ECA, y = stay_shift, color = GROUP_ECA), 
       alpha = 0.3, width = 0.05, height =0.0) + 
  theme_classic() + my_colors + my_colors2 +  ggtitle('Behavior after an easy reward') +
  ylab ("Likelihood to choose easy again") + xlab ("GROUP") + 
  theme(legend.position = "none")+ 
  geom_hline(aes(yintercept = 0.5), linetype = "dashed")

WSLS_hard_reward_plot <- ggplot(WSLS_hard_reward_effect, aes(x = GROUP_ECA, y = fit)) +
  geom_point(aes(fill = GROUP_ECA), stat = "identity", position = "dodge", alpha = 0.2)  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
  geom_jitter(data = filter(beh_scan_ECA_wide_WSLS, Effort_Choice_prior == "Hard" & Feedback_prior == "Reward"),
       aes(x = GROUP_ECA, y = stay_shift, color = GROUP_ECA),
       alpha = 0.3, width = 0.05, height =0.0) +
   theme_classic() + my_colors + my_colors2 +  ggtitle('Behavior after a hard reward') +
  ylab ("Likelihood to choose hard again") + xlab ("GROUP") + 
  theme(legend.position = "none")+ 
  geom_hline(aes(yintercept = 0.5), linetype = "dashed")


combined2 <- grid.arrange(WSLS_easy_setback_plot, WSLS_hard_setback_plot, 
                          WSLS_easy_reward_plot, WSLS_hard_reward_plot, nrow = 2)

ggsave(combined2, height = 8, width = 10, file = "figures/Aim1_hypothesis2b/WSLS_by_GROUPxprior_feedback_xprior_effort_brms.pdf")

```



## cumulative adversity: NS here!!  
### main effect is NS 
```{r}

load(file = "brms_models/results/aim1_hypothesis2b/WSLS_mod1_PC1.Rdata")    
blm_table(WSLS_mod1_PC1)

```


### cumulative adversity x effort x feedback: NS
but therer is a PC1 x effort effect, does it stick ? 
```{r}

load(file = "brms_models/results/aim1_hypothesis2b/WSLS_mod1_PC1xexf.Rdata")    
blm_table(WSLS_mod1_PC1xexf)

```



### ECA continuous x effort choice: SIG!!! 

```{r}
load(file = "brms_models/results/aim1_hypothesis2b/WSLS_mod1_PC1xe.Rdata")    
blm_table(WSLS_mod1_PC1xe)
```

### ECA continuous x age: NS
```{r}

load(file = "brms_models/results/aim1_hypothesis2b/WSLS_mod1_PC1xa.Rdata")    
blm_table(WSLS_mod1_PC1xa)

```

### ECA conditious x trial: NS
```{r}
load(file = "brms_models/results/aim1_hypothesis2b/WSLS_mod1_PC1xt.Rdata")    
blm_table(WSLS_mod1_PC1xt)
```


make a subject-by-choice level thing to plot raw data
```{r}
WSLS_by_effort_per_subj <- beh_scan_ECA_long_WSLS %>%
  group_by(SUBJECTID, Effort_Choice_prior) %>%
  dplyr::summarize(GROUP = GROUP[1],
            PC1_log = mean(PC1_log),
            AGE.c = mean(AGE.c), 
            SEX.c = mean(SEX.c), 
            IQ.c = mean(IQ.c), 
            perceived_control = mean(perceived_control), 
            proportion_hard.c = mean(proportion_hard.c),
            Reinforce_rate.c = mean(Reinforce_rate.c), 
            hard_effort_perceived = mean(hard_effort_perceived), 
            stay_shift = mean(stay_shift))
``` 


## plot of PC1 x effort effect
BRMS version: will give you effects for each condition, even from main effect model
```{r}
PC1_est <- c(min(beh_scan_ECA_wide$PC1_log), 1,1.5, 2,2.5, max(beh_scan_ECA_wide$PC1_log))
#length(PC1_est)
new_df <- data.frame(expand.grid(PC1_log =PC1_est,
                     Effort_Choice_prior = c("Hard", "Easy"),
                     Feedback_prior = c("Reward","Setback"),
                     AGE.c = 0, Trial_Number.c = 0, Reinforce_rate.c = 0, SEX.c = 0, proportion_hard.c = 0))

WSLS_effect<- fitted(WSLS_mod1_PC1xe, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate)
WSLS_hard_effect <- filter(WSLS_effect, Effort_Choice_prior == "Hard")
WSLS_easy_effect <- filter(WSLS_effect, Effort_Choice_prior == "Easy")

WSLS_hard_plot <- ggplot(WSLS_hard_effect, aes(x = PC1_log, y = fit)) +
  geom_line(size = 1,aes(color = Feedback_prior)) + 
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = Feedback_prior), alpha = 0.3) +
  #geom_point(data = filter(beh_scan_ECA_wide_WSLS, Effort_Choice_prior == "Hard" & Feedback_prior != "Too_slow"),
   #   aes(x = PC1_log, y = stay_shift, color = Feedback_prior), alpha = 0.3) +
   theme_classic() + my_colors + my_colors2 + ylim(0,1) +
  ylab ("Likelihood to choose hard again") + xlab ("Cumulative ECA Score") +
   theme(legend.position = "none") + ggtitle("Behavior after a hard trial") +
   geom_hline(aes(yintercept = 0.5), linetype = "dashed")  

WSLS_easy_plot <- ggplot(WSLS_easy_effect, aes(x = PC1_log, y = fit)) +
  geom_line(size = 1, aes(color = Feedback_prior)) + 
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = Feedback_prior), alpha = 0.3) +
  #geom_point(data = filter(beh_scan_ECA_wide_WSLS, Effort_Choice_prior == "Easy"& Feedback_prior != "Too_slow"),
  #     aes(x = PC1_log, y = stay_shift, color = Feedback_prior), alpha = 0.3) +
   theme_classic() + my_colors + my_colors2 + ylim(0,1) + 
  ylab ("Likelihood to choose easy again") + xlab ("Cumulative ECA Score") +
   theme(legend.position = "none") + ggtitle("Behavior after an easy trial") +
   geom_hline(aes(yintercept = 0.5), linetype = "dashed")  

combined2 <- grid.arrange(WSLS_easy_plot, WSLS_hard_plot, nrow = 1)
combined2
ggsave(combined2, height = 4, width = 6, file = "figures/Aim1_hypothesis2b/WSLS_by_PC1xprior_effort_brms.pdf")

```



## plot of Feedback x effort effect
```{r}
# make new data with mean-centered for everything else. 
new_df <- data.frame(expand.grid(PC1_log = mean(beh_scan_ECA_wide$PC1_log),
                     Effort_Choice_prior = c("Hard", "Easy"),
                     Feedback_prior = c("Reward","Setback"),
                     AGE.c = 0, Trial_Number.c = 0, Reinforce_rate.c = 0, SEX.c = 0, proportion_hard.c = 0))

WSLS_effect<- fitted(WSLS_mod1_PC1, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate)
WSLS_hard_effect <- filter(WSLS_effect, Effort_Choice_prior == "Hard")
WSLS_easy_effect <- filter(WSLS_effect, Effort_Choice_prior == "Easy")


WSLS_hard_plot <- ggplot(WSLS_hard_effect, aes(x = Feedback_prior, y = fit, fill= Feedback_prior)) +
  geom_point(size = 3, color = 'black')  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
   geom_jitter(data = subset(beh_scan_ECA_wide_WSLS, Feedback_prior != "Too_slow" & Effort_Choice_prior == "Hard"),
       aes(x = Feedback_prior, y = stay_shift, color = Feedback_prior), 
       alpha = 0.1, width = 0.05, height =0.0) + #stackratio = 1, stackdir = "center", binaxis = "y", binwidth = .01, dotsize = 1) + 
   theme_classic() + my_colors + my_colors2 +   theme(legend.position = "none") + 
  ylab ("Likelihood to choose hard again") + xlab ("Feedback on prior trial") + ggtitle("Behavior after a hard trial") + geom_hline(aes(yintercept = 0.5), linetype = "dashed")

WSLS_Easy_plot <- ggplot(WSLS_easy_effect, aes(x = Feedback_prior, y = fit, fill= Feedback_prior)) +
  geom_point(size = 3, color = 'black')  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
  geom_jitter(data = subset(beh_scan_ECA_wide_WSLS, Feedback_prior != "Too_slow" & Effort_Choice_prior == "Easy"),
       aes(x = Feedback_prior, y = stay_shift, color = Feedback_prior), 
       alpha = 0.1, width = 0.05, height =0.0) + #stackratio = 1, stackdir = "center", binaxis = "y", binwidth = .01, dotsize = 1) + 
   theme_classic() + my_colors + my_colors2 +   theme(legend.position = "none") + 
  ylab ("Likelihood to choose easy again") + xlab ("Feedback on prior trial") + ggtitle("Behavior after an easy trial") + geom_hline(aes(yintercept = 0.5), linetype = "dashed")


combined <- grid.arrange(WSLS_Easy_plot, WSLS_hard_plot, nrow = 1)
combined
ggsave(combined, height = 4, width = 6, file = "figures/Aim1_hypothesis2b/WSLS_feedbackXeffort.pdf")
```

## plot of effort x trial effect
```{r}

# make new data with mean-centered for everything else. 
new_df <- data.frame(expand.grid(PC1_log = mean(beh_scan_ECA_long$PC1_log),
                     Effort_Choice_prior = c("Hard", "Easy"),
                     Feedback_prior = c("Reward","Setback"),
                     AGE.c = 0, Trial_Number.c = c(-10, -5, 0, 5, 10), 
                     Reinforce_rate.c = 0, SEX.c = 0, proportion_hard.c = 0))

WSLS_effect<- fitted(WSLS_mod1_PC1, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate)
WSLS_hard_effect <- filter(WSLS_effect, Effort_Choice_prior == "Hard")
WSLS_easy_effect <- filter(WSLS_effect, Effort_Choice_prior == "Easy")


plot_hard_effect <- ggplot(WSLS_hard_effect, aes(x = Trial_Number.c, y = fit)) + 
   geom_line(size = 1, aes(group = Feedback_prior, color = Feedback_prior)) + 
  geom_ribbon(aes(ymin=lower, ymax=upper, 
                  group = Feedback_prior, fill = Feedback_prior), alpha =0.2, color = NA) +
   theme_classic() + ylab("Likelihood to choose hard again") + my_colors + my_colors2 + 
  xlab ("Trial Number") + geom_hline(aes(yintercept = 0.5), linetype = "dashed")  +
  theme(legend.position = "none") +ylim(0,1) + ggtitle ("Behavior after the hard task")
plot_hard_effect

plot_easy_effect <- ggplot(WSLS_easy_effect, aes(x = Trial_Number.c, y = fit)) + 
   geom_line(size = 1, aes(group = Feedback_prior, color = Feedback_prior)) + 
  geom_ribbon(aes(ymin=lower, ymax=upper, 
                  group = Feedback_prior, fill = Feedback_prior), alpha =0.2, color = NA) +
   theme_classic() + ylab("Likelihood to choose easy again") + my_colors + my_colors2 + 
  xlab ("Trial Number") + geom_hline(aes(yintercept = 0.5), linetype = "dashed")  +
  theme(legend.position = "none") +ylim(0,1) + ggtitle ("Behavior after the easy task")
plot_easy_effect


combined <- grid.arrange(plot_easy_effect, plot_hard_effect, nrow = 1)
combined
ggsave(combined, height = 4, width = 6, file = "figures/Aim1_hypothesis2b/WSLS_by_trialN_X_effort_choice.pdf")

```


## plot of effort x age effect
```{r}

# make new data with mean-centered for everything else. 
new_df <- data.frame(expand.grid(PC1_log = mean(beh_scan_ECA_long_WSLS$PC1_log),
                     Effort_Choice_prior = c("Hard", "Easy"),
                     Feedback_prior = c("Reward","Setback"),
                     AGE.c = c(min(beh_scan_ECA_long_WSLS$AGE.c), -1, 0,1, max(beh_scan_ECA_long_WSLS$AGE.c)), 
                     Trial_Number.c = 0, 
                     Reinforce_rate.c = 0, SEX.c = 0, proportion_hard.c = 0))

WSLS_effect<- fitted(WSLS_mod1_PC1, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate)
WSLS_hard_effect <- filter(WSLS_effect, Effort_Choice_prior == "Hard")
WSLS_easy_effect <- filter(WSLS_effect, Effort_Choice_prior == "Easy")


plot_hard_effect <- ggplot(WSLS_hard_effect, aes(x = AGE.c, y = fit)) + 
   geom_line(size = 1, aes(group = Feedback_prior, color = Feedback_prior)) + 
  geom_ribbon(aes(ymin=lower, ymax=upper, 
                  group = Feedback_prior, fill = Feedback_prior), alpha =0.2, color = NA) +
   theme_classic() + ylab("Likelihood to choose hard again") + my_colors + my_colors2 + 
  xlab ("Age (mean-centered)") + geom_hline(aes(yintercept = 0.5), linetype = "dashed")  +
  theme(legend.position = "none") +ylim(0,1) + ggtitle("Behavior after the hard task")
plot_hard_effect

plot_easy_effect <- ggplot(WSLS_easy_effect, aes(x = AGE.c, y = fit)) + 
   geom_line(size = 1, aes(group = Feedback_prior, color = Feedback_prior)) + 
  geom_ribbon(aes(ymin=lower, ymax=upper, 
                  group = Feedback_prior, fill = Feedback_prior), alpha =0.2, color = NA) +
   theme_classic() + ylab("Likelihood to choose easy again") + my_colors + my_colors2 + 
  xlab ("Age (mean-centered)") + geom_hline(aes(yintercept = 0.5), linetype = "dashed")  +
  theme(legend.position = "none") +ylim(0,1) + ggtitle("Behavior after the easy task")
plot_easy_effect


combined <- grid.arrange(plot_easy_effect, plot_hard_effect, nrow = 1)
combined
ggsave(combined, file = "figures/Aim1_hypothesis2b/WSLS_by_prior_effort_X_Age.pdf", width = 6, height = 4)

```

# Reaction Time for WSLS

##  group effects 
### main effect and prior effort x prior FB x stay/shift
stay shift x FB: NS 
stay shift X prior effort: SIG 
stay shift x prior effort x prior FB: NS
```{r}

load("brms_models/results/aim1_hypothesis2b/WSLS_RT_mod1_g.Rdata")
blm_table(WSLS_RT_mod1_g)

```


###  group x stay shift: trend 
main effect of FB
main effect of prior effort 
mainn effect of age
main effect of reinforce rate 
stay shift x FB: NS 
stay shift X prior effort: SIG 
```{r}

load("brms_models/results/aim1_hypothesis2b/WSLS_RT_mod1_gxss.Rdata")
blm_table(WSLS_RT_mod1_gxss)

```

### Group x stay shift x effort prior: NS
```{r}
load("brms_models/results/aim1_hypothesis2b/WSLS_RT_mod1_gxssxe.Rdata")
blm_table(WSLS_RT_mod1_gxssxe)
```

## cumulative ECA effects 
### PC1 main effect: NS
```{r}

load("brms_models/results/aim1_hypothesis2b/WSLS_RT_mod1_PC1.Rdata")
blm_table(WSLS_RT_mod1_PC1)

```

### PC1 x stay/shift : NS
```{r}

load("brms_models/results/aim1_hypothesis2b/WSLS_RT_mod1_PC1xss.Rdata")
blm_table(WSLS_RT_mod1_PC1xss)

```


### PC1 x stay/shift : NS
```{r}

load("brms_models/results/aim1_hypothesis2b/WSLS_RT_mod1_PC1xssxe.Rdata")
blm_table(WSLS_RT_mod1_PC1xssxe)

```

## plot of RT - prior effort x shift/stay
note: only plotting for Feedback prior == reward for simplicity, because there is no feedback effect and brms doesnt let you take the average of dummy coded factors. 
```{r}

WSLS_RT_df <- beh_scan_ECA_long_WSLS %>%
    mutate(stay_shift = as.factor(ifelse(stay_shift == 0, "Shift", "Stay"))) %>%
  group_by(SUBJECTID, stay_shift, Effort_Choice_prior) %>%
  dplyr::summarize(WSLS_RT = mean(key_resp_choice.rt)) 


# make new data with mean-centered for everything else. 
new_df <- data.frame(expand.grid(PC1_log = mean(beh_scan_ECA_wide$PC1_log),
                                 stay_shift = c(0,1),
                     Effort_Choice_prior = c("Hard", "Easy"),
                     Feedback_prior = "Reward",
                     AGE.c = 0, Trial_Number.c = 0, Reinforce_rate.c = 0, 
                     SEX.c = 0, proportion_hard.c = 0))

WSLS_effect<- fitted(WSLS_RT_mod1_PC1, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(stay_shift = as.factor(ifelse(stay_shift == 0, "Shift", "Stay")))
WSLS_hard_effect <- filter(WSLS_effect, Effort_Choice_prior == "Hard")
WSLS_easy_effect <- filter(WSLS_effect, Effort_Choice_prior == "Easy")


WSLS_hard_plot <- ggplot(WSLS_hard_effect, aes(x =stay_shift, y = fit)) +
  geom_point(size = 3)  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
  geom_jitter(data = filter(WSLS_RT_df, Effort_Choice_prior == "Hard"),
               aes(x = stay_shift, y = WSLS_RT), 
              color = dark_blue, alpha = 0.1, width = 0.05, height = 0.05) + 
   theme_classic() + my_colors + my_colors2 +   theme(legend.position = "none") + 
  ylab ("Reaction Time (seconds)") + xlab ("") + ggtitle("Behavior after a hard trial")

WSLS_Easy_plot <- ggplot(WSLS_easy_effect, aes(x = stay_shift, y = fit)) +
  geom_point(size = 3, position = "dodge")  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
  
  geom_jitter(data = filter(WSLS_RT_df,  Effort_Choice_prior == "Easy"), 
                            aes(x = stay_shift, y = WSLS_RT), 
              color = dark_blue, alpha = 0.1, width = 0.05, height = 0.05) + 
   theme_classic() + my_colors + my_colors2 +   theme(legend.position = "none") + 
  ylab ("Reaction Time (seconds)") + xlab ("") + ggtitle("Behavior after an easy trial") 

combined <- grid.arrange(WSLS_Easy_plot, WSLS_hard_plot, nrow = 1)
combined
ggsave(combined, height = 4, width = 6, file = "figures/Aim1_hypothesis2b/WSLS_RT_stay_shift_xEffort.pdf")
```

