---
title: "Aim1 Hypothesis 1b - Choice behavior"
author: "Michelle.VanTieghem"
date: "10/10/2019"
output:
  html_document:
    number_sections: no
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# notes 
Dec 1 2019: updated with new MICM variables and using PC1_log instead of sqrt. \
note: 8 subjects missing perceived effort post-test info \
*confound:* behavior varies by task version, so only including usable scan participants who were guaranteed to perform the task in scanner for both runs.

```{r, include = F, warnings = F, echo=FALSE, message = F}
source("../../../0_R_analysis_setup_file.R")
```


```{r}
# load all data with PCA added!
load("data/all_pacct_effort_data_with_PCA.rda")

beh_scan_ECA_long <- beh_scan_ECA_long %>%
  dplyr::select(SUBJECTID, Effort_Choice.n, PC1_log , Trial_Number.c ,
                          AGE.c , SEX.c , Reinforce_rate.c , perceived_effort_ave.c , 
                         motivated , perceived_reinforce , frustrated ,
                        lose_feeling , win_feeling , perceived_control , 
                          median_motor_RT_ave) %>%
  na.omit() 

beh_scan_ECA_wide <- beh_scan_ECA_wide %>%
  dplyr::select(SUBJECTID, prop_hard_choices, PC1_log ,
                          AGE.c , SEX.c , Reinforce_rate , perceived_effort_ave , 
                         motivated , perceived_reinforce , frustrated ,
                        lose_feeling , win_feeling , perceived_control , 
                          median_motor_RT_ave) %>%
  na.omit()
nrow(beh_scan_ECA_wide)
```


# Aim 1: Characterize effects of ECA exposure on neurobehavioral phenotype of persistence. Hypothesis 1b: ECA effects on Proportion of hard choices
At the group-level, children with ECA exposure will show fewer hard-effort vs. easy-effort choices.

## explore with self-report 
```{r}
choice_mod_full <- glmer(Effort_Choice.n ~ PC1_log + Trial_Number.c +
                          AGE.c + SEX.c + Reinforce_rate.c + perceived_effort_ave.c + 
                         motivated + perceived_reinforce + frustrated +
                        lose_feeling + win_feeling + perceived_control + 
                          median_motor_RT_ave + 
                          (1 + Trial_Number.c | SUBJECTID), 
                        family=binomial(link = "logit"),
                        data = beh_scan_ECA_long)
summary(choice_mod_full)
```

only covariates that vary by group 
```{r}
choice_mod_motiv <- glmer(Effort_Choice.n ~ PC1_log + Trial_Number.c +
                         # AGE.c + SEX.c + Reinforce_rate.c +
                         #  perceived_effort_ave.c + 
                         motivated + #perceived_reinforce + #frustrated +
                        #lose_feeling + win_feeling +
                          perceived_control + 
                          median_motor_RT_ave + 
                          (1 + Trial_Number.c | SUBJECTID), 
                        family=binomial(link = "logit"),
                        data = beh_scan_ECA_long)
summary(choice_mod_motiv)


choice_wide <- lm(prop_hard_choices ~ motivated + PC1_log + 
                    AGE.c + SEX.c + median_motor_RT_ave, 
                  data = beh_scan_ECA_wide)
summary(choice_wide)
```

# bayesian models 

## GROUP effects on choice behavior: NS
no main effects of group, age, sex, reinforcement rate
all subjects just prefer hard choioces and declines with trial N  
```{r}
load("brms_models/results/aim1_hypothesis1b/choice_mod1_brms.Rdata")
blm_table(choice_mod1_brms)
```

### average perceived effort x group: NS
```{r}
load("brms_models/results/aim1_hypothesis1b/choice_mod1_brms_gxpe.Rdata")  
blm_table(choice_mod1_brms_gxpe)

```


## PC1 effects on choice behavior: NS
 main effects: Trial Number
```{r}
# redo!!
load("brms_models/results/aim1_hypothesis1b/choice_mod2_brms.Rdata")
blm_table(choice_mod2_brms)
```

### cumulative ECA x perceived effort interaction: NS
```{r}
load("brms_models/results/aim1_hypothesis1b/choice_mod2_brms_PC1xpe.Rdata")  
blm_table(choice_mod2_brms_PC1xpe)
```

## plots 

### plot of NS cumulative ECA effects
```{r}
max(beh_scan_ECA_long$PC1_log)

new_df <- data.frame(expand.grid(PC1_log = c(min(beh_scan_ECA_long$PC1_log), 1, 2, max(beh_scan_ECA_long$PC1_log)), perceived_effort_ave.c = 0,
                                 AGE.c = 0, Trial_Number.c =0, Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(choice_mod2_brms, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(intercept = as.factor('intercept'), 
         Trial_Number = Trial_Number.c + max(Trial_Number.c))
head(effect_df)

effect_plot <- ggplot(effect_df, aes(x = PC1_log, y = fit)) +
  geom_line(color = dark_blue)  +
 geom_ribbon(aes(ymin= lower, ymax= upper), alpha = 0.25, fill = dark_blue) +
    geom_point(data = beh_scan_ECA_wide, color= dark_blue,
       aes(x = PC1_log, y = prop_hard_choices), 
       alpha = 0.2, width = 0.05, height =0.0) +
 geom_hline(aes(yintercept = 0.5), linetype = "dashed") + 
   theme_classic() + theme(legend.position = "none") + 
  ylab ("Likelihood to choose hard")  + xlab ("Cumulative ECA score") + ylim(0, 1)
effect_plot


ggsave(effect_plot, file = "figures/Aim1_hypothesis1b/prop_hard_by_PC1.png", width = 3, height = 4)
```


### plot of intercept > 0.50
```{r}
new_df <- data.frame(expand.grid(PC1_log = 0, AGE.c = 0, perceived_effort_ave.c = 0,
                                 Trial_Number.c = 0, Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(choice_mod2_brms, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(intercept = as.factor('intercept'))
head(effect_df)


effect_plot <- ggplot(effect_df, aes(x = intercept, y = fit)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.2, fill = dark_blue)  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
   geom_point(data = beh_scan_ECA_wide, color= dark_blue,
       aes(x = as.factor('intercept'), y = prop_hard_choices), 
       alpha = 0.2, width = 0.05, height =0.0) + geom_hline(aes(yintercept = 0.5), linetype = "dashed") + 
   theme_classic() + theme(legend.position = "none") + 
  ylab ("Likelihood to choose hard")  + xlab ("")
effect_plot

ggsave(effect_plot, file = "figures/aim1_hypothesis1b/choice_intercept_different_than_0.5.png", height = 4, width = 2)
```


### plot of trial N effect

```{r}
new_df <- data.frame(expand.grid(PC1_log = 0, AGE.c = 0, perceived_effort_ave.c = 0,
                                 Trial_Number.c = c(-10, -7, -5, 0, 5, 7, 10),
                                 Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(choice_mod2_brms, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(intercept = as.factor('intercept'), 
         Trial_Number = Trial_Number.c + max(Trial_Number.c))
head(effect_df)


effect_plot <- ggplot(effect_df, aes(x = Trial_Number, y = fit)) +
  geom_line(color = dark_blue)  +
 geom_ribbon(aes(ymin= lower, ymax= upper), alpha = 0.25, fill = dark_blue) +
 geom_hline(aes(yintercept = 0.5), linetype = "dashed") + 
   theme_classic() + theme(legend.position = "none") + 
  ylab ("Likelihood to choose hard")  + xlab ("Trial Number") + ylim(0, 1)
effect_plot

ggsave(effect_plot, file = "figures/aim1_hypothesis1b/prop_hard_by_Trial_N.png", height = 4, width = 4)
```



### plot of NS group effects
```{r}
new_df <- data.frame(expand.grid(GROUP_ECA.x = c("COMP", "ECA"), perceived_effort_ave.c = 0,
                                 AGE.c = 0, Trial_Number.c = 0, Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(choice_mod1_brms, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate,
         GROUP_ECA = GROUP_ECA.x)
head(effect_df)


effect_plot <- ggplot(effect_df, aes(x = GROUP_ECA, y = fit)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.2, fill = dark_blue)  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
   geom_point(data = beh_scan_ECA_wide,  color= dark_blue,
       aes(x = as.factor(GROUP_ECA), y = prop_hard_choices), 
       alpha = 0.2, width = 0.05, height =0.0) +
 geom_hline(aes(yintercept = 0.5), linetype = "dashed") + 
   theme_classic() + theme(legend.position = "none") + 
  ylab ("Likelihood to choose hard")  + xlab ("GROUP") + ylim(0, 1)
effect_plot
ggsave(effect_plot, file = "figures/Aim1_hypothesis1b/prop_hard_by_GROUP.png", width = 3, height = 4)
```


### plot NS perceived effort x group  effects 
```{r}
range(beh_scan_ECA_long$perceived_effort_ave.c, na.rm  = T)
new_df <- data.frame(expand.grid(GROUP_ECA.x = c("COMP", "ECA"),
                                 perceived_effort_ave.c = seq(from = min(beh_scan_ECA_long$perceived_effort_ave.c, na.rm  = T), 
                                                              to = max(beh_scan_ECA_long$perceived_effort_ave.c, na.rm  = T), by  = 0.1),
                                 AGE.c = 0, Trial_Number.c =0, Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(choice_mod1_brms_gxpe, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(intercept = as.factor('intercept'), 
         Trial_Number = Trial_Number.c + max(Trial_Number.c))

effect_plot <- ggplot(effect_df, aes(x = perceived_effort_ave.c, y = fit)) +
  geom_line(color = dark_blue)  + facet_grid(~GROUP_ECA.x) + 
 geom_ribbon(aes(ymin= lower, ymax= upper), alpha = 0.25, fill = dark_blue) +
   # geom_point(data = perceived_df, color= dark_blue,
    #   aes(x = perceived_effort_diff.c, y = prop_hard_choices), 
     #  alpha = 0.2, width = 0.05, height =0.0) +
 geom_hline(aes(yintercept = 0.5), linetype = "dashed") + 
   theme_classic() + theme(legend.position = "none") + 
  ylab ("Likelihood to choose hard")  + xlab ("Average perceived effort (Hard + Easy)") + ylim(0, 1)
effect_plot

ggsave(effect_plot, file = "figures/Aim1_hypothesis1b/choice_by_perceived_effort_ave_and_group.png", width = 3, height = 4)
```


# ECA effects on choice reaction time 

## make a mini-subject summary for plotting
```{r}
choice_RT_df <- beh_scan_ECA_long %>%
  group_by(SUBJECTID, Effort_Choice) %>%
  filter(!is.na(Effort_Choice) & Effort_Choice != "Miss") %>%
  dplyr::summarize(key_resp_choice.rt = mean(key_resp_choice.rt, na.rm = T), 
                   AGE.c = mean(AGE.c), 
                   perceived_effort_ave.c = mean(perceived_effort_ave.c, na.rm =T),
                   GROUP_ECA.x = GROUP_ECA.x[1], 
                   PC1_log = mean(PC1_log))
```

## check no outliers because response only recorded in 3sec
```{r}

outlier_groups <- beh_scan_ECA_long %>%
  group_by(Effort_Choice)

# get the means, SD, upper and lower limit (3 SD above or below mean) for *each* grouping of RT
outlier_info <- outlier_groups %>%
  dplyr::summarize( mean= mean(key_resp_choice.rt, na.rm = TRUE), 
                    sd= sd(key_resp_choice.rt, na.rm = TRUE), 
                    upper_limit= mean(key_resp_choice.rt, na.rm =TRUE) + 3*sd(key_resp_choice.rt, na.rm = TRUE),
                    lower_limit= mean(key_resp_choice.rt, na.rm = TRUE) - 3*sd(key_resp_choice.rt, na.rm = TRUE))

# make an empty dataframe to store new stuff in 
effort_RT_mark_outliers <- data.frame()

# make an empty column in outlier_info to store N outliers 
outlier_info$N_outliers <- NA

# for each grouping of cortisol data in outlier_info 
for (i in 1:nrow(outlier_info)){
  # choice 
  index <- outlier_info$Effort_Choice[i]
  # set the max and minimum values of cortisol that we will use as outlier threshold
  lower_limits <- outlier_info$lower_limit[i]
  upper_limits <- outlier_info$upper_limit[i]
  # get all of the original data by group & cort index  
  data_chunk <- filter(beh_scan_ECA_long, Effort_Choice == index)
  # mark the outliers as True 
  data_chunk$choice_RT_mark_outliers <- ifelse(data_chunk$key_resp_choice.rt >= upper_limits
                          | data_chunk$key_resp_choice.rt <= lower_limits, T, F)
  # replace outlier values with NAs in a new variable 
  data_chunk$choice_RT_no_outliers <- ifelse(data_chunk$choice_RT_mark_outliers == T, NA, data_chunk$key_resp_choice.rt)
  # count how many NAs there are - how many outliers there are.
  N_outliers <- sum(data_chunk$cort_mark_outliers, na.rm = TRUE)
  # save the N in your outlier table at the correct index 
  outlier_info$N_outliers[i] <- N_outliers 
  # save this into a new dataframe 
 effort_RT_mark_outliers <- rbind(effort_RT_mark_outliers, data_chunk) 
} 

outlier_info

```

## Group ECA effects
main effect of group: NS
sig effects of perceived effort, age, choice, and reinforcement rate. 
```{r}
load("brms_models/results/aim1_hypothesis1b/choice_RT_mod1_g.Rdata")
blm_table(choice_RT_mod1_g)
```

### Group x Age: NS
```{r}
load("brms_models/results/aim1_hypothesis1b/choice_RT_mod1_gxa.Rdata")
blm_table(choice_RT_mod1_gxa)

```


### Group x Choice: NS
```{r}
load("brms_models/results/aim1_hypothesis1b/choice_RT_mod1_gxc.Rdata")
blm_table(choice_RT_mod1_gxc)

```


### Group x perceived effort: NS
```{r}
load("brms_models/results/aim1_hypothesis1b/choice_RT_mod1_gxpe.Rdata")
blm_table(choice_RT_mod1_gxpe)
```


## continuous ECA effects 
### main effects of age, perceived effort, choices, reinforcement but not ECA 
```{r}
load("brms_models/results/aim1_hypothesis1b/choice_RT_mod1_PC1.Rdata")
blm_table(choice_RT_mod1_PC1)
```

### PC x age: NS
```{r}
load("brms_models/results/aim1_hypothesis1b/choice_RT_mod1_PC1xa.Rdata")
blm_table(choice_RT_mod1_PC1xa)
```

### PC x effort choice: NS
```{r}
load("brms_models/results/aim1_hypothesis1b/choice_RT_mod1_PC1xc.Rdata")
blm_table(choice_RT_mod1_PC1xc)
```

### PC x perceived effort: NS
```{r}

load("brms_models/results/aim1_hypothesis1b/choice_RT_mod1_PC1xpe.Rdata")
blm_table(choice_RT_mod1_PC1xpe)
```

### plot for main effect age
```{r}
new_df <- data.frame(expand.grid(PC1_log =0, AGE.c = seq(min(beh_scan_ECA_long$AGE.c, na.rm  = T), max(beh_scan_ECA_long$AGE.c, na.rm  = T),1), 
                                 perceived_effort_ave.c = 0, 
                                 Effort_Choice.n = c(0, 1), 
                                 Trial_Number.c = 0,
                                 Reinforce_rate.c = 0,
                                 SEX.c = 0))

effect_df <- fitted(choice_RT_mod1_PC1, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(Effort_Choice = ifelse(Effort_Choice.n == 1, "Hard", 
                                ifelse(Effort_Choice.n == 0, "Easy", NA)))
head(effect_df)

effect_plot <- ggplot(effect_df, aes(x = AGE.c, y = fit)) +
  geom_line(color = dark_blue)  +
 geom_ribbon(aes(ymin= lower, ymax= upper), alpha = 0.25, fill = dark_blue) +
    geom_point(data = choice_RT_df, color= dark_blue,
       aes(x = AGE.c, y = key_resp_choice.rt), 
       alpha = 0.2, width = 0.05, height =0.0) + ylim(0, 3) + 
   theme_classic() + theme(legend.position = "none") + facet_grid(~Effort_Choice) + 
  ylab ("Choice Reaction Time (seconds)")  + xlab ("Age (mean-centered)") 
effect_plot

ggsave(effect_plot, file = "figures/Aim1_hypothesis1b/choice_RT_by_age_and_Choice.png", width = 4, height = 4)
```


### plot for main effect of choice 
```{r}
new_df <- data.frame(expand.grid(PC1_log = 0, AGE.c = 0,
                perceived_effort_ave.c = 0,                 
                Effort_Choice.n = c(0, 1), 
                Trial_Number.c = 0, Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(choice_RT_mod1_PC1, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(Effort_Choice = ifelse(Effort_Choice.n == 1, "Hard", 
                                ifelse(Effort_Choice.n == 0, "Easy", NA)))

effect_plot <- ggplot(effect_df, aes(x = Effort_Choice, y = fit)) +
  geom_point(size = 4, color = dark_blue)  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
   geom_jitter(data = choice_RT_df,  color= dark_blue,
       aes(x = Effort_Choice, y = key_resp_choice.rt), 
       alpha = 0.2, width = 0.05, height =0.0) + ylim(0, 3) + 
   theme_classic() + theme(legend.position = "none") + 
  ylab ("Reaction Time (seconds)")  + xlab ("Choice") 
effect_plot

ggsave(effect_plot, file = "figures/Aim1_hypothesis1b/choice_RT_by_Effort.png", width = 2.5, height = 4)
```


### plot lack of ECA effects
```{r}
new_df <- data.frame(expand.grid(PC1_log = c(min(beh_scan_ECA_long$PC1_log), 1, 2, 2.3, max(beh_scan_ECA_long$PC1_log)),
                perceived_effort_ave.c = 0,                 
                AGE.c = 0,
                Effort_Choice.n = c(0, 1),
                Trial_Number.c = 0, Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(choice_RT_mod1_PC1, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(Effort_Choice = ifelse(Effort_Choice.n == 1, "Hard", 
                                ifelse(Effort_Choice.n == 0, "Easy", NA)))

effect_plot <- ggplot(effect_df, aes(x = PC1_log, y = fit)) +
  geom_line(color = dark_blue)  +
 geom_ribbon(aes(ymin= lower, ymax= upper), fill = dark_blue, alpha = 0.2) +
   geom_point(data = choice_RT_df,  color= dark_blue,
       aes(x = PC1_log, y = key_resp_choice.rt), 
       alpha = 0.2) + ylim(0, 3) + 
   theme_classic() + theme(legend.position = "none") + 
  ylab ("Reaction Time (seconds)")  + xlab ("Cumulative ECA score")  + 
  facet_grid(~Effort_Choice)
effect_plot

ggsave(effect_plot, file = "figures/Aim1_hypothesis1b/choice_RT_by_PC1.png", width = 6, height = 4)

```

### plot sig effect of perceived effort
slower reaction time for greater perceived effort. 
```{r}
new_df <- data.frame(expand.grid(PC1_log = mean(beh_scan_ECA_long$PC1_log),
                perceived_effort_ave.c = c(seq(min(beh_scan_ECA_long$perceived_effort_ave.c, na.rm = T), 
                                               max(beh_scan_ECA_long$perceived_effort_ave.c, na.rm = T), 1)),          
                AGE.c = 0,
                Effort_Choice.n = c(0, 1), Trial_Number.c = 0, Reinforce_rate.c = 0, SEX.c = 0))

effect_df <- fitted(choice_RT_mod1_PC1, newdata = new_df, re_formula = NA) %>%
  cbind(new_df, .) %>%
  rename(upper = Q97.5, 
         lower = Q2.5, 
         fit = Estimate) %>%
  mutate(Effort_Choice = ifelse(Effort_Choice.n == 1, "Hard", 
                                ifelse(Effort_Choice.n == 0, "Easy", NA)))

effect_plot <- ggplot(effect_df, aes(x =perceived_effort_ave.c, y = fit)) +
  geom_line(color = dark_blue)  +
 geom_ribbon(aes(ymin= lower, ymax= upper), fill = dark_blue, alpha = 0.2) +
   geom_point(data = choice_RT_df,  color= dark_blue,
       aes(x = perceived_effort_ave.c, y = key_resp_choice.rt), 
       alpha = 0.2) + ylim(0, 3) + 
   theme_classic() + theme(legend.position = "none") + 
  ylab ("Choice Reaction Time (seconds)")  + xlab ("Average perceived effort (mean-centered)")  + 
  facet_grid(~Effort_Choice)
effect_plot

ggsave(effect_plot, file = "figures/Aim1_hypothesis1b/choice_RT_by_perceived_effort.png", width = 6, height = 4)

```

