---
title: "Aggregate Motion data for effort task"
author: "Michelle Vantieghem"
date: "Nov 26, 2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# Notes
updated August 2019 to add PA257 
updated November 26, 2019 to check PA255 and to fix up sublists

*THIS SCRIPT MUST BE RUN ON ELVIS where raw imaging data lives*

# Exclusion criterion  
## motion threshold used for exclusion: 
censored TRs if Framewise displacement > 0.9
excluded runs if >100 TRs 
## N volumes threshold for exclusion:
if there aren't more than 300 out of 400 volumes in a run, (aka they stopped early) exclude it. 

*remember to change date stamps before running*
```{r,  message = F, warning = F}
library(stringi)
library(tidyverse)

```

# set  variables and paths 
```{r}
store_dir <- "/Volumes/danl/PACCT/scripts/effort_reward/FSL_pipeline/1.motion_assess/"
# get most current subject list
OG_sublist <-read.table("../3_brain_set_up_scripts/sublists/sublist_scans_2019-04-10.txt")
names(OG_sublist) <- "SUBJECTID"
OG_sublist$should_have_scan <- 1
# list path to find subject data.
sub_dir <- "/Volumes/danl/PACCT/subject_data/derivatives/effort_reward/"
```


## add number of TRs in each scan 
to make sure the scans included weren't cut short! 
```{r}
num_vols <- read.csv('data/Effort_scans_numVols_per_run.txt', header =FALSE, sep = "z")

#head(num_vols)
names(num_vols) <- c("subject_run", "TRs")
# split up the info in the path
split <- strsplit(as.character(num_vols$subject_run), "/")
sublist <- vector()

# extract the 6th element from the split string, which is PAxxx
 for (i in split){
    sub <- i[[7]]
    # save this into a list! 
    sublist <- rbind(sublist, sub)
 }
# extract the 9th element, which is run1 or run2
runlist <- vector()
 for (i in split){
    sub <- i[[10]]
    # save this into a list! 
    runlist <- rbind(runlist, sub)
 }
# save these into data frame 
num_vols$SUBJECTID <- as.factor(sublist)
num_vols$RunNumber <- as.factor(runlist)
```

# find subjects with no data -
not sure why these folders and files were ever generated!! 
```{r}
delete_folders <- num_vols %>%
  filter(is.na(TRs))

head(delete_folders)
nrow(delete_folders)
#write.csv(delete_folders, "DELETE_folders_created_when_no_fmri_data_collected_2018-01-09.txt", row.names = F, quote = F)

```


# sublist with runs - with actual data 
```{r}
subjects_keep <- num_vols %>% 
  filter(!is.na(TRs))
#head(subjects_keep)
```

## compare with OG sublist
sanity check, not missing any scans.
```{R}
sum(!subjects_keep$SUBJECTID %in% OG_sublist$SUBJECTID)

```

# begin compiling motion data with only those subs
```{r}
# make an empty dataframe to save stuff to
compiled_info <- data.frame()

```

## set a loop to get censored TRs for each run into df
```{r, eval = F, include = F}
#subject), run, numTRs, meanFD
for (subject in unique(subjects_keep$SUBJECTID)){

 # print(subject)
  sub_info <- subset(subjects_keep, SUBJECTID == subject)

  # this way it doesn't matter whether 1 or 2 runs, script won't crash
  for (r in 1:nrow(sub_info)){
      run <- paste0("run", r)
     #print(paste0(subject, run))
     # if subject doesn't have data for this run, skip ! 
     if (!dir.exists (paste0(sub_dir, subject, "/effort/BOLD/", run))){
        #print (paste0("no data for ", subject, run))
        }
     else {  # if subject has the run, but no motion folder... go fix.
          if(!file.exists(paste0(sub_dir, subject, "/effort/BOLD/", run, "/motion_assess/outlier_output.txt"))){
        	#  print(paste0("no motion_assess files for ", subject, run, ", go fix this!"))
            }
          else { # if the subject has the run, and the motion folder exists... 
          #print (paste0("getting motion info for", subject, run))
           motion_info <- read.table(paste0(sub_dir, subject, "/effort/BOLD/",run, "/motion_assess/censored_TR.txt"))
          numTRs_censored <- motion_info[1,1]
          sub_row <- data.frame(subject, run, numTRs_censored)
           compiled_info <- (rbind(compiled_info, sub_row))
           }
         }
      }
}

names(compiled_info) <- c("SUBJECTID", "RunNumber", "censored_TRs") 
head(compiled_info)
```

## set loop for framewise displacement 
(copied from Paul!)
```{r}
# Get average framewise displacement into dataframe
for(i in 1:nrow(compiled_info)){

  run <- compiled_info$RunNumber[i]
  subject <- compiled_info$SUBJECTID[i]
  # get the file that has the FD for each TR of each run
  fileName <- paste0(sub_dir, subject, "/effort/BOLD/", run, "/motion_assess/framewiseDisplacement.txt")
  
   if(!file.exists(fileName)){
        	print(paste0("no FD text file for ",  subject, run, ", go fix this!"))
      compiled_info$meanFD_all_trs[i] <- NA
     compiled_info$meanFD_included_trs[i] <- NA

       }else{ # if the subject has the run, and the motion folder exists... 
   # print(fileName)
    motionFrame <- read.table(fileName, stringsAsFactors = F) 
    names(motionFrame) <- c('fd')
    compiled_info$meanFD_all_trs[i] <- mean(motionFrame$fd)
    compiled_info$meanFD_included_trs[i] <- mean(motionFrame$fd[motionFrame$fd <= .9])
       }
}

head(compiled_info)
```

## merge and clean up a bit
```{r}
merged_df <- left_join(compiled_info, subjects_keep, by = c("SUBJECTID", "RunNumber"))
head(merged_df)
nrow(merged_df) # 

summary(merged_df$RunNumber)
```

# Mark scans for inclusion/exclusion
## identify complete scans (not cut short)
```{r}
# NA means the scan was incomplete...
merged_df$incomplete_scan <- ifelse(merged_df$TRs < 375, 1, 0)
merged_df$complete_scan <- ifelse(merged_df$TRs == 375, 1, 0)
N_incomplete <- sum(merged_df$incomplete_scan)
N_complete <- sum(merged_df$complete_scan)


print(paste0(nrow(merged_df), " total runs of effort task"))
print(paste0(N_incomplete, " runs of effort task cut short < 375 TRs"))
print(paste0(N_complete, " complete runs of effort task"))
```

## of complete scans, which have good enough motion to keep? 
```{r}
merged_df$censored_TRs <- as.numeric(as.character(merged_df$censored_TRs))
merged_df$include <- ifelse(merged_df$censored_TRs < 100, 1, 0)
merged_df$exclude <- ifelse(merged_df$censored_TRs >= 100, 1,0)

N_include <- sum(merged_df$include, na.rm = T)
N_exclude_motion <- sum(merged_df$exclude, na.rm = T)

print(paste0(N_include, " complete runs of effort task to include"))

print(paste0(N_exclude_motion, " complete runs of effort task excluded for motion"))

print(paste0("proportion of scans excluded for motion using 0.9 and 100TR threshold: ", N_exclude_motion/N_complete))

```

## save the compiled data file
```{r}

save(merged_df, file = paste0("data/compiled_motion_info_", Sys.Date(), ".Rdata"))

```