---
title: "Motion exclusion summary/log"
author: "Michelle Vantieghem"
date: "November 26, 2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---


# Exclusion criterion  
## motion threshold used for exclusion: 
censored TRs if Framewise displacement > 0.9
excluded runs if >100 TRs 
## N volumes threshold for exclusion:
if there aren't more than 300 out of 400 volumes in a run, (aka they stopped early) exclude it. 


# load motion data
```{r, warning = F, message = F}
library(tidyverse)
# this is the most recent motion assessment.
load("data/compiled_motion_info_2019-08-07.Rdata")

```


## How many subjects have 1 or 2 usable runs?
### 2 runs 
```{r}

# aggregate this data by subject,
# count how many runs they have in each category (include 0 or 1)
compiled_by_subject <- merged_df %>%
  group_by(SUBJECTID) %>%
  summarize(Numer_of_runs = n())
N_subs_with_attempted_effort <- nrow(compiled_by_subject)

compiled_by_subject2 <- merged_df %>%
  group_by(include,SUBJECTID) %>% 
  summarize(Number_of_runs = n())

# how many subjects have usable data 
keep_any_scans <- compiled_by_subject2 %>% filter(include == 1)
N_subs_with_any_included_scans <- nrow(keep_any_scans)

#how many subjects have 2 runs of usable data
keep_2_runs <- compiled_by_subject2 %>% filter(include == 1 & Number_of_runs == 2)
N_keep_2_runs <- nrow(keep_2_runs)

```

### 1 run 
```{r}
# how many subjects have 1 run of usable data
keep_1_run <- compiled_by_subject2 %>% 
  filter(include == 1 & Number_of_runs == 1)
N_keep_1_run <- nrow(keep_1_run)
# which run to keep?
by_run <- merged_df %>%
  dplyr::select(SUBJECTID, RunNumber, include) %>%
  spread(key = RunNumber, value = include) 

# run 1 only 
run1_only <- by_run %>%
  filter(run1 == 1 & (is.na(run2) | run2 == 0))

# run 1 only 
run2_only <- by_run %>%
  filter(run2 == 1 & (is.na(run1) | run1 == 0))

```

# RESULTS of most recent data assessment
*November 26, 2019* 
these stats are identical to august 2019. 
so we always had PA255 in the motion assessment! just didn't make it past behavioral QC. 
```{R}
print(paste0("subjects attempted effort scan: ", N_subs_with_attempted_effort))
print(paste0("subjects with any usable effort scans: ", N_subs_with_any_included_scans))
print(paste0("subjects with only 1 usable effort scan: ",N_keep_1_run))
print(paste0("subjects with 2 usable effort scans: ", N_keep_2_runs))
```

# August 2019 
[1] "subjects attempted effort scan: 166"
[1] "subjects with any usable effort scans: 138"
[1] "subjects with only 1 usable effort scan: 36"
[1] "subjects with 2 usable effort scans: 102"

# Jan 9, 2019 
[1] "subjects attempted effort scan: 149"
[1] "subjects with any usable effort scans: 125"
[1] "subjects with only 1 usable effort scan: 33"
[1] "subjects with 2 usable effort scans: 92"

# PRIOR RESULTS
## Nov 21 , 2018
1] "subjects attempted effort scan: 111"
[1] "subjects with any usable effort scans: 95"
[1] "subjects with only 1 usable effort scan: 30"
[1] "subjects with 2 usable effort scans: 65"

## SEPTEMBER 4, 2018
[1] "subjects attempted effort scan: 84" \
[1] "subjects with any usable effort scans: 70" \
[1] "subjects with only 1 usable effort scan: 23" \
[1] "subjects with 2 usable effort scans: 47" \ 


## Feb 20, 2018 
[1] "subjects attempted effort scan: 12" \ 
[1] "subjects with any usable effort scans: 10" \
[1] "subjects with only 1 usable effort scan: 6" \
[1] "subjects with 2 usable effort scans: 4" \
