---
title: "Persistence behavior analysis"
author: "Michelle Vantieghem"
date: "April 5, 2019"
output:
  pdf_document:
    toc: yes
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

```{r}
library(tidyverse)
library(lmerTest)
library(ggplot2)
library(effects)
my_colors <-  scale_color_manual(values=c("#0006CC", "#CC0000", "black", "black"))
my_colors2 <- scale_fill_manual(values=c("#0006CC", "#CC0000","black", "black"))



######### lmer Version #######
condslope.lmer.slopes <- function(x, z, c, y){
#  condslope.lmer( "age1","GROUP", 0, Amyg_piecewise_orig)
  # x = name of x variable
  # z = name of z variable (moderator)
  # c = conditional value of z
  # y = reg object
  # lmer model must be in this order x + z + x*z
# updated slightly by MVT on March 4, 2019 
# bcause tidy doesn't work.

out <- summary(y)
xz <- paste(x, z, sep=":")
#zx <- paste(z, x, sep = ":")
w0.intercept <- fixef(y)["(Intercept)"] + fixef(y)[z]*c
w1.slope <- fixef(y)[x] + fixef(y)[xz]*c 
#y.cond <- w0.intercept + w1.slope*xvalue
require(broom)
modtidy <- data.frame(summary(y)$coef)
modtidy$rownames <- rownames(modtidy)
modtidy$df <- 100
coef2.var <- subset(modtidy, rownames == x)$Std..Error^2
coef4.var <- subset(modtidy, rownames == xz)$Std..Error^2
out.vcov <- vcov(y)
cond.se <- sqrt(coef2.var + (c) * (c) * coef4.var + 2 * (c) * out.vcov[x, xz])
t.val <- w1.slope/cond.se
p.val <- 2*(1-pt(abs(t.val), subset(modtidy, rownames == x)$df, lower.tail=T))
lower95 <- w1.slope-qt(0.975, subset(modtidy, rownames == x)$df)*cond.se
upper95 <- w1.slope+qt(0.975, subset(modtidy, rownames == x)$df)*cond.se
# z.out <- z.test(w1.slope, sigma.x= cond.se)
return(list(w0.intercept=round(w0.intercept, digits = 2), w1.slope=round(w1.slope, digits = 2),
            df = subset(modtidy, rownames == x)$df[1],
            t.val = round(t.val, digits = 2), p.val = round(p.val, digits = 3), 
            lower95 = round(lower95, digits = 2), 
            upper95 = round(upper95, digits = 2)))
}


```


# 1. get data
## 1. load in cleaned behavior data.
```{r}

compiled.data <- read.csv("../behavior/behavioral_data/3_effort_task_data/compiled_effort_scan_version_filtered_usable_2019-04-02.csv")
#summary(compiled.data$Run_number)
```

## 2. load in compiled demographics and scan info 
```{r}
#load("progress_report_and_demographics2019-04-10.Rdata")

#name of this file changed 
load("progress_report_QC/data_QC_and_demographics2019-04-11.Rdata")
demo.data <- df_scans
```

## 3. load in long-formatted data per subject (trialwise)
```{r}
load(paste0("../behavior/behavioral_data/compiled_long_format_usable_2019-04-08.Rdata"))
data.long$SUBJECTID <- data.long$SUB
#head(data.long$SUBJECTID)

```

## merge 
```{r}
data.long.demo <- merge(data.long, demo.data, by = "SUBJECTID")

df_use <- merge(data.long.demo, compiled.data, by =  c("SUBJECTID", "Run_number"))

```

## check age - fixed!
```{r}
summary(df_use$AGE)

```

## check sex - fixed!
```{r}
summary(df_use$SEX)
```

# Hypothesis 1

## set up data:
filter out missed trials, too slow, and extreme reinforce rates.
```{r}
## sort the dataframe by trial
df_use$Run_Number.n <- ifelse(df_use$Run_number == "RUN1", 1, 2)
df_use <- df_use[order(df_use$SUBJECTID, df_use$Run_Number.n, df_use$Trial_Number),]

df_use_no_miss <- df_use %>%
   filter(Reinforce_rate > .3 & Reinforce_rate < .7 & 
          # exclude people with too many missing
          Prop_tooslow < .5 & N_choices_resp > 15 & 
          # exclude missed choices on the current trial, because stay/shift is meaningless for them. 
          Effort_Choice != "Miss") %>%
          mutate(GROUP = as.factor(ifelse(GROUP.final == 0, 0, 1)), 
          Effort_Choice.n = ifelse(Effort_Choice == "Easy", 0, 1)) %>%
   mutate(Trial_Number = as.numeric(as.character(Trial_Number)))

# make trial 1-42 instead of 2 blocks of 21 
df_use_no_miss$Trial_Number <- ifelse(df_use_no_miss$Run_number == "RUN1", df_use_no_miss$Trial_Number, ifelse(df_use_no_miss$Run_number == "RUN2", df_use_no_miss$Trial_Number + 21, NA))
```


# Descriptives check 
```{r}
summary(df_use_no_miss$Effort_Choice.n)

```

## mod1. choice behavior in comps only 
main effect of trial number, hard effort decreases over time.
```{r}
choice_mod1 <- glmer(Effort_Choice.n ~ 
                       Reinforce_rate + AGE + SEX + Trial_Number + 
                      (1 | SUBJECTID), 
                    family = binomial, 
                    data = subset(df_use_no_miss, GROUP == 0),
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod1)
```

## age x trialN interaction? no.
```{r}
choice_mod1b <- glmer(Effort_Choice.n ~ 
                       Reinforce_rate + AGE * Trial_Number + SEX + 
                      (1 | SUBJECTID), 
                    family = binomial, 
                    data = subset(df_use_no_miss, GROUP == 0),
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod1b)
```

```{r}
plot(effect("Trial_Number", choice_mod1))

```

## mod2:. choice behavior between groups (ECA vs. COMP)
main effect of trial number, hard-effort choices decrease over time.
```{r}

choice_mod2 <- glmer(Effort_Choice.n ~ 
                      GROUP +  Reinforce_rate + AGE + SEX + Trial_Number + 
                      (1 | SUBJECTID), 
                    family = binomial, 
                    data = df_use_no_miss,
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod2)
```

### age x trialN in all subs?
```{r}

choice_mod2b <- glmer(Effort_Choice.n ~ 
                      GROUP +  Reinforce_rate + Trial_Number*AGE + SEX + 
                      (1 | SUBJECTID), 
                    family = binomial, 
                    data = df_use_no_miss,
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod2b)
```

older kids are more persistent!! 
younger kids decrease in effort over time. 
```{r}
plot(effect("Trial_Number:AGE", choice_mod2b), multiline = T, rug = F)

```

### Age x Trial N x GROUP? No
also model is having trouble converging! 

```{r}
choice_mod2c <- glmer(Effort_Choice.n ~ 
                      GROUP*AGE*Trial_Number + Reinforce_rate + SEX + 
                      (1 | SUBJECTID), 
                    family = binomial, 
                    data = subset(df_use_no_miss, GROUP.final < 3),
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod2c)
```


## mod3: choice behavior by subtype (PI vs. DA vs. COMP)
main effect of trial number! 
```{r}
choice_mod3 <- glmer(Effort_Choice.n ~ 
                      GROUP.final +  Reinforce_rate + AGE + SEX + Trial_Number + 
                      (1 | SUBJECTID), 
                    family = binomial, 
                    data = subset(df_use_no_miss, GROUP.final < 3),
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod3)
```

# WSLS
## prep data 
using the entire dataset, including misses...
```{r}
# make a copy of the dataset, remove all of the first trials, and mark them as 100 to keep out of place.
df_copy2 <- df_use %>%
  mutate(Trial_Number = Trial_Number + 1) %>%
  select(SUBJECTID, Run_number, Trial_Number, Effort_Choice, Reward_received) %>%
  rename(Effort_Choice_prior = Effort_Choice, 
         Reward_received_prior = Reward_received)

# now re-sort the data, so that all trials are shifted up 1 place. 
df_copy2 <- df_copy2[order(df_copy2$SUBJECTID, df_copy2$Run_number, df_copy2$Trial_Number),]

#head(df_copy2)

# now merge this new thing with orig data, by sub, run, and Trial_Number! 
df_use2 <- merge(df_use, df_copy2, by = c("SUBJECTID", "Run_number", "Trial_Number"), all = T) %>%
  filter(!is.na(Effort_Choice ))

check <- df_use2 %>%
  select(Trial_Number, Effort_Choice, Effort_Choice_prior)
#check
```

## calculate stay-shift variables, 1 = stay, 0 = shift

```{r}
df_use3 <- df_use2 %>%
  # don't include missed choices. 
  mutate(stay_shift = ifelse(Effort_Choice == Effort_Choice_prior, 1, 0),
         reward_received_prior_inclturtle = ifelse(Reward_received_prior == 0 | is.na(Reward_received_prior), 0, 1))

summary(as.factor(df_use3$Effort_Choice_prior))
summary(as.factor(df_use3$Reward_received_prior))
summary(as.factor(df_use3$reward_received_prior_inclturtle))
```

## filter data for analysis: exclude: 
runs extreme reinforcement rates
runs with low response for choices, or too many turtles
runs with 0 for any of the cells in the feedback x effort interaction
trials where the current choice was missed.
```{r}
df_use_WSLS <- df_use3 %>%
  # exclude extreme reinforcement rates. 
 filter(Reinforce_rate > .3 & Reinforce_rate < .7 & 
          # exclude people with too many missing
          Prop_tooslow < .5 & N_choices_resp > 15 & 
          # exclude pppl with zero of each 4 cells for interaction
          N_easy_setback > 0 & N_hard_setback > 0 &
          N_hard_reward > 0 & N_easy_reward > 0 &
          # exclude missed choices on the current trial, and prior trial
          # because stay/shift is meaningless for them. 
          Effort_Choice_prior != "Miss" &
          Effort_Choice != "Miss") %>%
  mutate(Reward_received_prior = as.factor(as.character(Reward_received_prior)),
         reward_received_prior_inclturtle = as.factor(as.character(reward_received_prior_inclturtle)), 
         GROUP.final = as.factor(as.character(GROUP.final)), 
          GROUP = as.factor(ifelse(GROUP.final == 0, 0, 1)),
         Effort_Choice_prior = as.factor(ifelse(Effort_Choice_prior == "Easy", 0,
                                                   ifelse(Effort_Choice_prior == "Hard", 1, NA))),
         Effort_Choice.n = as.numeric(ifelse(Effort_Choice == "Easy", 0, 
                                             ifelse(Effort_Choice == "Hard", 1, NA))))
  
nrow(df_use_WSLS)

summary(df_use_WSLS$Reward_received_prior)
summary(df_use_WSLS$reward_received_prior_inclturtle)
```

# Hypothesis 2: WSLS behavior (excluding turtle trials)
## mod 1: COMPS

```{r}
WSLS_mod1 <- glmer(stay_shift ~ Reward_received_prior * Effort_Choice_prior + 
                      Reinforce_rate + AGE + SEX + Trial_Number +
                      ( 1 | SUBJECTID), 
                    family = binomial, 
                    data = subset(df_use_WSLS, GROUP == 0), 
                    control = glmerControl(optimizer = "bobyqa"))
summary(WSLS_mod1)
```

### main effect of effort choice prior.
more likely to STAY than shift after a hard trial.
so, more likely to choose hard after a hard choice. responses aren't random! 
```{r}
plot(effect("Effort_Choice_prior", WSLS_mod1))
```

### remove interaction

```{r}
WSLS_mod1b <- glmer(stay_shift ~ Reward_received_prior + Effort_Choice_prior + 
                      Reinforce_rate + AGE + SEX + Trial_Number +
                      ( 1 | SUBJECTID), 
                    family = binomial, 
                    data = subset(df_use_WSLS, GROUP == 0), 
                    control = glmerControl(optimizer = "bobyqa"))
summary(WSLS_mod1b)
```

###  main effect of prior feedback
more likely to stay after setback than reward! also makes sense
```{r}
plot(effect("Reward_received_prior", WSLS_mod1b))

```


## mod 2: GROUP (ECA vs. COMP) 
does group interact with effort & prior fB? 
```{r}

WSLS_mod2 <- glmer(stay_shift ~ GROUP * Reward_received_prior * Effort_Choice_prior + 
                      Reinforce_rate + AGE + SEX + Trial_Number +
                      ( 1 | SUBJECTID), 
                    family = binomial, 
                    data = df_use_WSLS,
                    control = glmerControl(optimizer = "bobyqa"))
summary(WSLS_mod2)

```


### main effect of feedback...
you're more likely to STAY after a SETBACK! 
```{r}
plot(effect("Reward_received_prior", WSLS_mod1))
```

### main effect of effort
you're more likely to stay following a hard task
```{r}
plot(effect("Effort_Choice_prior", WSLS_mod1))
```


### no sig effect of reinforcement rate!!
```{r}

plot(effect("Reinforce_rate", WSLS_mod1))

```

### main effect of AGE
kids actually get less persistent with older age! 
developing smarter decision-making strategies? 
```{r}

plot(effect("AGE", WSLS_mod2))
```


### post-hoc of 3 way interaction.
using katherine's function for this.
```{r}
# reference of reward received = setback
# reference group for GROUP = COMP
# reference of effort choice = Easy
group_diff_easy_setback <- data.frame(GROUP = "PIvsCOMP", condslope.lmer.slopes("GROUP1", "Effort_Choice_prior1", 0, WSLS_mod2)) # this reflects setbacks because Reward received 0= reference.

group_diff_hard_setback <- data.frame(GROUP = "PIvsCOMP", condslope.lmer.slopes("GROUP1", "Effort_Choice_prior1", 1, WSLS_mod2))# this reflects setbacks because Reward received 0= reference.

# make a variable with reward as the reference group! 
df_use_WSLS$Reward_received_prior_RewardRef <- as.factor(ifelse(df_use_WSLS$Reward_received_prior == 0, 1, 0))

WSLS_mod2_RewardRef <- glmer(stay_shift ~ GROUP * Reward_received_prior_RewardRef * Effort_Choice_prior + 
                      Reinforce_rate + AGE + SEX + Trial_Number +
                      ( 1 | SUBJECTID), 
                    family = binomial, 
                    data = df_use_WSLS,
                    control = glmerControl(optimizer = "bobyqa"))

# reference of effort choice = Easy
group_diff_easy_reward <- data.frame(GROUP = "PIvsCOMP", condslope.lmer.slopes("GROUP1", "Effort_Choice_prior1", 0, WSLS_mod2_RewardRef)) # this reflects setbacks because Reward received 0= reference.

group_diff_hard_reward <- data.frame(GROUP = "PIvsCOMP", condslope.lmer.slopes("GROUP1", "Effort_Choice_prior1", 1, WSLS_mod2_RewardRef))# this reflects setbacks because Reward received

posthoc_table <- rbind(group_diff_easy_reward, group_diff_hard_reward, group_diff_easy_setback, group_diff_hard_setback)

posthoc_table <- posthoc_table %>%
  dplyr::select(-w0.intercept) %>%
  dplyr::select(GROUP, w1.slope, t.val, p.val, lower95, upper95)

names(posthoc_table) <- c( "Contrast", "Difference", "t value", "p value", "lower 95% CI", "upper 95 CI%")
posthoc_table$Contrast <- c("ECAvsCOMP easy reward", "ECAvsCOMP  hard reward", "ECAvsCOMP easy setback", "ECAvsCOMP hard setback")
posthoc_table
save(posthoc_table, file = "behavior_model_output/Hypothesis2_group_posthoc.Rdata")
```

### plot this in ggplot!
note: individual data points represent subject-specific averages! 
```{r}
# calculate subject-specific proportions of stay vs. shift, for each of 4 conditions.
WSLS_subj_summary <- df_use_WSLS %>%
        mutate(Effort_Choice_prior = ifelse(Effort_Choice_prior == 0, "Easy", "Hard"), 
         Reward_received_prior= ifelse(Reward_received_prior == 0, "Setback", "Reward")) %>%
  group_by(SUBJECTID, Effort_Choice_prior, Reward_received_prior) %>%
  summarize(stay_shift = mean(stay_shift, na.rm = T), 
            GROUP = mean(as.numeric(as.character(GROUP)), na.rm = T)) %>%
     mutate(GROUP = ifelse(GROUP == 0, "COMP", "ECA"))


WSLS_effect <- as.data.frame(effect("GROUP:Reward_received_prior:Effort_Choice_prior", WSLS_mod2, confint=TRUE)) %>%
  mutate(GROUP = ifelse(GROUP == 0, "COMP", "ECA"), 
         Effort_Choice_prior = ifelse(Effort_Choice_prior == 0, "Easy", "Hard"), 
         Reward_received_prior= ifelse(Reward_received_prior == 0, "Setback", "Reward"))

WSLS_plot <- ggplot(WSLS_effect, aes(x = Effort_Choice_prior, y = fit, fill = GROUP)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.2)  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
  geom_dotplot(data = WSLS_subj_summary,position = "dodge",
       aes(x = Effort_Choice_prior, y = stay_shift, color = GROUP), 
       alpha = 0.3, stackratio = 1, stackdir = "center", binaxis = "y", binwidth = .01, dotsize = 1) + 
   facet_grid (~Reward_received_prior) + theme(legend.position = "none") +
   theme_classic() + my_colors + my_colors2 + ylab ("Stay = 1 , Shift = 0") + xlab ("Effort Choice")

#pdf("figures/Hypothesis2_WSLS_groupxeffortxfeedback.pdf")
WSLS_plot
#dev.off()
```

### summary of interaction effects
when ECA receive easy setback, they choose easy again.
when COMPS receive easy setback, they do more adaptive behavior to switch to hard.
when ECA receive hard reward, they choose hard again.
when COMPS receive hard reward, might still switch to easy.

## mod 3: GROUP subtypes (PI vs. DA vs. COMP) 
no effects when you separate DAs and PIs.
```{r}
df_use_WSLS$GROUP.final <- as.numeric(as.character(df_use_WSLS$GROUP.final))
WSLS_mod3 <- glmer(stay_shift ~ Reward_received_prior * Effort_Choice_prior * GROUP.final + 
                      Reinforce_rate + AGE + SEX + Trial_Number +
                      ( 1 | SUBJECTID), 
                    family = binomial, 
                    data = subset(df_use_WSLS, GROUP.final < 3),
                    control = glmerControl(optimizer = "bobyqa"))
summary(WSLS_mod3)

```

### just controlling for group, in all subjects.
```{r}
WSLS_mod3b <- glmer(stay_shift ~ Reward_received_prior * Effort_Choice_prior + GROUP.final + 
                      Reinforce_rate + AGE + SEX + Trial_Number +
                      ( 1 | SUBJECTID), 
                    family = binomial, 
                    data = subset(df_use_WSLS, GROUP.final < 3),
                    control = glmerControl(optimizer = "bobyqa"))
summary(WSLS_mod3b)
```

### effort x reward interaction
everyoen is more motivated for the hard task - persist regardless of prior feedback! 
```{r}
plot(effect("Reward_received_prior:Effort_Choice_prior", WSLS_mod3b))

```

