---
title: "Hypothesis1_analysis"
author: "Michelle.VanTieghem"
date: "6/7/2019"
output:
  pdf_document:
    toc: yes
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

# key for model categories:
mod1 - COMPS: comp only analysis, N = 52
mod2 - GROUP2: ECA vs. COMP
mod3 - GROUP3: PI vs. DA vs. COMP
mod4 - GROUP4: PI vs. DA vs. DC vs. COMP

# summary of results 
## Hypothesis 1: Prop Hard Effort Choices \
*COMPS:* Age x TrialN interaction, where older kids keep picking hard, but younger kids decline in hard-effort choies over time. \
*GROUP2:* No group differences or GROUP interactions with age or trialN. \
*GROUP3:* same \
*GROUP4:* same \

# To do
breakdown post-hoc tests for the group effects \
look at effects of sex, age, reinforcement rate, trial N. \
Find # of caregiver switches and add stuff \
symptoms! 

```{r}
library(tidyverse)
library(lmerTest)
library(ggplot2)
library(effects)
my_colors <-  scale_color_manual(values=c("#0006CC", "#CC0000", "black", "black"))
my_colors2 <- scale_fill_manual(values=c("#0006CC", "#CC0000","black", "black"))

######### lmer Version #######
condslope.lmer.slopes <- function(x, z, c, y){
#  condslope.lmer( "age1","GROUP", 0, Amyg_piecewise_orig)
  # x = name of x variable
  # z = name of z variable (moderator)
  # c = conditional value of z
  # y = reg object
  # lmer model must be in this order x + z + x*z
# updated slightly by MVT on March 4, 2019 
# bcause tidy doesn't work.

out <- summary(y)
xz <- paste(x, z, sep=":")
#zx <- paste(z, x, sep = ":")
w0.intercept <- fixef(y)["(Intercept)"] + fixef(y)[z]*c
w1.slope <- fixef(y)[x] + fixef(y)[xz]*c 
#y.cond <- w0.intercept + w1.slope*xvalue
require(broom)
modtidy <- data.frame(summary(y)$coef)
modtidy$rownames <- rownames(modtidy)
modtidy$df <- 100
coef2.var <- subset(modtidy, rownames == x)$Std..Error^2
coef4.var <- subset(modtidy, rownames == xz)$Std..Error^2
out.vcov <- vcov(y)
cond.se <- sqrt(coef2.var + (c) * (c) * coef4.var + 2 * (c) * out.vcov[x, xz])
t.val <- w1.slope/cond.se
p.val <- 2*(1-pt(abs(t.val), subset(modtidy, rownames == x)$df, lower.tail=T))
lower95 <- w1.slope-qt(0.975, subset(modtidy, rownames == x)$df)*cond.se
upper95 <- w1.slope+qt(0.975, subset(modtidy, rownames == x)$df)*cond.se
# z.out <- z.test(w1.slope, sigma.x= cond.se)
return(list(w0.intercept=round(w0.intercept, digits = 2), w1.slope=round(w1.slope, digits = 2),
            df = subset(modtidy, rownames == x)$df[1],
            t.val = round(t.val, digits = 2), p.val = round(p.val, digits = 3), 
            lower95 = round(lower95, digits = 2), 
            upper95 = round(upper95, digits = 2)))
}


```


# 1. get data
## 1. load in cleaned behavior (by run) data.
```{r}

load("../behavioral_data/3_effort_task_data/compiled/compiled_effort_scan_version_filtered_usable.Rdata")
head(behavior_filtered)

length(unique(behavior_filtered$SUBJECTID))
```

## 2. load in compiled demographics (by run)
and set up grouping variables.
```{r}

#name of this file changed 
load("../behavior_preproc_scripts/progress_report_QC/behavior_only/beh_data_QC_and_demographics2019-06-06.Rdata")
head(df_beh)
summary(as.factor(df_beh$GROUP.final))
demo.data <- df_beh %>%
  mutate(GROUP.4 = ifelse(GROUP.final == 4, 3, GROUP.final), 
         GROUP.3 = ifelse(GROUP.final > 2, NA, GROUP.final ),
         GROUP.2 = ifelse(GROUP.final >= 1, 1, 0 ))
# make a 4 group variable
summary(as.factor(demo.data$GROUP.4))

# make a 3 group variable (no DCs- NA)
summary(as.factor(demo.data$GROUP.3))

# make a 2 goup variable
summary(as.factor(demo.data$GROUP.2))
```

check subj N usable 
```{r}
print(paste0("total subjects with any behavior: ", length(unique(demo.data$SUBJECTID))))

usable <- subset(demo.data, behavior_include == 1)
print(paste0("total behavior usable subjects: ", length(unique(usable$SUBJECTID))))

not_usable <- subset(demo.data, is.na(behavior_include))
nrow(not_usable) # 59 runs are not usable.
print(paste0("total excluded behavior subjects: ", length(unique(not_usable$SUBJECTID))))
```

demo table for this sample by 2 groups: ECA vs. comp
```{r}
names(usable)
usable_subjects <- usable %>% 
  group_by(IDENT_SUBID) %>%
  summarize( GROUP.2 = mean(GROUP.2),
             GROUP.4 = mean(GROUP.4),
              AGE = mean(AGE, na.rm = T),  
             Sex = mean(Sex, na.rm = T))

usable_subjects %>%
  group_by(GROUP.2) %>%
  summarize( N = n(), mean_Age = mean(AGE, na.rm = T), 
             sd_age = sd(AGE, na.rm = T),
             min_age = min(AGE, na.rm = T),
             max_age = max(AGE, na.rm = T), 
             prop_female = mean(Sex, na.rm = T), 
             N_female = sum(Sex, na.rm = T), 
             N_male = n() - sum(Sex, na.rm =T))

```


## 3. load in long-formatted data per subject (trialwise)
```{r}
load(paste0("../behavior/behavioral_data/compiled_long_format_usable_2019-04-08.Rdata"))
data.long$SUBJECTID <- data.long$SUB

length(unique(data.long$SUBJECTID)) # 

```

## merge 
```{r}
data.long.demo <- merge(data.long, demo.data, by = "SUBJECTID")
length(unique(data.long.demo$SUBJECTID))


df_use <- merge(data.long.demo, behavior_filtered, by =  c("SUBJECTID", "Run_number"))
length(unique(df_use$SUBJECTID))
```

## check age
fixed! (no neg #s)
```{r}
summary(df_use$AGE)
hist(df_use$AGE)
```


# Hypothesis 1

## set up data:
filter out missed trials, too slow, and extreme reinforce rates.
```{r}
## sort the dataframe by trial
df_use$Run_Number.n <- ifelse(df_use$Run_number == "RUN1", 1, 2)
summary(df_use$Run_Number.n)

df_use <- df_use[order(df_use$SUBJECTID, df_use$Run_Number.n, df_use$Trial_Number),]

df_use_no_miss <- df_use %>%
   filter(Reinforce_rate > .3 & Reinforce_rate < .7 & 
          # exclude people with too many missing
          Prop_tooslow < .5 & N_choices_resp > 15 & 
          # exclude missed choices on the current trial, because stay/shift is meaningless for them. 
          Effort_Choice != "Miss") %>%
          mutate( Effort_Choice.n = ifelse(Effort_Choice == "Easy", 0, 1)) %>%
   mutate(Trial_Number = as.numeric(as.character(Trial_Number)))

# make trial 1-42 instead of 2 blocks of 21 
df_use_no_miss$Trial_Number <- ifelse(df_use_no_miss$Run_number == "RUN1", df_use_no_miss$Trial_Number, ifelse(df_use_no_miss$Run_number == "RUN2", df_use_no_miss$Trial_Number + 21, NA))
```

## create mean centered covariates
```{r}
df_use_no_miss <- df_use_no_miss %>%
  mutate (Reinforce_rate.c = Reinforce_rate - mean(Reinforce_rate, na.rm = T), 
          AGE.c = AGE - mean(AGE, na.rm = T), 
          SEX.c = Sex - mean(Sex, na.rm = T), 
          Trial_Number.c = Trial_Number - mean(Trial_Number, na.rm= T))

```

## Descriptives check 
```{r}
summary(df_use_no_miss$Effort_Choice.n)

# make a subject-specific summary of their overall choices
df_subj <- df_use_no_miss %>%
  group_by(SUBJECTID) %>%
  summarize(mean_prop_hard = mean(Effort_Choice.n, na.rm = T))

hist(df_subj$mean_prop_hard)
```

## mod1. choice behavior in comps only 
main effect of trial number, hard effort decreases over time.
```{r}
choice_mod1 <- glmer(Effort_Choice.n ~ 
                       Reinforce_rate + AGE.c+ SEX.c + Trial_Number + 
                      (1 | SUBJECTID), 
                    family = binomial, 
                    data = subset(df_use_no_miss, GROUP.2 == 0),
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod1)
```

## HUGE age x trial N interaction!
```{r}
choice_mod1b <- glmer(Effort_Choice.n ~ 
                       Trial_Number.c*AGE.c + SEX.c + Reinforce_rate + 
                      (1 | SUBJECTID), 
                    family = binomial, 
                    data = subset(df_use_no_miss, GROUP.2 == 0),
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod1b)
```

younger kids are declining in hard-effort over time, older kids stay high.
doesn't make sense to plot raw data, because going to be 1s or 0s
```{r}
# get effect  df tidy
agextrialN_effect <-  as.data.frame(effect("Trial_Number.c:AGE.c", choice_mod1b, confint=TRUE))
agextrialN_effect$AGE <- as.factor(round(agextrialN_effect$AGE.c + mean(df_use_no_miss$AGE, na.rm = T), 1)) 
agextrialN_effect$Trial_Number <- agextrialN_effect$Trial_Number.c + mean(df_use_no_miss$Trial_Number, na.rm = T)
agextrialN_effect <- agextrialN_effect %>%
  filter(AGE != "5.9" & AGE != "12.9")

plot_effect <- ggplot(agextrialN_effect,aes(x = Trial_Number, y = fit)) +
   geom_line(size = 1, aes(color = AGE)) + geom_ribbon(aes(ymin=lower, ymax=upper, 
                  group = AGE, fill = AGE), alpha =0.2, color = NA) +
   theme_classic() + ylab("Proportion of Hard vs. Easy Choices") + 
  xlab ("Trial Number") + facet_grid(~AGE)+ theme(legend.position = "none")
  
pdf("figures/Hypothesis1_comp_agextrial_hard_choices.pdf", width = 6, height = 4)
plot_effect
dev.off()
```

## mod2:. choice behavior between groups (ECA vs. COMP)
main effect of trial number, hard-effort choices decrease over time.
```{r}

choice_mod2 <- glmer(Effort_Choice.n ~ 
                      GROUP.2 +  Reinforce_rate.c + AGE.c+ SEX.c + Trial_Number.c + 
                      (1 | SUBJECTID), 
                    family = binomial, 
                    data = df_use_no_miss,
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod2)
```

### age x trialN in all subs?
yes, replicates effects in COMPS only. 
```{r}

choice_mod2b <- glmer(Effort_Choice.n ~ 
                      GROUP.2 +  Reinforce_rate.c + Trial_Number.c*AGE.c+ SEX.c + 
                      (1 | SUBJECTID), 
                    family = binomial, 
                    data = df_use_no_miss,
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod2b)
```

older kids are more persistent, younger kids decrease in effort over time. 
nearly identical results to the COMP-only sample.
```{r}
# get effect  df tidy
agextrialN_effect <-  as.data.frame(effect("Trial_Number.c:AGE.c", choice_mod2b, confint=TRUE))
agextrialN_effect$AGE <- as.factor(round(agextrialN_effect$AGE.c + mean(df_use_no_miss$AGE, na.rm = T), 1)) 
agextrialN_effect$Trial_Number <- agextrialN_effect$Trial_Number.c + mean(df_use_no_miss$Trial_Number, na.rm = T)
agextrialN_effect <- agextrialN_effect %>%
  filter(AGE != "5.9" & AGE != "12.9")

plot_effect <- ggplot(agextrialN_effect,aes(x = Trial_Number, y = fit)) +
   geom_line(size = 1, aes(color = AGE)) + geom_ribbon(aes(ymin=lower, ymax=upper, 
                  group = AGE, fill = AGE), alpha =0.2, color = NA) +
   theme_classic() + ylab("Proportion of Hard vs. Easy Choices") + 
  xlab ("Trial Number") + facet_grid(~AGE)+ theme(legend.position = "none")
  
plot_effect
```

### Age x Trial N x GROUP? No
also model is having trouble converging! 

```{r}
choice_mod2c <- glmer(Effort_Choice.n ~ 
                      GROUP.2 * AGE * Trial_Number.c + Reinforce_rate.c + SEX.c + 
                      (1 | SUBJECTID), 
                    family = binomial, 
                    data = df_use_no_miss,
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod2c)
```

plot the 3 way interaction
```{r}
# get effect  df tidy
agextrialN_effect <-  as.data.frame(effect("GROUP.2:AGE:Trial_Number.c", choice_mod2c, confint=TRUE))
agextrialN_effect$Trial_Number <- agextrialN_effect$Trial_Number.c + mean(df_use_no_miss$Trial_Number, na.rm = T)
agextrialN_effect <- agextrialN_effect %>%
  filter(AGE != "6" & AGE != "13") 
agextrialN_effect

plot_effect <- ggplot(agextrialN_effect,aes(x = Trial_Number, y = fit)) +
   geom_line(size = 1, aes(group = GROUP.2, color = GROUP.2)) + geom_ribbon(aes(ymin=lower, ymax=upper, 
                  group = GROUP.2, fill = GROUP.2), alpha =0.2, color = NA) +
   theme_classic() + ylab("Proportion of Hard vs. Easy Choices") + 
  xlab ("Trial Number") + facet_grid(~AGE)
  
pdf("figures/Hypothesis1_2group_agextrial_hard_choices.pdf", width = 6, height = 4)
plot_effect
dev.off()
```


## mod3: choice behavior by subtype (PI vs. DA vs. COMP)
main effect of trial number! 
```{r}
choice_mod3 <- glmer(Effort_Choice.n ~ 
                      GROUP.3 +  Reinforce_rate.c + AGE.c+ SEX.c + Trial_Number.c + 
                      (1 | SUBJECTID), 
                    family = binomial, 
                    data = df_use_no_miss,
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod3)
```

### Age x trialN - sig 
(same thing)
```{r}
choice_mod3b <- glmer(Effort_Choice.n ~ 
                      GROUP.3 +  Reinforce_rate.c + AGE.c*Trial_Number.c + SEX.c +
                      (1 | SUBJECTID), 
                    family = binomial, 
                    data = df_use_no_miss,
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod3b)
```


### GROUP x AGE.cx trialN 
sig 3 way interaction!! 
```{r}

choice_mod3c <- glmer(Effort_Choice.n ~ 
                    GROUP.3*AGE.c*Trial_Number.c + SEX.c + Reinforce_rate.c + 
                      (1 | SUBJECTID), 
                    family = binomial, 
                    data = df_use_no_miss,
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod3c)
```

possible interaction here but don't understand what's driving it. based on CI, looks like they really overlap.
```{r}
# get effect  df tidy
agextrialN_effect <-  as.data.frame(effect("GROUP.3:AGE.c:Trial_Number.c", choice_mod3c, confint=TRUE))
agextrialN_effect$AGE <- as.factor(round(agextrialN_effect$AGE.c + mean(df_use_no_miss$AGE, na.rm = T), 1)) 
agextrialN_effect$Trial_Number <- agextrialN_effect$Trial_Number.c + mean(df_use_no_miss$Trial_Number, na.rm = T)
agextrialN_effect <- agextrialN_effect %>%
  filter(AGE != "5.9" & AGE != "12.9") %>%
  filter(GROUP.3 != 0.5 & GROUP.3 != 1.5) %>%
  mutate(GROUP.3 = as.factor(GROUP.3))
agextrialN_effect

plot_effect <- ggplot(agextrialN_effect,aes(x = Trial_Number, y = fit)) +
   geom_line(size = 1, aes(group = GROUP.3, color = GROUP.3)) + geom_ribbon(aes(ymin=lower, ymax=upper, 
                  group = GROUP.3, fill = GROUP.3), alpha =0.2, color = NA) +
   theme_classic() + ylab("Proportion of Hard vs. Easy Choices") + 
  xlab ("Trial Number") + facet_grid(~AGE)
  
plot_effect
```

## mod 4: including DCs - no group effects.
```{r}
choice_mod3c <- glmer(Effort_Choice.n ~ 
                    GROUP.4 + AGE.c*Trial_Number.c + SEX.c + Reinforce_rate.c + 
                      (1 | SUBJECTID), 
                    family = binomial, 
                    data = df_use_no_miss,
                    control = glmerControl(optimizer = "bobyqa"))
summary(choice_mod3c)
```
