---
title: "Hypothesis 2 analysis"
author: "Michelle.VanTieghem"
date: "6/7/2019"
output:
  pdf_document:
    toc: yes
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

## Hypothesis 2: WSLS Strategies \
*COMPS:* Effort X Feedback interaction, more likely to stay after a hard-effort setback than hard-effort reward, or easy-effort setback/reward. \
Main effects of sex, reinforcement rate, trialN. \

*GROUP2:* Group x Effort x Feedback interaction, ECA are more likely to show win-stay behavior following a hard-effort reward than comparisons. At trend level, ECA are more likely to show lose-stay behavior following an easy-effort setback than comparisons. Also main effects of sex, age, reinforcement rate, trial N \

*GROUP3:* Group x Effort x Feedback interaction, DA > PI > COMP for win-stay behavior following hard-effort reward.  \

*GROUP4:* Group x Effort x Feedback interaction, DC > DA > PI > COMP for win-stay behavior following hard-effort reward. So sub-group differences in reward sensitivity. \

*No group differences for hard-effort setbacks*: all subjects are showing similar levels of persistence behavior across groups! but still individual differences to look at! 


# WSLS
## prep data 
using the entire dataset, including misses...
```{r}
# make a copy of the dataset, remove all of the first trials, and mark them as 100 to keep out of place.
df_copy2 <- df_use %>%
  mutate(Trial_Number = Trial_Number + 1) %>%
  select(SUBJECTID, Run_number, Trial_Number, Effort_Choice, Reward_received) %>%
  rename(Effort_Choice_prior = Effort_Choice, 
         Reward_received_prior = Reward_received)

# now re-sort the data, so that all trials are shifted up 1 place. 
df_copy2 <- df_copy2[order(df_copy2$SUBJECTID, df_copy2$Run_number, df_copy2$Trial_Number),]

#head(df_copy2)

# now merge this new thing with orig data, by sub, run, and Trial_Number! 
df_use2 <- merge(df_use, df_copy2, by = c("SUBJECTID", "Run_number", "Trial_Number"), all = T) %>%
  filter(!is.na(Effort_Choice ))

```

## calculate stay-shift variables, 1 = stay, 0 = shift

```{r}
df_use3 <- df_use2 %>%
  # don't include missed choices. 
  mutate(stay_shift = ifelse(Effort_Choice == Effort_Choice_prior, 1, 0),
         reward_received_prior_inclturtle = ifelse(Reward_received_prior == 0 | is.na(Reward_received_prior), 0, 1))

summary(as.factor(df_use3$Effort_Choice_prior))
summary(as.factor(df_use3$Reward_received_prior))
summary(as.factor(df_use3$reward_received_prior_inclturtle))
```

## filter data for analysis: exclude: 
runs extreme reinforcement rates
runs with low response for choices, or too many turtles
runs with 0 for any of the cells in the feedback x effort interaction
trials where the current choice was missed.
```{r}
df_use_WSLS <- df_use3 %>%
  # exclude extreme reinforcement rates. 
 filter(Reinforce_rate > .3 & Reinforce_rate < .7 & 
          # exclude people with too many missing
          Prop_tooslow < .5 & N_choices_resp > 15 & 
          # exclude pppl with zero of each 4 cells for interaction
          N_easy_setback > 0 & N_hard_setback > 0 &
          N_hard_reward > 0 & N_easy_reward > 0 &
          # exclude missed choices on the current trial, and prior trial
          # because stay/shift is meaningless for them. 
          Effort_Choice_prior != "Miss" &
          Effort_Choice != "Miss") %>%
  mutate(Reward_received_prior = as.factor(as.character(Reward_received_prior)),
         reward_received_prior_inclturtle = as.factor(as.character(reward_received_prior_inclturtle)),
         Effort_Choice_prior = as.factor(ifelse(Effort_Choice_prior == "Easy", 0,
                                                   ifelse(Effort_Choice_prior == "Hard", 1, NA))),
         Effort_Choice.n = as.numeric(ifelse(Effort_Choice == "Easy", 0, 
                                             ifelse(Effort_Choice == "Hard", 1, NA))))
  

# why isn't this converion working?? fix late.r
summary(df_use_WSLS$Reward_received_prior)
summary(df_use_WSLS$reward_received_prior_inclturtle)
```

## add prop. hard effort as covariate at subj level
```{r}
subj_prop_hard <- df_use_no_miss %>%
  group_by(IDENT_SUBID) %>%
  summarize(prop_hard_choices = mean(Effort_Choice.n))


df_use_WSLS <- merge(df_use_WSLS, subj_prop_hard, by = "IDENT_SUBID")

```

## make mean centered variables
```{r}

df_use_WSLS <- df_use_WSLS %>%
  mutate (Reinforce_rate.c = Reinforce_rate - mean(Reinforce_rate, na.rm = T), 
          AGE.c = AGE - mean(AGE, na.rm = T), 
          SEX.c = Sex - mean(Sex, na.rm = T), 
          Trial_Number.c = Trial_Number - mean(Trial_Number, na.rm= T), 
          prop_hard_choices.c = prop_hard_choices - mean(prop_hard_choices, na.rm = T))

```


# Hypothesis 2: WSLS behavior (excluding turtle trials)
## mod 1: COMPS

```{r}
WSLS_mod1 <- glmer(stay_shift ~ Reward_received_prior * Effort_Choice_prior + 
                      Reinforce_rate.c + AGE.c + SEX.c + Trial_Number.c + prop_hard_choices.c + 
                      ( 1 | SUBJECTID), 
                    family = binomial, 
                    data = subset(df_use_WSLS, GROUP.2 == 0), 
                    control = glmerControl(optimizer = "bobyqa"))
summary(WSLS_mod1)
```

main effect of age - stay behavior decreased with age
main effect of trial number - stay behavior increased over time
main effect of reinforce rate - stay behavior increased with higher reinforcement rate
main effect of sex - females stayed more than males?

### significant interaction of prior effort & feedback
```{r}
# get individual data
WSLS_subj_summary <- df_use_WSLS %>%
  filter(GROUP.2 == 0) %>%
        mutate(Effort_Choice_prior = ifelse(Effort_Choice_prior == 0, "Easy", "Hard"), 
         Reward_received_prior= ifelse(Reward_received_prior == 0, "Setback", "Reward")) %>%
  group_by(SUBJECTID, Effort_Choice_prior, Reward_received_prior) %>%
  summarize(stay_shift = mean(stay_shift, na.rm = T))


WSLS_effect <- as.data.frame(effect("Reward_received_prior:Effort_Choice_prior", WSLS_mod1, confint=TRUE)) %>%
  mutate(Effort_Choice_prior = ifelse(Effort_Choice_prior == 0, "Easy", "Hard"), 
         Reward_received_prior= ifelse(Reward_received_prior == 0, "Setback", "Reward"))

WSLS_plot <- ggplot(WSLS_effect, aes(x = Reward_received_prior, y = fit, fill = Effort_Choice_prior)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.2)  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
  geom_dotplot(data = WSLS_subj_summary,position = "dodge",
       aes(x = Reward_received_prior, y = stay_shift), 
       alpha = 0.3, stackratio = 1, stackdir = "center", binaxis = "y", binwidth = .01, dotsize = 1.5) + 
   theme(legend.position = "none") +
   theme_classic() + my_colors + my_colors2 + ylab ("Stay = 1 , Shift = 0") + xlab ("Feedback on prior trial")

pdf("figures/Hypothesis2_comp_WSLS_effortxfeedback.pdf", width = 6, height = 4)
WSLS_plot
dev.off()
```

***do post-hoc test to see which conditions are sig different from 0.5% 

### does age interact? no.
```{r}
WSLS_mod1c <- glmer(stay_shift ~  AGE.c*Effort_Choice_prior*Reward_received_prior +
                      Reinforce_rate +    SEX.c + Trial_Number.c +prop_hard_choices.c + 
                      ( 1 | SUBJECTID), 
                    family = binomial, 
                    data = subset(df_use_WSLS, GROUP.2 == 0), 
                    control = glmerControl(optimizer = "bobyqa"))
summary(WSLS_mod1c)
```

### does interact with trialN?
```{r}
WSLS_mod1d <- glmer(stay_shift ~  Trial_Number.c*Effort_Choice_prior*Reward_received_prior + 
                      Reinforce_rate +    SEX.c +  AGE.c +prop_hard_choices.c + 
                      ( 1 | SUBJECTID), 
                    family = binomial, 
                    data = subset(df_use_WSLS, GROUP.2 == 0), 
                    control = glmerControl(optimizer = "bobyqa"))
summary(WSLS_mod1d)
```

over the course of the task, kids always choose hard again after a hard setback. but they increase in how much they persist after a hard reward.
```{r}
plot(effect("Trial_Number.c:Effort_Choice_prior:Reward_received_prior", WSLS_mod1d), multiline = T)
```


plot with ggplot
```{r}
WSLS_effect <- as.data.frame(effect("Trial_Number.c:Effort_Choice_prior:Reward_received_prior", WSLS_mod1d, confint=TRUE)) %>%
  mutate(Effort_Choice_prior = ifelse(Effort_Choice_prior == 0, "Easy", "Hard"), 
         Reward_received_prior= ifelse(Reward_received_prior == 0, "Setback", "Reward"), 
          Trial_Number = Trial_Number.c + mean(df_use_no_miss$Trial_Number, na.rm = T))


plot_effect <- ggplot(WSLS_effect,aes(x = Trial_Number, y = fit)) +
   geom_line(size = 1, aes(group = Effort_Choice_prior, color = Effort_Choice_prior)) + geom_ribbon(aes(ymin=lower, ymax=upper, 
                  group = Effort_Choice_prior, fill = Effort_Choice_prior), alpha =0.2, color = NA) +
   theme_classic() + ylab("Stay = 1 , Shift = 0") + 
  xlab ("Trial Number") + facet_grid(~Reward_received_prior)
 
  
pdf("figures/Hypothesis2_comp_WSLS_effortxfeedbackxtrialN.pdf", width = 6, height = 4)
plot_effect
dev.off()
```



## mod 2: GROUP (ECA vs. COMP) 
does group interact with effort & prior fB? 
```{r}

WSLS_mod2 <- glmer(stay_shift ~ GROUP.2 * Reward_received_prior * Effort_Choice_prior + 
                      Reinforce_rate.c + AGE.c + SEX.c + Trial_Number.c + prop_hard_choices.c + 
                      ( 1 | SUBJECTID), 
                    family = binomial, 
                    data = df_use_WSLS,
                    control = glmerControl(optimizer = "bobyqa"))
summary(WSLS_mod2)

```


### main effect of Trial N
shifting decreases, staying increases over AGE.c.
this is kind of confusing, because they are making fewer hard effort choices over time. 
```{r}

plot(effect("Trial_Number.c", WSLS_mod2))
```

### main effect of AGE
kids actually get less persistent with older AGE.c! 
developing smarter decision-making strategies? 
```{r}

plot(effect("AGE.c", WSLS_mod2))
```

### main effect of Prop hard choices 
more likely to show more stay behavior if you choose more hard choices.
```{r}
plot(effect("prop_hard_choices.c", WSLS_mod2))


```

### main effect of reinforcement rate 
more likely to show more stay behavior if you have higher rate of reinforcement
```{r}
plot(effect("Reinforce_rate.c", WSLS_mod2))

```


### post-hoc of 3 way interaction.
ECA show more win-stay behavior following a hard-effort reward than comps.
ECA show trend level more lose-stay behavior following an easy-effort setback than comps. 
No difference in lose-stay behavior following hard-effort setbacks
no difference in win-stay behavior following easy-effort rewards
```{r}
# reference of reward received = setback
# reference group for GROUP = COMP
# reference of effort choice = Easy
group_diff_easy_setback <- data.frame(GROUP = "PIvsCOMP", condslope.lmer.slopes("GROUP.2", "Effort_Choice_prior1", 0, WSLS_mod2)) # this reflects setbacks because Reward received 0= reference.

group_diff_hard_setback <- data.frame(GROUP = "PIvsCOMP", condslope.lmer.slopes("GROUP.2", "Effort_Choice_prior1", 1, WSLS_mod2))# this reflects setbacks because Reward received 0= reference.

# make a variable with reward as the reference group! 
df_use_WSLS$Reward_received_prior_RewardRef <- as.factor(ifelse(df_use_WSLS$Reward_received_prior == 0, 1, 0))

WSLS_mod2_RewardRef <- glmer(stay_shift ~ GROUP.2 * Reward_received_prior_RewardRef * Effort_Choice_prior + 
                      Reinforce_rate + AGE.c + SEX.c + Trial_Number.c +
                      ( 1 | SUBJECTID), 
                    family = binomial, 
                    data = df_use_WSLS,
                    control = glmerControl(optimizer = "bobyqa"))

# reference of effort choice = Easy
group_diff_easy_reward <- data.frame(GROUP = "PIvsCOMP", condslope.lmer.slopes("GROUP.2", "Effort_Choice_prior1", 0, WSLS_mod2_RewardRef)) # this reflects setbacks because Reward received 0= reference.

group_diff_hard_reward <- data.frame(GROUP = "PIvsCOMP", condslope.lmer.slopes("GROUP.2", "Effort_Choice_prior1", 1, WSLS_mod2_RewardRef))# this reflects setbacks because Reward received

posthoc_table <- rbind(group_diff_easy_reward, group_diff_hard_reward, group_diff_easy_setback, group_diff_hard_setback)

posthoc_table <- posthoc_table %>%
  dplyr::select(-w0.intercept) %>%
  dplyr::select(GROUP, w1.slope, t.val, p.val, lower95, upper95)

names(posthoc_table) <- c( "Contrast", "Difference", "t value", "p value", "lower 95% CI", "upper 95 CI%")
posthoc_table$Contrast <- c("ECAvsCOMP easy reward", "ECAvsCOMP  hard reward", "ECAvsCOMP easy setback", "ECAvsCOMP hard setback")
posthoc_table
save(posthoc_table, file = "behavior_model_output/Hypothesis2_group_posthoc.Rdata")
```

### plot this in ggplot!
note: individual data points represent subject-specific averages! 
```{r}
# calculate subject-specific proportions of stay vs. shift, for each of 4 conditions.
WSLS_subj_summary <- df_use_WSLS %>%
        mutate(Effort_Choice_prior = ifelse(Effort_Choice_prior == 0, "Easy", "Hard"), 
         Reward_received_prior= ifelse(Reward_received_prior == 0, "Setback", "Reward")) %>%
  group_by(SUBJECTID, Effort_Choice_prior, Reward_received_prior) %>%
  summarize(stay_shift = mean(stay_shift, na.rm = T), 
            GROUP.2 = mean(as.numeric(as.character(GROUP.2)), na.rm = T)) %>%
     mutate(GROUP.2 = ifelse(GROUP.2 == 0, "COMP", "ECA"))


WSLS_effect <- as.data.frame(effect("GROUP:Reward_received_prior:Effort_Choice_prior", WSLS_mod2, confint=TRUE)) %>%
  mutate(GROUP = ifelse(GROUP.2 == 0, "COMP", "ECA"), 
         Effort_Choice_prior = ifelse(Effort_Choice_prior == 0, "Easy", "Hard"), 
         Reward_received_prior= ifelse(Reward_received_prior == 0, "Setback", "Reward"))

WSLS_plot <- ggplot(WSLS_effect, aes(x = Effort_Choice_prior, y = fit, fill = GROUP.2)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.2)  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
  geom_dotplot(data = WSLS_subj_summary,position = "dodge",
       aes(x = Effort_Choice_prior, y = stay_shift, color = GROUP), 
       alpha = 0.3, stackratio = 1, stackdir = "center", binaxis = "y", binwidth = .01, dotsize = 1.5) + 
   facet_grid (~Reward_received_prior) + theme(legend.position = "none") +
   theme_classic() + my_colors + my_colors2 + ylab ("Stay = 1 , Shift = 0") + xlab ("Effort Choice")

pdf("figures/Hypothesis2_WSLS_groupxeffortxfeedback.pdf", width = 6, height = 4)
WSLS_plot
dev.off()
```


## mod 3: GROUP subtypes (PI vs. DA vs. COMP) 
SIG INTERACTION! 
```{r}


WSLS_mod3 <- glmer(stay_shift ~ Reward_received_prior * Effort_Choice_prior * GROUP.3 + 
                      Reinforce_rate.c + AGE.c + SEX.c + Trial_Number.c + prop_hard_choices.c + 
                      ( 1 | SUBJECTID), 
                    family = binomial, 
                    data = df_use_WSLS,
                    control = glmerControl(optimizer = "bobyqa"))
summary(WSLS_mod3)

```



### plot: DAs show more sensitivity to hard-rewards 
```{r}
# calculate subject-specific proportions of stay vs. shift, for each of 4 conditions.
WSLS_subj_summary <- df_use_WSLS %>%
  filter(!is.na(GROUP.3)) %>%
        mutate(Effort_Choice_prior = ifelse(Effort_Choice_prior == 0, "Easy", "Hard"), 
         Reward_received_prior= ifelse(Reward_received_prior == 0, "Setback", "Reward")) %>%
  group_by(SUBJECTID, Effort_Choice_prior, Reward_received_prior) %>%
  summarize(stay_shift = mean(stay_shift, na.rm = T), 
            GROUP.3 = mean(as.numeric(as.character(GROUP.3)), na.rm = T)) %>%
     mutate(GROUP.3.f = ifelse(GROUP.3 == 0, "COMP", ifelse(GROUP.3 == 1, "PI","DA")))


WSLS_effect <- as.data.frame(effect("Reward_received_prior:Effort_Choice_prior:GROUP.3", 
                                    WSLS_mod3, confint=TRUE)) %>%
  # get rid of 0.5 group estimations.
  filter(GROUP.3 == 1 | GROUP.3 == 0 | GROUP.3 == 2) %>%
  mutate(GROUP.3.f = ifelse(GROUP.3 == 0, "COMP", ifelse(GROUP.3 == 1, "PI", "DA")), 
         Effort_Choice_prior = ifelse(Effort_Choice_prior == 0, "Easy", "Hard"), 
         Reward_received_prior= ifelse(Reward_received_prior == 0, "Setback", "Reward"))

WSLS_plot <- ggplot(WSLS_effect, aes(x = Effort_Choice_prior, y = fit, fill = GROUP.3.f)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.2)  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
  geom_dotplot(data = WSLS_subj_summary,position = "dodge",
       aes(x = Effort_Choice_prior, y = stay_shift, color = GROUP.3.f), 
       alpha = 0.3, stackratio = 1, stackdir = "center", binaxis = "y", binwidth = .01, dotsize = 1) + 
   facet_grid (~ Reward_received_prior) + theme(legend.position = "none") +
   theme_classic() + my_colors + my_colors2 + ylab ("Stay = 1 , Shift = 0") + xlab ("Effort Choice")

pdf("figures/Hypothesis2_WSLS_group.3xeffortxfeedback.pdf")
WSLS_plot
dev.off()
```


## mod 3b: across 4 GROUP subtypes (PI vs. DA vs. COMP vs. DC) 
```{r}

WSLS_mod3b <- glmer(stay_shift ~ Reward_received_prior * Effort_Choice_prior * GROUP.4 + 
                      Reinforce_rate.c + AGE.c + SEX.c + Trial_Number.c + prop_hard_choices.c + 
                      ( 1 | SUBJECTID), 
                    family = binomial, 
                    data = df_use_WSLS,
                    control = glmerControl(optimizer = "bobyqa"))
summary(WSLS_mod3b)

```


### N per 4 groups for this
```{r}
# calculate subject-specific proportions of stay vs. shift, for each of 4 conditions.
WSLS_subj_summary <- df_use_WSLS %>%
        mutate(Effort_Choice_prior = ifelse(Effort_Choice_prior == 0, "Easy", "Hard"), 
         Reward_received_prior= ifelse(Reward_received_prior == 0, "Setback", "Reward")) %>%
  group_by(SUBJECTID, Effort_Choice_prior, Reward_received_prior) %>%
  summarize(stay_shift = mean(stay_shift, na.rm = T), 
            GROUP.4 = mean(as.numeric(as.character(GROUP.4)), na.rm = T)) %>%
     mutate(GROUP.4.f = ifelse(GROUP.4 == 0, "COMP", ifelse(GROUP.4 == 1, "PI",
                                                                    ifelse(GROUP.4 == 2, "DA", "DC"))))

summary(as.factor(WSLS_subj_summary$GROUP.4.f))
```

### plot:
```{r}
WSLS_effect <- as.data.frame(effect("Reward_received_prior:Effort_Choice_prior:GROUP.4", 
                                    WSLS_mod3b, confint=TRUE)) %>%
  # get rid of 0.5 group estimations.
  filter(GROUP.4 == 1 | GROUP.4 == 0 | GROUP.4 == 2 | GROUP.4 == 3) %>%
  mutate(GROUP.4.f = ifelse(GROUP.4 == 0, "COMP", ifelse(GROUP.4 == 1, "PI", 
                                                                 ifelse(GROUP.4 == 2, "DA", "DC"))), 
         Effort_Choice_prior = ifelse(Effort_Choice_prior == 0, "Easy", "Hard"), 
         Reward_received_prior= ifelse(Reward_received_prior == 0, "Setback", "Reward"))
summary(as.factor(WSLS_effect$GROUP.4.f))

WSLS_plot <- ggplot(WSLS_effect, aes(x = Effort_Choice_prior, y = fit, fill = GROUP.4.f)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.2)  +
 geom_errorbar(aes(ymin= lower, ymax= upper), position= position_dodge(.9), width = .2) +
  geom_dotplot(data = WSLS_subj_summary,position = "dodge",
       aes(x = Effort_Choice_prior, y = stay_shift, color = GROUP.4.f), 
       alpha = 0.3, stackratio = 1, stackdir = "center", binaxis = "y", binwidth = .01, dotsize = 1) + 
   facet_grid (~ Reward_received_prior) + theme(legend.position = "none") +
   theme_classic() + ylab ("Stay = 1 , Shift = 0") + xlab ("Effort Choice")

#pdf("figures/Hypothesis2_WSLS_groupxeffortxfeedback.pdf")
WSLS_plot
#dev.off()
```


# symptom follow-up
Does WSLS behavior moderate effect of group on symptoms?

## get data for analysis
### get subject-level data for WSLS behavior in each condition of the task
```{r}
# get subject-level proportions of win-stay lose-shift behavior for the 4 conditions 
subj_level_df <- df_use_WSLS %>%
  group_by(IDENT_SUBID, Effort_Choice_prior, Reward_received_prior) %>%
  summarize(prop_stay = mean(stay_shift), 
            AGE = mean(AGE), 
            Sex = mean(Sex), 
            GROUP = mean(as.numeric(as.character(GROUP))), 
            GROUP.4 = mean(as.numeric(as.character(GROUP.4))), 
            Reinforce_rate = mean(Reinforce_rate, na.rm = T)) # where 1 = all stays, 0 = all shifts
tail(subj_level_df)

# make this a wide DF
WSLS_hard_reward <- subj_level_df %>%
  filter(Effort_Choice_prior == 1 & Reward_received_prior == 1) %>%
  rename("prop_stay_hard_reward" = prop_stay) %>%
  select(IDENT_SUBID, GROUP, GROUP.4, Sex, AGE, prop_stay_hard_reward, Reinforce_rate)

WSLS_hard_setback <- subj_level_df %>%
  filter(Effort_Choice_prior == 1 & Reward_received_prior == 0) %>%
  rename("prop_stay_hard_setback" = prop_stay)%>%
  select(IDENT_SUBID,prop_stay_hard_setback)

WSLS_easy_reward <- subj_level_df %>%
  filter(Effort_Choice_prior == 0 & Reward_received_prior == 1) %>%
  rename("prop_stay_easy_reward" = prop_stay)%>%
  select(IDENT_SUBID, prop_stay_easy_reward)

WSLS_easy_setback <- subj_level_df %>%
  filter(Effort_Choice_prior == 0 & Reward_received_prior == 0) %>%
  rename("prop_stay_easy_setback" = prop_stay)%>%
  select(IDENT_SUBID, prop_stay_easy_setback)

WSLS_subj_level <- merge(WSLS_hard_reward, WSLS_hard_setback, by = "IDENT_SUBID" )
WSLS_subj_level <- merge(WSLS_subj_level, WSLS_easy_reward, by = "IDENT_SUBID" ) %>%
  select(-starts_with("Effort"))
WSLS_subj_level <- merge(WSLS_subj_level, WSLS_easy_setback, by = "IDENT_SUBID" ) %>%
  select(-starts_with("Effort"))
head(WSLS_subj_level)
```

### get symptom data from master.
```{r}
library(readxl)
master <- read_excel("../subj_demo/MASTER_20190502.xlsx")

RCADS_master <- master %>%
  select(IDENT_SUBID, starts_with("J.RCADS")) %>%
  select(-ends_with("missing_new"))

CBCL_master <- master %>%
  select(IDENT_SUBID, starts_with("CBCL"))
```


### merge with subj level behavior
```{r}
# combine subject-level computations of WSLS and proportion hard
subj_level_all <- merge(WSLS_subj_level, subj_prop_hard, by = "IDENT_SUBID")
# add master 
subj_level_all <- merge(subj_level_all, RCADS_master, by = "IDENT_SUBID")
subj_level_all <- merge(subj_level_all, CBCL_master, by = "IDENT_SUBID")

head(subj_level_all)

```

## RCADS Total
```{r}
ggplot(subj_level_all, aes(x = as.factor(GROUP), y = J.RCADS_Total_Score_T_new, color = as.factor(GROUP))) + 
  theme_classic() + geom_violin() + geom_jitter(width = 0.05, alpha = 0.5) 

```

```{r}
ggplot(subj_level_all, aes(x = as.factor(GROUP), y = J.RCADS_Total_Score_T_new, color = as.factor(GROUP))) + 
  theme_classic() + geom_boxplot() #+ geom_jitter(width = 0.05, alpha = 0.5) 

```

### check outliers 
```{r}
 subj_level_all %>%
  group_by(GROUP) %>%
  summarize(mean_RCADS = mean(J.RCADS_Total_Score_T_new, na.rm =T), 
            sd_RCADS = sd(J.RCADS_Total_Score_T_new, na.rm = T), 
            outlier_RCADS = mean_RCADS + 3*sd_RCADS)

subj_level_all <- subj_level_all %>%
  mutate(outlier_RCADS = ifelse(GROUP == 0 & J.RCADS_Total_Score_T_new > 75.4, 1, 
                                ifelse(GROUP == 1 & J.RCADS_Total_Score_T_new > 76.1, 1,0)), 
         RCADS_Total_T = ifelse(outlier_RCADS !=1 , J.RCADS_Total_Score_T_new, NA))

```

```{r}
ggplot(subj_level_all, aes(x = as.factor(GROUP), y = RCADS_Total_T, color = as.factor(GROUP))) + 
  theme_classic() + geom_boxplot() #+ geom_jitter(width = 0.05, alpha = 0.5) 

```


### RCADS Total: no group differences, and no behavior differences
```{r}

symptom_mod1 <- lm(RCADS_Total_T ~ GROUP + prop_stay_hard_reward + prop_stay_easy_reward + 
                     prop_stay_hard_setback + prop_stay_easy_setback + prop_hard_choices + 
                     AGE + Sex + Reinforce_rate, 
                   data = subj_level_all)
summary(symptom_mod1)
```


 this is a random spurious finding!!! 
```{r}
ggplot(subj_level_all, aes(x = Reinforce_rate, y = J.RCADS_Anxiety_Total_raw_new)) + 
  geom_point() + geom_smooth()
```

##  CBCL int instead
```{r}
ggplot(subj_level_all, aes(x = as.factor(GROUP), y = CBCL_4_INTERNPROB_T, color = as.factor(GROUP))) + 
  theme_classic() + geom_boxplot() #+ geom_jitter(width = 0.05, alpha = 0.5) 

```

### CBCL int: sig group differences, but not behavior
but does not correlate at all with task behavior!! 
```{r}

symptom_mod2 <- lm(CBCL_4_INTERNPROB_T ~ GROUP + prop_stay_hard_reward + prop_stay_easy_reward + 
                     prop_stay_hard_setback + prop_stay_easy_setback + prop_hard_choices + 
                     AGE + Sex + Reinforce_rate, 
                   data = subj_level_all)
summary(symptom_mod2)
```


### check CBCL ext instead
```{r}
ggplot(subj_level_all, aes(x = as.factor(GROUP), y = CBCL_4_EXTERNPROB_T, color = as.factor(GROUP))) + 
  theme_classic() + geom_boxplot() #+ geom_jitter(width = 0.05, alpha = 0.5) 

```

## CBCL ext: sig group differences, and...
but does not correlate at all with task behavior!! 
```{r}

symptom_mod3 <- lm(CBCL_4_EXTERNPROB_T ~ GROUP + prop_stay_hard_reward + prop_stay_easy_reward + 
                     prop_stay_hard_setback + prop_stay_easy_setback + prop_hard_choices + 
                     AGE + Sex + Reinforce_rate, 
                   data = subj_level_all)
summary(symptom_mod3)
```

### lose-stay after easy setback correlates with externalizing?? 
this doesn't really make sense.
the more you stay after an easy setback, the more externalizing behavior you have?
```{r}
plot(effect("prop_stay_easy_setback", symptom_mod3))

```

## RCADS MDD 
```{r}

ggplot(subj_level_all, aes(x = as.factor(GROUP), y = J.RCADS_MDD_T_new, color = as.factor(GROUP))) + 
  theme_classic() + geom_violin() + geom_jitter(width = 0.05, alpha = 0.5) 

```

### RCADS MDD: group differences, no behavior effects
```{r}

symptom_mod4 <- lm(J.RCADS_MDD_T_new ~ GROUP + prop_stay_hard_reward + prop_stay_easy_reward + 
                     prop_stay_hard_setback + prop_stay_easy_setback + prop_hard_choices + 
                     AGE + Sex + Reinforce_rate, 
                   data = subj_level_all)
summary(symptom_mod4)

CBCL_4_ANXDEPR_T
```

## CBCL MDD 
```{r}

ggplot(subj_level_all, aes(x = as.factor(GROUP), y = CBCL_4_ANXDEPR_T, color = as.factor(GROUP))) + 
  theme_classic() + geom_violin() + geom_jitter(width = 0.05, alpha = 0.5) 

```

### CBCL MDD: no group differences, no behavior effects
```{r}

symptom_mod5 <- lm(CBCL_4_ANXDEPR_T ~ GROUP + prop_stay_hard_reward + prop_stay_easy_reward + 
                     prop_stay_hard_setback + prop_stay_easy_setback + prop_hard_choices + 
                     AGE + Sex + Reinforce_rate, 
                   data = subj_level_all)
summary(symptom_mod5)

CBCL_4_ANXDEPR_T
```
