---
title: 'Progress report: usable scans with demographic info'
author: "Michelle Vantieghem"
date: "November 26, 2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      df_print: paged
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

#  Notes
Updating June 6, 2019 to just include updated master variables! \
updated August: to add PA257 \
updated November 26, 2019: PA157 added due to updating the motion_info from 08-07-2019. usable scans changed from N = 126 to N = 127 \
for some reason it wasn't being included before!

```{r, include = F, warnings = F, error = F}
library(stringi)
library(tidyverse)
library(readxl)
library(ggplot2)
library(foreign)
```


# MERGE TOGETHER SCAN & BEH DATA 

## open behavior data 
compiled behavior from effort, post-test, and finger tapping - with QC variables added
includes all subjects who ever did effort task, no one excluded yet.
```{r}
load("../../behavioral_data/3_effort_task_data/compiled/compiled_effort_scan_version_with_QC.Rdata")
nrow(beh_master)
```


##  merge behavior  with demo
Impt note: behavior master is by RUN, and demographics is by SUBJECT.
```{r}
load("../2_beh_QC_and_demo/data/demographics_from_master_20191118.Rdata")
# all is NOT true, because we only want to keep subjects with valid data!! 

demo_behavior <- merge(beh_master, demo, by = "SUBJECTID") %>%
  mutate(RunNumber = Run_number) %>%
  mutate(PI_DA = ifelse(GROUP == "C" | GROUP == "DC", 0, 1))

```


## get motion info 
```{r}
# make sure you're loading the most updated version
load("../4_brain_motion_QC/data/compiled_motion_info_2019-08-07.Rdata")

# PA034 only did half a run in scanner, and then did the PILOT version outside scanner... omit this subject.
scan_df <- merged_df %>%
  filter(!SUBJECTID =="PA034") %>%
  rename(scan_QC_motion_include = include,
         scan_QC_complete_run = complete_scan) %>%
  mutate(RunNumber = ifelse(RunNumber == "run1", "RUN1", "RUN2"))
```

## merge scanning data with behavior & demo.
make new variables to define behavior and scan inclusion criterion
```{r, include =F, warnings = F, error = F}

df_by_run <- merge(demo_behavior,  scan_df, by = c("SUBJECTID", "RunNumber"), all = T)  %>%
  mutate(behavior_usable = ifelse(beh_QC_complete_run == 1 & 
                                            beh_QC_choices_resp_70_include == 1 &
                                             beh_QC_tooslow_50_include == 1, 1, 0), 
           scan_and_beh_runs_usable = ifelse(beh_QC_complete_run == 1 & 
                                            beh_QC_choices_resp_70_include == 1 &
                                             beh_QC_tooslow_50_include == 1 & 
                                             scan_QC_complete_run == 1 & 
                                             scan_QC_motion_include, 1, 0))
nrow(df_by_run)
```

# ORGANIZE BEHAVIOR + SCAN DATA 
## make wide version of behavioral data for demo tables.
```{r}
df_wide <- df_by_run %>%
  group_by(SUBJECTID) %>%
  # getting demographics 
    dplyr::summarize(AGE = mean(AGE, na.rm = T), 
            SEX = mean(SEX, na.rm = T),
            Race = Race[1], 
            Ethnicity = Ethnicity[1],
            GROUP = GROUP [1],
            PI_DA = mean(PI_DA, na.rm = T),
            # getting beh QC 
            beh_QC_complete_runs = sum(beh_QC_complete_run, na.rm = T), 
            beh_QC_choices_resp_70_include_runs = sum(beh_QC_choices_resp_70_include, na.rm = T), 
            beh_QC_tooslow_50_include_runs = sum(beh_QC_tooslow_50_include, na.rm = T),
            # scan QC data
             scan_QC_complete_runs = sum(scan_QC_complete_run, na.rm = T),
             scan_QC_motion_usable_runs = sum(scan_QC_motion_include, na.rm = T), 
            beh_runs_usable = sum(behavior_usable, na.rm = T),
            scan_and_beh_runs_usable = sum(scan_and_beh_runs_usable, na.rm = T), 
            # getting adverages across both runs, if they have 2 runs
            total_censored_TRs = sum(censored_TRs, na.rm = T), 
            prop_censored_TRs = (sum(censored_TRs, na.rm = T)/ sum(TRs, na.rm = T)), 
            meanFD_all_TRs = mean(meanFD_all_trs, na.rm = T), 
            meanFD_included_trs = mean(meanFD_included_trs, na.rm = T))

save(df_wide, file = paste0("data/all_data_QC_and_demographics_wide", Sys.Date(), ".Rdata"))
```

## make long version of dataset with demographics
```{r}
# also save data for all subjects, prior to exclusion.
save(df_by_run, file = "../../behavioral_data/3_effort_task_data/compiled/compiled_effort_scan_version_not_filtered_with_demo.Rdata")

# now save filtered version, only usable behavior 
df_by_run_usable_beh <- df_by_run %>%
  filter(behavior_usable == 1)
nrow(df_by_run_usable_beh)
length(unique(df_by_run_usable_beh$SUBJECTID)) # 178 subjects! 

save(df_by_run_usable_beh, file = "../../behavioral_data/3_effort_task_data/compiled/compiled_effort_scan_version_filtered_usable_with_demo.Rdata")
```


# make sublist for preproc-level1 prrocessing of brain data
## include for any usable data
```{r}
df_by_subject <- df_by_run %>%
  group_by(scan_and_beh_runs_usable, SUBJECTID) %>% 
  summarize(Number_of_runs = n())

# how many subjects have any usable data 
keep_any_scans <- df_by_subject %>% 
  filter(scan_and_beh_runs_usable == 1)
nrow(keep_any_scans) # still 127. 
# save the list: by subject 
write.table(keep_any_scans$SUBJECTID, file =  paste0("sublists/include_scan_and_beh_by_subject", Sys.Date(), ".txt"), quote= F, row.names =  F, col.names =  F)

# how many runs have any usable data 
keep_any_scans <- df_by_run %>% 
  filter(scan_and_beh_runs_usable == 1) %>%
  select(SUBJECTID, RunNumber)
nrow(keep_any_scans) # still 127. 

# save the list 
write.table(keep_any_scans, file = paste0("sublists/include_scan_and_beh_by_run", Sys.Date(), ".txt"), quote= F, row.names =  F, col.names =  F)

```


## 2 runs of usable data
```{r}

#how many subjects have 2 runs of usable data
keep_2_runs <- df_by_subject %>% 
  filter(scan_and_beh_runs_usable == 1 & Number_of_runs == 2)
nrow(keep_2_runs)

write.table(keep_2_runs$SUBJECTID, file =  paste0("sublists/sublists_include_2_runs", Sys.Date(), ".txt"), quote= F, row.names =  F, col.names =  F)
```

### 1 run 
```{r}
# how many subjects have 1 run of usable data
keep_1_run <- df_by_subject %>% 
  filter(scan_and_beh_runs_usable == 1 & Number_of_runs == 1)
nrow(keep_1_run)
write.table(keep_1_run$SUBJECTID, file =   paste0("sublists/sublists_include_1_run", Sys.Date(), ".txt"), quote= F, row.names =  F, col.names =  F)

# which run to keep?
include_1_run <- df_by_run %>%
  dplyr::select(SUBJECTID, RunNumber, scan_and_beh_runs_usable) %>%
  # take only the subejcts with 1 usable run
  filter(SUBJECTID %in% keep_1_run$SUBJECTID) %>%
  # now only keep runs with usable = 1
  filter(scan_and_beh_runs_usable == 1)


# run 1 only 
run1_only <- include_1_run %>%
  filter(RunNumber == "RUN1")

write.table(run1_only$SUBJECTID, file =   paste0("sublists/sublists_include_Run1_only", Sys.Date(), ".txt"), quote= F, row.names =  F, col.names =  F)

# run 2 only 
run2_only <- include_1_run %>%
  filter(RunNumber == "RUN2")

write.table(run2_only$SUBJECTID, file =   paste0("sublists/sublists_include_Run2_only", Sys.Date(), ".txt"), quote= F, row.names =  F, col.names =  F)
```



# DEMOGRAPHICS FOR BEH AND SCAN.

## summary of total vs. unusable data overall 
```{r}
inclusion_table <- df_wide %>%
  dplyr::summarize (n_any_data = n(), 
                    n_complete_behavior_subjects = sum(ifelse(beh_QC_complete_runs > 0, 1, 0), na.rm = T),
                    n_complete_behavior_runs = sum(beh_QC_complete_runs, na.rm = T),
                    n_behavior_usable_subjects = sum(ifelse(beh_runs_usable > 0, 1, 0), na.rm = T),
                    n_behavior_usable_runs = sum(beh_runs_usable, na.rm = T), 
                    n_complete_scan_subjects = sum(ifelse(scan_QC_complete_runs > 0, 1, 0), na.rm = T),
                    n_complete_scan_runs = sum(scan_QC_complete_runs, na.rm = T),
                    n_motion_usable_subjects = sum(ifelse(scan_QC_motion_usable_runs > 0, 1, 0), na.rm = T),
                    n_motion_usable_runs = sum(scan_QC_motion_usable_runs, na.rm = T), 
                    n_scan_and_beh_runs_usable_subjects = sum(ifelse(scan_and_beh_runs_usable > 0, 1, 0), na.rm = T),
                    n_scan_and_beh_runs_usable_runs = sum(scan_and_beh_runs_usable, na.rm = T))

better_inclusion_table <- t(inclusion_table)

better_inclusion_table 
save(better_inclusion_table, file = "tables/entire_dataset_inclusion_table.Rdata")
```

## summary of total vs. usable data by group.
```{r}
inclusion_by_group <- df_wide %>%
  # exclude ppl withno usable data
 # filter (usable_runs != 0) %>%
  group_by(PI_DA) %>% 
  dplyr::summarize (n_any_data = n(), 
                    n_complete_behavior_subjects = sum(ifelse(beh_QC_complete_runs > 0, 1, 0), na.rm = T),
                    n_complete_behavior_runs = sum(beh_QC_complete_runs, na.rm = T),
                    n_behavior_usable_subjects = sum(ifelse(beh_runs_usable > 0, 1, 0), na.rm = T),
                    n_behavior_usable_runs = sum(beh_runs_usable, na.rm = T), 
                    n_complete_scan_subjects = sum(ifelse(scan_QC_complete_runs > 0, 1, 0), na.rm = T),
                    n_complete_scan_runs = sum(scan_QC_complete_runs, na.rm = T),
                    n_motion_usable_subjects = sum(ifelse(scan_QC_motion_usable_runs > 0, 1, 0), na.rm = T),
                    n_motion_usable_runs = sum(scan_QC_motion_usable_runs, na.rm = T), 
                    n_scan_and_beh_runs_usable_subjects = sum(ifelse(scan_and_beh_runs_usable > 0, 1, 0), na.rm = T),
                    n_scan_and_beh_runs_usable_runs = sum(scan_and_beh_runs_usable, na.rm = T))
inclusion_by_group
save(inclusion_by_group, file = "tables/entire_dataset_inclusion_by_group.Rdata")

# comps only 
inclusion_COMPS <- inclusion_by_group %>% 
  filter(PI_DA == 0) %>% 
  select(-(PI_DA))
t(inclusion_COMPS)
save(inclusion_COMPS, file = "tables/COMP_dataset_inclusion.Rdata")

```

## make behavior sample demo table of only usable subjects. 
```{r}
behavior_demo_by_group <- df_wide %>%
  # exclude ppl withno usable data
  filter (beh_runs_usable > 0) %>%
  group_by(PI_DA) %>% 
  dplyr::summarize (n = n(), 
             mean_age = mean(AGE, na.rm = T), 
             min_age = min(AGE, na.rm = T), 
             max_age = max(AGE, na.rm = T), 
             prop_female = mean(SEX, na.rm = T), 
             N_Female = sum(SEX, na.rm = T))

behavior_demo_by_group
save(behavior_demo_by_group, file = "tables/demo_table_usable_behavior.Rdata")

```

## make scan sample demo table of usable vs. unusable 
### for 0,1,2 of usable runs
```{r}
summary_by_group <- df_wide %>%
  # exclude ppl withno usable data
  filter (scan_QC_complete_runs != 0) %>%
  group_by(PI_DA, scan_and_beh_runs_usable) %>% 
  dplyr::summarize (n = n(), 
             mean_age = mean(AGE, na.rm = T), 
             min_age = min(AGE, na.rm = T), 
             max_age = max(AGE, na.rm = T), 
             prop_female = mean(SEX, na.rm = T), 
             N_Female = sum(SEX, na.rm = T))

summary_by_group # all subjects
save(summary_by_group, file = "tables/demo_table_usable_vs_unusable_scans.Rdata")


COMP_summary <- summary_by_group %>%
  filter(PI_DA == 0) %>%
  select(-PI_DA) # only comps 

save(COMP_summary, file = "tables/COMP_demo_table_usable_vs_unusable_scans.Rdata")
```

### for any usable runs
```{r}
all_usable_by_group <- df_wide %>%
  # exclude ppl withno usable data
  filter (scan_and_beh_runs_usable != 0) %>%
  group_by(PI_DA) %>% 
  summarize (n = n(), 
             mean_age = mean(AGE, na.rm = T), 
             min_age = min(AGE, na.rm = T), 
             max_age = max(AGE, na.rm = T), 
             sd_age = sd(AGE, na.rm = T),
             prop_female = mean(SEX, na.rm = T), 
             N_Female = sum(SEX, na.rm = T))
all_usable_by_group 
sum(all_usable_by_group$n) # this changed from N= 126 to 127 after adding PA255 on Nov 26, 2019.

save(all_usable_by_group, file = paste0("tables/demo_table_any_usable_scans.Rdata"))

COMP_all_usable <- all_usable_by_group %>%
  filter(PI_DA == 0) %>%
  select(-PI_DA)

save(COMP_all_usable, file = "tables/COMP_demo_table_any_unusable_scans.Rdata")
```

# check group distribution by age
```{r}
ggplot(subset(df_wide,scan_and_beh_runs_usable  > 0 & AGE > 5 & !is.na(GROUP)), aes(AGE)) + geom_histogram(binwidth= 1,fill  = "dark blue", alpha = 0.5) +
   theme_classic () + facet_grid (~ PI_DA)

```

```{r}
ggplot(data = subset(all_usable_by_group, !is.na(PI_DA)), 
       aes(x = as.factor(PI_DA), y = mean_age)) +
  geom_violin(data = subset(df_wide, scan_and_beh_runs_usable >0 & !is.na(PI_DA) & AGE> 5), 
              aes(x = as.factor(PI_DA), y= AGE)) +
  geom_errorbar( aes(ymin= mean_age - sd_age,ymax= mean_age + sd_age, width = .1)) +
  geom_jitter(data = subset(df_wide, scan_and_beh_runs_usable >0 & !is.na(PI_DA) & AGE > 5), 
              aes(x = as.factor(PI_DA), y= AGE), 
             alpha = 0.5, width= 0.1) + 
  theme_classic () + geom_point(color = "blue" , size = 3) 

```

### for 2 usable runs
```{r}
scan_2runs_usable_by_group <- df_wide %>%
  # exclude ppl withno usable data
  filter (scan_and_beh_runs_usable  == 2) %>%
  group_by(PI_DA) %>% 
  summarize (n = n(), 
             mean_age = mean(AGE, na.rm = T), 
             min_age = min(AGE, na.rm = T), 
             max_age = max(AGE, na.rm = T), 
             sd_age = sd(AGE, na.rm = T),
             prop_female = mean(SEX, na.rm = T), 
             N_Female = sum(SEX, na.rm = T))

scan_2runs_usable_by_group 

usable_2run_scans_N <- sum(scan_2runs_usable_by_group$n)

save(scan_2runs_usable_by_group, file = paste0("tables/demo_table_2_usable_runs.Rdata"))
#write.csv(scan_2runs_usable_by_group, file = paste0("tables/demo_table_2_usable_runs.csv"))
```

```{r}

ggplot(subset(df_wide, scan_and_beh_runs_usable >1), aes(AGE)) + geom_histogram(binwidth=1) +
   theme_classic () + facet_grid (~ PI_DA)
```

```{r}
ggplot(data = scan_2runs_usable_by_group,
        aes(x = as.factor(PI_DA), y = mean_age)) +
  geom_violin(data = subset(df_wide, scan_and_beh_runs_usable >1), 
              aes(x = as.factor(PI_DA), y= AGE)) +
  geom_errorbar( aes(ymin= mean_age - sd_age,ymax= mean_age + sd_age, width = .1)) +
  geom_point(data = subset(df_wide, scan_and_beh_runs_usable >1),
             aes(x =as.factor(PI_DA), y= AGE), alpha = 0.5) + 
  theme_classic () + geom_point(color = "blue" , size = 3) 

```


# FINAL BREAKDOWN OF USABLE DATA 
```{r}
inclusion_table
print(paste0('Total behavior subjects: ', inclusion_table$n_any_data))
print(paste0('Usable behavior subjects: ', inclusion_table$n_behavior_usable_subjects))
print(paste0('Proportion usable behavior: ', inclusion_table$n_complete_behavior_subjects/ inclusion_table$n_any_data))

print(paste0('Total scan subjects: ', inclusion_table$n_complete_scan_subjects))
print(paste0('Usable scan motion subjects: ', inclusion_table$n_motion_usable_subjects))
print(paste0('Usable scan motion & behavior subjects: ', inclusion_table$n_scan_and_beh_runs_usable_subjects))
print(paste0('Proportion usable scans: ', inclusion_table$n_scan_and_beh_runs_usable_subjects/inclusion_table$n_complete_scan_subjects))
```


## use this to make enrollment report sheet for NIH RPPR
complted on august 1, 2019 for NIH NRSA renewal. Will be identical for subsequent report because no further data collection occurred.
```{r, include = F, eval = F, echo = F} 
summary(as.factor(df_wide$Race))
summary(as.factor(df_wide$Ethnicity))


Inclusion_enrollment <- df_wide %>%
  mutate(Race = ifelse(Race == "Other" | is.na(Race), "Unknown", as.character(Race)), 
         Ethnicity = ifelse(is.na(Ethnicity), "Unknown", as.character(Ethnicity)),
         Gender = ifelse(SEX == 0, "Male", "Female")) %>%
  select(Race, Ethnicity, Gender, AGE) %>%
  rename( Age = AGE) %>%
  mutate('Age Unit' = "years", 
         Age = round(Age))
head(Inclusion_enrollment)

summary(as.factor(Inclusion_enrollment$Race))
summary(as.factor(Inclusion_enrollment$Ethnicity))

df_wide$SUBJECTID[is.na(df_wide$AGE)]

df_wide$AGE[is.na(df_wide$AGE)] <- 7

Table <- Inclusion_enrollment %>%
  group_by(Race, Ethnicity, Gender) %>%
summarize(n = n())

#write.csv(Inclusion_enrollment, "tables/Inclusion_enrollment_2019_Partipant_Level_Data_Effort_2019-08-01.csv", row.names = F)

```
